### 2018-02-02 draft.tex
Add files via upload
initialize the repository

\documentclass[journal]{IEEEtran}

\usepackage{cite}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage[unicode,pdftex]{hyperref}

\usepackage{xcolor}

\ifCLASSINFOpdf
\usepackage[pdftex]{graphicx}
\else
\fi

\hyphenation{op-tical net-works semi-conduc-tor}

\newcommand{\reffig}[1]{Fig. \ref{#1}}
\newcommand{\refsec}[1]{Section \ref{#1}}
\newcommand{\refeq}[1]{Eq. \ref{#1}}
\newcommand{\reftab}[1]{Table \ref{#1}}

\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}

\definecolor{level2}{RGB}{255,255,255}
\definecolor{level3}{RGB}{10,10,10}
\definecolor{revised}{RGB}{100,101,140}
\definecolor{continue}{RGB}{255,0,0}
\definecolor{filltext}{RGB}{0,255,255}

\begin{document}
\title{Background Subtraction based on Deep Feature Transformation Learning Background Subtraction}

\author{Xinyu Ren,
        Chenqiu Zhao,
		Yongxin Ge }

\maketitle

\begin{abstract}
% the background of problem
One of the main challenges of Background Subtraction comes from the diversity and complexity of real-world scenes.
While most of previous works in this field were proposed by designing an artificial model, we tend to present a self-adaption solution, by combining the fully convolutional networks, which is named as the Deep Pixels’ Variation Learning model (DPVL).
Our main job is to find a new representation of pixels’ historical observations in a new feature space.
In this paper, videos are divided into fixed length image blocks, which are later transformed into the pixel’s observation patches as the input of a FCN for learning the variation of pixels.
We conduct our training and prediction processes on block level.
The architecture of the FCN is devised from the semantic segmentation problem.
Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ variation.
We compare our method with some of the state-of-art methods… 
\end{abstract}

\begin{IEEEkeywords} 
    Background Subtraction, Freely Moving Camera, Foreground and Background Cues,
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}
Background subtraction or foreground object detection, as a fundamental problem in computer vision, has been much discussed with the increasing number of outdoor cameras over the last few decades.
It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.
vehicles and humans, thus saving us huge amount of computing resources.
Typically, Background subtraction is a binary classification task that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.

With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes.
However, background Subtraction is still unsolved because of the diversity in background scenes and the changes originated from the camera itself.
Scene variations can be in many forms such as, camera jitter, dynamic background, bad weather, illumination changes, intermittent object motion.
This is principally because the major methods, in most cases, try to find a universal solution by generating some universal background models for later linear classification; for instance, the earlier Frame Difference Methods, trying to get a fixed image as background to classify each pixels.
The fundamental problem lies in that linear classifier might not be powerful enough for the job, due to the complexity and the diversity of natural scenes.

In order to present a better and universal solution, we proposed the Deep Pixels’ Variation Learning (DPVL) model for Background Subtraction in diversely natural scenes.
In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.
\begin{equation}
    sq_1 = \{p_1,p_2,\cdots, p_n\} -> sq_2 = \{f_1, f_2, \cdots, f_n\}
\end{equation}
For $sq_1$, it is a sequence of pixels' intensity, which is hard to classify which entry is foreground or background.
%
But in $sq_2$, it is more easy to classified, since the output of

In this paper, pixel’s observation patches are proposed to describe the historical observation of pixels.
And a random initialized FCN network is trained to learn the historical observation of pixels and generate a new representation in a new feature space.
We take advantage of the strong learning ability of FCN to learn a new representation of the Pixel’s observation patches in a new space where the pixels can be easily classified to background and foreground.

\section{Related Work}
Over the last few decades, Background subtraction has been well studied. Meanwhile, a huge number of methods were proposed. These methods can be broadly categorized into pixels-based, region-based, frame-based and Deep Learning.

\subsection{A. pixels-based methods}
\label{sec_spa}
The most widely used algorithms in Background subtraction are pixels-based methods.
And one of the famous method is Gaussian Mixture Model (GMM), in which a GMM is used to model the history over time of pixel’s intensity values.
It is assumed that pixels are independent from their neighbors.
Incoming pixels are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound.
For learning the parameters, that maximize the likelihood, the authors proposed an online method that approximates the Expectation Maximization (EM) algorithm.

In XXX , Mingliang Chen et al.
propose a background subtraction algorithm using hierarchical superpixels segmentation, spanning trees and optical flow.
Their Background model combine the GMM with constrains of temporal and spatial from optical flow and superpixels.

Kim et al used a codebook to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model.
This allows them efficient in memory and speed compared with other background modeling techniques.
The final foreground is detected by a distance measurement in a cylindrical color model.

In XXX, Zhi Zeng et al.
proposed an equal-qualification updating strategy to replace the maximum-negative-run-length-based filtering strategy.
Their experiments show that, the proposed method outperforms well, despite using only color information.

Elgammal et al.
introduced a probabilistic non-parametric method to model the background.
It is assumed that each background pixel is drawn from a PDF.
The PDF for each pixel is estimated with Kernel Density Estimation (KDE).

\subsection{region-based approach}
\label{sec_geo}
region-based approach assumpt that the neighbouring pixels have a similar variation as the pixel itself.

In xxx, Sriram Varadarajan et al.
propose a region-based MoG to takes in which the updated mixtures represent the scene distribution in a neighbourhood region.

In (PCA), classification is done by comparing a block in current frame to its reconstruction from PCA coefficients and declaring it as background if the reconstruction is close.

A recently region based method is presented in XXX which used the statistical circular shift moments (SCSM) in image regions for change detection.

subspace learning method in xxx, is used to compress the background into the eigenbackground.
For each video, the mean and the covariance matrix are calculated.
After a PCA of the covariance matrix, a projection matrix is set up with M eigenvectors.
Then, incoming images are compared with their projection onto the eigenvectors.
Foreground labels are assigned to pixels with large distances, after calculating the distances between the image and the projection and comparing them with the corresponding threshold value.

Marghes et al.
used a mixed method that combines a reconstructive method (PCA) with a discriminative one (LDA) to robustly model the background.

single Gaussians are employed for foreground modeling.
By computing flux tensors, which depict variations of optical flow within a local 3D spatio-temporal volume, blob motion is detected.
With the combination of the different information from blob motion, foreground models and background models, moving and static foreground objects can be spotted.
Also, by applying edge matching, static foreground objects can be classified as ghosts or intermittent motions.

Frame-based background modeling via Principal Component Analysis (PCA) and low-rank/sparse decomposition approaches is a popular alternative to pixel-level modeling xx.
These approaches are however not ideal for surveillance applications as most rely on batch or offline processing or suffer from scaling problems.

In XXX, ss et al.
addressed scaling problems by reformulating principal component analysis for 2D images.
Meanwhile their method takes much lower memory consumption and computational cost than others.
Some online approaches have also been proposed recently, but they are still very computationally expensive.

\subsection{Algorithms based on Super-pixels}
\label{sec_sup}
A novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck.
They used a fixed background model, which was generated from a temporal median operation over N video frames.

In XXX, Yi Wang et al.
tried a CNN architecture combined with a Cascade model for segmentation in Background subtraction.
Given 200 labelled images as training set, their model performed excellently in dataset2014.

Braham et al.
present an Deep learning-based method.
with the help of CNN, they generated a fixed background model from a temporal median operation over N video frames.
Then, a scene-specific CNN is trained with corresponding image patches from the background image.

In xxx, M.
Babaee et al.
combine the segmentation mask from SuBSENSE algorithm and the output of Flux Tensor algorithm, which can dynamically change the parameters used in the background model based on the motion changes in the video frames.
They also used spatial-median filtering as the post processing of the network outputs.

\section{The IFB Framework}
\label{sec3}
In this section, we introduce our DPVL model that consists of a pixels-based observation patches and a novel FCN networks for background subtraction.
We explain the details of the procedures of capturing the observation patches and the architecture of network in our DPVL model.
The complete system is illustrated in Figure XXX.
We use a set of input and ground true images to generalize the Pixels’ Variation Permutations, and reshape them into fixed-size image patches as and fed into a FCN.
After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.

% 
% 
% \begin{figure}[!t]	\centering
% \includegraphics[width=\linewidth]{figure/extraction.pdf}
% \DeclareGraphicsExtensions.
% \caption{Extraction of foreground and background cues .}
% \label{fig_extraction}		\end{figure}

\subsection{A. Image blocks to observation  patches}
\label{sec3_fc}
The historical observations of pixels which belong to the background are usually share a common variation pattern.
In more specific terms, the variations of pixels in background are generally keeping in some pattern.
And we want to use a FCN network to learn a new representation of pixels’ observations in a new feature space.

In order to get enough pixels’ observations, we conduct our experiment on block-level.
In this paper, we divide each video into smaller image blocks, which share a common frame length of t.
For each image blocks, it contains M*N pixels’ historical observations in a temporal sequence of t frames.
We need to take them out for later transformation as our network input.

Observation patch is purposed to take advantage of the strong learning ability of the FCNs.
And what we need is an pixel-to-pixel transformation.
More precisely, Every historical pixels’ observation in these observation patches has an corresponding transformation  at the last layer of FCNs.
Here is how we get these observation patches.
First, we transform each image block into M*N pixel’s observation series which are the  single pixels’ historical observation series in a frame length of t.
Next, we reshape the observation sequence into a rectangle image which size is $\sqrt{t}\cdot \sqrt{t}$.
That rectangle image is what we called observation patch.
The observation patches are taken as network training sample set.

Another conception about observation patches is interval sampling.
For a sequence like this: 
\begin{equation}
    p_t\{p_1,o_2,\cdots,p_n\} -> \{p_1,p_{11},p_{21}, \cdots, p_n\}
\end{equation}
where $t$
denote the sequence number of frames.
By this way, we can get an new sequence contains more temporary information  than the continuous pixel sequences.
This works well when it comes to some situation where the moving objects keep stationary for a long time.

\subsection{Fully Convolutional Network}
\label{sec3_bc}
The primary task of our network is to learn an optimal feature transform of pixel’s observation series, thus we can find a new representation which is easy for classification from raw RGB data. There needs to be a consistent one-to-one match between pixels’ observation sequence and our network output on the time series. In these circumstances, traditional convolutional network cannot meet our requirements. 
Different with those traditional ones, fully convolutional networks can take input of arbitrary size and produce correspondingly-sized output with efficient inference. FCNs have already been used in many areas like sematic segmentation and so on. Researchers found FCNs has a strong learning ability which won’t lost to the traditional ones, meanwhile, it also has a high efficient computation ability.   
FCNs utilize 1*1 kernels to take the place of fully connected layers.
Therefore, we take a fixed size of pixel’s observation patches as the input of our network. For the convenience of calculations, we transform observation sequence into observation patches.

\subsection{Network Architecture}
The architectures of our proposed FCN is illustrated in Figure xx, our network contains 5 convolutional layers, 2 pool layers and a convolutional layer which have a filter size of 1*1.
A short calculation revealed that the network output will less 10 pixels after forward calculating.
In order to make output the same size as input, we borrowed ideas from Image semantic segmentation, which is doing zero-padding before the training.
After the forward computing, we can get the new representation of input observation values in a new feature space.
Then, after some thresholding calculations.
Our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery.

\section{Experiments}
Our experiments are conducted on the computer with Nvidia tasela K20c GPU.
 And the DeepLearning tool we use is the matconvnet-23.
4 beta.

Our FCN network is random initialized, and the training epoch is set to 20.
For each video, we divide it into image blocks, which have a fixed frame length of 144.
For each image block, M*N pixel’s historical observations were taken out, where the M and N denoted the size of images.
After a simple transformation, we can get M*N pixel’s observation patches.
Each of them contains the historical observation of a pixels in a frame length of 144.

For each video, we take only one image block to generate the observation patches as our training sample set.
The other image blocks are saved for testing.

In dataset2014, most of the videos have a number of frames over 1000, thus our training data only accounts for 5% of total dataset.
But we can still get plenty of training data cause the number of the training set based on the size of images.
For example, in the video Highway of dataset2014, the image size is 320*240, so the number of observation patches for training is 76800.
In our experiment, the finally result would be better if we slightly magnify the observation patches.
We do the same to label data, but with no 0 padding.

\subsection{Evaluation Metric and Dataset}
The subjective results of background modeling approaches based on the foreground detection binary maps.
And the general international standards is F-Measure.
F-Measure is defined as:

\begin{equation}
    F=\frac{precision \dot recall}{precision - recall}
\end{equation}
\begin{figure}[!t]	% FIGURE: figure/fig1 
\centering
\includegraphics[width=.5\textwidth]{figure/fig_roc_fg}
\DeclareGraphicsExtensions.
    \caption{The example of latex figure.}
\label{fig_FBMS_nobk}
\end{figure}

\begin{table}[!t]				% TABLE
    \caption{The example of latex table}
\label{tab_FBMS_nobk}
\centering
    \begin{tabular}{|l@{  }c@{  }c@{  }cc@{  }c@{  }c@{  }c|}
\hline
     \multirow{2}{*}{Videos} & \multicolumn{3}{c}{$\text{IFB}_{nobk}$} &  & \multicolumn{3}{c|}{IFB} \\
    \cline{2-4} \cline{6-8}
       & Re &Pr & Fm &  &  Re & Pr & Fm  \\
\hline
cats03          &   (\textbf{0.9472} ,\   &  0.5428 ,\  &   0.6901 )   &  &    (0.9063 ,\	 &  \textbf{0.7955} ,\	 &  \textbf{0.8473} )   \\
bear01          &   (\textbf{0.9854} ,\   &  0.4806 ,\  &   0.6461 )   &  &    (0.8695 ,\	 &  \textbf{0.8673} ,\	 &  \textbf{0.8684} )   \\
rabbits01       &   (\textbf{0.9530} ,\   &  0.4433 ,\  &   0.6051 )   &  &    (0.9510 ,\	 &  \textbf{0.8730} ,\	 &  \textbf{0.9103} )   \\
cars5           &   (\textbf{0.9887} ,\   &  0.3693 ,\  &   0.5378 )   &  &    (0.9437 ,\	 &  \textbf{0.7108} ,\	 &  \textbf{0.8109} )   \\
tennis          &   (\textbf{0.9364} ,\   &  0.4558 ,\  &   0.6132 )   &  &    (0.8808 ,\	 &  \textbf{0.7345} ,\	 &  \textbf{0.8010} )   \\
farm01          &   (\textbf{0.9887} ,\   &  0.3897 ,\  &   0.5591 )   &  &    (0.8954 ,\	 &  \textbf{0.7462} ,\	 &  \textbf{0.8140} )   \\
\hline                                                                                                           
Average         &   (\textbf{0.9666} ,\   &  0.4469 ,\  &   0.6086 )   &  &    (0.9078 ,\    &  \textbf{0.7879} ,\   &  \textbf{0.8420} )   \\
\hline
\end{tabular}
\end{table}

% Videos & GBSSP\cite{Lim2014_2014_ECCV} & calMoSeg\cite{2016_ECCV_Bideau2016}  & MLayer\cite{2017_ICCV_zhu2017multilayer}  & $\text{IFB}_{SU}$ & $\text{IFB}_{KA}$ & $\text{IFB}_{SI}$ & Videos & GBSSP\cite{Lim2014_2014_ECCV} & calMoSeg\cite{2016_ECCV_Bideau2016} & MLayer\cite{2017_ICCV_zhu2017multilayer}  &  $\text{IFB}_{SU}$ &  $\text{IFB}_{KA}$  &  $\text{IFB}_{SI}$  \\
\section{Conclusions}
In this paper,
we proposed the IFB framework for background subtraction for the case of a freely moving camera.
Unlike previous work in which attempts were made to improve the accuracy of the estimation of motion,
our IFB focuses on integrating rough foreground and background cues for foreground segmentation.
In particular, 
foreground cues are detected by a GMM model with the estimation of background motion,
while background cues are captured from spatio-temporal features filtered by homography transformation,
where the SURF\cite{2006_SURF}, KAZE\cite{2012_KAZE}, SIFT\cite{lowe2004distinctive} features are used as examples.
% the geometric constraints between the SIFT features.
Then, super-pixels under multiple levels are utilized to integrate these cues.
The efficiency of IFB results from the complementarity between foreground and background cues.
The accuracy of the proposed approach is improved though the utilization of super-pixels under multiple levels.
A comprehensive experiment to compare our results with the state-of-the-art shows the efficiency of our framework and points to its potential for use in practical applications.

\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\bibliographystyle{IEEEtran}  
\bibliography{ref}

\end{document}

### 2018-02-02 main.tex
Add files via upload
initialize the repository

\documentclass[journal]{IEEEtran}

\usepackage{cite}
\usepackage{amsmath}
\usepackage{verbatim}%长篇注释宏包

\ifCLASSINFOpdf
\usepackage[pdftex]{graphicx}
\else
\fi

\hyphenation{op-tical net-works semi-conduc-tor}

\newcommand{\reffig}[1]{Fig. \ref{#1}}
\newcommand{\refsec}[1]{Section \ref{#1}}
\newcommand{\refeq}[1]{Eq. \ref{#1}}
\newcommand{\reftab}[1]{Table \ref{#1}}

\begin{document}
\title{A Noval Framework for Background Subtraction in Moving Camera}

% information of authors

\begin{comment}
\author{Chenqiu Zhao,
        Xiaohong Zhang and
		Sheng Huang, ~\IEEEmembership{Student Member,~IEEE}
		\thanks{Dan Yang is with School of Software Engineering,
		Chongqing University, Chongqing (401331), PR China.}
		\thanks{Chenqiu Zhao is with School of Software Engineering,
		Chongqing University, Chongqing (401331), PR China (e-mail: zhaochenqiu@gmail.com).}
		\thanks{Xiaohong Zhang is with Key Laboratory of Dependable
		Service Computing in Cyber Physical Society Ministry of
		Education, Chongqing (400044), P. R China, with School of
		Software Engineering, Chongqing University, Chongqing
		(401331), PR China, and with State Key laboratory of Coal
		Mine Disaster Dynamics and Control, Chongqing (400044), P. R
		China (e-mail: xhongz@cqu.edu.cn).}
		\thanks{Sheng Huang is with School of Software Engineering,
		Chongqing University, Chongqing (401331), PR China.}
		\thanks{Corresponding author: xhongz@cqu.edu.cn (X. H. Zhang),
		School of Software Engineering, Chongqing University, Huxi Town,
		Shapingba, Chongqing, P. R. China 410331.}}
\end{comment}
% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~13, No.~9, September~2014}
%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract															   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\indent Background subtraction in moving camera is a challenging problem
in computer vision, since the position of pixels are varying during time
sequences and is hard to say what is background. In this paper, we assume
the main body of relative static part in scenes as the background, and 
proposed a novel framework named MDS(matching, detection and segmentation)
which utilize matching to counteract the displacement of camera and 
segmentation to improve the efficiency and robust of our framework. In MDS
we matching the image between two frames, and moving the background with
the frames. In this condition, the algorithms in static camera can work
in moving camera. And we utilized GMM to get the foreground. Moreover,
the matching point also showing the position of background. And 
we utilized the segmentation to mix the foreground and background.
Comprehensive evaluation demonstrates the superiority of framework 
against state of the art.
\begin{comment}
In this paper, we following the definition of background which
is the main body of relative static part in scenes, and proposed a novel
framework named MDS(matching, detection and segmentation) which utilize
matching to counteract the displacement of camera. In this condition,

\indent The background subtraction is a challenging problem in computer
vision, since the all the position of pixels is change and is hard to said 
what is background. In this paper, we follows the means of background
which assume the relative static part and main part as background and 
proposed a novel framework named MDS(matching, detection and segmentation)
which utilize matching to counteract the displacement of camera moving.
In this condition, the algorithms in static camera like GMM can work in 
moving camera. Moreover, the matching point also show the background
information, in order to improve the robust and the efficiency of our
framework, we utilized segmentation to mix the foreground capture by
GMM and the background captured by matching point.
Comprehensive evaluation demonstrates the superiority of framework against state of the art.

\indent In background subtraction, the background is recognized as the static
part of scenes. But in video captured by moving camera, 
\indent Background subtraction is a crucial in computer vision. 
In preview work, many algorithms segment background by analysing the variation
of pixel's value, since the camera is assumed to be non-moving camera and
the position of pixel is not change. However, once the video is captured by
a free moving camera, all those algorithms is work hard. To solve this problem,
we proposed a novel framework named MSD(matching, segmentation and detection),
which

utilize matching to counteract the displacement of camera, and the 
segmentation to improve the efficiency and robust of framework. In MSD, we 
assume the relatively static and main part is the background. In this assumption,
the matching algorithms also show the point of background. Then we utilized
segmentation to mix the foreground inforation by GMM, and the backgrond information
by matching point. Comprehensive evaluation demonstrates the superiority of 
framework against state of the art.

\indent The background is recognized as the static part of scenes in background
subtraction. In the preview work, people usually analysing the variation 
of pixel's value, since they assume the video is captured by non-moving camera.
However, once the camera produce some jitter or even dipacement, all those
algorthms will failed, which cause a challenge problem background subtraction

    Commonly, the background is recognized as the static part of scene.
So many algorithms segment background by analysing the variatin of pixel's
value, since all those work assumed the camera is a nonmoving camera. 
However, once the image sequences is captured by moving camerea, all those
algorithms will failed. To solve this problem, we present a novel framework
named MSD(matching, segmentation and detection) which assume the relative 
static part of scene as background. In MSD, the static part is capture by
mathcing algorithms. and the displacement of camera is reduce by it. In 
this condition, the moving camera is became static camera. And any algorithms
based on static camera can work well in moving camera. However, the error
is and we utilized segmentation algorithms to mix the foreground information 
and background information. Comprehensive evalution demonstrate our algorithms
get the state of the art in moving camera,and promissing result in  static 
camera.
\end{comment}
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Background Subtraction, motion, moving camera.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%																		%
% 1.Introdution														    %
%																		%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\indent Background subtraction is a crucial problem in computer
vision, which has a wide range of applications including monitoring,
optical motion capturing and so on\cite{Han2012}. In the preview work, 
large numbers of algorithms assumed the camera is an Non-moving camera,
and segmented background by analysing the variation of pixels' value
\cite{Bouwmans2014}. However, in the free camera, the position of pixels
are varying during video sequences, it is hard to find a probabilistic
model for background subtraction.  To solve this problem, we proposed a 
novel framework named MSD(matching, segmentation and detection), which 
can let the algorithms in static camera can work in moving camera.\\
\indent Background is recognized as the static part of scenes. When
the video is captured by static camera, the value of pixels in background
is keep invariant, and a probabilistic model can be used for background
subtraction. However, in the video captured by moving camera, all the
position of pixels are change. In this condition, is hard to say what 
is background. To solve this problem, we follows the native means of
background and assume the main body of relatively static part in
scenes as background. Like \reffig{fig1} shown, the matching algorithms
can utilized to find the relatively static part. Then the GMM is used to 
detection the firegourd. Finally, segmntation algorithms is utilized to
mix the foregorund and background. \\
\begin{comment}
\indent Background is recognized as the static part of scenes. However
in the video captured by moving camera, it is hard to say what is 
background, sinceall the position of pixels is change. In this condition
, we follows the native means of background which is the main body of 
relative static part in scenes. Like the figure shown. The mathcing algorithms
can utilized to find those part. Then the matrix can be captured by those
part. Then, the segmentation can be utilized to mix the foreground and
background. \\
\end{comment}
% /%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% figure:fig1
\label{fig1}
\begin{figure}[!t]	% FIGURE: figure/fig1 
\centering
\includegraphics[width=3.5in]{figure/fig1}
\DeclareGraphicsExtensions.
\vspace{-10pt}
\caption{The illustration of complex scenes are recognized as the
mixture of R1, R2, R3, R4 and R5 which characterized by green color,
gray, texture, red color and blue color as dominant features,
respectively. Different dominant features are utilized for modelling
the background in each zone.}
\label{fig1}		% LABEL: fig1
\end{figure}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%/ figure:fig1
\indent In MDS framework, matching algorithms is used to matching the displacement
of two frames. We set a plot in four dimenstrate. In this condition, the camera
is become static camera. And all the algorithms based on static camera can
work well in moving camera. However, the matching algorithms can get no error.
And for solve this problem, we need to improve the robust. We used segmentation
the image into several segments And count the foreground and background for
the finally result. In fact, so we scale the segment in different scale.for 
the finally background. We utlized the GMM into our framework, and apply our 
work to some standard change detection dataset. The comparion of out algorithms
with other state of art in different videos shown that proposed approach state
of art approaches.
\begin{comment}
In this condition, the matching can used 
to find those part, and captured the matrix. For those, the displacement of
camera can be counteract, and the

\indent In moving objects detection, the background is recognized 
Background subtraction in moving camera is a challenging 
Background subtraction has a wide range of applications, 
\indent Background subtraction has a wide range of applications, including video
monitoring[], optical motion capturing[] and multimedia applications[].
In preview work, so many algorithms labeled a pixel as background when 
the variation of it is keep invariant, since they assumed the camera is
a non-moving camera. However, in the real work, the moving camera is 
everywhere and has many challenging problem. This paper assume the relative
static part as background which found the relative staic part of scene 
instead of analysing the value of pixle in time sequences.
\indent The background is recognized as the staic part of scene. However
in the video captued by moving camera, all the position of pixel is
changing, which caused large different to segment background by analysing 
pixel's value. 
\indent In this work, we assume the backgroud in moving camera is the
relatively static and main part scene. We used SIFT feature point and 
ransac to mathcing image, to reduce the camera moving. Then the algorithms
in static camera can work well in the moving camera. and  we used gmm to
get the foreground information. In the same time, the ransac algorithms
also show the background part of scene. And we used superpixel to solve
this problem.
here is introduction.\cite{Stauffer1999}
\end{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%																		%
% 2.Related work														%
%																		%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related work}
\indent Recently, many impressive work were proposed for background subtraction
in moving camera. In this paper, we divided those algorithms in two
categories. The first categories try to find the new stable features to
segment background. The second categories is focus on how to reduce
the displacement of camera moving, and our work is belong to the second
categories.
\subsection{Algorithms based on new stable features}
\subsection{Algorithms focus on counteract camera moving}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%																		%
% 3.Feature extraction													%
%																		%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The MSD framework}
\indent In this section, we explaining the processing of MSD. In, we introduction
how to let the algorithms in static can work in moving camera. In , how
to mix the foreground and background.
\subsection{The moving of camera}
\indent The processing of counteract moving of camera is shown like Fig2.
We set a plot in time sequences to like the background moving with camera
moving.
\indent In MSD, we are try counteract the moving of camera. Let's donate
the frames of video is ${f_1,f_2,...f_n}$ .There are two matching, the first
matching is used two frames $f_i$ and $f_{i+1}$The background, the matrix
 is $H$
, then we rotate the image intothen we get the 
\begin{displaymath}
    f'(x,y) = f(x,y)H.
\end{displaymath}
\indent The second matching is for best background and the frames to get
the background information.
\subsection{Mixing of foreground and background}
herer is feature extraction.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%																		%
% 4. Modeling the background with multi-feature							%
%																		%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%																		%
% 5.Experiments															%
%																		%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}
In this section, we compare our framework with XXX state-of-art algorithms
in different dataset.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%																		%
% 6.Conclusion															%
%																		%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
here is conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%																		%
% 7.Acknowledgement														%
%																		%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{comment}

\section*{Acknowledgement}
\noindent The work described in this paper was partially supported by the National
Natural Science Key Foundation (Grant no. 91118005), the National
Natural Science Foundation of China (Grant no. 61173131), the Natural
Science Foundation of Chongqing (Grant no. CSTS2010BB2061), the
Fundamental Research Funds for the Central Universities (Grant Nos.
CDJZR12098801 and CDJZR11095501) and the Chongqing Graduate Student
Research Innovation Project (Grant no. CYB14034).	\\

\end{comment}
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

 %\bibliographystyle{plain}
 %\bibliography{ref}

\bibliographystyle{IEEEtran}  
\bibliography{ref_abb}

\begin{comment}
\begin{IEEEbiographynophoto}{Dan Yang}
received the B.Eng. degree in automation,
the M.S. degree in applied mathematics, the
Ph.D. degree in machinery manufacturing and
automation from Chongqing University, Chongqing.
From 1997 to 1999, he held a postdoctoral position
with the University of Electro-Communications,
Tokyo, Japan. He is the Vice President of
Chongqing University, and a  Professor with the
School of Software Engin
eering. He has authored
over 100 scientific papers and some of them
are published in some authoritative journals and conferences,  such  as  the  IEEE  TRANSACTIONS  ON PATTERN ANALYSIS AND MACHINE INTELLIGENCE, CVPR, and BMVC. His research interests
include computer vision, image proce
ssing, pattern recognition, software
engineering, and scientific computing.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Chenqiu Zhao}
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Xiaohong Zhang}
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Sheng Huang}
(S' 14) received the B.Eng. degree in software engineering and the Ph.D. degree in computer science from Chongqing University,
Chongqing, in 2010 and 2015, respectively. From
2012 to 2014, he was a Visiting Student with the
Department of Computer Science, Rutgers Univer-
sity, Piscataway, NJ, USA. He has authored several
scientific papers in venues, such as CVPR, BMVC,
ICME, ISBI, and ICIP. His research interests include
pattern recognition, computer vision, machine
learning, and biometrics.
\end{IEEEbiographynophoto}
\end{comment}

%\begin{IEEEbiography}{Dan Yang}
%Biography text here.
%\end{IEEEbiography}

\end{document}

### 2018-02-02 draft.tex
test
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Your branch is up-to-date with 'origin/master'.
 Changes to be committed:
	modified:   draft.tex
revised the abstract

@@
 \begin{abstract}
-% the background of problem
-One of the main challenges of Background Subtraction comes from the diversity and complexity of real-world scenes.
-While most of previous works in this field were proposed by designing an artificial model, we tend to present a self-adaption solution, by combining the fully convolutional networks, which is named as the Deep Pixels’ Variation Learning model (DPVL).
-Our main job is to find a new representation of pixels’ historical observations in a new feature space.
-In this paper, videos are divided into fixed length image blocks, which are later transformed into the pixel’s observation patches as the input of a FCN for learning the variation of pixels.
+% 背景建模是一个复杂的问题
+Background subtraction is a fundamental problem of computer vision.
+% 为什么复杂
+The main challenges of background subtraction comes from the diversity and the complexity of natural scenes.
+% 以前的工作是怎么做的
+Plenty of previous works are proposed to handle this problem by artificial model.
+% 我们是怎么做的
+%Previous works in this field were proposed by designing an artificial model, 
+In this paper,
+we propose a self-adaption solution with the utilization of convolutional neural networks, 
+and a novel background subtraction model named Deep Feature Transformation Learning is proposed.
+% 动机是什么
+With the motivation of finding a new representation of pixels’ historical observations in a new feature space.
+% 怎么做的
+The videos are divided into fixed length image blocks, which are later transformed into the pixel’s observation patches as the input of a FCN for learning the variation of pixels.
 We conduct our training and prediction processes on block level.
 The architecture of the FCN is devised from the semantic segmentation problem.
-Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ variation.
-We compare our method with some of the state-of-art methods… 
+% 效果好
+Comparisons with several state-of-the-art algorithms in well-known benchmark show the superiority of proposed approach.
 \end{abstract}

### 2018-02-02 draft.tex
revised the first part of introduction

@@
 With the motivation of finding a new representation of pixels’ historical observations in a new feature space.
-% 怎么做的
+% 怎么做的 XXX 这两句话介绍方法，但我实在是看不懂，你再改改
 The videos are divided into fixed length image blocks, which are later transformed into the pixel’s observation patches as the input of a FCN for learning the variation of pixels.
@@
 \begin{IEEEkeywords} 
-    Background Subtraction, Freely Moving Camera, Foreground and Background Cues,
+    Background Subtraction, Feature Transformation, Deep Learning,
 \end{IEEEkeywords}
@@
 \section{Introduction}
-Background subtraction or foreground object detection, as a fundamental problem in computer vision, has been much discussed with the increasing number of outdoor cameras over the last few decades.
-It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.
-vehicles and humans, thus saving us huge amount of computing resources.
-Typically, Background subtraction is a binary classification task that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.
+% introduction 的第一段介绍这个问题为什么有做的意义
+% 这个问题的意义
+Background subtraction or foreground object detection is a fundamental problem of computer vision, 
+which has been developed over the last few decades.
+% 难点在哪
+The main challenges of this problem comes from the diversely natural scenes,
+such as the illumination variation \cite{2017_REVIEW_7914756}, wrapping tree \cite{2014_CVIU_SOBRAL20144} and running water \cite{Bouwmans2014}.
+% 现状是什么
+Previous work already achieve well performances in the scenes with low complexity.
+% 现有的方法是怎么做的
+In particular,
+a large numbers of studies are focus designing artificial model according to the characteristic of a particular scenes.
+%　效果如何
+Example, the multiple background model are proposed for dynamic background,
+and the texture are used to handle the shadow of objects.
+%　为什么这个问题还有做下去的意义
+However,
+in view of
+the continuous growth in videos obtained from diversely natural scenes,
+more challenging scenes are proposed for background subtraction.
+%　总结，这个问题很难，还能做
+It remains a challenging problem to proposed a general solution for background subtraction in all exist and potential scenes.
+%
+% 
+% 
+% robust background 
+% 
+% via moving cameras
+% in recent years, the matter of background subtraction for
+% moving cameras has attracted sustained levels of interest from
+% researchers
+% 
+% It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.
+% vehicles and humans, thus saving us huge amount of computing resources.
+% Typically, Background subtraction is a binary classification task that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.
 
+% 第二段介绍你的解决思路
 With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes.
@@
 
+% 第三段介绍具体是怎么做的
 In order to present a better and universal solution, we proposed the Deep Pixels’ Variation Learning (DPVL) model for Background Subtraction in diversely natural scenes.
@@
 \label{sec_spa}
+% 把你想引的论文都贴上，太多了，而且你的Zhi Zeng et al. 是ｔｍ的谁啊？？
 The most widely used algorithms in Background subtraction are pixels-based methods.
-And one of the famous method is Gaussian Mixture Model (GMM), in which a GMM is used to model the history over time of pixel’s intensity values.
+And one of the famous method is Gaussian Mixture Model (GMM) \cite{Zivkovic2004}, in which a GMM is used to model the history over time of pixel’s intensity values.
 It is assumed that pixels are independent from their neighbors.
@@
 
-In XXX , Mingliang Chen et al.
-propose a background subtraction algorithm using hierarchical superpixels segmentation, spanning trees and optical flow.
-Their Background model combine the GMM with constrains of temporal and spatial from optical flow and superpixels.
+In XXX , Mingliang Chen et al.\ \cite{2017_TPAMI_GANGWANG} propose a background subtraction algorithm using hierarchical super-pixels segmentation, spanning trees and optical flow.
+Their Background model combine the GMM with constrains of temporal and spatial from optical flow and super-pixels \cite{6205760_2012_TPAMI}.
 
-Kim et al used a codebook to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model.
+Kim et al.\ \cite{Kim2004} used a codebook to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model.
 This allows them efficient in memory and speed compared with other background modeling techniques.
@@
 After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
-
-% 
-% 
-% \begin{figure}[!t]	\centering
-% \includegraphics[width=\linewidth]{figure/extraction.pdf}
-% \DeclareGraphicsExtensions.
-% \caption{Extraction of foreground and background cues .}
-% \label{fig_extraction}		\end{figure}
 

### 2018-02-02 draft.tex
add comments for writting introduction

@@
 
+% With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes.
+% However, background Subtraction is still unsolved because of the diversity in background scenes and the changes originated from the camera itself.
+% Scene variations can be in many forms such as, camera jitter, dynamic background, bad weather, illumination changes, intermittent object motion.
+% for instance, the earlier Frame Difference Methods, trying to get a fixed image as background to classify each pixels.
+% The fundamental problem lies in that linear classifier might not be powerful enough for the job, due to the complexity and the diversity of natural scenes.
 % 第二段介绍你的解决思路
-With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes.
-However, background Subtraction is still unsolved because of the diversity in background scenes and the changes originated from the camera itself.
-Scene variations can be in many forms such as, camera jitter, dynamic background, bad weather, illumination changes, intermittent object motion.
-This is principally because the major methods, in most cases, try to find a universal solution by generating some universal background models for later linear classification; for instance, the earlier Frame Difference Methods, trying to get a fixed image as background to classify each pixels.
-The fundamental problem lies in that linear classifier might not be powerful enough for the job, due to the complexity and the diversity of natural scenes.
+
+% 说明问题的本质是什么
+
+% 以这个本质为基础来评价现存方法
+
+% 现存方法失败的原因是什么
+
+% 我们的方法针对这个原因怎么样了
+
+% XXX 为什么效果会好，同时也是我们方法的创新点, 最重要的还要结合图来说，
+
+% 总结方法的思路
 
 % 第三段介绍具体是怎么做的
+% 首先一句到两句，最多３句话总结你的方法的过程
+
+% 补充方法的细节
+
+% 这些细节带来的好处
+
+% 最后整个ｌｉｓｔ把方法的contribution 列出来
+The contribution of proposed approach are summarized as follows:
+\begin{itemize}
+    \item We proposed the Deep Feature Transformation Learning model for background subtraction in complexly natural scenes.
+        % 以前怎么做的
+        Unlike previous XXX
+        % 我们这么做有什么好处
+
+        % 为什么要reshape 
+    \item The observations in a particular pixel are reshaped into block 
+        % 这么做额目的是什么，好处什么
+\end{itemize}
+
 In order to present a better and universal solution, we proposed the Deep Pixels’ Variation Learning (DPVL) model for Background Subtraction in diversely natural scenes.
 In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.
+%XXX introduction 里最好不要出现公式
 \begin{equation}
@@
 \section{Related Work}
+%  XXX 我觉的针对方法使用的特征对方法分类比较容易。例如颜色特征，纹理特征，时空间特征,最后引出你的，特征转换
 Over the last few decades, Background subtraction has been well studied.

### 2018-03-10 draft.tex
introduction 修改

@@
 % 怎么做的 XXX 这两句话介绍方法，但我实在是看不懂，你再改改
-The videos are divided into fixed length image blocks, which are later transformed into the pixel’s observation patches as the input of a FCN for learning the variation of pixels.
-We conduct our training and prediction processes on block level.
-The architecture of the FCN is devised from the semantic segmentation problem.
+% We conduct our training and prediction processes on block level.
+The videos are divided into image blocks, which are later transformed into the pixel’s observation patches.
+Moreover, these patches are taken as the input of a Fully Convolutional Network(FCN). 
+With the strong learning ability of FCN, we can finally get a new representation from raw RGB data, which is easier for the classification.
+
+The architecture of the FCN proposed in this paper is devised from the semantic segmentation problem.
 % 效果好
@@
 %　为什么这个问题还有做下去的意义
-However,
-in view of
-the continuous growth in videos obtained from diversely natural scenes,
+However, in view of the continuous growth in videos obtained from diversely natural scenes,
 more challenging scenes are proposed for background subtraction.
@@
 % 说明问题的本质是什么 
+Typically, Background subtraction can be viewed as a binary classification, where pixels in video stream are divided into two
+types, either foreground or background.
 
 % 以这个本质为基础来评价现存方法
+With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity,
+such as the indoor scenes. However, those performance on real-world scenes like dynamic background, bad weather, illumination changes,
+intermittent object motion are still not satisffied.
 
 % 现存方法失败的原因是什么
+This is principally because the major methods, in most cases, try to find a universal solution by generating some universal 
+background models for later linear classification; for instance, the earlier Frame Difference Methods, trying to get a fixed 
+image as background to classify each pixels. The fundamental problem lies in that linear classifier might not be powerful enough for the job,
+due to the complexity and the diversity of natural scenes.
 
-% 我们的方法针对这个原因怎么样了
+%我们的方法针对这个原因怎么样了
+In order to present a better and universal solution, we proposed the Deep Feature Transformation Learning model for Background Subtraction 
+in complexly natural scenes.
 
 % XXX 为什么效果会好，同时也是我们方法的创新点, 最重要的还要结合图来说，
+With the strong learning ability of FCN, we can easily get a new representation of pixels' historical observations which are much easier and clearer to distinguish.
 
 % 总结方法的思路
+In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.
+
+sq1 = {p_1,p_2,...p_n} -> sq2 = {f_1,f_2,...f_n}                     (1)
+
+For sq1, it is a sequence of pixels' intensity, which is hard to classify which entry is foreground or background.
+But in sq2, it is more easy to classified, since the output of the network is the label of each entry in sequence.
 
 % 第三段介绍具体是怎么做的
+More particularly, videos are divided into image blocks at the beginning. Then, pixel's observation patches are extracted from these blocks and sent to a FCN.
+The FCN will learn and transform these patches into prediction patches where pixels are clearly for classification.
 % 首先一句到两句，最多３句话总结你的方法的过程
@@
 % 补充方法的细节
+In this paper, pixel’s observation patches are proposed to describe the historical observation of pixels and also as the input of our network. 
+A random initialized FCN network is trained to learn the historical observation of pixels and generate a new representation in a new feature space.
 
 % 这些细节带来的好处
+We take advantage of the strong learning ability of FCN to learn a new representation of the Pixel’s observation patches in a new space where 
+the pixels can be easily classified to background and foreground.
 
@@
 The contribution of proposed approach are summarized as follows:
+(1) We present the Pixel's observation patches which give us the ability to process the pixel's historical observation with a FCN.
+(2) We present a novel FCN architecture for Background Subtraction.
+
 \begin{itemize}
-    \item We proposed the Deep Feature Transformation Learning model for background subtraction in complexly natural scenes.
+    \item    
         % 以前怎么做的
-        Unlike previous XXX
+        Most existed methods are based on Background models. 
+        Unlike previous Background model based algorithms, we focus on the pixels stream itself, trying to find a space where the new representation
+        of pixels are easier to distinguish. 
         % 我们这么做有什么好处
+        The reason why we choose this way for the job is because we can't find a perfect background model which can adapt to all kinds of nature 
+        scenes and various tasks. In this condition, we avoid to build a universal background model. And the experiment shows a good performance 
+        compared with some state-of-art methods.
 
         % 为什么要reshape 
-    \item The observations in a particular pixel are reshaped into block 
+    \item The observations in a particular pixel are reshaped into blocks, that's because our network needs fixed size input, we also tried different 
+        size of input.
         % 这么做额目的是什么，好处什么
 \end{itemize}
-
-In order to present a better and universal solution, we proposed the Deep Pixels’ Variation Learning (DPVL) model for Background Subtraction in diversely natural scenes.
-In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.
 %XXX introduction 里最好不要出现公式
@@
 %
-But in $sq_2$, it is more easy to classified, since the output of
-
-In this paper, pixel’s observation patches are proposed to describe the historical observation of pixels.
-And a random initialized FCN network is trained to learn the historical observation of pixels and generate a new representation in a new feature space.
-We take advantage of the strong learning ability of FCN to learn a new representation of the Pixel’s observation patches in a new space where the pixels can be easily classified to background and foreground.
+But in $sq_2$, it is more easy to classified, since the output of the network is the label of each entry in sequence.
 

### 2018-05-05 build.sh
Ð޸ÄʵÑéÖÐ

@@ -1,5 +1,0 @@
-pdflatex draft.tex 
-bibtex draft.aux 
-pdflatex draft.tex 
-pdflatex draft.tex
-evince draft.pdf

### 2018-05-05 draft.tex
add fig1 to illustrate the idea of paper
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.aux 	modified:   draft.log 	modified:   draft.pdf 	modified:   draft.tex

@@
 % Typically, Background subtraction is a binary classification task that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.
+\begin{figure}[!t]	% FIGURE: figure/fig1 
+\centering
+\includegraphics[width=.5\textwidth]{figure/fig1}
+\DeclareGraphicsExtensions.
+    \caption{The illustration of Proposed approach}
+\label{fig_FBMS_nobk}
+\end{figure}
 
@@
 
-sq1 = {p_1,p_2,...p_n} -> sq2 = {f_1,f_2,...f_n}                     (1)
+% sq1 = {p_1,p_2,...p_n} -> sq2 = {f_1,f_2,...f_n}                     (1)
 
@@
 The PDF for each pixel is estimated with Kernel Density Estimation (KDE).
-
-\subsection{region-based approach}
 \label{sec_geo}
@@
 Some online approaches have also been proposed recently, but they are still very computationally expensive.
-
-\subsection{Algorithms based on Super-pixels}
 \label{sec_sup}
@@
 
-\section{The IFB Framework}
+\section{The  Framework}
 \label{sec3}
@@
 Different with those traditional ones, fully convolutional networks can take input of arbitrary size and produce correspondingly-sized output with efficient inference. 
-FCNs have already been used in many areas like sematic segmentation and so on.
-Researchers found FCNs has a strong learning ability which won’t lost to the traditional ones, meanwhile, it also has a high efficient computation ability.
+FCNs have already been used in many areas like sematic segmentation and so on. Researchers found FCNs has a strong learning ability which won’t lost to the traditional ones, 
+meanwhile, it also has a high efficient computation ability.   
 FCNs utilize 1*1 kernels to take the place of fully connected layers. 
@@
 In this paper,
-we proposed the IFB framework for background subtraction for the case of a freely moving camera.
+we proposed the framework for background subtraction for the case of pixels' historical observation.
 Unlike previous work in which attempts were made to improve the accuracy of the estimation of motion,
-our IFB focuses on integrating rough foreground and background cues for foreground segmentation.
+our method focuses on transform the foreground cues for Background Subtruction.
 In particular, 
-foreground cues are detected by a GMM model with the estimation of background motion,
-while background cues are captured from spatio-temporal features filtered by homography transformation,
-where the SURF\cite{2006_SURF}, KAZE\cite{2012_KAZE}, SIFT\cite{lowe2004distinctive} features are used as examples.
+pixels' historical observations are obtained from image blocks with the estimation of background motion,
 % the geometric constraints between the SIFT features.
 Then, super-pixels under multiple levels are utilized to integrate these cues.
-The efficiency of IFB results from the complementarity between foreground and background cues.
-The accuracy of the proposed approach is improved though the utilization of super-pixels under multiple levels.
+The efficiency of historical observation from the complementarity between foreground and background cues.
 A comprehensive experiment to compare our results with the state-of-the-art shows the efficiency of our framework and points to its potential for use in practical applications.

### 2018-06-20 deeplearning_bg/deeplearning_bg/abstract.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	new file:   build.bat 	new file:   build.sh 	new file:   config 	modified:   deep background feature transformation learning.doc 	new file:   deeplearning_bg.rar 	new file:   deeplearning_bg/deeplearning_bg/abstract.aux 	new file:   deeplearning_bg/deeplearning_bg/abstract.bbl 	new file:   deeplearning_bg/deeplearning_bg/abstract.blg 	new file:   deeplearning_bg/deeplearning_bg/abstract.log 	new file:   deeplearning_bg/

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{verbatim}%长篇注释宏包
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{url}
\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\newcommand{\reffig}[1]{Fig. \ref{#1}}
\newcommand{\refsec}[1]{Section \ref{#1}}
% \newcommand{\refeq}[1]{Eq. \ref{#1}}
\newcommand{\reftab}[1]{Table \ref{#1}}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Background Subtraction based on Superpixels under Multi-Scale in
Complex Scenes}

% a short form should be given in case it is too long for the running head
\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Alfred Hofmann
\thanks{Please note that the LNCS Editorial assumes that all authors have used
the western naming convention, with given names preceding surnames. This determines
the structure of the names in the running heads and the author index.}%
\and Ursula Barth\and Ingrid Haas\and Frank Holzwarth\and\\
Anna Kramer\and Leonie Kunz\and Christine Rei\ss\and\\
Nicole Sator\and Erika Siebert-Cole\and Peter Stra\ss er}
%
\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Springer-Verlag, Computer Science Editorial,\\
Tiergartenstr. 17, 69121 Heidelberg, Germany\\
\mailsa\\
\mailsb\\
\mailsc\\
\url{http://www.springer.com/lncs}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}
Background subtraction in complex scenes has been a challenging problem
in computer vision.
% Previous work
Most previous algorithms analyzed the variation of pixels or region for
background subtraction, which ignored the neighbor information and
similarity between pixels themselves.
% our work
In this paper, a novel background subtraction method based on
superpixels under multi-scale (SPMS) in complex scenes is proposed.
% 说明方法新颖的地方,优点
Since superpixel implied the neighbor information between similar
pixels, proposed approach achieves encouraging robustness in complex
scenes including adverse weather and dynamic scenes.
% 具体的方法
In our SPMS, pixels are clustered into several superpixels according to
the similarity between them.
% 每一个超像素的标记方法
Each super-pixel is subtracting from the respective zone of background
image to label as foreground or background.
% background image 如何得到
In particular, the background image is learned from the statistic of
pixels' intensity during video sequence.
% 多尺度
Moreover, in order to improve the robustness and efficiency of proposed
approach, the integration of foregrounds captured in different scales is
used as the final result of SPMS.
% 实验结果
The experiments on standard benchmark demonstrate the encouraging
performance of proposed approach in comparison with some
state-of-thee-art approaches.
\keywords{Background Subtraction, Motion, Superpixels, Multi-Scale}
\end{abstract}

\end{document}

### 2018-06-20 deeplearning_bg/deeplearning_bg/typeinst.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	new file:   build.bat 	new file:   build.sh 	new file:   config 	modified:   deep background feature transformation learning.doc 	new file:   deeplearning_bg.rar 	new file:   deeplearning_bg/deeplearning_bg/abstract.aux 	new file:   deeplearning_bg/deeplearning_bg/abstract.bbl 	new file:   deeplearning_bg/deeplearning_bg/abstract.blg 	new file:   deeplearning_bg/deeplearning_bg/abstract.log 	new file:   deeplearning_bg/

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{verbatim}%长篇注释宏包
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\newcommand{\reffig}[1]{Fig. \ref{#1}}
\newcommand{\refsec}[1]{Section \ref{#1}}
% \newcommand{\refeq}[1]{Eq. \ref{#1}}
\newcommand{\reftab}[1]{Table \ref{#1}}

\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Background Subtraction via Deep Variation Transformation}

% a short form should be given in case it is too long for the running head
 \titlerunning{Background Subtraction via Deep Variation Transformation}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%i
\author{Yongxin Ge, Xinyu Ren, Chenqiu Zhao}
%
\authorrunning{Lecture Notes in Computer Science: Chongqing University}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Laboratory of Intelligent Services and Software Engineering, \\
School of Software Engineering,\\
Chongqing University, Chongqing 401331, China\\
\url{xxx@cqu.edu.cn}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Chongqing University}
\maketitle

\begin{abstract}
%Background subtraction in complex scenes is a challenging problem
One of the main challenges of foreground detection comes from the diversity and complexity of real-world scenes. While most of previous works in this field were proposed by designing an artificial model, we tend to present a self-adaption solution, by combining the fully convolutional networks (FCNs), which is named as the Deep Pixels Variation Learning model (DPVL). Our main job is to find a new representation of pixels historical observations in a new feature space. In this paper, videos are divided into fixed length image stacks, which are later transformed into the pixel observation matrixes as the input of a FCN for learning the variation of pixels. We conduct our training and prediction processes on stack level. The architecture of the FCN is devised from the semantic segmentation problem. Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ variation. We compare our method with some state-of-the-art methods, and the results show that the proposed approach outperform its
\keywords{Background Subtraction, Motion Detection, Superpixels, Neighborhood Information, Multi-Scale}
\end{abstract}

\section{Introduction}
% 问题的意义
% 问题的挑战
% previous work
% 这些方法的缺点
% 我们的思路
% 具体的方法
% 从描述现象开始
% 开始描述图
% 左边的图混合在一起
%For example, as the left part of \reffig{thinking} shows, the pixels labeled as
%However, a pixel is not independent \cite{2009_ICASSP_ViBe} but related
%\begin{figure}
%    \centering
%    \includegraphics[width=\textwidth]{figure/fig_idea}
%    \caption{The variation in pixels and superpixels with foreground or background labels.}
%    \label{thinking}
%\end{figure}
% 我们方法的具体细节...
% 最终的目的
%% 论文的贡献
%The contributions of this paper are summarized as follows:
%\begin{enumerate}
%    \item Our SPMS utilizes superpixels instead of pixels or regions for
%        background subtraction. Since the superpixel reveals the neighborhood
%        information and the similarity among pixels, proposed approach achieves
%        encouraging robustness in complex scenes, such as adverse weather and
%        dynamic scene.
%    \item The final foreground of SPMS is captured by the summary of
%        foregrounds captured in different scales. Benefited from the difference
%        about superpixels' zone in multiple scales, the accuracy of our SPMS
%        background model is improved by the summary process.
%\end{enumerate}
	Background subtraction or foreground object detection, as a fundamental problem in computer vision, has been much discussed with the increasing number of outdoor cameras over the last few decades. It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.g. vehicles and humans, thus saving us huge amount of computing resources. Typically, Background subtraction can be viewed as a binary classification that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.

	With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. However, background Subtraction is still unsolved because of the diversity in background scenes and the changes originated from the camera itself. Scene variations can be in many forms such as, camera jitter, dynamic background, bad weather, illumination changes, intermittent object motion. This is principally because the major methods, in most cases, try to find a universal solution by generating some universal background models for later linear classification; for instance, the earlier Frame Difference Methods, trying to get a fixed image as background to classify each pixels. The fundamental problem lies in that linear classifier might not be powerful enough for the job, due to the complexity and the diversity of natural scenes.

	In order to present a better and universal solution, we proposed the Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes. In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.

	For \emph{Sq}, it is a sequence of pixel variation, which is hard to classify which entry is foreground or background. But in \emph{Sq'}, it is more easy to classified, since the output of the network is the label of each entry in sequence.

	In this paper, pixel observation matrixes are proposed to describe the historical variation of pixels. And a random initialized FCN network is trained to learn the pixel variation and generate a new representation in a new feature space. We take advantage of the strong learning ability of FCN to learn a new representation of the pixel observation matrixes in a new space where the pixels can be easily classified to background and foreground.

\section{Related Work}
% 引子，简单介绍不利用领域信息的方法
% 以前方法的没有考虑的东西
% 近期的工作开始利用领域信息
% 引子
% 蕴含领域信息的特征 texture
% 论文的好处
% 增强算法
% multileve
% multi-scale codebook
% the spatio-temporal features
% the pursuing dynamic spatio-temporal
% multiscale spatioi
% ViBe and ViBe++
% ViBe 具体的做法
% histogram
% Background modeling by combining joint intensity histogram with time-sequential data
% 我们方法与它们的区别
% the region based algorithms
% rect gauss
% regions-based spatio-temporal features
% XXX 解释和区域方法的不同
% 超像素
% pixels layers
% reshape the foreground.
% superpixel
Over the last few decades, Background subtraction has been well studied. Meanwhile, a huge number of methods were proposed. These methods can be broadly categorized into pixels-based, region-based, frame-based and Deep Learning.
\subsection{pixels-based methods}
The most widely used algorithms in Background subtraction are pixels-based methods. And one of the famous method is Gaussian Mixture Model (GMM), in which a GMM is used to model the history over time of pixel’s intensity values. It is assumed that pixels are independent from their neighbors. Incoming pixels are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound. For learning the parameters, that maximize the likelihood, the authors proposed an online method that approximates the Expectation Maximization (EM) algorithm. 
In XXX , Mingliang Chen et al. propose a background subtraction algorithm using hierarchical superpixels segmentation, spanning trees and optical flow. Their Background model combine the GMM with constrains of temporal and spatial from optical flow and superpixels. 
Kim et al used a codebook to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model. This allows them efficient in memory and speed compared with other background modeling techniques. The final foreground is detected by a distance measurement in a cylindrical color model.
In XXX, Zhi Zeng et al. proposed an equal-qualification updating strategy to replace the maximum-negative-run-length-based filtering strategy. Their experiments show that, the proposed method outperforms well, despite using only color information.
Elgammal et al. introduced a probabilistic non-parametric method to model the background. It is assumed that each background pixel is drawn from a PDF. The PDF for each pixel is estimated with Kernel Density Estimation (KDE).
\subsection{region-based approach}
region-based approach assumpt that the neighboring pixels have a similar variation as the pixel itself. 
In xxx, Sriram Varadarajan et al. propose a region-based MoG to takes in which the updated mixtures represent the scene distribution in a neighborhood region.
In (PCA), classification is done by comparing a stack in current frame to its reconstruction from PCA coefficients and declaring it as background if the reconstruction is close.
A recently region based method is presented in XXX which used the statistical circular shift moments (SCSM) in image regions for change detection.
subspace learning method in xxx, is used to compress the background into the eigenbackground. For each video, the mean and the covariance matrix are calculated. After a PCA of the covariance matrix, a projection matrix is set up with M eigenvectors. Then, incoming images are compared with their projection onto the eigenvectors. Foreground labels are assigned to pixels with large distances, after calculating the distances between the image and the projection and comparing them with the corresponding threshold value. 
Marghes et al. used a mixed method that combines a reconstructive method (PCA) with a discriminative one (LDA) to robustly model the background.
single Gaussians are employed for foreground modeling. By computing flux tensors, which depict variations of optical flow within a local 3D spatio-temporal volume, blob motion is detected. With the combination of the different information from blob motion, foreground models and background models, moving and static foreground objects can be spotted. Also, by applying edge matching, static foreground objects can be classified as ghosts or intermittent motions.
Frame-based background modeling via Principal Component Analysis (PCA) and low-rank/sparse decomposition approaches is a popular alternative to pixel-level modeling xx. These approaches are however not ideal for surveillance applications as most rely on batch or offline processing or suffer from scaling problems. 
In XXX, ss et al. addressed scaling problems by reformulating principal component analysis for 2D images. Meanwhile their method takes much lower memory consumption and computational cost than others. Some online approaches have also been proposed recently, but they are still very computationally expensive.
\subsection{Deep learning methods}
A novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck. They used a fixed background model, which was generated from a temporal median operation over N video frames.
In XXX, Yi Wang et al. tried a CNN architecture combined with a Cascade model for segmentation in Background subtraction. Given 200 labelled images as training set, their model performed excellently in dataset2014.
Braham et al. present an Deep learning-based method. with the help of CNN, they generated a fixed background model from a temporal median operation over N video frames. Then, a scene-specific CNN is trained with corresponding image matrixes from the background image.
In xxx, M. Babaee et al. combine the segmentation mask from SuBSENSE algorithm and the output of Flux Tensor algorithm, which can dynamically change the parameters used in the background model based on the motion changes in the video frames. They also used spatial-median filtering as the post processing of the network outputs.

\section{VARIATION TRANSFORMATION}
In this section, we will elaborate on the motivation of the proposed approach and how does the variation transformation works in background subtraction.

Background subtraction is essentially an binary classification in time sequence, where pixels in a video stream are separated into two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops). In most cases, if we print out the historical observations of a single pixel, it is not hard to see that they usually keep their stability when belonging to the background. However, there are some exceptions: historical observations varies regularly when belonging to some dynamic background scenes(e.g. waves, swaying tree leaves). Generally, pixels from the background are sharing some common patterns of variation. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figure/fig1}
    % 图例里描述一下。
    \caption{It is hard to separate the foreground pixels from the background precisely in a time sequence.}
    \label{variation_chart}
\end{figure}
To give an intuitive understanding of the pixel variations, we plot the historical observations and corresponding groundtruth of a single pixel in Figure.1, with the X axis showing their range of variation and the Y axis representing the time. As we can see, there are several lines in three colors: blue, red and green. The blue one is called the pixel variation curve, which containing 100 original observations. Accordingly, the red one, the groundtruth curve is made of a piece of groundtruth data corresponding to the observations. The green one, which we call the transformed variation curve, is made of the outputs of the proposed approach. In practice, background subtraction is to produce a prediction curve, which is as near as possible to the groundtruth carve, by given the pixel variation carve.

Under ideal conditions like indoor videos, previous methods perform quite effectively, when distributions of background and foreground observations are remarkably different and the backgrounds are normally keeping static. While in fact, backgrounds can be rather turbulent and dynamic due to the complexity and diversity of nature scenes. Especially when illumination and camouflages are involved, background and foreground observations are easily confused and mixed up.

For example, in Figure.1, it is noticeable that some foreground observations in blue line share the similarly value with background ones. In that case, those popular solutions will inevitably yield some sticky moments when separating the pixels in the blue line. Statistical methods, for instance, are no longer valid, because they only focus on establishing a statistical model for the background, while having little or no concern for the temporal coherence of these observations. Unfortunately, most previous methods, as far as we know, are not capable to take advantage of the temporal coherence of pixel variation. In other words, despite knowing that pixels from the background share some common patterns of variation in a temporal sequence, we still let the order information of sequential images all go to waste. To alleviate this, order information of pixels must be taken in consideration. More concretely, we must find an efficient method to model the patterns of background pixels variations.

In this paper, a method of background subtraction based on variation transformation are proposed. Pixel observations are no longer considered independent of each other but regarded as a whole, which we call the pixel variation. Consequently, the classification of pixels can be viewed as a transformation of pixel variations, from the observation sequences to the prediction sequences. In the specific implementation, we trained a FCN to learn a transformation for the pixel variations by mapping them into a new space where it is close to the groundtruth, just like the green line in Figure.1. After thresholding, we can easily get the labels of each observation. The benefits from variation transformation are evident and clearly seen. It is hard to distinguish a foreground observation when its value are similar to the background ones. However, classification on the transformed variation is much convenient and intuitive, due to the advantage of temporal information. With the aid of deep learning method, the proposed approach can be effectively implemented.

% 公式
%\begin{equation}
%\{\mathcal{SP}_1,
%\mathcal{SP}_2, \dots \mathcal{SP}_s \} = \{ Sp_{i,j}|i \in [1,s], j \in [1,N_i] \},
%\end{equation}
%where $i$ is the index of scale and $N_i$ is the number of superpixels under scale $i$.

% 最后的前景是综合得到

% 公式表达
And the definition of region searching method $G(x,y)$ is shown as follows:
\begin{equation}
    G(x,y) =  \mathop{\argmin}_{}{ \lVert I_t(m,n) - I_b(x,y) \rVert_{1}  } \quad  m,n \in x,y \pm R,
\end{equation}
where $x$ and $y$ is the location of pixels. And $I_t$ is the current frame, where $t$ is the
time index.

%me
\section{BACKGROUND SUBTRACTION VIA DEEP VARIATION TRANSFORMATION}
In this section, we introduce the proposed approach that consists of a novel FCN network for background subtraction. We explain the details of the procedures of pixel matrixes, which is a specific form of pixel variation, and the architecture of our network.

The complete system is illustrated in Figure 1. Firstly, we temporally sample the input and ground truth images to generalize the pixel variations, and reshape them into fixed-size matrixes and fed them into the network. After reassembling the matrixes into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figure/fig2}
    \caption{Fully convolutional networks can efficiently learn to make dense predictions for per-pixel tasks like semantic segmentation.}
    \label{flow_chart}
\end{figure}
Given different videos, the number of frames are generally different. However, the size of our input is fixed, which means a sampling processing is required to keep the length of pixel variations invariant. Therefore, image stacks are sampled form the given videos before the pixel variations are extracted. The given video and image stacks can be defined as follows: 
\begin{equation}
	Given \  Video=\{ I_1,I_2,I_3,\dots,I_L\} ,
\end{equation}
\begin{equation}
Stack_{(x)}=\{I_x,I_{(x+p)},I_{(x+2p)},\dots,I_L \},\quad p*l=L,\quad 1\leqslant   x\leqslant p , 
\end{equation}
Where $I_t$ represent the frame $t$ of the given video. And $p$ is an integer number depended on the video frames length. For each video, we can produce multiple image stacks and choose one of them for the training. In addition, thanks to the temporal sampling, we can get compact pixel historical observations containing more temporal information than the continuous pixel sequences. This works well when it comes to some situation where the moving objects keep stationary for a long time.

In order to make use of the temporal information of pixel historical observations, we regard the sampled observations from a single pixel as a whole, namely the pixel variation. After the temporal sampling, a large number of observation sequences, or pixel variations, are extracted from the chosen stack, which is shown as follows:
\begin{equation}
Sq_{(m)}=\{P_1^m,P_2^m,P_3^m,\dots,P_n^m\},
\end{equation}
Where $P_t^m$ denotes the numerical value of pixel $m$ at frame $t$ in the chosen stack. Each of the pixel variation is a piece of temporal information which containing the changing patterns of background pixels. And each of them is of fixed length $n$. It is notable that the quantity of observation sequences is exactly the resolution of the given video, which means an abundance of training data can be obtained with just one image stack.

Our intention is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. However, vectors are not appropriate for the network training and learning. Besides, we hope the pixel observations can be interacted with their further compatriots in temporal sequence. Thus we reshape the variations into pixel matrixes as the input of our network. A sample of pixel matrix $H$ is like this:
\begin{equation}
H=P_{i+j*d}=\begin{bmatrix}
 P_1& P_2  &\dots  &P_d \\ 
\vdots &  &  &\vdots \\ 
 P_{1+(d-1)d}& \dots & \dots & P_D
\end{bmatrix},\quad d^2=D,
\end{equation}
Pixel observations are put into the $d*d$ matrix according to the order of top to bottom and left to right. The parameter $i$ and $j$ represent the column and row respectively. And the parameter $D$ is the total frame length of a variation. To put it from another way, pixel matrix is just a specific form of the pixel variation. Although the pixel matrix and the observation sequence belong to different forms of the pixel variation, they are formed of the same components, and share the common temporal information from the pixel variation. Since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack.

In the previous steps, videos are broken down into pixel matrixes which containing abundant background information. Next, the groundtruth matrixes are obtained in the same way. Both of them are put into the network for the training. However, the size of the input will decreased after the network computing. In order to make output the same size as input, we borrowed ideas from Image semantic segmentation, which is doing padding to the input before the training. After the forward computing, variations are transformed in a new space where they can be easily classified by thresholding. The new representation of input pixel variation is defined as:
\begin{equation}
H_p= \mathcal L (E_x (H)),
\end{equation}
Where, $H_p$ denotes the output of network, which we call the prediction matrix, the forward computation of network is represented by $L$, and $E_x$ denotes the symmetric padding of pixel matrix where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel matrix $H$. Another advantage of symmetric padding is that the order information still remains.

For the loss function, we choose the Sigmoid Cross Entropy (SCE), which are helpful to address the learning slowdown. The formulation is as follows:
\begin{equation}
 \begin{aligned}
loss_{(H_p,H_gt)}= \left \sum_{x\in X,y\in Y} H_{gt}(x,y) \log 
{(Sigmoid(H_p (x,y)))}+ \right.\\ 
\left. (1-H_{gt}(x,y))\log{(1-Sigmoid(H_p(x,y))}\right ,
\end{aligned}
\end{equation}
\begin{equation}
Sigmoid(x)=\frac{1}{1+e^{-x}}\  ,
\end{equation}
Where $H_{gt}$ denotes the groundtruth matrix which is given by the corresponding GT stack. The SCE is calculated between the transformed matrixes and the corresponding groundtruth matrixes. Boundaries of moving objects and pixels that out of the region of interest are ignored in the cost function.
Finally, we get the transformed variation through the FCN, which are easier for classification. We globally threshold the values for each observation in order to map them to $\{0,1\}$ . The threshold function is given by
\begin{equation}
    \label{piecewise_fg}
    g(x,y) =
 \begin{cases}
  1,  \quad x < y       \\
  0,  \quad otherwise   \\
\end{cases}.
\end{equation}
\begin{equation}
M(x,y)=g(H_p,r) ,
\end{equation}
After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery. And the major contribution is that we demonstrate the effectiveness of temporal information in background 
subtraction.

Here we make a detailed introduction to the deep learning model we used and explain why we choose it.

Different with CNNs, fully convolution neural networks (FCNs) utilize convolutional layers with $1*1$ kernels to take the place of fully connected layers, which largely resolves these above-mentioned problems. First and foremost, the size of outputs are adjustable in FCNs, which allows an end-to-end mapping of pixel observation sequences and network outputs on the time sequence. We hope to determine the label of a pixel through the comparison of its compatriot in time sequence. There is one more point I ought to touch on, that since the feature maps are no longer need to be converted into vectors, spatial information can be retained . The last but not the least, FCNs have been used in sematic segmentation and researchers found FCNs have a strong learning ability which won’t lost to the traditional ones. Meanwhile, it’s also a high efficient computation model.

Based on above-mentioned factors, FCN is designed as the alternative network architecture in this paper. The structure of our FCN for background modeling is shown in Fig.1. The proposed FCN contains 5 convolutional layers, 2 pool layers and a convolutional layer which have a filter size of $1*1$. We use the Rectified Linear Unit (ReLU) as activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.

\section{EXPERIMENTAL RESULTS}

In this section, we ran comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark and CAMO-UOW. The CDnet is the largest dataset for background subtraction so far as we are aware, containing 11 categories with several complexly challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on. The CAMO-UOW is another challenging benchmark which contains 10 high resolution videos. For each video, one or two persons appear in the scene with the clothes in the similar color as the background.

The proposed approach is compared with several existing traditional state-of-the-art background subtraction algorithms, including the IUTIS-5, the SuBSENSE, the WeSamBE, sharable GMM, the SharedModel, word-dictionaries-based method and PAWCS, the SemanticBGS, the AAPSA, etc. Moreover, two deep learning based algorithms are also compared with the proposed approach, which include DeepBS, and DBMF. All the results of compared algorithms are provided by authors.

During the comparison, the F-measure(Fm) has been used for evaluation. The Fm is a general international standard in background subtraction which measures the segmentation accuracy by considering both the recall and the precision. The definition of Fm is shown as follows:
\begin{equation}
Fm= \frac{2\times precision \times recall}{precision + recall} = \frac{2TP}{2TP+FN+FP},
\end{equation}
Where TP, FP, and FN are true positives, false positives, and false negatives respectively, computed in pixels of all test frames for each video.

The quantitative and qualitative comparisons are shown in \reftab{tab1} and Fig.3 respectively. Due to the paper length, several typical videos are selected for the qualitative comparisons as well as the discussion. In the dynamic background scene, the video “canoe” is a typically challenging video which includes a large area of water rippling. The main challenge comes from the dynamic background, in which it is so hard to describe the background by a single image. In this condition, since the traditional background subtraction method such as the SharedModel and the WeSamBE do not have the enough ability to describe the complex dynamically background, they are fail to detect the people on the boat, as shown in the Fig. X. Besides, the detected moving objects of the SharedModel are not accurate in boundary due to the utilization of texture features. In contrast, benefited from the strong learning ability of Deep Learning network, the DeepBS successfully detected the people. Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even the deep learning based algorithm is suffering from the detection of the boat shape. In contrast, the proposed approach performed superior than others in this scene, since the essence of background subtraction is considered as a binary classification of pixels’ observation in time sequence. Based on this insight, the FCN network focuses on learning the patterns of the pixel variation rather than a static background image, and proposed approach achieves promising performance in the canoe video.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figure/fig3}
    \caption{The qualitative evaluation of the proposed method. All the results is followed in the CDnet 2014.}
    \label{results_chart}
\end{figure}
As for the case of shadow scene, ‘peopleInShade’ is a typical example with prevalent hard and soft shadows. In the traditional approaches, these shadow regions are usually segmented as foreground since it is also moving with the objects. Therefore, traditional methods like the PAWCS, the WeSamBE and the SharedModel falsely segments part of shadows as moving objects. In addition, the foreground provided by the UBSS is incomplete on the part of the pedestrian’s body due to the interference of shades, which can be owing to the severe dependency of texture features. Whereas, the DeepBS performs well in this video benefited from the utilization of CNN. However, the shape of pedestrians are slightly deformed as the result of their matrix-wise processing of CNN. In contrast, derived from the fact that our DPVL focus on learning the pattern of pixels’ variation in the shadow regions, proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.

In the video “corridor” among the Thermal scene, there is no color information since the videos are obtained through a Thermal camera. Moreover, the moving objects in these videos are exceedingly fuzzy and indistinct, which is the main challenge of this category. The WeSamBE, the SharedModel and the PAWCS successfully detect the target objects, owing to a stable background in this indoor video. However, they fail to remove the reflections since their modeling ability have already reached a limit under the extreme condition of thermal map. The DeepBS, by contrast, succeeds in eliminating most of the reflections. Meanwhile, the moving objects are also clearly divided from the background thanks to the strong modeling ability of CNN. However, due to the dependency of edge feature, a small object were missed in the detection result. Fortunately, the proposed approach focus on the pattern of pixels’ variation, which should be theoretically effective even in the observation without the color information. Consequently, our DPVL performed much better than compared algorithms, with the situation that most parts of shadow are removed and the segmentation results are more accurate.

% 解释超像素的相似度%which is shown in \reftab{tab1}, in our $\text{SPMS}_1$ and
\begin{table}[tab1]
\centering
\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CDnet 2014.}
\label{tab1_res}
\begin{tabular}{lllllllllllll}
\hline
Videos      & baseline & dyna.bg & cam.jitter & int.obj.m & shadow & thermal & bad.weat & low f.rate & night vid. & PTZ    & turbul. & overall \\ \hline
DeepBS      & 0.9580   & 0.8761  & \textbf{0.8990}     & 0.6097    & 0.9304 & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & \textbf{0.8993}  & 0.7458  \\
IUTIS-5     & 0.9567   & 0.8902  & 0.8332     & 0.7296    & 0.9084 & 0.8303  & 0.8289   & \textbf{0.7911}     & 0.5132     & 0.4703 & 0.8507  & 0.7717  \\
FTSG        & 0.9330   & 0.8792  & 0.7513     & 0.7891    & 0.8832 & 0.7768  & 0.8228   & 0.6259     & 0.5130     & 0.3241 & 0.7127  & 0.7283  \\
AAPSA       & 0.9183   & 0.6706  & 0.7207     & 0.5098    & 0.7953 & 0.7030  & 0.7742   & 0.4942     & 0.4161     & 0.3302 & 0.4643  & 0.6179  \\
CwisarDH    & 0.9145   & 0.8274  & 0.7886     & 0.5753    & 0.8581 & 0.7866  & 0.6837   & 0.6406     & 0.3735     & 0.3218 & 0.7227  & 0.6812  \\
PAWCS       & 0.9397   & 0.8938  & 0.8137     & 0.7764    & 0.8934 & 0.8324  & 0.8059   & 0.6433     & 0.4171     & 0.4450 & 0.7667  & 0.7403  \\
SuBSENSE    & 0.9503   & 0.8177  & 0.8152     & 0.6569    & 0.8986 & 0.8171  & 0.8594   & 0.6594     & 0.4918     & 0.3894 & 0.8423  & 0.7408  \\
SemanticBGS & 0.9604   & \textbf{0.9489}  & 0.8388     & 0.7878    & 0.9244 & 0.8219  & 0.8260   & 0.7888     & 0.5014     & 0.5673 & 0.6921  & 0.7892  \\
MBS         & 0.9287   & 0.7915  & 0.8367     & 0.7568    & 0.8262 & 0.8194  & 0.7980   & 0.6350     & 0.5158     & 0.5520 & 0.5858  & 0.7288  \\
WeSamBE     & 0.9413   & 0.7440  & 0.7976     & 0.7392    & 0.8999 & 0.7962  & 0.8608   & 0.6602     & 0.5929     & 0.3844 & 0.7737  & 0.7446  \\
ShareM      & 0.9522   & 0.8222  & 0.8141     & 0.6727    & 0.8898 & 0.8319  & 0.8480   & 0.7286     & 0.5419     & 0.3860 & 0.7339  & 0.7474  \\
GMM         & 0.8245   & 0.633   & 0.5969     & 0.5207    & 0.7370 & 0.6621  & 0.7380   & 0.5373     & 0.4097     & 0.1522 & 0.4663  & 0.5707  \\
RMoG        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
Ours        & \textbf{0.9668}   & 0.8639  & 0.8446     & \textbf{0.9181}    & \textbf{0.9390} & \textbf{0.9268}  & \textbf{0.9265}   & 0.7338     & \textbf{0.7306}     & \textbf{0.5845} & 0.8761  & \textbf{0.8504} \\ \hline
\end{tabular}
\end{table}

\begin{table}[tab2]
\centering
\caption{The performance comparison of the proposed approach and some classical methods and deep-based method DBMF .}
\label{tab2_res}
\begin{tabular}{llllllll}
\hline
Methods  & highway & office & Pedestrians & PETS2006 & Fall   & sofa   & overall \\ \hline
GMM      & 0.5788  & 0.2338 & 0.5202      & 0.6011   & 0.8026 & 0.5225 & 0.5432  \\
CodeBook & 0.8356  & 0.5939 & 0.7293      & 0.7808   & 0.3921 & 0.8149 & 0.6911  \\
ViBe     & 0.7535  & 0.6676 & 0.8367      & 0.6668   & 0.6829 & 0.4298 & 0.6729  \\
PBAS     & 0.8071  & 0.6839 & 0.7902      & 0.7280   & 0.3420 & 0.5768 & 0.6547  \\
P2M      & 0.9160  & 0.3849 & 0.9121      & 0.7322   & 0.5819 & 0.4352 & 0.6604  \\
DBMF     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
ours     & \textbf{0.9775}  & \textbf{0.9565} & \textbf{0.9652}      & \textbf{0.9681}   & \textbf{0.9157} & \textbf{0.8943} & \textbf{0.9462}  \\ \hline
\end{tabular}
\end{table}

\begin{table}[tab3]
\centering
\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CAMO-UOW.}
\label{tab3_res}
\begin{tabular}{lllllllllll}
\toprule
Methods  & MOG2 & FCI  & LBA-SOM & PBAS & SuBSENSE & ML-BGS & DECOLOR       & COROLA & FWFC          & Ours          \\ \midrule
Video 1  & 0.79 & 0.88 & 0.8     & 0.9  & 0.89     & 0.89   & 0.92          & 0.8    & \textbf{0.94} & \textbf{0.94} \\
Video 2  & 0.82 & 0.79 & 0.8     & 0.82 & 0.88     & 0.8    & 0.83          & 0.58   & 0.96          & \textbf{0.98} \\
Video 3  & 0.88 & 0.86 & 0.85    & 0.91 & 0.9      & 0.8    & 0.9           & 0.82   & \textbf{0.94} & \textbf{0.94} \\
Video 4  & 0.89 & 0.9  & 0.76    & 0.93 & 0.78     & 0.88   & 0.95          & 0.87   & 0.94          & \textbf{0.97} \\
Video 5  & 0.84 & 0.86 & 0.82    & 0.83 & 0.82     & 0.8    & 0.82          & 0.75   & 0.91          & \textbf{0.97} \\
Video 6  & 0.93 & 0.87 & 0.77    & 0.95 & 0.92     & 0.95   & \textbf{0.97} & 0.72   & 0.94          & 0.96          \\
Video 7  & 0.76 & 0.83 & 0.88    & 0.91 & 0.87     & 0.79   & 0.91          & 0.83   & 0.96          & \textbf{0.99} \\
Video 8  & 0.83 & 0.87 & 0.85    & 0.87 & 0.93     & 0.86   & 0.86          & 0.68   & 0.96          & \textbf{0.98} \\
Video 9  & 0.89 & 0.9  & 0.87    & 0.84 & 0.92     & 0.87   & 0.86          & 0.78   & 0.88          & \textbf{0.99} \\
Video 10 & 0.89 & 0.86 & 0.89    & 0.91 & 0.92     & 0.9    & 0.94          & 0.85   & 0.96          & \textbf{0.97} \\
average  & 0.85 & 0.86 & 0.83    & 0.89 & 0.88     & 0.85   & 0.90          & 0.77   & 0.94          & \textbf{0.97} \\ \bottomrule
\end{tabular}
\end{table}

The quantitative evaluation of proposed approach on CDnet 2014 is shown in the \reftab{tab1}. It can be inferred that the proposed approach significantly outperformed all of the compared state-of-the-art algorithms in most of complex scenes and achieved 6\% gain in FM over the second one on the whole dataset. Moreover, in order to compare proposed approach with the DBMF, which is also based on deep learning and only publish their results in several special vides. The proposed approach has also ran in these video and the results are shown in Table 2. Again, the proposed approach has noticeably better performance than the DBMF and some other classical background approaches.

	As shown in the \reftab{tab1} and \reftab{tab2}, previous deep learning based methods like the DeepBS and the DBMF achieve well performance. From our own perspective, that good performance should attribute to the stronger modeling ability and learning adaptation of CNN and FCN. However, the proposed approach focused on the pixels variation in temporal sequence rather than low-level static features such as color, edges and textures, which gives us the ability to avoid the shortcomings of the background models. Consequently, the proposed approach still get considerably better results, which over 10.46\% in FM metrics compared with the DeepBS and over 6.38\% compared with the DBMF.
The evaluation of proposed approach in CAMO-UOW dataset is shown in the \reftab{tab3}. Unlike the CDnet dataset, the videos of CAMO-UOW dataset are specially proposed for the moving objects with camouflage, which is the main challenge of this dataset. As shown in the \reftab{tab3} proposed approach achieves better performance compared to its competitions, with an average F-measure of 0.97, compared to values between 0.77 and 0.94 for the other methods. Therefore, it is fair to say that proposed approach performs better compared with their peers.

In this dataset, target objects have the similar color and textures with the background, which brings a lot of difficulties and obstacles to traditional methods. However, our FCN is a powerful Neural Network model which is good at capturing the non-linearities of the manifold of pixel variations.

All these experiments of the proposed method were implemented in matlab and ran on the computer with Nvidia tasela K80 GPU and all images are keep their original resolution. For each video in CDnet 2014, 100 training frames are extracted to produce the image matrix. It should be noted that the 100 frames only accounts for less than 10\% of total Groundtruth in CDnet 2014. In contrast, 90\% of data were used as training samples in the DBMF, which suggest that the proposed approach achieves well performance with limited training frames. Considering that the videos in CAMO-UOW have fewer frames, we reduce the number of training frames to 49. During the experience, the training set and testing set are completely separated. More specifically, our FCN network is random initialized. We train the network with mini-batches of size 100, a learning rate $α = 1 ∗ 10^{−3}$ over 20 epochs. The last threshold $R$ is set to 0.6.

\section{Conclusion}
In this paper, we proposed the 
Moreover, we captured different superpixels under multiple scales and
integrating these superpixels to improve the accuracy of proposed approach.

\begin{thebibliography}{4}

\bibitem{2014_CSR_reviews} T. Bouwmans, “Traditional and recent approaches in
    background modeling for foreground detection: An overview,” Comput. Sci.
        Rev., vol. 1112, pp. 31 – 66, 2014.

\bibitem{1997_TPAMI_GAUSS} C. Wren, A. Azarbayejani, T. Darrell, and A.
    Pentland, “Pfinder: realtime tracking of the human body,” IEEE Trans.             %mog
        Pattern Anal. Mach. Intell., vol. 19, no. 7, pp. 780–785, Jul 1997.

\bibitem{1999_CVPR_MoG} C. Stauffer and W. Grimson, “Adaptive background
    mixture models for real-time tracking,” in Proc. IEEE Conf. Comput. Vis.    %mog
        Pattern Recognit., vol. 2, 1999, pp. –252 Vol. 2.

\bibitem{2004_ICIP_CodeBook} K. Kim, T. Chalidabhongse, D. Harwood, and L.
    Davis, “Background modeling and subtraction by codebook construction,” in   %code book
        Proc. Int. Conf. Image Process., vol. 5, Oct 2004, pp. 3061–3064 Vol.
        5.

\bibitem{2006_RTI_CodeBook} K. Kim, T. H. Chalidabhongse, D. Harwood, and L.
    Davis, “Real-time foreground-background segmentation using codebook model,”	%code book
        Real- Time Imaging, vol. 11, pp. 172–185, 2005.

\bibitem{2009_ICASSP_ViBe} O. Barnich and M. Van Droogenbroeck, “Vibe: A
    powerful random technique to estimate the background in video sequences,”in      %vibe
        Proc. IEEE Int. Conf. Acoust. Speech Signal Process., April 2009, pp.
        945–948.

\bibitem{2011_TIP_ViBep} O. Barnich and M. V. Droogenbroeck, “Vibe: A universal
    background subtraction algorithm for video sequences,” IEEE Trans. Image	        %vibe
        Process., vol. 20, no. 6, pp. 1709–1724, June 2011.

\bibitem{2006_TPAMI_TexBased} M. Heikkila and M. Pietikainen, “A texture-based
    method for modeling the background and detecting moving objects,” IEEE                %neighbor infor
        Trans. Pattern Anal. Mach. Intell., vol. 28, no. 4, pp. 657–662, 2006.

\bibitem{2012_PD_RECTGAUSS} D. Riahi, P. St-Onge, and G. Bilodeau, “
    RECTGAUSS-tex: Blockbased background subtraction,” in Proc. Dept. g´enie
        Inform. g´enie logiciel, E´cole Polytechn. Montr. Montr. QC, Canada,,
        2012, pp. 1–9.

\bibitem{2011_ICCV_MultiScale_Zaharescu} A. Zaharescu and M. Jamieson,“
    Multi-scale multi-feature codebookbased background subtraction,”in Proc.
    IEEE Int. Conf. Comput. Vis. Work., 2011, pp. 1753–1760.

\bibitem{2014_CVPR_CDnet_Wang} Y. Wang, P.-M. Jodoin, F. Porikli, J. Konrad, Y.
    Benezeth, and P. Ishwar, CDnet 2014: An Expanded Change Detection Benchmark
    Dataset, in Proc. IEEE Workshop on Change Detection (CDW-2014) at
    CVPR-2014, pp. 387-394. 2014

\bibitem{2014_ICIP_MultiScaleSpatio_Lu} X. Lu, “A multiscale spatio-temporal
    background model for motion detection,” in Proc. IEEE Int. Conf. Image
    Process., 2014, pp. 3268– 3271.

\bibitem{2013_ICAVSBS_SpatialMoG_Varadarajan} S. Varadarajan, P. Miller, and H.
    Zhou, “Spatial mixture of Gaussians for dynamic background modelling,” in
    Proc. IEEE Int. Conf. Adv. Video Signal Based Surveillance, 2013, pp. 63–
    68.

\bibitem{2012_CVPRW_ViBe_Van} M. Van Droogenbroeck and O. Paquot, “Background
    subtraction: Experiments and improvements for ViBe,”IEEE Conf. Comput. Vis.
    Pattern Recognit. Work., pp. 32–37, 2012.

\bibitem{2013_AVSS_RMoG_Varadarajan} Varadarajan, S.; Miller, P.; Huiyu Zhou,
    "Spatial mixture of Gaussians for dynamic background modelling," Advanced
    Video and Signal Based Surveillance (AVSS), 2013 10th IEEE International
    Conference on , pp.63,68, 27-30 Aug. 2013

\bibitem{2013_ICAVSBS_RMoG} S. Varadarajan, P. Miller, and H. Zhou, “Spatial
    mixture of Gaussians for dynamic background modelling,” in Proc. IEEE Int.
    Conf. Adv. Video Signal Based Surveillance, 2013, pp. 63–68.

\bibitem{2014_ICIP_MST} X. Lu, “A multiscale spatio-temporal background model
    for motion detection,” in Proc. IEEE Int. Conf. Image Process., 2014, pp.
    3268–3271.

\bibitem{2014_CCPR_RefPaper} Wu L, Zhang Z, Wang Y, et al. A Segmentation Based
    Change Detection Method for High Resolution Remote Sensing
    Image[M]//Pattern Recognition. Springer Berlin Heidelberg, 2014: 314-324.

\end{thebibliography}

\end{document}

### 2018-06-20 deeplearning_bg/deeplearning_bg/typeinst_old.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	new file:   build.bat 	new file:   build.sh 	new file:   config 	modified:   deep background feature transformation learning.doc 	new file:   deeplearning_bg.rar 	new file:   deeplearning_bg/deeplearning_bg/abstract.aux 	new file:   deeplearning_bg/deeplearning_bg/abstract.bbl 	new file:   deeplearning_bg/deeplearning_bg/abstract.blg 	new file:   deeplearning_bg/deeplearning_bg/abstract.log 	new file:   deeplearning_bg/

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{verbatim}%长篇注释宏包
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\newcommand{\reffig}[1]{Fig. \ref{#1}}
\newcommand{\refsec}[1]{Section \ref{#1}}
% \newcommand{\refeq}[1]{Eq. \ref{#1}}
\newcommand{\reftab}[1]{Table \ref{#1}}

\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Background Subtraction via Deep Variation Transformation}

% a short form should be given in case it is too long for the running head
 \titlerunning{Background Subtraction via Deep Variation Transformation}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%i
\author{Yongxin Ge, Xinyu Ren, Chenqiu Zhao}
%
\authorrunning{Lecture Notes in Computer Science: Chongqing University}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Laboratory of Intelligent Services and Software Engineering, \\
School of Software Engineering,\\
Chongqing University, Chongqing 401331, China\\
\url{xxx@cqu.edu.cn}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Chongqing University}
\maketitle

\begin{abstract}
%Background subtraction in complex scenes is a challenging problem
One of the main challenges of foreground detection comes from the diversity and complexity of real-world scenes. While most of previous works in this field were proposed by designing an artificial model, we tend to present a self-adaption solution, by combining the fully convolutional networks (FCNs), which is named as the Deep Pixels Variation Learning model (DPVL). Our main job is to find a new representation of pixels historical observations in a new feature space. In this paper, videos are divided into fixed length image stacks, which are later transformed into the pixel observation matrixes as the input of a FCN for learning the variation of pixels. We conduct our training and prediction processes on stack level. The architecture of the FCN is devised from the semantic segmentation problem. Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ variation. We compare our method with some state-of-the-art methods, and the results show that the proposed approach outperform its
\keywords{Background Subtraction, Motion Detection, Superpixels, Neighborhood Information, Multi-Scale}
\end{abstract}

\section{Introduction}
% 问题的意义
背景建模一直都是视频分析的基础，不仅可以帮助研究人员在视频中提取出感兴趣区域，其在现实生活中也有着广反的应用，

Background subtraction is a fundamental issue of computer vision,
which has a wide range of application \cite{2014_CSR_reviews} \cite{2014_CCPR_RefPaper}.
% 问题的挑战
在这个问题中，主要的挑战来自于运动物体的运动模式难以预测，以及野外的复杂动态背景，例如流动的水和摇晃的树木。
The main challenge in background subtraction comes from the complexity
of nature scenes, such as waving tree or rippling water.
% previous work
绝大多数现有的方法都是
Recently, large numbers of works used pixels' neighborhood information to
improve the robustness of background subtraction.
% 这些方法的缺点
Unfortunately, most of those algorithms were based on pixels or regions and
ignored the similarity between pixels themselves.
% 一个像素，有很多邻居，以前的方法把所有的都用上了
And those pixels or regions based algorithms utilize the information of all
pixels' neighborhoods.
% 像素的相似度是不同的，不是所有的像素，都是正面影响
However, since the similarity between a pixel and their neighborhoods is
different,
%
not all pixels' neighborhoods contribute positively to improve the robustness of algorithms.
% 我们的思路
In this work, the superpixel contains the pixels'
neighborhood information as well as the similarity among them is utilized to
detect moving objects.
% 具体的方法
And a novel background subtraction based on superpixels under multi-scale is
proposed to background subtraction in complex scenes.

% 从描述现象开始
Background subtraction is the classification of pixels according its variation.
% 开始描述图
Since the complexity of natural scenes, several pixels with different labels have the
similar variation.
% 左边的图混合在一起
For example, as the left part of \reffig{thinking} shows, the pixels labeled as
foreground or background are mixing together in the variation of RGB space.
% 
However, a pixel is not independent \cite{2009_ICASSP_ViBe} but related
with its neighborhoods, especially the similar one.
% 
Since the superpixels contain the information on pixels and their similar neighborhoods, the variation in
the superpixels is easier to be classified, such as the right part
of \reffig{thinking} shows.
% 
Unlike previous work, we analyze the variation in superpixels instead of pixels for
background subtraction.
% 超像素只能把物体分开，不能确定哪里是前景
Moreover, since the segmentation of superpixels does not refer to motion
information, not all the pixels belong to a particular superpixel are shared
the same label of foreground or background.
% 为了解决这个被引入的问题，用了一个多尺度的方法
To solve this brought issue, the labelled superpixels are obtained under
multiple scales to compose different foreground in each scale.
% 我们的前景是怎么由这个方法得到的
And the final foreground of our SPMS is captured by the summary of several foregrounds
consisted of superpixels under different scales.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figure/fig_idea}
    \caption{The variation in pixels and superpixels with foreground or background labels.}
    \label{thinking}
\end{figure}

% 我们方法的具体细节
Our SPMS method can be divided into three step.
% 跟以前的方法一样，获取背景图像
The first step of SPMS is learning a background via the statistical function such as
Gaussian function \cite{1997_TPAMI_GAUSS}.
% 超像素获取的方法
Meanwhile, the current frame is segmented into several superpixels by a
\emph{K-means} based superpixel segmentation algorithm \cite{2012_TPAMI_SLIC}.
% 相减获得每一个的变化
Then, we subtract the current frame and background to capture the variation of each pixel.
% 统计变化，得到superpixel的变化
And the means of pixels' variation in a particular superpixel is used as the
variation in it.
% 变化直接二值化
The variation is classified by a threshold to decide whether it
is foreground or background.
% 标记好的超像素为SPMS的foreground
And the foreground of SMPS is consisting of these labeled superpixels in a
particular scale.
% 使用了多尺度
Finally, the segmentation of foreground in SPMS is done under multiple scales.
% 多尺度里超像素尺寸不同
We modify the size and zone of superpixels in each scale to capture different foregrounds.
% 最终的目的
And the summary of these foregrounds under different scales is used as our final
foreground result.
% 论文的贡献
The contributions of this paper are summarized as follows:
\begin{enumerate}
    \item Our SPMS utilizes superpixels instead of pixels or regions for
        background subtraction. Since the superpixel reveals the neighborhood
        information and the similarity among pixels, proposed approach achieves
        encouraging robustness in complex scenes, such as adverse weather and
        dynamic scene.
    \item The final foreground of SPMS is captured by the summary of
        foregrounds captured in different scales. Benefited from the difference
        about superpixels' zone in multiple scales, the accuracy of our SPMS
        background model is improved by the summary process.
\end{enumerate}

\section{Related Work}
% 引子，简单介绍不利用领域信息的方法
In the early works about background subtraction, pixels are assumed independent
of each other.
The MoG \cite{1997_TPAMI_GAUSS} \cite{1999_CVPR_MoG} and the CodeBook
\cite{2004_ICIP_CodeBook} \cite{2006_RTI_CodeBook} algorithms are two
popular approaches to segment foreground.
% 以前方法的没有考虑的东西
However, since those works ignored the neighborhood information, both
the MoG \cite{1999_CVPR_MoG} and CodeBook \cite{2006_RTI_CodeBook} are
working hard in complex scenes, like waving tree and rippling water.

% 近期的工作开始利用领域信息
Recently, larger numbers of works improved the robustness of background
subtraction by neighborhood information (e.g. \cite{2010_CVPR_SILTP},
\cite{2014_IS_MulLevTex}, \cite{2009_ICASSP_ViBe}, \cite{2011_TIP_ViBep},
\cite{2012_CVPRW_ViBe_Van}, \cite{2006_TPAMI_TexBased},
\cite{2014_TIP_Spatio_Lin} and \cite{2011_ICCV_MultiScale_Zaharescu}).
% 引子
Among those works, several algorithms are based on features with
neighborhood information.
% 蕴含领域信息的特征 texture
Heikkila et al. \cite{2006_TPAMI_TexBased} modeling the background by LBP
\cite{2006_TPAMI_TexBased} texture descriptor, which is captured from pixels
and its neighborhoods.
% 论文的好处
Since the LBP is robust to illumination change and noise, the algorithm
in \cite{2006_TPAMI_TexBased} work well in the shade regions.
% 增强算法
Similarly, Liao et al. \cite{2010_CVPR_SILTP} improved the LBP into SILTP and
segmented the foreground by Kernel Density Estimation.
% multilevel
Hence, Lin et al. \cite{2014_IS_MulLevTex} detected moving objects in different levels
to improve the efficiency of their algorithm.
% multi-scale codebook
And Zaharescu et al. \cite{2011_ICCV_MultiScale_Zaharescu} extended the
CodeBook algorithm by multiple scales for the accuracy of
foreground.

% the spatio-temporal features
Besides the texture features, the spatio-temporal features (e.g.
\cite{2014_TIP_Spatio_Lin} and \cite{2014_ICIP_MultiScaleSpatio_Lu}) also
reveals the neighborhood information.
% the pursuing dynamic spatio-temporal
Lin et al. \cite{2014_TIP_Spatio_Lin} detect moving objects by pursuing dynamic
spatio-temporal model.
They employed the auto regressive moving average model
to pursue the subspace. And model joints the appearance consistency and temporal
coherence of the observations.
% multiscale spatioi
Lu et al. \cite{2014_ICIP_MultiScaleSpatio_Lu} collected a set of samples on
different spatial scales for each location in a dynamic scene. And the
foreground is segmented by a non-parametric model.
% ViBe and ViBe++
Barnich et al. proposed the ViBe \cite{2009_ICASSP_ViBe} and ViBe+
\cite{2011_TIP_ViBep} algorithm, which is an excellent method to utilize
neighborhood information.
% ViBe 具体的做法
The ViBe algorithm maintains a sample set,which contains
the pixels and their neighborhoods, for each pixels.
And the pixel is label as background if it is matched with
any entries of the sample set.
% histogram
In addition, the histogram is another technique of the
utilization about neighborhood information.
% Background modeling by combining joint intensity histogram with time-sequential data
Kita et al. \cite{2010_ICPR_KitaHis} segmented foreground by analysing the
intensity histogram during video sequence. And a similar method also based on
histogram is proposed in \cite{2009_ICIC_KuoHis}.
% 我们方法与它们的区别

% the region based algorithms
Furthermore, these are also several works detected moving objects by regions
instead of pixels.
% rect gauss
Riahi et al. \cite{2012_PD_RECTGAUSS} extended the MoG with rectangle region.
Since the variation in the regions' intensity is robust to environment
change, the algorithm in
\cite{2012_PD_RECTGAUSS} achieves well performance in complex scenes.
% regions-based spatio-temporal features
Varadarajan et al. \cite{2013_AVSS_RMoG_Varadarajan} proposed a
region-based MoG algorithm. In particular, the spatio-temporal features
is extracted from the regions and as the input of MoG to segment
foreground.
% XXX 解释和区域方法的不同
The main difference between our work and regions based algorithms is the consideration of similarity between pixels themselves.
% 
The pixels in a superpixel have stronger connection with each others compared with pixels in a region.
%
And the stronger connection prevents the accuracy of our superpixel-based approach.

% 超像素
One should note, the superpixels also utilized for background subtraction in
several algorithms (e.g. \cite{2014_CVPR_Superpixel_Zhu},
\cite{2008_TPAMI_PixelLayers_Patwardhan}, \cite{2015_TCSVT_Reshape_Wu}).
% pixels layers
In the \cite{2008_TPAMI_PixelLayers_Patwardhan}, Patwardhan et al.
\cite{2008_TPAMI_PixelLayers_Patwardhan} cluster pixels into several pixel
layers. And the foregrounds are segmented from different pixel layers.
% reshape the foreground
Moreover, Wu et al. \cite{2015_TCSVT_Reshape_Wu} detect moving objects by
the trajectory, and reshape the foreground by superpixels.
% superpixel
In addition, proposed approach is closely related with the work in
\cite{2014_CVPR_Superpixel_Zhu}, which is a saliency detection algorithm.
However, besides the difference in purpose, the similarity measure also
different between us.
The algorithm in \cite{2014_CVPR_Superpixel_Zhu} just
threshold the gray-scale of current frames. And in this work, the similarity of
superpixels is captured by the analysing of its variation during time sequence.

\section{Modeling Background by Superpixels}
\label{model_SPMS}
In this section, the details of SPMS model are explained and its flow chart is
shown in \reffig{flow_chart}
% 总结这段的作用，而且要以本文的方法总结，来突出我们方法的新异
In the \refsec{model_segmentation}, we introduce the segmentation of foreground
via analysing the variation of superpixels' intensity under multi-scale.
% 解释背景的作用，已经背景的更新
Simultaneously, the process of capturing background, which is used to compare
with current frame for extracting superpixels' variation, is explained in
\refsec{model_update}.

\subsection{Foreground Segmentation via Superpixels under Multi-Scale}
\label{model_segmentation}
% 前景是由带标签的超像素组成的
In our SPMS model, the foreground consists of superpixels with foreground or
background label.
% 超像素的标签是由背景和当前帧对比得到
The label of each superpixel is decided by its variation.
% variation 怎么得的
And the variation in a superpixel is actually the means of their pixels'
variation compared with the corresponding pixels in the background.
% Backgroudn
In particular, the process of capturing background will be explained later.
% 多尺度的怎么用的
Moreover, in order to improve the accuracy of proposed approach, we segment
several foregrounds under multiple scales, and the summary of all these
foreground information is used as the final result of proposed approach.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figure/fig1}
    % XXX 图例里描述一下。
    \caption{The pipeline of proposed approach.}
    \label{flow_chart}
\end{figure}
% 超像素获取的方法
In this work, the superpixel are obtained from current frame by the SLIC algorithm \cite{2012_TPAMI_SLIC}.
% 这个方法的特
Since the SLIC \cite{2012_TPAMI_SLIC} is based on \emph{K-Means}, it is
convenient to control the size of superpixels according to the numbers.
%
And the convenience is the main reason we choose SLIC algorithm
\cite{2012_TPAMI_SLIC}.
% 假设超像素的公式
Let's denote the superpixels segmented under multi-scale are:
\begin{equation}
\{\mathcal{SP}_1,
\mathcal{SP}_2, \dots \mathcal{SP}_s \} = \{ Sp_{i,j}|i \in [1,s], j \in [1,N_i] \},
\end{equation}
where $i$ is the index of scale and $N_i$ is the number of superpixels under scale $i$.

% 最后的前景是综合得到
As we mentioned before, the final foreground is captured by the summary of
foregrounds segmented under multiple scales.
% 每一个前期是怎么得到的
And the foreground in each scale consists of superpixels with foreground or
background segmented under this scale.
% 解释一个超像素
In the superpixel $Sp_{i,j}$, all their pixels are subtract from
pixels of background $I_b(x,y)$ in the corresponding position.
% 解释相减的细节
Moreover, in the subtracting process, we utilized a region searching method to
improve the robustness of the subtraction result.
% 
In the region searching method, for each a pixel, we find the most similar pixels of
background in a small region $R$ on respective position of it.
% 公式表达
And the definition of region searching method $G(x,y)$ is shown as follows:
\begin{equation}
    G(x,y) =  \mathop{\argmin}_{}{ \lVert I_t(m,n) - I_b(x,y) \rVert_{1}  } \quad  m,n \in x,y \pm R,
\end{equation}
where $x$ and $y$ is the location of pixels. And $I_t$ is the current frame, where $t$ is the
time index.

% 解释超像素的相似度
Then, the score of this superpixel labelled as background is captured from the
means of all the subtraction results on it, which is shown as follows:
\begin{equation}
    P(Sp_{i,j}) = \quad \frac{ \sum\limits_{ \mathclap{x,y \in Sp_{i,j}} }G(x,y)}{|Sp_{i,j}|} ,
\end{equation}
where $N_i$ is the number of pixels belong to superpixel $Sp_{i,j}$, and
$G(x,y)$ is the similarity function of position $(x,y)$. The $P(Sp_{i,j})$ is
compared with a threshold $T_{sp}$ to decide whether the superpixel $Sp_{i,j}$
is foreground or background. And foreground of our SPMS under a particular
scale $i$ consists of all the labelled superpixels. And the process is shown as
follows:
\begin{equation}
    Fg_{i}(x,y) = g(Sp_{i,j}(x,y),T_{sp}), \quad I_t(x,y) \in Sp_{i,j},
\end{equation}
where $g(x,y)$ is the piecewise function to decide whether the pixel with
location $(x,y)$ is foreground or background, and the definition is shown as
follows:
\begin{equation}
    \label{piecewise_fg}
    g(x,y) =
 \begin{cases}
  1,  \quad x < y       \\
  0,  \quad otherwise   \\
\end{cases}.
\end{equation}

The superpixel is the set of similar pixels and does not consider motion
information. Background subtraction based on superpixel achieves well
robustness but suffer from accuracy problem. We captured foregrounds
under different scales. The summary of all these foregrounds improve the
accuracy of proposed approach, which is defined as:
\begin{equation}
    Fg(x,y) = \frac{ \sum\limits_{i = 0}^{s}Fg_i(x,y)}{s}
\end{equation}
where $Fg(x,y)$ is the proximity image of SPMS and is utilized to compare
with threshold $T$ for our final foreground segmentation.

\subsection{Background Updating}
\label{model_update}
% 背景更新的目的是为了得到一个没有前景的图像
The purpose of background updating is to capture a background without
moving objects.
% 背景会更新去适应场景变化
The updating procedures are different to the pixels labeled as foreground and background.
%
If a pixel is labelled as background in the procedure of foreground segmentation.
%
The respective pixel in background is replaced by this pixel.
%
When a pixel is labeled as foreground, the process shown in
\reffig{fig_bkupdate} is done to capture the background intensity.
%
And the background intensity is used to update the pixel with the corresponding
location in the background.
% 背景是怎么得到的
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figure/fig5}
    \caption{The process of updating foreground is analysing the variation of
    pixels' intensity.}
    \label{fig_bkupdate}
\end{figure}

% 总结fig中的过程
The procedure shown in \reffig{fig_bkupdate} is a histogram of the pixel's
variation during time sequence.
Let's denote the observation of a pixel labeled as foreground in time sequence as $P = {p_1,p_2,\dots,p_t}$.
The variation of this pixel is analyzed by the histogram.
and the intensity with the max peak value is used as the
background intensity. Mathematically, the background intensity is defined as:
\begin{equation}
    p_{bk} = \mathop{\argmax}_{p}{\sum\limits_{i = 1}^{t} p_i \cap p} \quad p = \{p_1,p_2,\dots,p_t\},
\end{equation}
where the $p$ is pixel's intensity. Next, the $P_{bk}$ is used to update the
corresponding pixel in background.

\section{Experiment}
In this section, we have conducted the comprehensive experiments to
analyze our SPMS.
% 介绍对比方法
We compare proposed approach to four state-of-the-art algorithms with
or without pixels' neighborhood information.
% 方法运行的数据集
All the experiments are ran in several video sequences of
ChangeDetection.Net \cite{2014_CVPR_CDnet_Wang} (CDN) benchmark.

% 对比度量
In this work, The Recall (Re), Precision (Pr) and F-measure (Fm) metrics
are utilized to compare proposed approach with other algorithms.
% 介绍具体的度量
Re and Pr means the measures of completeness and accurateness
respectively. The Fm is a combination of Re and Pr. The definition of
these metrics is shown as follows:
\begin{equation}
    \begin{aligned}
        Re = \frac{TP}{TP + FN},
        Pr = \frac{TP}{TP + FN},
        Fm = \frac{2 \times Pr \times Re}{Pr + Re}
    \end{aligned},
\end{equation}
where the TP and FP is the True Positive and False Positive. In detail,
the positive represents foreground, and negative represents background.
True means the result of this detection is right, and Negative means the
result of this detection is wrong. So the TP means the result of
detection is foreground as well as the groundtruth.

% introduce the comparison algorithms
The comparison algorithms include MoG \cite{2004_ICPR_iMoG}, ViBe+
\cite{2011_TIP_ViBep}, RMoG \cite{2013_ICAVSBS_RMoG} and MST
\cite{2014_ICIP_MST}.
% 大致介绍下对比方法
In particular, the MoG algorithm is based on the pixels and without using
neighborhood information.
% ViBe ViBe+
The ViBe and ViBe+ are pixel-based algorithms and utilizing neighborhood information 
for foreground segmentation.
% RMoG
And RMoG is a region-based algorithm, MST is algorithm based on feature
contains neighborhood information.
% the reason why we choose these algorithms
In contrast, proposed algorithms is based on superpixels and improve the
robustness of foreground by neighborhood information.

% introduce the benchmark
The CDN \cite{2014_CVPR_CDnet_Wang} benchmark is almost the largest dataset for
Change Detection, which contains 11 categories video sequences.
% 选择的类别分
And in this work, the Baseline, Dynamic Background, Camera Jitter and
Bad Weather categories include with thousand frames are chosen for
evaluating our SPMS.
% 对比方法结果的来源
The detection result of comparison state-of-the-art algorithms is available in
CDN \cite{2014_CVPR_CDnet_Wang} benchmark. And for SPMS, we used two different
parameters, which is shown in \reftab{tab_para}, in our $\text{SPMS}_1$ and
$\text{SPMS}_2$.
% 大致解释一下参数
In \reftab{tab_para}, $T$ is the threshold value for foreground segmentation,
and $(N_{b},N_{a},N_{s})$ are utilized to control the number of superpixels in
multiple scales. $N_{a}$ is the number of scales. $N_{b}$ is the number of
superpixels in first scale, and $N_{s}$ is the increment of superpixels' number
in different scales.

\begin{table*}[!t]				% TABLE
\caption{The performance comparison of SoAF and four state-of-the-art
algorithms on the video sequences belong to Baseline, Dynamic
Background, Camera Jitter and Bad Weather scenes under the metrics of
Re, Pr and Fm (from left to right in each cell).}
\label{tab_res}					% LABEL: tab1
\centering
% \begin{tabular}{ccccccc}
\begin{tabular*}{1.02\textwidth}{@{\extracolsep{\fill}}ccccccc}
\hline
\multirow{2}*{Videos}  &    \multicolumn{4}{c}{Baseline} & & \multicolumn{1}{c}{Camera Jitter}  \\
\cline{2-5} \cline{7-7}
& highway & office & pedestrians & PETS2006 & & badminton \\
\hline
    MoG \cite{2004_ICPR_iMoG}   & 0.92 0.93 0.92 & 0.49 0.75 0.59 & \textbf{0.99} 0.92 0.95 &\textbf{0.88} 0.79 \textbf{0.83} & & 0.76 0.64 0.69 \\
RMoG \cite{2013_ICAVSBS_RMoG}   & 0.79 0.95 0.87 & 0.43 0.92 0.59 & 0.91 0.96 0.94 & 0.70 0.81 0.75 & &0.72 0.87 0.79 \\
MST \cite{2014_ICIP_MST}        & 0.83 0.92 0.87 & 0.70 0.94 0.80 & 0.95 0.96 0.95 & 0.78 0.73 0.75 & &0.81 0.45 0.58 \\
    ViBe+ \cite{2011_TIP_ViBep} & \textbf{0.93} 0.93 \textbf{0.93} & 0.70 0.92 0.80 & 0.95 0.96 \textbf{0.96} & 0.73 \textbf{0.89} 0.80 & &0.85 \textbf{0.93} \textbf{0.89} \\
\hline
$\text{SPMS}_1$                 & 0.70 \textbf{1.00} 0.82 & 0.75 \textbf{0.92} 0.83 & 0.91 \textbf{0.98} 0.94 & 0.59 0.79 0.67 & &0.88 0.74 0.80 \\
$\text{SPMS}_2$                 & 0.76 0.97 0.85 & \textbf{0.88} 0.87 \textbf{0.87} & 0.97 0.89 0.93 & 0.78 0.72 0.75 & &\textbf{0.97} 0.39 0.56 \\
\hline
\end{tabular*} 
\begin{tabular*}{1.02\textwidth}{@{\extracolsep{\fill}}ccccccc}
\hline
\multirow{2}*{Videos}  &    \multicolumn{3}{c}{Camera Jitter} & & \multicolumn{2}{c}{Dynamic Background}  \\
\cline{2-4} \cline{6-7}
& boulevard & sidewalk & traffic & & boats & canoe \\
\hline
MoG \cite{2004_ICPR_iMoG}       & 0.83 0.40 0.54 & 0.58 0.43 0.49 					& 0.76 0.59 0.66 			& & 0.76 0.70 0.73 & 0.87 0.90 0.88 \\
RMoG \cite{2013_ICAVSBS_RMoG}   & 0.60 0.45 0.51 & 0.62 \textbf{0.94} \textbf{0.75} & 0.72 \textbf{0.77} 0.75 	& & 0.82 0.85 0.83 & 0.90 \textbf{0.97} 0.94 \\
MST \cite{2014_ICIP_MST}        & 0.77 0.53 0.63 & 0.45 0.27 0.34 					& 0.83 0.34 0.48 			& & 0.51 0.45 0.48 & 0.91 0.86 0.89 \\
ViBe+ \cite{2011_TIP_ViBep}     & 0.76 \textbf{0.80} \textbf{0.78} & 0.43 0.77 0.55 & 0.87 0.73 \textbf{0.79} & & 0.43 0.69 0.53 & 0.92 \textbf{0.97} 0.94 \\
\hline
$\text{SPMS}_1$                 & 0.92 0.38 0.54 					& 0.45 0.48 0.46 & 0.95 0.45 0.62 			& & 0.74 \textbf{0.96} 0.83 & 0.94 0.96 \textbf{0.95} \\
$\text{SPMS}_2$                 & \textbf{0.97} 0.33 0.49 		& \textbf{0.69} 0.22 0.33 & \textbf{0.99} 0.30 0.46 & & \textbf{0.93} 0.83 \textbf{0.88} & \textbf{0.97} 0.72 0.83 \\
\hline
\end{tabular*} 
\begin{tabular*}{1.02\textwidth}{@{\extracolsep{\fill}}ccccccc}
\hline
\multirow{2}*{Videos}  &    \multicolumn{4}{c}{Dynamic Background} & & \multicolumn{1}{c}{Camera Jitter}  \\
\cline{2-5} \cline{7-7}
& fall & fountain01 & fountain02 & overpass & & blizzard	\\ 
\hline
MoG \cite{2004_ICPR_iMoG}       & 0.88 0.29 0.44 & \textbf{0.80} 0.04 0.08 & 0.87 0.75 0.80 & 0.83 0.92 0.87 & & \textbf{0.81} 0.68 0.74 \\
RMoG \cite{2013_ICAVSBS_RMoG}   & 0.72 0.64 0.67 & 0.55 0.12 0.20 & \textbf{0.91} 0.83 0.87 & 0.84 0.97 0.90 & & 0.43 0.90 0.58 \\
MST \cite{2014_ICIP_MST}        & 0.85 0.27 0.41 & 0.49 0.08 0.14 & 0.85 0.79 0.82 & 0.82 0.85 0.84 & & 0.56 \textbf{0.99} 0.71 \\
ViBe+ \cite{2011_TIP_ViBep}     & 0.89 \textbf{0.71} \textbf{0.79} & 0.62 \textbf{0.19} \textbf{0.30} & 0.87 0.88 0.87 & 0.84 0.93 0.88 & & - \\
\hline
$\text{SPMS}_1$                 & 0.91 0.39 0.55 & 0.23 0.06 0.09 & 0.64 \textbf{0.98} 0.78 & 0.85 \textbf{0.99} 0.92 & & 0.65 0.97 0.78 \\
$\text{SPMS}_2$                 & \textbf{0.97} 0.15 0.26 & 0.44 0.02 0.03 & 0.86 0.91 \textbf{0.89} & \textbf{0.94} 0.96 \textbf{0.95} & & 0.71 0.93 \textbf{0.80} \\
\hline
\end{tabular*} 
\begin{tabular*}{0.718\textwidth}{@{\extracolsep{\fill}}cccc} \hline
\multirow{2}*{Videos}  & \multicolumn{3}{c}{Bad Weather}  \\
\cline{2-4}
& skating & snowFall & wetSnow \\
\hline
MoG \cite{2004_ICPR_iMoG}       & 0.80 0.97 0.88 & 0.72 0.74 0.73 & 0.54 0.69 0.61 \\
RMoG \cite{2013_ICAVSBS_RMoG}   & 0.67 0.98 0.79 & 0.66 0.89 0.76 & 0.47 \textbf{0.82} 0.60 \\
MST \cite{2014_ICIP_MST}        & 0.81 0.46 0.59 & 0.58 0.92 0.71 & 0.43 0.70 0.53 \\
\hline
$\text{SPMS}_1$                 & 0.89 \textbf{0.99} 0.94 & 0.80 \textbf{0.96} 0.87 & 0.56 0.81 0.67 \\
$\text{SPMS}_2$                 & \textbf{0.95} 0.95 \textbf{0.95} & \textbf{0.90} 0.93 \textbf{0.91} & \textbf{0.74} 0.63 \textbf{0.68} \\
\hline
\end{tabular*}
\end{table*}
\begin{figure*}[!t]	% FIGURE: figure/fig1 
\label{fig_foreground}
\centering
\includegraphics[width=\textwidth]{figure/visually.pdf}
\DeclareGraphicsExtensions.
\vspace{-10pt}
\caption{The qualitative evaluation of SPMS model, all the qualitative
result is followed in the CDN \cite{2014_CVPR_CDnet_Wang} Benchmark.}
\label{fig3}		% LABEL: fig1
\end{figure*}

% tab_res 展示了数字化的结果
\reftab{tab_res} reports the performances of SPMS and other comparison
algorithms on the video sequence belonging to Baseline, Dynamic
Background and Bad Weather scenes under the metrics of Re. Pr and Fm.
% 展示可视化的结果
Moreover, due to the length of paper, \reffig{fig_foreground} only shows the
foreground of SPMS and other algorithms in Dynamic Background and Bad Weather
scenes.
In addition, since the result of ViBe+ \cite{2011_TIP_ViBep} in Bad Weather scenes is
not published, there is a empty on the
foreground of ViBe+ in \reffig{fig_foreground}.

% 对整个类别的结果做一个总结
In the Baseline scenes, there are four video sequences and SPMS achieves
significant improvement in office video sequence under Fm and Pr metric.
% 分析效果好的原因
The foreground of our SPMS consists of superpixels which contributed
the completeness of proposed approach.
% 同样的原因，re也高
With the same reason, the Re score of proposed approach also better than other
algorithms in pedestrians video sequence.
% 分析效果好的原因
Moreover, since the neighborhood information reserved in superpixels contributed
the robustness of our SPMS model, proposed approach also achieves well
result under Pr metric.
% 效果不好
However, the SPMS does not work well in the highway and PETS2006 video
sequences. 
The reason of this situation is the shade of cars and
pedestrians. And the similarity measures in SPMS can not handle the
moving objects' shadow.

% dynamic background scenes
In the Dynamic Background category, proposed approach work well in the boats
canoe, fountain02 and overpass video sequences.
% 分析这个类别的难点
In this kind of category, the main challenges are come from the dynamic
background, such as waving tree and rippling water.
% XXX
Although the intensity of pixels in the background is dynamic changing, the variation in the superpixels more
invariant.
% 我们方法如何解决的
In addition, the SPMS algorithm utilizes the range search method to against the
variation of pixels' position.
% 
And the robustness of superpixels also improves the efficiency of our
SPMS.
% 两者共同作用
Both these methods contributed the ability of SPMS to adapt the environment change and handle the noise.
% 
However, the SPMS does not work well in fall and fountain01 video
sequences, which may result from the parameter we used in SPMS.

% bad weather
In the Bad Weather scene, our SPMS method achieves good performance in
all four video sequences included blizzard, skating, snowFall and
wetSnow.
% XXX
The main challenges of Bad Weather scene result from the raindrop and snowflake which
can be recognized as kinds of noise.
% superpixel的鲁棒性
In our SPMS, the robustness of superpixels' variation
improves the efficiency of proposed approach.
% 
And the accuracy of proposed approach is prevented by the integration of
multiple scales.
%
And SPMS work well in the Bad Weather scene.

Unfortunately, the SPMS does not perform well in the Camera Jitter
scene. Besides the effect from the arguments we utilized. The similarity
measure we utilized is another reason that our SPMS does not work well
in Camera Jitter scene.

\begin{table}[!t]			% TABLE
\caption{The Parameter value of SPMS model.}
\label{tab_para}				% LABEL: tab7
\centering
\begin{tabular*}{0.6\textwidth}{@{\extracolsep{\fill}}ccccc}
\hline
    Method      & $R$ & $(N_{b},N_{a},N_{s})$  & $T_{sp}$   & $T$ \\
\hline
    $\text{SPMS}_1$ & 2   & $(20,16,20)$    &   0.3      & 0.45 \\
    $\text{SPMS}_1$ & 2   & $(20,16,20)$     &      0.3   & 0.25 \\
\hline
\end{tabular*}
\end{table}

\section{Conclusion}
In this paper, we proposed the SPMS background model to detect moving in
complex scenes via the integration of superpixels with foreground or background
label under multi-scale.
% 方法基于什么原理
Our SPMS analysing the variation of the superpixel to label if it is foreground or
background. And the superpixel revered neighborhood information contributed
the robustness of proposed approach.
% multi-scale
Moreover, we captured different superpixels under multiple scales and
integrating these superpixels to improve the accuracy of proposed approach.
% 实验结果
Both the utilization of neighborhood information and multi-scale contributed
the performance of our SPMS.
And proposed approach achieves encouraging performance in complex
scenes included Dynamic Background and Bad Weather.
%  实验结果
The comprehensive experiment demonstrate that the proposed approach achieves
encouraging performance in comparison with some state-of-the-art approaches.

\begin{thebibliography}{4}

\bibitem{2012_TPAMI_SLIC} Achanta, R., Shaji, A., Smith, K., Lucchi, A., Fua,
    P., Susstrunk, S.: Slic su- perpixels compared to state-of-the-art
        superpixel methods. ” IEEE Trans Pattern Anal. Mach. Intell., 34(11) (Nov 2012) 2274-2282

\bibitem{2014_CSR_reviews} T. Bouwmans, “Traditional and recent approaches in
    background modeling for foreground detection: An overview,” Comput. Sci.
        Rev., vol. 1112, pp. 31 – 66, 2014.

\bibitem{1997_TPAMI_GAUSS} C. Wren, A. Azarbayejani, T. Darrell, and A.
    Pentland, “Pfinder: realtime tracking of the human body,” IEEE Trans.
        Pattern Anal. Mach. Intell., vol. 19, no. 7, pp. 780–785, Jul 1997.

\bibitem{1999_CVPR_MoG} C. Stauffer and W. Grimson, “Adaptive background
    mixture models for real-time tracking,” in Proc. IEEE Conf. Comput. Vis.
        Pattern Recognit., vol. 2, 1999, pp. –252 Vol. 2.

\bibitem{2004_ICIP_CodeBook} K. Kim, T. Chalidabhongse, D. Harwood, and L.
    Davis, “Background modeling and subtraction by codebook construction,” in
        Proc. Int. Conf. Image Process., vol. 5, Oct 2004, pp. 3061–3064 Vol.
        5.

\bibitem{2006_RTI_CodeBook} K. Kim, T. H. Chalidabhongse, D. Harwood, and L.
    Davis, “Real-time foreground-background segmentation using codebook model,”
        Real- Time Imaging, vol. 11, pp. 172–185, 2005.

\bibitem{2009_ICASSP_ViBe} O. Barnich and M. Van Droogenbroeck, “Vibe: A
    powerful random technique to estimate the background in video sequences,”in
        Proc. IEEE Int. Conf. Acoust. Speech Signal Process., April 2009, pp.
        945–948.

\bibitem{2011_TIP_ViBep} O. Barnich and M. V. Droogenbroeck, “Vibe: A universal
    background subtraction algorithm for video sequences,” IEEE Trans. Image
        Process., vol. 20, no. 6, pp. 1709–1724, June 2011.

\bibitem{2006_TPAMI_TexBased} M. Heikkila and M. Pietikainen, “A texture-based
    method for modeling the background and detecting moving objects,” IEEE
        Trans. Pattern Anal. Mach. Intell., vol. 28, no. 4, pp. 657–662, 2006.

\bibitem{2010_ICPR_KitaHis} Y. Kita, “Background modeling by combining joint
    intensity histogram with time-sequential data,” in Proc. Int. Conf. Pattern
        Recognit., Aug 2010, pp. 991–994.

\bibitem{2009_ICIC_KuoHis} C. M. Kuo, W. H. Chang, S. B. Wang, and C. S. Liu, “
    An efficient histogram-based method for background modeling,” in Proc. IEEE
        Int. Conf. Innov. Comput. Inf. Control., 2009, pp. 480–483.

\bibitem{2010_CVPR_SILTP} Liao S, Zhao G, Kellokumpu V, et al. “ Modeling pixel
    process with scale invariant local patterns for background subtraction in
        complex scenes” Computer Vision and Pattern Recognition (CVPR), 2010
        IEEE Conf. on. 2010: 1301-1306.

    \bibitem{2014_IS_MulLevTex} C. H. Yeh, C. Y. Lin, K. Muchtar, and L. W.
        Kang, “Real-time background modeling based on a multi-level texture
        description,”Inf. Sci. (Ny)., pp. 106–127, 2014.

\bibitem{2012_PD_RECTGAUSS} D. Riahi, P. St-Onge, and G. Bilodeau, “
    RECTGAUSS-tex: Blockbased background subtraction,” in Proc. Dept. g´enie
        Inform. g´enie logiciel, E´cole Polytechn. Montr. Montr. QC, Canada,,
        2012, pp. 1–9.

\bibitem{2014_TIP_Spatio_Lin} L. Lin, Y. Xu, X. Liang, and J. Lai, “Complex
    background subtraction by pursuing dynamic spatio-temporal models,” IEEE
    Trans. Image Process., vol. 23, no. 7, pp. 3191–3202, 2014.

\bibitem{2014_TIP_Neigh_Chiranjeevi} P. Chiranjeevi and S. Sengupta, “
    neighborhoodhood supported model level fuzzy aggregation for moving object
    segmentation,” IEEE Trans. Image Process., no. 2, pp. 645–657, 2014.

\bibitem{2011_ICCV_MultiScale_Zaharescu} A. Zaharescu and M. Jamieson,“
    Multi-scale multi-feature codebookbased background subtraction,”in Proc.
    IEEE Int. Conf. Comput. Vis. Work., 2011, pp. 1753–1760.

\bibitem{2007_CVPR_MultiLayer_Yao} J. Y. J. Yao and J.-M. Odobez, “Multi-Layer
    Background Subtraction Based on Color and Texture,” in Proc. IEEE Conf.
    Comput. Vis. Pattern Recognit., 2007, pp. 1–8.

\bibitem{2014_CVPR_CDnet_Wang} Y. Wang, P.-M. Jodoin, F. Porikli, J. Konrad, Y.
    Benezeth, and P. Ishwar, CDnet 2014: An Expanded Change Detection Benchmark
    Dataset, in Proc. IEEE Workshop on Change Detection (CDW-2014) at
    CVPR-2014, pp. 387-394. 2014

\bibitem{2014_ICIP_MultiScaleSpatio_Lu} X. Lu, “A multiscale spatio-temporal
    background model for motion detection,” in Proc. IEEE Int. Conf. Image
    Process., 2014, pp. 3268– 3271.

\bibitem{2013_ICAVSBS_SpatialMoG_Varadarajan} S. Varadarajan, P. Miller, and H.
    Zhou, “Spatial mixture of Gaussians for dynamic background modelling,” in
    Proc. IEEE Int. Conf. Adv. Video Signal Based Surveillance, 2013, pp. 63–
    68.

\bibitem{2012_CVPRW_ViBe_Van} M. Van Droogenbroeck and O. Paquot, “Background
    subtraction: Experiments and improvements for ViBe,”IEEE Conf. Comput. Vis.
    Pattern Recognit. Work., pp. 32–37, 2012.

\bibitem{2013_AVSS_RMoG_Varadarajan} Varadarajan, S.; Miller, P.; Huiyu Zhou,
    "Spatial mixture of Gaussians for dynamic background modelling," Advanced
    Video and Signal Based Surveillance (AVSS), 2013 10th IEEE International
    Conference on , pp.63,68, 27-30 Aug. 2013

\bibitem{2014_CVPR_Superpixel_Zhu} Zhu, W., Liang, S.,Wei, Y., Sun, J.:
    Saliency optimization from robust background detection. In: IEEE Conference
    on Computer Vision and Pattern Recognition (CVPR). (June 2014) 2814-2821

\bibitem{2008_TPAMI_PixelLayers_Patwardhan} Patwardhan, K., Sapiro, G.,
    Morellas, V.: Robust foreground detection in video using pixel layers. IEEE
    Transactions on Pattern Analysis and Machine Intelligence 30(4) (April
    2008) 746-751

\bibitem{2015_TCSVT_Reshape_Wu} Wu, Y., He, X., Nguyen, T.: Moving objects
    detection with freely moving camera via background motion subtraction. IEEE
    Transactions on Circuits and Systems for Video Technology PP(99) (2015) 1-1

\bibitem{2004_ICPR_iMoG} Z. Zivkovic, “Improved adaptive Gaussian mixture model
    for background subtraction,” in Proc. Int. Conf. Pattern Recognition, vol.
    2, 2004.

\bibitem{2013_ICAVSBS_RMoG} S. Varadarajan, P. Miller, and H. Zhou, “Spatial
    mixture of Gaussians for dynamic background modelling,” in Proc. IEEE Int.
    Conf. Adv. Video Signal Based Surveillance, 2013, pp. 63–68.

\bibitem{2014_ICIP_MST} X. Lu, “A multiscale spatio-temporal background model
    for motion detection,” in Proc. IEEE Int. Conf. Image Process., 2014, pp.
    3268–3271.

\bibitem{2014_CCPR_RefPaper} Wu L, Zhang Z, Wang Y, et al. A Segmentation Based
    Change Detection Method for High Resolution Remote Sensing
    Image[M]//Pattern Recognition. Springer Berlin Heidelberg, 2014: 314-324.

\end{thebibliography}

\end{document}

### 2018-06-20 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	new file:   build.bat 	new file:   build.sh 	new file:   config 	modified:   deep background feature transformation learning.doc 	new file:   deeplearning_bg.rar 	new file:   deeplearning_bg/deeplearning_bg/abstract.aux 	new file:   deeplearning_bg/deeplearning_bg/abstract.bbl 	new file:   deeplearning_bg/deeplearning_bg/abstract.blg 	new file:   deeplearning_bg/deeplearning_bg/abstract.log 	new file:   deeplearning_bg/

--- 2018-02-02 draft.tex
@@
 \begin{document}
-\title{Background Subtraction based on Deep Feature Transformation Learning Background Subtraction}
+\title{Background Subtraction via Deep Variation Transformation}
 
-\author{Xinyu Ren,
-        Chenqiu Zhao,
-		Yongxin Ge }
+\author{Yongxin Ge, 
+        Xinyu Ren, 
+        Chenqiu Zhao}
+
+% XXX there is no such command of authorruning!!!!!!
+% XXX 根本就没有authorruning 命令！！！
+% \authorrunning{Lecture Notes in Computer Science: Chongqing University}
 
@@
 \begin{abstract}
-% 背景建模是一个复杂的问题
-Background subtraction is a fundamental problem of computer vision.
-% 为什么复杂
-The main challenges of background subtraction comes from the diversity and the complexity of natural scenes.
-% 以前的工作是怎么做的
-Plenty of previous works are proposed to handle this problem by artificial model.
-% 我们是怎么做的
-%Previous works in this field were proposed by designing an artificial model, 
-In this paper,
-we propose a self-adaption solution with the utilization of convolutional neural networks, 
-and a novel background subtraction model named Deep Feature Transformation Learning is proposed.
-% 动机是什么
-With the motivation of finding a new representation of pixels’ historical observations in a new feature space.
-% 怎么做的 XXX 这两句话介绍方法，但我实在是看不懂，你再改改
-The videos are divided into fixed length image blocks, which are later transformed into the pixel’s observation patches as the input of a FCN for learning the variation of pixels.
-We conduct our training and prediction processes on block level.
+One of the main challenges of foreground detection comes from the diversity and complexity of real-world scenes. 
+While most of previous works in this field were proposed by designing an artificial model, we tend to present a self-adaption solution, by combining the fully convolutional networks (FCNs), which is named as the Deep Pixels Variation Learning model (DPVL).
+Our main job is to find a new representation of pixels historical observations in a new feature space. 
+In this paper, videos are divided into fixed length image stacks, which are later transformed into the pixel observation matrixes as the input of a FCN for learning the variation of pixels. 
+We conduct our training and prediction processes on stack level. 
 The architecture of the FCN is devised from the semantic segmentation problem. 
-% 效果好
-Comparisons with several state-of-the-art algorithms in well-known benchmark show the superiority of proposed approach.
+Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ variation. 
+We compare our method with some state-of-the-art methods, and the results show that the proposed approach outperform its
 \end{abstract}
@@
 \section{Introduction}
-% introduction 的第一段介绍这个问题为什么有做的意义
-% 这个问题的意义
-Background subtraction or foreground object detection is a fundamental problem of computer vision, 
-which has been developed over the last few decades.
-% 难点在哪
-The main challenges of this problem comes from the diversely natural scenes,
-such as the illumination variation \cite{2017_REVIEW_7914756}, wrapping tree \cite{2014_CVIU_SOBRAL20144} and running water \cite{Bouwmans2014}.
-% 现状是什么
-Previous work already achieve well performances in the scenes with low complexity.
-% 现有的方法是怎么做的
-In particular,
-a large numbers of studies are focus designing artificial model according to the characteristic of a particular scenes.
-%　效果如何
-Example, the multiple background model are proposed for dynamic background,
-and the texture are used to handle the shadow of objects.
-%　为什么这个问题还有做下去的意义
-However,
-in view of
-the continuous growth in videos obtained from diversely natural scenes,
-more challenging scenes are proposed for background subtraction.
-%　总结，这个问题很难，还能做
-It remains a challenging problem to proposed a general solution for background subtraction in all exist and potential scenes.
-%
-% 
-% 
-% robust background 
-% 
-% via moving cameras
-% in recent years, the matter of background subtraction for
-% moving cameras has attracted sustained levels of interest from
-% researchers
-% 
-% It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.
-% vehicles and humans, thus saving us huge amount of computing resources.
-% Typically, Background subtraction is a binary classification task that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.
+Background subtraction or foreground object detection, as a fundamental problem in computer vision, has been much discussed with the increasing number of outdoor cameras over the last few decades. 
+It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.g. 
+vehicles and humans, thus saving us huge amount of computing resources. 
+Typically, Background subtraction can be viewed as a binary classification that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.
 
-% With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes.
-% However, background Subtraction is still unsolved because of the diversity in background scenes and the changes originated from the camera itself.
-% Scene variations can be in many forms such as, camera jitter, dynamic background, bad weather, illumination changes, intermittent object motion.
-% for instance, the earlier Frame Difference Methods, trying to get a fixed image as background to classify each pixels.
-% The fundamental problem lies in that linear classifier might not be powerful enough for the job, due to the complexity and the diversity of natural scenes.
-% 第二段介绍你的解决思路
+With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
+However, background Subtraction is still unsolved because of the diversity in background scenes and the changes originated from the camera itself. 
+Scene variations can be in many forms such as, camera jitter, dynamic background, bad weather, illumination changes, intermittent object motion. 
+This is principally because the major methods, in most cases, try to find a universal solution by generating some universal background models for later linear classification; for instance, the earlier Frame Difference Methods, trying to get a fixed image as background to classify each pixels.
+The fundamental problem lies in that linear classifier might not be powerful enough for the job, due to the complexity and the diversity of natural scenes.
 
-% 说明问题的本质是什么
+In order to present a better and universal solution, we proposed the Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes. 
+In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.
 
-% 以这个本质为基础来评价现存方法
+For \emph{Sq}, it is a sequence of pixel variation, which is hard to classify which entry is foreground or background. 
+But in \emph{Sq'}, it is more easy to classified, since the output of the network is the label of each entry in sequence.
 
-% 现存方法失败的原因是什么
-
-% 我们的方法针对这个原因怎么样了
-
-% XXX 为什么效果会好，同时也是我们方法的创新点, 最重要的还要结合图来说，
-
-% 总结方法的思路
-
-% 第三段介绍具体是怎么做的
-% 首先一句到两句，最多３句话总结你的方法的过程
-
-% 补充方法的细节
-
-% 这些细节带来的好处
-
-% 最后整个ｌｉｓｔ把方法的contribution 列出来
-The contribution of proposed approach are summarized as follows:
-\begin{itemize}
-    \item We proposed the Deep Feature Transformation Learning model for background subtraction in complexly natural scenes.
-        % 以前怎么做的
-        Unlike previous XXX
-        % 我们这么做有什么好处
-
-        % 为什么要reshape 
-    \item The observations in a particular pixel are reshaped into block 
-        % 这么做额目的是什么，好处什么
-\end{itemize}
-
-In order to present a better and universal solution, we proposed the Deep Pixels’ Variation Learning (DPVL) model for Background Subtraction in diversely natural scenes.
-In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.
-%XXX introduction 里最好不要出现公式
-\begin{equation}
-    sq_1 = \{p_1,p_2,\cdots, p_n\} -> sq_2 = \{f_1, f_2, \cdots, f_n\}
-\end{equation}
-For $sq_1$, it is a sequence of pixels' intensity, which is hard to classify which entry is foreground or background.
-%
-But in $sq_2$, it is more easy to classified, since the output of
-
-In this paper, pixel’s observation patches are proposed to describe the historical observation of pixels.
-And a random initialized FCN network is trained to learn the historical observation of pixels and generate a new representation in a new feature space.
-We take advantage of the strong learning ability of FCN to learn a new representation of the Pixel’s observation patches in a new space where the pixels can be easily classified to background and foreground.
+In this paper, pixel observation matrixes are proposed to describe the historical variation of pixels. 
+And a random initialized FCN network is trained to learn the pixel variation and generate a new representation in a new feature space. 
+We take advantage of the strong learning ability of FCN to learn a new representation of the pixel observation matrixes in a new space where the pixels can be easily classified to background and foreground.
 
 \section{Related Work}
-%  XXX 我觉的针对方法使用的特征对方法分类比较容易。例如颜色特征，纹理特征，时空间特征,最后引出你的，特征转换
+% XXX 引用文章的方式，Bouwmans2014 在ref.bib文件里,不懂去问曲师兄！！！！
+\cite{Bouwmans2014}
 Over the last few decades, Background subtraction has been well studied. 
@@
 These methods can be broadly categorized into pixels-based, region-based, frame-based and Deep Learning.
-
-\subsection{A. pixels-based methods}
-\label{sec_spa}
-% 把你想引的论文都贴上，太多了，而且你的Zhi Zeng et al. 是ｔｍ的谁啊？？
+\subsection{pixels-based methods}
 The most widely used algorithms in Background subtraction are pixels-based methods. 
-And one of the famous method is Gaussian Mixture Model (GMM) \cite{Zivkovic2004}, in which a GMM is used to model the history over time of pixel’s intensity values.
+And one of the famous method is Gaussian Mixture Model (GMM), in which a GMM is used to model the history over time of pixel’s intensity values. 
 It is assumed that pixels are independent from their neighbors. 
@@
 
-In XXX , Mingliang Chen et al.\ \cite{2017_TPAMI_GANGWANG} propose a background subtraction algorithm using hierarchical super-pixels segmentation, spanning trees and optical flow.
-Their Background model combine the GMM with constrains of temporal and spatial from optical flow and super-pixels \cite{6205760_2012_TPAMI}.
+In XXX , Mingliang Chen et al. 
+propose a background subtraction algorithm using hierarchical superpixels segmentation, spanning trees and optical flow. 
+Their Background model combine the GMM with constrains of temporal and spatial from optical flow and superpixels.
 
-Kim et al.\ \cite{Kim2004} used a codebook to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model.
+Kim et al used a codebook to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model. 
 This allows them efficient in memory and speed compared with other background modeling techniques. 
 The final foreground is detected by a distance measurement in a cylindrical color model.
-
 In XXX, Zhi Zeng et al. 
@@
 Their experiments show that, the proposed method outperforms well, despite using only color information.
-
 Elgammal et al. 
@@
 The PDF for each pixel is estimated with Kernel Density Estimation (KDE).
-
 \subsection{region-based approach}
-\label{sec_geo}
-region-based approach assumpt that the neighbouring pixels have a similar variation as the pixel itself.
+region-based approach assumpt that the neighboring pixels have a similar variation as the pixel itself.
 
 In xxx, Sriram Varadarajan et al. 
-propose a region-based MoG to takes in which the updated mixtures represent the scene distribution in a neighbourhood region.
-
-In (PCA), classification is done by comparing a block in current frame to its reconstruction from PCA coefficients and declaring it as background if the reconstruction is close.
-
-A recently region based method is presented in XXX which used the statistical circular shift moments (SCSM) in image regions for change detection.
-
+propose a region-based MoG to takes in which the updated mixtures represent the scene distribution in a neighborhood region.
+In (PCA), classification is done by comparing a stack in current frame to its reconstruction from PCA coefficients and declaring it as background if the reconstruction is close.
+recently region based method is presented in XXX which used the statistical circular shift moments (SCSM) in image regions for change detection.
 subspace learning method in xxx, is used to compress the background into the eigenbackground. 
@@
 used a mixed method that combines a reconstructive method (PCA) with a discriminative one (LDA) to robustly model the background.
-
 single Gaussians are employed for foreground modeling. 
@@
 Also, by applying edge matching, static foreground objects can be classified as ghosts or intermittent motions.
-
 Frame-based background modeling via Principal Component Analysis (PCA) and low-rank/sparse decomposition approaches is a popular alternative to pixel-level modeling xx. 
@@
 Some online approaches have also been proposed recently, but they are still very computationally expensive.
-
-\subsection{Algorithms based on Super-pixels}
-\label{sec_sup}
-A novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck.
+\subsection{Deep learning methods}
+novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck. 
 They used a fixed background model, which was generated from a temporal median operation over N video frames.
-
 In XXX, Yi Wang et al. 
@@
 Given 200 labelled images as training set, their model performed excellently in dataset2014.
-
 Braham et al. 
@@
 with the help of CNN, they generated a fixed background model from a temporal median operation over N video frames. 
-Then, a scene-specific CNN is trained with corresponding image patches from the background image.
-
+Then, a scene-specific CNN is trained with corresponding image matrixes from the background image.
 In xxx, M. 
@@
 
-\section{The IFB Framework}
-\label{sec3}
-In this section, we introduce our DPVL model that consists of a pixels-based observation patches and a novel FCN networks for background subtraction.
-We explain the details of the procedures of capturing the observation patches and the architecture of network in our DPVL model.
-The complete system is illustrated in Figure XXX.
-We use a set of input and ground true images to generalize the Pixels’ Variation Permutations, and reshape them into fixed-size image patches as and fed into a FCN.
-After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
+\section{VARIATION TRANSFORMATION}
+In this section, we will elaborate on the motivation of the proposed approach and how does the variation transformation works in background subtraction.
 
-\subsection{A. Image blocks to observation  patches}
-\label{sec3_fc}
-The historical observations of pixels which belong to the background are usually share a common variation pattern.
-In more specific terms, the variations of pixels in background are generally keeping in some pattern.
-And we want to use a FCN network to learn a new representation of pixels’ observations in a new feature space.
+Background subtraction is essentially an binary classification in time sequence, where pixels in a video stream are separated into two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops).
+In most cases, if we print out the historical observations of a single pixel, it is not hard to see that they usually keep their stability when belonging to the background. 
+However, there are some exceptions: historical observations varies regularly when belonging to some dynamic background scenes(e.g. 
+waves, swaying tree leaves). 
+Generally, pixels from the background are sharing some common patterns of variation.
 
-In order to get enough pixels’ observations, we conduct our experiment on block-level.
-In this paper, we divide each video into smaller image blocks, which share a common frame length of t.
-For each image blocks, it contains M*N pixels’ historical observations in a temporal sequence of t frames.
-We need to take them out for later transformation as our network input.
+\begin{figure}[!t]	% FIGURE: figure/fig1 
+\centering
+    \includegraphics[width=\linewidth]{figure/fig1}
+    % 图例里描述一下。
+    \caption{It is hard to separate the foreground pixels from the background precisely in a time sequence.}
+    \label{variation_chart}
+\end{figure}
 
-Observation patch is purposed to take advantage of the strong learning ability of the FCNs.
-And what we need is an pixel-to-pixel transformation.
-More precisely, Every historical pixels’ observation in these observation patches has an corresponding transformation  at the last layer of FCNs.
-Here is how we get these observation patches.
-First, we transform each image block into M*N pixel’s observation series which are the  single pixels’ historical observation series in a frame length of t.
-Next, we reshape the observation sequence into a rectangle image which size is $\sqrt{t}\cdot \sqrt{t}$.
-That rectangle image is what we called observation patch.
-The observation patches are taken as network training sample set.
+To give an intuitive understanding of the pixel variations, we plot the historical observations and corresponding groundtruth of a single pixel in Figure.1, with the X axis showing their range of variation and the Y axis representing the time.
+As we can see, there are several lines in three colors: blue, red and green. 
+The blue one is called the pixel variation curve, which containing 100 original observations. 
+Accordingly, the red one, the groundtruth curve is made of a piece of groundtruth data corresponding to the observations. 
+The green one, which we call the transformed variation curve, is made of the outputs of the proposed approach. 
+In practice, background subtraction is to produce a prediction curve, which is as near as possible to the groundtruth carve, by given the pixel variation carve.
 
-Another conception about observation patches is interval sampling.
-For a sequence like this: 
+Under ideal conditions like indoor videos, previous methods perform quite effectively, when distributions of background and foreground observations are remarkably different and the backgrounds are normally keeping static.
+While in fact, backgrounds can be rather turbulent and dynamic due to the complexity and diversity of nature scenes. 
+Especially when illumination and camouflages are involved, background and foreground observations are easily confused and mixed up.
+
+For example, in Figure.1, it is noticeable that some foreground observations in blue line share the similarly value with background ones. 
+In that case, those popular solutions will inevitably yield some sticky moments when separating the pixels in the blue line. 
+Statistical methods, for instance, are no longer valid, because they only focus on establishing a statistical model for the background, while having little or no concern for the temporal coherence of these observations.
+Unfortunately, most previous methods, as far as we know, are not capable to take advantage of the temporal coherence of pixel variation. 
+In other words, despite knowing that pixels from the background share some common patterns of variation in a temporal sequence, we still let the order information of sequential images all go to waste.
+To alleviate this, order information of pixels must be taken in consideration. 
+More concretely, we must find an efficient method to model the patterns of background pixels variations.
+
+In this paper, a method of background subtraction based on variation transformation are proposed. 
+Pixel observations are no longer considered independent of each other but regarded as a whole, which we call the pixel variation. 
+Consequently, the classification of pixels can be viewed as a transformation of pixel variations, from the observation sequences to the prediction sequences. 
+In the specific implementation, we trained a FCN to learn a transformation for the pixel variations by mapping them into a new space where it is close to the groundtruth, just like the green line in Figure.1.
+After thresholding, we can easily get the labels of each observation. 
+The benefits from variation transformation are evident and clearly seen. 
+It is hard to distinguish a foreground observation when its value are similar to the background ones. 
+However, classification on the transformed variation is much convenient and intuitive, due to the advantage of temporal information. 
+With the aid of deep learning method, the proposed approach can be effectively implemented.
+
+% 公式表达
+And the definition of region searching method $G(x,y)$ is shown as follows:
 \begin{equation}
-    p_t\{p_1,o_2,\cdots,p_n\} -> \{p_1,p_{11},p_{21}, \cdots, p_n\}
+    G(x,y) =  \mathop{\argmin}_{}{ \lVert I_t(m,n) - I_b(x,y) \rVert_{1}  } \quad  m,n \in x,y \pm R,
 \end{equation}
-where $t$
-denote the sequence number of frames.
-By this way, we can get an new sequence contains more temporary information  than the continuous pixel sequences.
+where $x$ and $y$ is the location of pixels. And $I_t$ is the current frame, where $t$ is the
+time index.
+
+%me
+\section{BACKGROUND SUBTRACTION VIA DEEP VARIATION TRANSFORMATION}
+In this section, we introduce the proposed approach that consists of a novel FCN network for background subtraction. 
+We explain the details of the procedures of pixel matrixes, which is a specific form of pixel variation, and the architecture of our network.
+
+The complete system is illustrated in Figure 1. 
+Firstly, we temporally sample the input and ground truth images to generalize the pixel variations, and reshape them into fixed-size matrixes and fed them into the network. 
+After reassembling the matrixes into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
+\begin{figure*}[!t]	% FIGURE: figure/fig1 
+\centering
+\includegraphics[width=\textwidth]{figure/fig2}
+\DeclareGraphicsExtensions.
+    \caption{Fully convolutional networks can efficiently learn to make dense predictions for per-pixel tasks like semantic segmentation.}
+    \label{flow_chart}
+\end{figure*}
+
+Given different videos, the number of frames are generally different. 
+However, the size of our input is fixed, which means a sampling processing is required to keep the length of pixel variations invariant. 
+Therefore, image stacks are sampled form the given videos before the pixel variations are extracted. 
+The given video and image stacks can be defined as follows: 
+\begin{equation}
+	Given \  Video=\{ I_1,I_2,I_3,\dots,I_L\} ,
+\end{equation}
+\begin{equation}
+Stack_{(x)}=\{I_x,I_{(x+p)},I_{(x+2p)},\dots,I_L \},\quad p*l=L,\quad 1\leq   x\leq p , 
+\end{equation}
+Where $I_t$ represent the frame $t$ of the given video. 
+And $p$ is an integer number depended on the video frames length. 
+For each video, we can produce multiple image stacks and choose one of them for the training. 
+In addition, thanks to the temporal sampling, we can get compact pixel historical observations containing more temporal information than the continuous pixel sequences. 
 This works well when it comes to some situation where the moving objects keep stationary for a long time.
 
-\subsection{Fully Convolutional Network}
-\label{sec3_bc}
-The primary task of our network is to learn an optimal feature transform of pixel’s observation series, thus we can find a new representation which is easy for classification from raw RGB data.
-There needs to be a consistent one-to-one match between pixels’ observation sequence and our network output on the time series.
-In these circumstances, traditional convolutional network cannot meet our requirements.
-Different with those traditional ones, fully convolutional networks can take input of arbitrary size and produce correspondingly-sized output with efficient inference.
-FCNs have already been used in many areas like sematic segmentation and so on.
-Researchers found FCNs has a strong learning ability which won’t lost to the traditional ones, meanwhile, it also has a high efficient computation ability.
-FCNs utilize 1*1 kernels to take the place of fully connected layers.
-Therefore, we take a fixed size of pixel’s observation patches as the input of our network. For the convenience of calculations, we transform observation sequence into observation patches.
+In order to make use of the temporal information of pixel historical observations, we regard the sampled observations from a single pixel as a whole, namely the pixel variation. 
+After the temporal sampling, a large number of observation sequences, or pixel variations, are extracted from the chosen stack, which is shown as follows:
+\begin{equation}
+Sq_{(m)}=\{P_1^m,P_2^m,P_3^m,\dots,P_n^m\},
+\end{equation}
+Where $P_t^m$ denotes the numerical value of pixel $m$ at frame $t$ in the chosen stack. 
+Each of the pixel variation is a piece of temporal information which containing the changing patterns of background pixels. 
+And each of them is of fixed length $n$. 
+It is notable that the quantity of observation sequences is exactly the resolution of the given video, which means an abundance of training data can be obtained with just one image stack.
 
-\subsection{Network Architecture}
-The architectures of our proposed FCN is illustrated in Figure xx, our network contains 5 convolutional layers, 2 pool layers and a convolutional layer which have a filter size of 1*1.
-A short calculation revealed that the network output will less 10 pixels after forward calculating.
-In order to make output the same size as input, we borrowed ideas from Image semantic segmentation, which is doing zero-padding before the training.
-After the forward computing, we can get the new representation of input observation values in a new feature space.
-Then, after some thresholding calculations.
-Our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery.
+Our intention is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. 
+However, vectors are not appropriate for the network training and learning. 
+Besides, we hope the pixel observations can be interacted with their further compatriots in temporal sequence. 
+Thus we reshape the variations into pixel matrixes as the input of our network. 
+A sample of pixel matrix $H$ is like this:
+\begin{equation}
+H=P_{i+j*d}=\begin{bmatrix}
+ P_1& P_2  &\dots  &P_d \\ 
+\vdots &  &  &\vdots \\ 
+ P_{1+(d-1)d}& \dots & \dots & P_D
+\end{bmatrix},\quad d^2=D,
+\end{equation}
+Pixel observations are put into the $d*d$ matrix according to the order of top to bottom and left to right. 
+The parameter $i$ and $j$ represent the column and row respectively. 
+And the parameter $D$ is the total frame length of a variation. 
+To put it from another way, pixel matrix is just a specific form of the pixel variation. 
+Although the pixel matrix and the observation sequence belong to different forms of the pixel variation, they are formed of the same components, and share the common temporal information from the pixel variation.
+Since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack.
+
+In the previous steps, videos are broken down into pixel matrixes which containing abundant background information. 
+Next, the groundtruth matrixes are obtained in the same way. 
+Both of them are put into the network for the training. 
+However, the size of the input will decreased after the network computing. 
+In order to make output the same size as input, we borrowed ideas from Image semantic segmentation, which is doing padding to the input before the training. 
+After the forward computing, variations are transformed in a new space where they can be easily classified by thresholding. 
+The new representation of input pixel variation is defined as:
+\begin{equation}
+H_p= \mathcal L (E_x (H)),
+\end{equation}
+Where, $H_p$ denotes the output of network, which we call the prediction matrix, the forward computation of network is represented by $L$, and $E_x$ denotes the symmetric padding of pixel matrix where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel matrix $H$.
+Another advantage of symmetric padding is that the order information still remains.
+
+For the loss function, we choose the Sigmoid Cross Entropy (SCE), which are helpful to address the learning slowdown. 
+The formulation is as follows:
+\begin{equation}
+    \begin{aligned}
+        & \ell_{H_p, H_{gt}} =  \sum\limits_{x \in X, y \in Y}^{} H_{gt}(x,y) log(Sigmoid(H_p(x,y)))  \\
+        & + (1 - H_{gt}(x,y)) log(1 - Sigmoid(H_p(x,y))) \\
+        & Sigmoid(x) =\frac{1}{1+e^{-x}}\  ,
+    \end{aligned}
+\end{equation}
+
+Where $H_{gt}$ denotes the groundtruth matrix which is given by the corresponding GT stack. 
+The SCE is calculated between the transformed matrixes and the corresponding groundtruth matrixes. 
+Boundaries of moving objects and pixels that out of the region of interest are ignored in the cost function.
+Finally, we get the transformed variation through the FCN, which are easier for classification. 
+We globally threshold the values for each observation in order to map them to $\{0,1\}$ . 
+The threshold function is given by
+\begin{equation}
+    \label{piecewise_fg}
+    g(x,y) =
+ \begin{cases}
+  1,  \quad x < y       \\
+  0,  \quad otherwise   \\
+\end{cases}.
+\end{equation}
+\begin{equation}
+M(x,y)=g(H_p,r) ,
+\end{equation}
+After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery. 
+And the major contribution is that we demonstrate the effectiveness of temporal information in background 
+subtraction.
+
+Here we make a detailed introduction to the deep learning model we used and explain why we choose it.
+
+Different with CNNs, fully convolution neural networks (FCNs) utilize convolutional layers with $1*1$ kernels to take the place of fully connected layers, which largely resolves these above-mentioned problems.
+First and foremost, the size of outputs are adjustable in FCNs, which allows an end-to-end mapping of pixel observation sequences and network outputs on the time sequence. 
+We hope to determine the label of a pixel through the comparison of its compatriot in time sequence. 
+There is one more point I ought to touch on, that since the feature maps are no longer need to be converted into vectors, spatial information can be retained . 
+The last but not the least, FCNs have been used in sematic segmentation and researchers found FCNs have a strong learning ability which won’t lost to the traditional ones. 
+Meanwhile, it’s also a high efficient computation model.
+
+Based on above-mentioned factors, FCN is designed as the alternative network architecture in this paper. 
+The structure of our FCN for background modeling is shown in Fig.1. 
+The proposed FCN contains 5 convolutional layers, 2 pool layers and a convolutional layer which have a filter size of $1*1$. 
+We use the Rectified Linear Unit (ReLU) as activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
+We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
 
 \section{Experiments}
-Our experiments are conducted on the computer with Nvidia tasela K20c GPU.
- And the DeepLearning tool we use is the matconvnet-23.
-4 beta.
 
-Our FCN network is random initialized, and the training epoch is set to 20.
-For each video, we divide it into image blocks, which have a fixed frame length of 144.
-For each image block, M*N pixel’s historical observations were taken out, where the M and N denoted the size of images.
-After a simple transformation, we can get M*N pixel’s observation patches.
-Each of them contains the historical observation of a pixels in a frame length of 144.
+In this section, we ran comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark and CAMO-UOW. 
+The CDnet is the largest dataset for background subtraction so far as we are aware, containing 11 categories with several complexly challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
+The CAMO-UOW is another challenging benchmark which contains 10 high resolution videos. 
+For each video, one or two persons appear in the scene with the clothes in the similar color as the background.
 
-For each video, we take only one image block to generate the observation patches as our training sample set.
-The other image blocks are saved for testing.
+The proposed approach is compared with several existing traditional state-of-the-art background subtraction algorithms, including the IUTIS-5, the SuBSENSE, the WeSamBE, sharable GMM, the SharedModel, word-dictionaries-based method and PAWCS, the SemanticBGS, the AAPSA, etc.
+Moreover, two deep learning based algorithms are also compared with the proposed approach, which include DeepBS, and DBMF. 
+All the results of compared algorithms are provided by authors.
 
-In dataset2014, most of the videos have a number of frames over 1000, thus our training data only accounts for 5% of total dataset.
-But we can still get plenty of training data cause the number of the training set based on the size of images.
-For example, in the video Highway of dataset2014, the image size is 320*240, so the number of observation patches for training is 76800.
-In our experiment, the finally result would be better if we slightly magnify the observation patches.
-We do the same to label data, but with no 0 padding.
+During the comparison, the F-measure(Fm) has been used for evaluation. 
+The Fm is a general international standard in background subtraction which measures the segmentation accuracy by considering both the recall and the precision. 
+The definition of Fm is shown as follows:
+\begin{equation}
+Fm= \frac{2\times precision \times recall}{precision + recall} = \frac{2TP}{2TP+FN+FP},
+\end{equation}
+% 
+% 
+% \begin{equation}
+%     F=\frac{precision \dot recall}{precision - recall}  = \frac{2TP}{2TP+FN+FP},
+% \end{equation}
+%
+Where TP, FP, and FN are true positives, false positives, and false negatives respectively, computed in pixels of all test frames for each video.
 
-\subsection{Evaluation Metric and Dataset}
-The subjective results of background modeling approaches based on the foreground detection binary maps.
-And the general international standards is F-Measure.
-F-Measure is defined as:
+The quantitative and qualitative comparisons are shown in \reftab{tab1} and Fig.3 respectively. 
+Due to the paper length, several typical videos are selected for the qualitative comparisons as well as the discussion. 
+In the dynamic background scene, the video “canoe” is a typically challenging video which includes a large area of water rippling. 
+The main challenge comes from the dynamic background, in which it is so hard to describe the background by a single image. 
+In this condition, since the traditional background subtraction method such as the SharedModel and the WeSamBE do not have the enough ability to describe the complex dynamically background, they are fail to detect the people on the boat, as shown in the Fig.
+X. 
+Besides, the detected moving objects of the SharedModel are not accurate in boundary due to the utilization of texture features. 
+In contrast, benefited from the strong learning ability of Deep Learning network, the DeepBS successfully detected the people. 
+Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even the deep learning based algorithm is suffering from the detection of the boat shape.
+In contrast, the proposed approach performed superior than others in this scene, since the essence of background subtraction is considered as a binary classification of pixels’ observation in time sequence.
+Based on this insight, the FCN network focuses on learning the patterns of the pixel variation rather than a static background image, and proposed approach achieves promising performance in the canoe video.
 
-\begin{equation}
-    F=\frac{precision \dot recall}{precision - recall}
-\end{equation}
-\begin{figure}[!t]	% FIGURE: figure/fig1 
+\begin{figure*}[!t]	\centering
+    \includegraphics[width=\textwidth]{figure/fig3}
+\DeclareGraphicsExtensions.
+    \caption{The qualitative evaluation of the proposed method. All the results is followed in the CDnet 2014.}
+    \label{results_chart}
+\end{figure*}
+As for the case of shadow scene, ‘peopleInShade’ is a typical example with prevalent hard and soft shadows. 
+In the traditional approaches, these shadow regions are usually segmented as foreground since it is also moving with the objects. 
+Therefore, traditional methods like the PAWCS, the WeSamBE and the SharedModel falsely segments part of shadows as moving objects. 
+In addition, the foreground provided by the UBSS is incomplete on the part of the pedestrian’s body due to the interference of shades, which can be owing to the severe dependency of texture features. 
+Whereas, the DeepBS performs well in this video benefited from the utilization of CNN. 
+However, the shape of pedestrians are slightly deformed as the result of their matrix-wise processing of CNN. 
+In contrast, derived from the fact that our DPVL focus on learning the pattern of pixels’ variation in the shadow regions, proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.
+
+In the video “corridor” among the Thermal scene, there is no color information since the videos are obtained through a Thermal camera. 
+Moreover, the moving objects in these videos are exceedingly fuzzy and indistinct, which is the main challenge of this category. 
+The WeSamBE, the SharedModel and the PAWCS successfully detect the target objects, owing to a stable background in this indoor video. 
+However, they fail to remove the reflections since their modeling ability have already reached a limit under the extreme condition of thermal map. 
+The DeepBS, by contrast, succeeds in eliminating most of the reflections. 
+Meanwhile, the moving objects are also clearly divided from the background thanks to the strong modeling ability of CNN. 
+However, due to the dependency of edge feature, a small object were missed in the detection result. 
+Fortunately, the proposed approach focus on the pattern of pixels’ variation, which should be theoretically effective even in the observation without the color information. 
+Consequently, our DPVL performed much better than compared algorithms, with the situation that most parts of shadow are removed and the segmentation results are more accurate.
+
+% \begin{table}[tab1]
+\begin{table*}[!t]				% TABLE
 \centering
-\includegraphics[width=.5\textwidth]{figure/fig_roc_fg}
-\DeclareGraphicsExtensions.
-    \caption{The example of latex figure.}
-\label{fig_FBMS_nobk}
-\end{figure}
+\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CDnet 2014.}
+\label{tab1}
+\begin{tabular}{lllllllllllll}
+\hline
+Videos      & baseline & dyna.bg & cam.jitter & int.obj.m & shadow & thermal & bad.weat & low f.rate & night vid. & PTZ    & turbul. & overall \\ \hline
+DeepBS      & 0.9580   & 0.8761  & \textbf{0.8990}     & 0.6097    & 0.9304 & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & \textbf{0.8993}  & 0.7458  \\
+IUTIS-5     & 0.9567   & 0.8902  & 0.8332     & 0.7296    & 0.9084 & 0.8303  & 0.8289   & \textbf{0.7911}     & 0.5132     & 0.4703 & 0.8507  & 0.7717  \\
+FTSG        & 0.9330   & 0.8792  & 0.7513     & 0.7891    & 0.8832 & 0.7768  & 0.8228   & 0.6259     & 0.5130     & 0.3241 & 0.7127  & 0.7283  \\
+AAPSA       & 0.9183   & 0.6706  & 0.7207     & 0.5098    & 0.7953 & 0.7030  & 0.7742   & 0.4942     & 0.4161     & 0.3302 & 0.4643  & 0.6179  \\
+CwisarDH    & 0.9145   & 0.8274  & 0.7886     & 0.5753    & 0.8581 & 0.7866  & 0.6837   & 0.6406     & 0.3735     & 0.3218 & 0.7227  & 0.6812  \\
+PAWCS       & 0.9397   & 0.8938  & 0.8137     & 0.7764    & 0.8934 & 0.8324  & 0.8059   & 0.6433     & 0.4171     & 0.4450 & 0.7667  & 0.7403  \\
+SuBSENSE    & 0.9503   & 0.8177  & 0.8152     & 0.6569    & 0.8986 & 0.8171  & 0.8594   & 0.6594     & 0.4918     & 0.3894 & 0.8423  & 0.7408  \\
+SemanticBGS & 0.9604   & \textbf{0.9489}  & 0.8388     & 0.7878    & 0.9244 & 0.8219  & 0.8260   & 0.7888     & 0.5014     & 0.5673 & 0.6921  & 0.7892  \\
+MBS         & 0.9287   & 0.7915  & 0.8367     & 0.7568    & 0.8262 & 0.8194  & 0.7980   & 0.6350     & 0.5158     & 0.5520 & 0.5858  & 0.7288  \\
+WeSamBE     & 0.9413   & 0.7440  & 0.7976     & 0.7392    & 0.8999 & 0.7962  & 0.8608   & 0.6602     & 0.5929     & 0.3844 & 0.7737  & 0.7446  \\
+ShareM      & 0.9522   & 0.8222  & 0.8141     & 0.6727    & 0.8898 & 0.8319  & 0.8480   & 0.7286     & 0.5419     & 0.3860 & 0.7339  & 0.7474  \\
+GMM         & 0.8245   & 0.633   & 0.5969     & 0.5207    & 0.7370 & 0.6621  & 0.7380   & 0.5373     & 0.4097     & 0.1522 & 0.4663  & 0.5707  \\
+RMoG        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
+Ours        & \textbf{0.9668}   & 0.8639  & 0.8446     & \textbf{0.9181}    & \textbf{0.9390} & \textbf{0.9268}  & \textbf{0.9265}   & 0.7338     & \textbf{0.7306}     & \textbf{0.5845} & 0.8761  & \textbf{0.8504} \\ \hline
+\end{tabular}
+\end{table*}
 
-\begin{table}[!t]				% TABLE
-    \caption{The example of latex table}
-\label{tab_FBMS_nobk}
+\begin{table*}[!t]
 \centering
-    \begin{tabular}{|l@{  }c@{  }c@{  }cc@{  }c@{  }c@{  }c|}
+\caption{The performance comparison of the proposed approach and some classical methods and deep-based method DBMF .}
+\label{tab2}
+\begin{tabular}{llllllll}
 \hline
-     \multirow{2}{*}{Videos} & \multicolumn{3}{c}{$\text{IFB}_{nobk}$} &  & \multicolumn{3}{c|}{IFB} \\
-    \cline{2-4} \cline{6-8}
-       & Re &Pr & Fm &  &  Re & Pr & Fm  \\
-\hline
-cats03          &   (\textbf{0.9472} ,\   &  0.5428 ,\  &   0.6901 )   &  &    (0.9063 ,\	 &  \textbf{0.7955} ,\	 &  \textbf{0.8473} )   \\
-bear01          &   (\textbf{0.9854} ,\   &  0.4806 ,\  &   0.6461 )   &  &    (0.8695 ,\	 &  \textbf{0.8673} ,\	 &  \textbf{0.8684} )   \\
-rabbits01       &   (\textbf{0.9530} ,\   &  0.4433 ,\  &   0.6051 )   &  &    (0.9510 ,\	 &  \textbf{0.8730} ,\	 &  \textbf{0.9103} )   \\
-cars5           &   (\textbf{0.9887} ,\   &  0.3693 ,\  &   0.5378 )   &  &    (0.9437 ,\	 &  \textbf{0.7108} ,\	 &  \textbf{0.8109} )   \\
-tennis          &   (\textbf{0.9364} ,\   &  0.4558 ,\  &   0.6132 )   &  &    (0.8808 ,\	 &  \textbf{0.7345} ,\	 &  \textbf{0.8010} )   \\
-farm01          &   (\textbf{0.9887} ,\   &  0.3897 ,\  &   0.5591 )   &  &    (0.8954 ,\	 &  \textbf{0.7462} ,\	 &  \textbf{0.8140} )   \\
-\hline                                                                                                           
-Average         &   (\textbf{0.9666} ,\   &  0.4469 ,\  &   0.6086 )   &  &    (0.9078 ,\    &  \textbf{0.7879} ,\   &  \textbf{0.8420} )   \\
-\hline
+Methods  & highway & office & Pedestrians & PETS2006 & Fall   & sofa   & overall \\ \hline
+GMM      & 0.5788  & 0.2338 & 0.5202      & 0.6011   & 0.8026 & 0.5225 & 0.5432  \\
+CodeBook & 0.8356  & 0.5939 & 0.7293      & 0.7808   & 0.3921 & 0.8149 & 0.6911  \\
+ViBe     & 0.7535  & 0.6676 & 0.8367      & 0.6668   & 0.6829 & 0.4298 & 0.6729  \\
+PBAS     & 0.8071  & 0.6839 & 0.7902      & 0.7280   & 0.3420 & 0.5768 & 0.6547  \\
+P2M      & 0.9160  & 0.3849 & 0.9121      & 0.7322   & 0.5819 & 0.4352 & 0.6604  \\
+DBMF     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
+ours     & \textbf{0.9775}  & \textbf{0.9565} & \textbf{0.9652}      & \textbf{0.9681}   & \textbf{0.9157} & \textbf{0.8943} & \textbf{0.9462}  \\ \hline
 \end{tabular}
-\end{table}
+\end{table*}
+
+    \begin{table*}[!t]
+\centering
+\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CAMO-UOW.}
+\label{tab3}
+\begin{tabular}{lllllllllll}
+Methods  & MOG2 & FCI  & LBA-SOM & PBAS & SuBSENSE & ML-BGS & DECOLOR       & COROLA & FWFC          & Ours          \\ 
+Video 1  & 0.79 & 0.88 & 0.8     & 0.9  & 0.89     & 0.89   & 0.92          & 0.8    & \textbf{0.94} & \textbf{0.94} \\
+Video 2  & 0.82 & 0.79 & 0.8     & 0.82 & 0.88     & 0.8    & 0.83          & 0.58   & 0.96          & \textbf{0.98} \\
+Video 3  & 0.88 & 0.86 & 0.85    & 0.91 & 0.9      & 0.8    & 0.9           & 0.82   & \textbf{0.94} & \textbf{0.94} \\
+Video 4  & 0.89 & 0.9  & 0.76    & 0.93 & 0.78     & 0.88   & 0.95          & 0.87   & 0.94          & \textbf{0.97} \\
+Video 5  & 0.84 & 0.86 & 0.82    & 0.83 & 0.82     & 0.8    & 0.82          & 0.75   & 0.91          & \textbf{0.97} \\
+Video 6  & 0.93 & 0.87 & 0.77    & 0.95 & 0.92     & 0.95   & \textbf{0.97} & 0.72   & 0.94          & 0.96          \\
+Video 7  & 0.76 & 0.83 & 0.88    & 0.91 & 0.87     & 0.79   & 0.91          & 0.83   & 0.96          & \textbf{0.99} \\
+Video 8  & 0.83 & 0.87 & 0.85    & 0.87 & 0.93     & 0.86   & 0.86          & 0.68   & 0.96          & \textbf{0.98} \\
+Video 9  & 0.89 & 0.9  & 0.87    & 0.84 & 0.92     & 0.87   & 0.86          & 0.78   & 0.88          & \textbf{0.99} \\
+Video 10 & 0.89 & 0.86 & 0.89    & 0.91 & 0.92     & 0.9    & 0.94          & 0.85   & 0.96          & \textbf{0.97} \\
+average  & 0.85 & 0.86 & 0.83    & 0.89 & 0.88     & 0.85   & 0.90          & 0.77   & 0.94          & \textbf{0.97} \\
+\end{tabular}
+\end{table*}
+
+The quantitative evaluation of proposed approach on CDnet 2014 is shown in the \reftab{tab1}. 
+It can be inferred that the proposed approach significantly outperformed all of the compared state-of-the-art algorithms in most of complex scenes and achieved 6\% gain in FM over the second one on the whole dataset.
+Moreover, in order to compare proposed approach with the DBMF, which is also based on deep learning and only publish their results in several special vides. 
+The proposed approach has also ran in these video and the results are shown in Table 2. 
+Again, the proposed approach has noticeably better performance than the DBMF and some other classical background approaches.
+
+	As shown in the \reftab{tab1} and \reftab{tab2}, previous deep learning based methods like the DeepBS and the DBMF achieve well performance. 
+From our own perspective, that good performance should attribute to the stronger modeling ability and learning adaptation of CNN and FCN. 
+However, the proposed approach focused on the pixels variation in temporal sequence rather than low-level static features such as color, edges and textures, which gives us the ability to avoid the shortcomings of the background models.
+Consequently, the proposed approach still get considerably better results, which over 10.46\% in FM metrics compared with the DeepBS and over 6.38\% compared with the DBMF.
+The evaluation of proposed approach in CAMO-UOW dataset is shown in the \reftab{tab3}. 
+Unlike the CDnet dataset, the videos of CAMO-UOW dataset are specially proposed for the moving objects with camouflage, which is the main challenge of this dataset. 
+As shown in the \reftab{tab3} proposed approach achieves better performance compared to its competitions, with an average F-measure of 0.97, compared to values between 0.77 and 0.94 for the other methods.
+Therefore, it is fair to say that proposed approach performs better compared with their peers.
+
+In this dataset, target objects have the similar color and textures with the background, which brings a lot of difficulties and obstacles to traditional methods. 
+However, our FCN is a powerful Neural Network model which is good at capturing the non-linearities of the manifold of pixel variations.
+
+All these experiments of the proposed method were implemented in matlab and ran on the computer with Nvidia tasela K80 GPU and all images are keep their original resolution. 
+For each video in CDnet 2014, 100 training frames are extracted to produce the image matrix. 
+It should be noted that the 100 frames only accounts for less than 10\% of total Groundtruth in CDnet 2014. 
+In contrast, 90\% of data were used as training samples in the DBMF, which suggest that the proposed approach achieves well performance with limited training frames. 
+Considering that the videos in CAMO-UOW have fewer frames, we reduce the number of training frames to 49. 
+During the experience, the training set and testing set are completely separated. 
+More specifically, our FCN network is random initialized. 
+We train the network with mini-batches of size 100, a learning rate $α = 1 ∗ 10^{−3}$ over 20 epochs. 
+The last threshold $R$ is set to 0.6.
+
+% \begin{table}[!t]				% TABLE
+%     \caption{The example of latex table}
+% \label{tab_FBMS_nobk}
+% \centering
+%     \begin{tabular}{|l@{  }c@{  }c@{  }cc@{  }c@{  }c@{  }c|}
+% \hline
+%      \multirow{2}{*}{Videos} & \multicolumn{3}{c}{$\text{IFB}_{nobk}$} &  & \multicolumn{3}{c|}{IFB} \\
+%     \cline{2-4} \cline{6-8}
+%        & Re &Pr & Fm &  &  Re & Pr & Fm  \\
+% \hline
+% cats03          &   (\textbf{0.9472} ,\   &  0.5428 ,\  &   0.6901 )   &  &    (0.9063 ,\	 &  \textbf{0.7955} ,\	 &  \textbf{0.8473} )   \\
+% bear01          &   (\textbf{0.9854} ,\   &  0.4806 ,\  &   0.6461 )   &  &    (0.8695 ,\	 &  \textbf{0.8673} ,\	 &  \textbf{0.8684} )   \\
+% rabbits01       &   (\textbf{0.9530} ,\   &  0.4433 ,\  &   0.6051 )   &  &    (0.9510 ,\	 &  \textbf{0.8730} ,\	 &  \textbf{0.9103} )   \\
+% cars5           &   (\textbf{0.9887} ,\   &  0.3693 ,\  &   0.5378 )   &  &    (0.9437 ,\	 &  \textbf{0.7108} ,\	 &  \textbf{0.8109} )   \\
+% tennis          &   (\textbf{0.9364} ,\   &  0.4558 ,\  &   0.6132 )   &  &    (0.8808 ,\	 &  \textbf{0.7345} ,\	 &  \textbf{0.8010} )   \\
+% farm01          &   (\textbf{0.9887} ,\   &  0.3897 ,\  &   0.5591 )   &  &    (0.8954 ,\	 &  \textbf{0.7462} ,\	 &  \textbf{0.8140} )   \\
+% \hline                                                                                                           
+% Average         &   (\textbf{0.9666} ,\   &  0.4469 ,\  &   0.6086 )   &  &    (0.9078 ,\    &  \textbf{0.7879} ,\   &  \textbf{0.8420} )   \\
+% \hline
+% \end{tabular}
+% \end{table}
 
 % Videos & GBSSP\cite{Lim2014_2014_ECCV} & calMoSeg\cite{2016_ECCV_Bideau2016}  & MLayer\cite{2017_ICCV_zhu2017multilayer}  & $\text{IFB}_{SU}$ & $\text{IFB}_{KA}$ & $\text{IFB}_{SI}$ & Videos & GBSSP\cite{Lim2014_2014_ECCV} & calMoSeg\cite{2016_ECCV_Bideau2016} & MLayer\cite{2017_ICCV_zhu2017multilayer}  &  $\text{IFB}_{SU}$ &  $\text{IFB}_{KA}$  &  $\text{IFB}_{SI}$  \\
-\section{Conclusions}
-In this paper,
-we proposed the IFB framework for background subtraction for the case of a freely moving camera.
-Unlike previous work in which attempts were made to improve the accuracy of the estimation of motion,
-our IFB focuses on integrating rough foreground and background cues for foreground segmentation.
-In particular, 
-foreground cues are detected by a GMM model with the estimation of background motion,
-while background cues are captured from spatio-temporal features filtered by homography transformation,
-where the SURF\cite{2006_SURF}, KAZE\cite{2012_KAZE}, SIFT\cite{lowe2004distinctive} features are used as examples.
-% the geometric constraints between the SIFT features.
-Then, super-pixels under multiple levels are utilized to integrate these cues.
-The efficiency of IFB results from the complementarity between foreground and background cues.
-The accuracy of the proposed approach is improved though the utilization of super-pixels under multiple levels.
-A comprehensive experiment to compare our results with the state-of-the-art shows the efficiency of our framework and points to its potential for use in practical applications.
 
+\section{Conclusion}
+In this paper, we proposed the 
+Moreover, we captured different superpixels under multiple scales and
+integrating these superpixels to improve the accuracy of proposed approach.
+
+% \section{Conclusions}
+% In this paper,
+% we proposed the IFB framework for background subtraction for the case of a freely moving camera.
+% Unlike previous work in which attempts were made to improve the accuracy of the estimation of motion,
+% our IFB focuses on integrating rough foreground and background cues for foreground segmentation.
+% In particular, 
+% foreground cues are detected by a GMM model with the estimation of background motion,
+% while background cues are captured from spatio-temporal features filtered by homography transformation,
+% where the SURF\cite{2006_SURF}, KAZE\cite{2012_KAZE}, SIFT\cite{lowe2004distinctive} features are used as examples.
+% % the geometric constraints between the SIFT features.
+% Then, super-pixels under multiple levels are utilized to integrate these cues.
+% The efficiency of IFB results from the complementarity between foreground and background cues.
+% The accuracy of the proposed approach is improved though the utilization of super-pixels under multiple levels.
+% A comprehensive experiment to compare our results with the state-of-the-art shows the efficiency of our framework and points to its potential for use in practical applications.
+% 
 \ifCLASSOPTIONcaptionsoff

### 2018-06-20 build.sh

@@ -1,0 +1,5 @@
+pdflatex draft.tex 
+bibtex draft.aux 
+pdflatex draft.tex 
+pdflatex draft.tex
+evince draft.pdf

### 2018-06-20 deeplearning_bg/deeplearning_bg/program/bftab/main.cpp

@@ -1,0 +1,32 @@
+#include <iostream>
+#include <string>
+
+using namespace std;
+
+int main()
+{
+    string str;
+    string value;
+
+    while (cin >> str)
+    {
+        if (str == "-1")
+        {
+            cin >> value;
+            cout << "\\textbf{" << value << "}" << " ";
+        }
+        else if (str == "\\\\")
+        {
+            cout << "\\\\" << endl;
+        }
+        else if (str == "\\hline")
+        {
+            cout << "\\hline" << endl;
+        }
+        else
+        {
+            cout << str << " ";
+        }
+    }
+    return 0;
+}

### 2018-06-20 deeplearning_bg/deeplearning_bg/program/fulltable/main.cpp

@@ -1,0 +1,384 @@
+#include <iostream>
+#include <string>
+#include <fstream>
+#include <iomanip>
+
+using namespace std;
+
+static double data_MST[63];
+static double data_RMoG[63];
+static double data_MoG[63];
+static double data_IMoG[63];
+static double data_ViBe[63];
+static double data_ViBep[63];
+static double data_RECTGAUSS[63];
+static double data_MultiLayer[63];
+static double data_MultiCue[63];
+
+void captureValue(string str,char* filename,double &re,double &pr,double &fm);
+
+void fullData(char* filename,double data[63])
+{
+    ifstream infile("list.txt");
+    string str;
+    int count = 0;
+    double re = 0;
+    double pr = 0;
+    double fm = 0;
+
+    while (infile >> str)
+    {
+        re = -1;
+        pr = -1;
+        fm = -1;
+        captureValue(str,filename,re,pr,fm);
+
+       // cout << re << " " << pr << " "<< fm << endl;
+
+
+        data[count] = re;
+        data[count + 1] = pr;
+        data[count + 2] = fm;
+
+        count += 3;
+    }
+}
+
+void captureValue(string str,char* filename,double &re,double &pr,double &fm)
+{
+    ifstream infile(filename);
+    string input;
+
+    while (infile >> input)
+    {
+        if (input == str)
+        {
+            infile >> re >> pr >> fm;
+            break;
+        }
+    }
+
+    infile.close();
+}
+
+void printfData(double data[63])
+{
+     ifstream infile("list.txt");
+     string str = "";
+     int i = 0;
+
+     while (infile >> str)
+     {
+         cout << str << " " <<  data[i] << " " << data[i + 1] << " " << data[i + 2] << endl;
+         i += 3;
+     }
+
+     infile.close();
+}
+
+float fixValue(double input)
+{
+     float value = input*100;
+     value = (int)(value + 0.5);
+
+     return value/100;
+}
+
+int main(int argc,char* argv[])
+{
+    fullData("result_MST.txt",data_MST);
+    fullData("result_RMoG.txt",data_RMoG);
+    fullData("result_MoG.txt",data_MoG);
+    fullData("result_improveMoG.txt",data_IMoG);
+    fullData("result_ViBe.txt",data_ViBe);
+    fullData("result_ViBe+.txt",data_ViBep);
+    fullData("result_045_full.txt",data_RECTGAUSS);
[…]

### 2018-06-20 deeplearning_bg/deeplearning_bg/program/mix/run.sh

@@ -1,0 +1,20 @@
+./a.exe < result_005.txt > result_005_full.txt
+./a.exe < result_010.txt > result_010_full.txt
+./a.exe < result_015.txt > result_015_full.txt
+./a.exe < result_020.txt > result_020_full.txt
+./a.exe < result_025.txt > result_025_full.txt
+./a.exe < result_030.txt > result_030_full.txt
+./a.exe < result_035.txt > result_035_full.txt
+./a.exe < result_040.txt > result_040_full.txt
+./a.exe < result_045.txt > result_045_full.txt
+./a.exe < result_050.txt > result_050_full.txt
+./a.exe < result_1_005.txt > result_1_005_full.txt
+./a.exe < result_1_010.txt > result_1_010_full.txt
+./a.exe < result_1_015.txt > result_1_015_full.txt
+./a.exe < result_1_020.txt > result_1_020_full.txt
+./a.exe < result_1_025.txt > result_1_025_full.txt
+./a.exe < result_1_030.txt > result_1_030_full.txt
+./a.exe < result_1_035.txt > result_1_035_full.txt
+./a.exe < result_1_040.txt > result_1_040_full.txt
+./a.exe < result_1_045.txt > result_1_045_full.txt
+./a.exe < result_1_050.txt > result_1_050_full.txt

### 2018-06-27 draft.tex
¸üÐÂժҪºÍintroduction

@@
 \begin{abstract}
-One of the main challenges of foreground detection comes from the diversity and complexity of real-world scenes. 
-While most of previous works in this field were proposed by designing an artificial model, we tend to present a self-adaption solution, by combining the fully convolutional networks (FCNs), which is named as the Deep Pixels Variation Learning model (DPVL).
-Our main job is to find a new representation of pixels historical observations in a new feature space. 
-In this paper, videos are divided into fixed length image stacks, which are later transformed into the pixel observation matrixes as the input of a FCN for learning the variation of pixels. 
-We conduct our training and prediction processes on stack level. 
-The architecture of the FCN is devised from the semantic segmentation problem. 
-Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ variation. 
-We compare our method with some state-of-the-art methods, and the results show that the proposed approach outperform its
+%什么是背景检测
+Background subtraction can be generally viewed as a binary classification on each pixels in a video stream. 
+%之前方法
+Previous works in this field were generally proposed by designing an artificial model, using lowlevel or hand-crafted features such as color, texture and local binary patterns.
+%我们的改进
+In this paper, we focus on the variation patterns of pixels to take advantage of the temporal information in a video stream.
+A novel conception of pixel variation transformation is brought up, which can be perceived as a feature mapping to find a new representation of pixels historical observations in a new feature space.
+We also provide a self-adaption solution, by combining the fully convolutional networks (FCNs), which is named as the Deep Pixels Variation Transformation Learning model (DPVTL). 
+%方法简介
+In the DPVTL model, videos are divided into fixed length image stacks by temporal sampling.
+Next, image stacks is broken down into pixel observation matrixes as the input of the FCN to learn the patterns of pixel variation.
+Each of the pixel matrixes contains a piece of temporal information about pixel variation over a period of time.
+The architecture of our FCN is devised from the semantic segmentation problem. 
+%效果
+Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ observations.
+Compared with some state-of-the-art methods, both deep learning and traditional methods, the proposed approach outperform its conventional counterparts significantly owing to the utilizing of temporal information.
 \end{abstract}
@@
 \section{Introduction}
+%背景检测的背景介绍
 Background subtraction or foreground object detection, as a fundamental problem in computer vision, has been much discussed with the increasing number of outdoor cameras over the last few decades.
@@
 
-With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
-However, background Subtraction is still unsolved because of the diversity in background scenes and the changes originated from the camera itself. 
-Scene variations can be in many forms such as, camera jitter, dynamic background, bad weather, illumination changes, intermittent object motion. 
-This is principally because the major methods, in most cases, try to find a universal solution by generating some universal background models for later linear classification; for instance, the earlier Frame Difference Methods, trying to get a fixed image as background to classify each pixels.
-The fundamental problem lies in that linear classifier might not be powerful enough for the job, due to the complexity and the diversity of natural scenes.
+%实际应用中的挑战
+Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes.
+However, background subtraction is still unsolved because of the complexity and the diversity of natural scenes.
+There are many forms of natrual scenes, for example, camera jitter, dynamic background, bad weather, illumination changing, intermittent object motion.
+In these situations, the backgrounds are no longer being static, while in fact, the background can be dynamic and complex, which brings some severe challenges to the traditional methods.
 
-In order to present a better and universal solution, we proposed the Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes. 
-In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.
+%本文的想法和优势
+The previous methods have already made great progress in generating some sophisticated background models with given videos.
+Unfortunately, some instructive clues have been long put aside and neglected, since there is no efficient way to deal with them.
+For instance, the static methods model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream.
+To solve this problem, we bring up a novel conception of pixel variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation.
+Each piece of pixel variation contains the complete temproal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.
 
-For \emph{Sq}, it is a sequence of pixel variation, which is hard to classify which entry is foreground or background. 
-But in \emph{Sq'}, it is more easy to classified, since the output of the network is the label of each entry in sequence.
+%具体介绍
+In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes.
+In the DPVTL model, a Fully Convolutinal Network(FCN) is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space.
+Our contributions can be summarized as follows:
+\begin{itemize}
+\item We proposed the pixel observation matrix to describe the pixel variation, which encode both the intensity distribution and sequential information over time.
+The observation matrix is obtained by reshaping the vector of a pixel's historical observations, subtracted from the image stacks.
+Since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack, which promise that sufficient training data can be obtained with limited groundtruth.
+\item We propose a deep neural network for variation transformation.
+Our FCN network is trained to learn the pixel variation and generate a new representation in a new feature space.
+We take advantage of the strong learning ability of FCN to learn an end-to-end representation of the pixel observation matrixes in a new space where the pixels can be easily classified to background and foreground.
+\end{itemize}
 
-In this paper, pixel observation matrixes are proposed to describe the historical variation of pixels. 
-And a random initialized FCN network is trained to learn the pixel variation and generate a new representation in a new feature space. 
-We take advantage of the strong learning ability of FCN to learn a new representation of the pixel observation matrixes in a new space where the pixels can be easily classified to background and foreground.
-
+%文章结构
+The outline of this paper is as follows: In Section II, we give a brief discussion about the early and recent relevant works.
+The details of the variation transformation are presented in Section III.
+The proposed fully convolutional network is illustrated in Section IV, followed by experiments and result comparison in Section V and conclude the paper in Section VI.
 \section{Related Work}
@@
 \cite{Bouwmans2014}
-Over the last few decades, Background subtraction has been well studied. 
-Meanwhile, a huge number of methods were proposed. 
-These methods can be broadly categorized into pixels-based, region-based, frame-based and Deep Learning.
+Over the last few decades, Background subtraction has been well studied. Meanwhile, a huge number of methods were proposed. 
+These methods can be broadly categorized into pixels-based, region-based and Deep Learning based methods.
 \subsection{pixels-based methods}
@@
 Some online approaches have also been proposed recently, but they are still very computationally expensive.
-\subsection{Deep learning methods}
+
+\subsection{Deep learning based methods}
 novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck. 
@@
 \begin{tabular}{lllllllllll}
-Methods  & MOG2 & FCI  & LBA-SOM & PBAS & SuBSENSE & ML-BGS & DECOLOR       & COROLA & FWFC          & Ours          \\ 
+\hline
+Methods  & MOG2 & FCI  & LBA-SOM & PBAS & SuBSENSE & ML-BGS & DECOLOR       & COROLA & FWFC          & Ours          \\ \hline
 Video 1  & 0.79 & 0.88 & 0.8     & 0.9  & 0.89     & 0.89   & 0.92          & 0.8    & \textbf{0.94} & \textbf{0.94} \\
@@
 Video 9  & 0.89 & 0.9  & 0.87    & 0.84 & 0.92     & 0.87   & 0.86          & 0.78   & 0.88          & \textbf{0.99} \\
-Video 10 & 0.89 & 0.86 & 0.89    & 0.91 & 0.92     & 0.9    & 0.94          & 0.85   & 0.96          & \textbf{0.97} \\
-average  & 0.85 & 0.86 & 0.83    & 0.89 & 0.88     & 0.85   & 0.90          & 0.77   & 0.94          & \textbf{0.97} \\
+Video 10 & 0.89 & 0.86 & 0.89    & 0.91 & 0.92     & 0.9    & 0.94          & 0.85   & 0.96          & \textbf{0.97} \\ \hline
+average  & 0.85 & 0.86 & 0.83    & 0.89 & 0.88     & 0.85   & 0.90          & 0.77   & 0.94          & \textbf{0.97} \\ \hline
 \end{tabular}

### 2018-06-28 draft.tex
finished the revision of abstract, pls check!

@@
 \newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
+\newcommand{\stodo}[1]{\todo[size=\tiny]{#1}}
 
@@
 \begin{abstract}
-%什么是背景检测
-Background subtraction can be generally viewed as a binary classification on each pixels in a video stream. 
-%之前方法
-Previous works in this field were generally proposed by designing an artificial model, using lowlevel or hand-crafted features such as color, texture and local binary patterns.
+%什么是背景检测 避免多次使用同一个词 generally
+Background subtraction is fundamentally considered as the binary classification of pixels in a video stream. 
+%之前方法 下一句用的focus on加ing，这就用ed，形成对比
+Previous works generally proposed the artificial model with the utilization of lowlevel or hand-crafted features to analyze the variation of pixels' observation in time sequence.
+% 为什么之前方法会失败
+However, due to the complexity and diversity of nature,
+the variation of observations becomes so hard to classify by hand-crafted features.
+    %in complexly natural scenes.
 %我们的改进
-In this paper, we focus on the variation patterns of pixels to take advantage of the temporal information in a video stream.
-A novel conception of pixel variation transformation is brought up, which can be perceived as a feature mapping to find a new representation of pixels historical observations in a new feature space.
-We also provide a self-adaption solution, by combining the fully convolutional networks (FCNs), which is named as the Deep Pixels Variation Transformation Learning model (DPVTL). 
-%方法简介
-In the DPVTL model, videos are divided into fixed length image stacks by temporal sampling.
-Next, image stacks is broken down into pixel observation matrixes as the input of the FCN to learn the patterns of pixel variation.
-Each of the pixel matrixes contains a piece of temporal information about pixel variation over a period of time.
-The architecture of our FCN is devised from the semantic segmentation problem. 
-%效果
-Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ observations.
-Compared with some state-of-the-art methods, both deep learning and traditional methods, the proposed approach outperform its conventional counterparts significantly owing to the utilizing of temporal information.
+In this paper, we focus on transforming the obserations sequence into another easier classfied space,
+and a novel background subtraction method based on Deep Variation Transformation (DVT) is proposed.
+% XXX 为什么是networks，不是network呢？
+In the DVT model,
+the fully convolutional network (FCN) is untlized to transform the sequence of pixels' observations into a new representation of pixels' observations with more obvious features for classfication.
+%
+In particlar, 
+a the variation of observation represented by pixel sequence is reshaped into a image patch as the input of FCN network.
+%
+Then, the output of network is classfied and reverted to the corresponding sequence for the binary classfication of oberservations' variation.
+%
+Benefied from the ingenious utilization of FCN network leading by our clear congnition of essence about background subtractoin problem,
+proposed approached adaptively generate superior peroformances in diversly complex scenes.
+%
+Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including 
+% both deep learning and traditional methods.
+% 
+% 
+% 
+% videos are divided into fixed length image stacks by temporal sampling. 
+%     Next, image stacks is broken down into pixel observation matrixes as the input of the FCN to learn the patterns of pixel variation. 
+%     Each of the pixel matrixes contains a piece of temporal information about pixel variation over a period of time.  
+% The architecture of our FCN is devised from the semantic segmentation problem. 
+% %效果
+% Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ observations. 
+%     Compared with some state-of-the-art methods, both deep learning and traditional methods, the proposed approach outperform its conventional counterparts significantly owing to the utilizing of temporal information.
 \end{abstract}

### 2018-07-03 draft.tex
增加图1，表达论文思想
none

--- 2018-06-27 draft.tex
@@
 Unfortunately, some instructive clues have been long put aside and neglected, since there is no efficient way to deal with them.
-For instance, the static methods model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream.
+For instance, the statistical methods model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream.
 To solve this problem, we bring up a novel conception of pixel variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation.
@@
 \cite{Bouwmans2014}
-Over the last few decades, Background subtraction has been well studied. Meanwhile, a huge number of methods were proposed. 
+Over the last few decades, background subtraction has been well studied. Meanwhile, a huge number of background modeling methods have been proposed. 
 These methods can be broadly categorized into pixels-based, region-based and Deep Learning based methods.
 \subsection{pixels-based methods}
-The most widely used algorithms in Background subtraction are pixels-based methods. 
-And one of the famous method is Gaussian Mixture Model (GMM), in which a GMM is used to model the history over time of pixel’s intensity values. 
-It is assumed that pixels are independent from their neighbors. 
-Incoming pixels are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound. 
-For learning the parameters, that maximize the likelihood, the authors proposed an online method that approximates the Expectation Maximization (EM) algorithm.
+Pixels-based methods are generally based on low-level features, such as color and gradients, these methods are computationally efficient and easy to deploy.
+However, they demonstrate a poor performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
+The most popular approaches are Gaussian Mixture Model (GMM) and its improved methods, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time. 
+Mingliang Chen et al. proposed a Spatiotemporal GMM algorithm, which combines the GMM with constrains of temporal and spatial information from the optical flow and superpixels.
 
-In XXX , Mingliang Chen et al. 
-propose a background subtraction algorithm using hierarchical superpixels segmentation, spanning trees and optical flow. 
-Their Background model combine the GMM with constrains of temporal and spatial from optical flow and superpixels.
+. 
+Each pixels are assumed to be independent from their neighbors.
+
+%
+low-level features (e.g. color intensities, gradients pixel-based
+
+PBAS [10] and ViBe+ [14], follow this paradigm as they are both based on stochastic intensity sampling.
+Parametric approaches based on Gaussian Mixture Models (GMM) [15] or non-parametric ones based on Kernel Density Estimation (KDE)  
+%
 

### 2018-07-03 draft.tex

--- 2018-06-28 draft.tex
@@
 In these situations, the backgrounds are no longer being static, while in fact, the background can be dynamic and complex, which brings some severe challenges to the traditional methods.
+\begin{figure}[!t]	% FIGURE: figure/fig1 
+\centering
+    \includegraphics[width=\linewidth]{figure/idea.pdf}
+    % 图例里描述一下。
+    \caption{XXX.}
+    \label{idea}
+\end{figure}
 

### 2018-07-04 draft.tex
relative work

@@
 Over the last few decades, background subtraction has been well studied. Meanwhile, a huge number of background modeling methods have been proposed. 
-These methods can be broadly categorized into pixels-based, region-based and Deep Learning based methods.
+These methods can be broadly categorized into pixels-based, region-based and Learning-based methods.
 \subsection{pixels-based methods}
-Pixels-based methods are generally based on low-level features, such as color and gradients, these methods are computationally efficient and easy to deploy.
-However, they demonstrate a poor performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
-The most popular approaches are Gaussian Mixture Model (GMM) and its improved methods, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time. 
-Mingliang Chen et al. proposed a Spatiotemporal GMM algorithm, which combines the GMM with constrains of temporal and spatial information from the optical flow and superpixels.
+Pixel-based techniques assume that the historical observations over time are independent at each pixel.
+Based on low-level features, such as color and gradients, these methods are computationally efficient and easy to deploy.
+However, they demonstrate a comparatively poor performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
 
-. 
-Each pixels are assumed to be independent from their neighbors.
+%GMM
+The most famous pixels-based methods are Gaussian Mixture Model (GMM) methods, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time.
+Pixels are considered to be background if there exists a Gaussian includes their values with sufficient evidence.
+%GMM+
+Zoran Zivkovic extend the GMM through the use of recursive equations, where the parameters keep constantly updating and the number of components are adaptable to each pixel. 
+%codebook
+Another popular algorithms in pixel based category are based on Codebook.
+In [], Kim et al present the codebook method to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model.
+The final foreground is detected by a distance measurement in a cylindrical color model.
+%KDE
+A non-parametric background model is proposed in [].
+Elgammal et al.
+assume that each background pixel is drawn from a Probability Distribution Function(PDF).
+The PDF for each pixel is estimated with Kernel Density Estimation(KDE).
+%Vibe
+Another non-parametric method is proposed by O.
+Barnich, called the Visual Background Extractor (ViBe).
+ViBe is a sample based method, which consists of pixel samples from the video stream.
+Each pixel in the current frame is compared with N pixel samples from the corresponding background model.
+A pixel is labeled as the foreground only when there exist at least K samples with a distance to itself within a certain range R.
+%PBAS
+To adaptively update the parameters, Hofmann et al. [] improve the ViBe by presenting an adaptive threshold R(x), which depended on the pixel position and a background dynamics metric.
+%
+\subsection{region-based approach}
+Region-based approaches assume that the neighboring pixels have a similar variation as the pixel itself.
+Hence the spatial correlation is taken into consideration to refine the pixel-level classification.
+
+%(Regularized region-based)
+A region-based MoG is proposed by Sriram Varadarajan et al.
+Their model are derived from expectation maximization theory, which takes into consideration neighboring pixels while generating the model of the observed scene.
+% Spatiotemporal GMM
+Another GMM based method named Spatiotemporal GMM algorithm was proposed in [].
+Mingliang Chen et al.
+combine the GMM with constrains of temporal and spatial information from the optical flow and superpixels.
+%(Bayesian Modeling)
+In [], Yaser Sheikh et al. introduce a MAP-MRF framework, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
+%(Robust Foreground Object ICPR2010 Vikas Reddy )
+In [], given frames are divided into overlapping blocks.
+Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure, and a temporal correlation check.
+%( Robust Region-Based ICPR)
+Mohammad Izadi et al.
+present a robust region-based approach, which generates a pair of foreground maps based on gradient and color.
+Any foreground region that does not exist in map1 could be recovered from map2.
+\subsection{learning-based methods}
+The last category of background subtraction methods apply traditional machine learning or deep learning on different features for the background modeling.
+
+%SVM
+Traditional machine learning methods are commonly involved with support vector machines (SVM) and Bayesian methods.
+For example, in [], the authors integrate gradient, color, and Haar-like features to address the spatiotemporal variations for each pixel.
+A pixel wise background model is obtained for each feature in a kernel density framework and a SVM is employed for segmentation.
 
 %
-low-level features (e.g. color intensities, gradients pixel-based
-
-PBAS [10] and ViBe+ [14], follow this paradigm as they are both based on stochastic intensity sampling.
-Parametric approaches based on Gaussian Mixture Models (GMM) [15] or non-parametric ones based on Kernel Density Estimation (KDE)  
+Recent years, deep learning start to flourish in many fields, such as face recognition and natural language processing, significantly improving the state-of-the-art.
+A novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck.
+They employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth, or alternatively, segmentation results coming from other background subtraction methods.
+Patches are extracted around a pixel, then they are feed into the network and compared with a threshold.
 %
-
-Kim et al used a codebook to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model. 
-This allows them efficient in memory and speed compared with other background modeling techniques. 
-The final foreground is detected by a distance measurement in a cylindrical color model.
-In XXX, Zhi Zeng et al. 
-proposed an equal-qualification updating strategy to replace the maximum-negative-run-length-based filtering strategy. 
-Their experiments show that, the proposed method outperforms well, despite using only color information.
-Elgammal et al. 
-introduced a probabilistic non-parametric method to model the background. 
-It is assumed that each background pixel is drawn from a PDF. 
-The PDF for each pixel is estimated with Kernel Density Estimation (KDE).
-\subsection{region-based approach}
-region-based approach assumpt that the neighboring pixels have a similar variation as the pixel itself.
-
-In xxx, Sriram Varadarajan et al. 
-propose a region-based MoG to takes in which the updated mixtures represent the scene distribution in a neighborhood region.
-In (PCA), classification is done by comparing a stack in current frame to its reconstruction from PCA coefficients and declaring it as background if the reconstruction is close.
-recently region based method is presented in XXX which used the statistical circular shift moments (SCSM) in image regions for change detection.
-subspace learning method in xxx, is used to compress the background into the eigenbackground. 
-For each video, the mean and the covariance matrix are calculated. 
-After a PCA of the covariance matrix, a projection matrix is set up with M eigenvectors. 
-Then, incoming images are compared with their projection onto the eigenvectors. 
-Foreground labels are assigned to pixels with large distances, after calculating the distances between the image and the projection and comparing them with the corresponding threshold value.
-
-Marghes et al. 
-used a mixed method that combines a reconstructive method (PCA) with a discriminative one (LDA) to robustly model the background.
-single Gaussians are employed for foreground modeling. 
-By computing flux tensors, which depict variations of optical flow within a local 3D spatio-temporal volume, blob motion is detected. 
-With the combination of the different information from blob motion, foreground models and background models, moving and static foreground objects can be spotted. 
-Also, by applying edge matching, static foreground objects can be classified as ghosts or intermittent motions.
-Frame-based background modeling via Principal Component Analysis (PCA) and low-rank/sparse decomposition approaches is a popular alternative to pixel-level modeling xx. 
-These approaches are however not ideal for surveillance applications as most rely on batch or offline processing or suffer from scaling problems.
-
-In XXX, ss et al. 
-addressed scaling problems by reformulating principal component analysis for 2D images. 
-Meanwhile their method takes much lower memory consumption and computational cost than others. 
-Some online approaches have also been proposed recently, but they are still very computationally expensive.
-
-\subsection{Deep learning based methods}
-novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck. 
-They used a fixed background model, which was generated from a temporal median operation over N video frames.
-In XXX, Yi Wang et al. 
+In [], Yi Wang et al.
 tried a CNN architecture combined with a Cascade model for segmentation in Background subtraction.
 Given 200 labelled images as training set, their model performed excellently in dataset2014.
-Braham et al. 
-present an Deep learning-based method. 
-with the help of CNN, they generated a fixed background model from a temporal median operation over N video frames. 
-Then, a scene-specific CNN is trained with corresponding image matrixes from the background image.
-In xxx, M. 
+%
+In [], M.
 Babaee et al.
-combine the segmentation mask from SuBSENSE algorithm and the output of Flux Tensor algorithm, which can dynamically change the parameters used in the background model based on the motion changes in the video frames.
+present a novel CNN for background subtraction.
+They also combine the segmentation mask from SuBSENSE algorithm and the output of Flux Tensor algorithm, which is able to adaptively update the parameters used in the background model based on the motion changes in video stream.
 They also used spatial-median filtering as the post processing of the network outputs.
-
 \section{VARIATION TRANSFORMATION}
@@
 \section{Conclusion}
-In this paper, we proposed the 
-Moreover, we captured different superpixels under multiple scales and
-integrating these superpixels to improve the accuracy of proposed approach.
 

### 2018-07-05 draft.tex
references

@@
 In the DVT model,
-the fully convolutional network (FCN) is untlized to transform the sequence of pixels' observations into a new representation of pixels' observations with more obvious features for classfication.
+the fully convolutional network (FCN)\cite{Shelhamer2017fcn} is untlized to transform the sequence of pixels' observations into a new representation of pixels' observations with more obvious features for classfication.
 %
@@
 %背景检测的背景介绍
-Background subtraction or foreground object detection, as a fundamental problem in computer vision, has been much discussed with the increasing number of outdoor cameras over the last few decades.
+Background subtraction or foreground object detection, as a fundamental problem in computer vision\cite{Bouwmans201431}, has been much discussed with the increasing number of outdoor cameras over the last few decades.
 It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.g.
@@
 However, background subtraction is still unsolved because of the complexity and the diversity of natural scenes.
-There are many forms of natrual scenes, for example, camera jitter, dynamic background, bad weather, illumination changing, intermittent object motion.
+There are many forms of natrual scenes, for example, camera jitter, dynamic background, bad weather, illumination changing, intermittent object motion\cite{CDN2014}.
 In these situations, the backgrounds are no longer being static, while in fact, the background can be dynamic and complex, which brings some severe challenges to the traditional methods.
@@
 Unfortunately, some instructive clues have been long put aside and neglected, since there is no efficient way to deal with them.
-For instance, the statistical methods model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream.
+For instance, the statistical methods\cite{Stauffer1999} model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream.
 To solve this problem, we bring up a novel conception of pixel variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation.
@@
 In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes.
-In the DPVTL model, a Fully Convolutinal Network(FCN) is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space.
+In the DPVTL model, a Fully Convolutinal Network(FCN)\cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space.
 Our contributions can be summarized as follows:
@@
 % XXX 引用文章的方式，Bouwmans2014 在ref.bib文件里,不懂去问曲师兄！！！！
-\cite{Bouwmans2014}
+%\cite{Bouwmans2014}
 Over the last few decades, background subtraction has been well studied. Meanwhile, a huge number of background modeling methods have been proposed. 
@@
 %GMM
-The most famous pixels-based methods are Gaussian Mixture Model (GMM) methods, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time.
+The most famous pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time.
 Pixels are considered to be background if there exists a Gaussian includes their values with sufficient evidence.
 %GMM+
-Zoran Zivkovic extend the GMM through the use of recursive equations, where the parameters keep constantly updating and the number of components are adaptable to each pixel. 
+Zoran Zivkovic\cite{Zivkovic2004} extend the GMM through the use of recursive equations, where the parameters keep constantly updating and the number of components are adaptable to each pixel. 
 %codebook
 Another popular algorithms in pixel based category are based on Codebook.
-In [], Kim et al present the codebook method to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model.
+In \cite{Kim2005}, Kim et al present the codebook method to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model.
 The final foreground is detected by a distance measurement in a cylindrical color model.
 %KDE
-A non-parametric background model is proposed in [].
+A non-parametric background model is proposed in \cite{Elgammal2000Non}.
 Elgammal et al.
@@
 Another non-parametric method is proposed by O.
-Barnich, called the Visual Background Extractor (ViBe).
+Barnich, called the Visual Background Extractor (ViBe)\cite{Barnich2011_2011_TIP}.
 ViBe is a sample based method, which consists of pixel samples from the video stream.
@@
 %PBAS
-To adaptively update the parameters, Hofmann et al. [] improve the ViBe by presenting an adaptive threshold R(x), which depended on the pixel position and a background dynamics metric.
+To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold R(x), which depended on the pixel position and a background dynamics metric.
 %
@@
 %(Regularized region-based)
-A region-based MoG is proposed by Sriram Varadarajan et al.
-Their model are derived from expectation maximization theory, which takes into consideration neighboring pixels while generating the model of the observed scene.
+A region-based MoG is proposed by Varadarajan et al.\cite{2015_PR_Varadarajan20153488} Their model are derived from expectation maximization theory, which takes into consideration neighboring pixels while generating the model of the observed scene.
 % Spatiotemporal GMM
-Another GMM based method named Spatiotemporal GMM algorithm was proposed in [].
-Mingliang Chen et al.
-combine the GMM with constrains of temporal and spatial information from the optical flow and superpixels.
+Another GMM based method named Spatiotemporal GMM algorithm was proposed in \cite{2017_TPAMI_GANGWANG}.
+the authors combine the GMM with constrains of temporal and spatial information from the optical flow and superpixels.
 %(Bayesian Modeling)
-In [], Yaser Sheikh et al. introduce a MAP-MRF framework, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
+In \cite{Sheikh2005Bayesian}, Sheikh et al. introduce a MAP-MRF framework, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
 %(Robust Foreground Object ICPR2010 Vikas Reddy )
-In [], given frames are divided into overlapping blocks.
+In \cite{Reddy2010Robust}, given frames are divided into overlapping blocks.
 Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure, and a temporal correlation check.
 %( Robust Region-Based ICPR)
-Mohammad Izadi et al.
-present a robust region-based approach, which generates a pair of foreground maps based on gradient and color.
+Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color.
 Any foreground region that does not exist in map1 could be recovered from map2.
@@
 %SVM
-Traditional machine learning methods are commonly involved with support vector machines (SVM) and Bayesian methods.
-For example, in [], the authors integrate gradient, color, and Haar-like features to address the spatiotemporal variations for each pixel.
+Traditional machine learning methods are commonly involved with support vector machines (SVM) and Bayesian methods\cite{Zhang2014Statis}.
+For example, in \cite{Han2012}, the authors integrate gradient, color, and Haar-like features to address the spatiotemporal variations for each pixel.
 A pixel wise background model is obtained for each feature in a kernel density framework and a SVM is employed for segmentation.
@@
 Recent years, deep learning start to flourish in many fields, such as face recognition and natural language processing, significantly improving the state-of-the-art.
-A novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck.
+A novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck\cite{Braham2016deep}.
 They employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth, or alternatively, segmentation results coming from other background subtraction methods.
@@
 %
-In [], Yi Wang et al.
+In \cite{wang2016PRL}, Wang et al.
 tried a CNN architecture combined with a Cascade model for segmentation in Background subtraction.
@@
 %
-In [], M.
+In \cite{Babaee2017deep}, M.
 Babaee et al.
 present a novel CNN for background subtraction.
-They also combine the segmentation mask from SuBSENSE algorithm and the output of Flux Tensor algorithm, which is able to adaptively update the parameters used in the background model based on the motion changes in video stream.
+They also combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm, which is able to adaptively update the parameters used in the background model based on the motion changes in video stream.
 They also used spatial-median filtering as the post processing of the network outputs.
@@
 
-In this section, we ran comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark and CAMO-UOW. 
+In this section, we ran comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW. 
 The CDnet is the largest dataset for background subtraction so far as we are aware, containing 11 categories with several complexly challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
@@
 
-The proposed approach is compared with several existing traditional state-of-the-art background subtraction algorithms, including the IUTIS-5, the SuBSENSE, the WeSamBE, sharable GMM, the SharedModel, word-dictionaries-based method and PAWCS, the SemanticBGS, the AAPSA, etc.
-Moreover, two deep learning based algorithms are also compared with the proposed approach, which include DeepBS, and DBMF. 
+The proposed approach is compared with several existing traditional state-of-the-art background subtraction algorithms, including the IUTIS-5\cite{Bianco2017TEC}, the SuBSENSE\cite{St-Charles2015SuBSENSE}, the WeSamBE\cite{Jiang2017WeSamBE}, sharable GMM the SharedModel\cite{Chen2015SharedModel}, word-dictionaries-based method the PAWCS\cite{Charles2015PAWCS}, the SemanticBGS\cite{Braham2017Semantic}, the AAPSA\cite{RAMIREZALONSO2016990}, etc.
+Moreover, two deep learning based algorithms are also compared with the proposed approach, which include DeepBS\cite{Babaee2017deep}, and DBMF\cite{Yang2018DBMF}. 
 All the results of compared algorithms are provided by authors.
@@
 Videos      & baseline & dyna.bg & cam.jitter & int.obj.m & shadow & thermal & bad.weat & low f.rate & night vid. & PTZ    & turbul. & overall \\ \hline
-DeepBS      & 0.9580   & 0.8761  & \textbf{0.8990}     & 0.6097    & 0.9304 & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & \textbf{0.8993}  & 0.7458  \\
-IUTIS-5     & 0.9567   & 0.8902  & 0.8332     & 0.7296    & 0.9084 & 0.8303  & 0.8289   & \textbf{0.7911}     & 0.5132     & 0.4703 & 0.8507  & 0.7717  \\
-FTSG        & 0.9330   & 0.8792  & 0.7513     & 0.7891    & 0.8832 & 0.7768  & 0.8228   & 0.6259     & 0.5130     & 0.3241 & 0.7127  & 0.7283  \\
-AAPSA       & 0.9183   & 0.6706  & 0.7207     & 0.5098    & 0.7953 & 0.7030  & 0.7742   & 0.4942     & 0.4161     & 0.3302 & 0.4643  & 0.6179  \\
-CwisarDH    & 0.9145   & 0.8274  & 0.7886     & 0.5753    & 0.8581 & 0.7866  & 0.6837   & 0.6406     & 0.3735     & 0.3218 & 0.7227  & 0.6812  \\
-PAWCS       & 0.9397   & 0.8938  & 0.8137     & 0.7764    & 0.8934 & 0.8324  & 0.8059   & 0.6433     & 0.4171     & 0.4450 & 0.7667  & 0.7403  \\
-SuBSENSE    & 0.9503   & 0.8177  & 0.8152     & 0.6569    & 0.8986 & 0.8171  & 0.8594   & 0.6594     & 0.4918     & 0.3894 & 0.8423  & 0.7408  \\
-SemanticBGS & 0.9604   & \textbf{0.9489}  & 0.8388     & 0.7878    & 0.9244 & 0.8219  & 0.8260   & 0.7888     & 0.5014     & 0.5673 & 0.6921  & 0.7892  \\
-MBS         & 0.9287   & 0.7915  & 0.8367     & 0.7568    & 0.8262 & 0.8194  & 0.7980   & 0.6350     & 0.5158     & 0.5520 & 0.5858  & 0.7288  \\
-WeSamBE     & 0.9413   & 0.7440  & 0.7976     & 0.7392    & 0.8999 & 0.7962  & 0.8608   & 0.6602     & 0.5929     & 0.3844 & 0.7737  & 0.7446  \\
-ShareM      & 0.9522   & 0.8222  & 0.8141     & 0.6727    & 0.8898 & 0.8319  & 0.8480   & 0.7286     & 0.5419     & 0.3860 & 0.7339  & 0.7474  \\
-GMM         & 0.8245   & 0.633   & 0.5969     & 0.5207    & 0.7370 & 0.6621  & 0.7380   & 0.5373     & 0.4097     & 0.1522 & 0.4663  & 0.5707  \\
-RMoG        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
+DeepBS\cite{Babaee2017deep}      & 0.9580   & 0.8761  & \textbf{0.8990}     & 0.6097    & 0.9304 & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & \textbf{0.8993}  & 0.7458  \\
+IUTIS-5\cite{Bianco2017TEC}     & 0.9567   & 0.8902  & 0.8332     & 0.7296    & 0.9084 & 0.8303  & 0.8289   & \textbf{0.7911}     & 0.5132     & 0.4703 & 0.8507  & 0.7717  \\
+FTSG\cite{Wang2014FTSG}        & 0.9330   & 0.8792  & 0.7513     & 0.7891    & 0.8832 & 0.7768  & 0.8228   & 0.6259     & 0.5130     & 0.3241 & 0.7127  & 0.7283  \\
+AAPSA\cite{RAMIREZALONSO2016990}       & 0.9183   & 0.6706  & 0.7207     & 0.5098    & 0.7953 & 0.7030  & 0.7742   & 0.4942     & 0.4161     & 0.3302 & 0.4643  & 0.6179  \\
+CwisarDH\cite{Gregorio2014CwisarDH}    & 0.9145   & 0.8274  & 0.7886     & 0.5753    & 0.8581 & 0.7866  & 0.6837   & 0.6406     & 0.3735     & 0.3218 & 0.7227  & 0.6812  \\
+PAWCS\cite{Charles2015PAWCS}       & 0.9397   & 0.8938  & 0.8137     & 0.7764    & 0.8934 & 0.8324  & 0.8059   & 0.6433     & 0.4171     & 0.4450 & 0.7667  & 0.7403  \\
+SuBSENSE\cite{St-Charles2015SuBSENSE}    & 0.9503   & 0.8177  & 0.8152     & 0.6569    & 0.8986 & 0.8171  & 0.8594   & 0.6594     & 0.4918     & 0.3894 & 0.8423  & 0.7408  \\
+SemanticBGS\cite{Braham2017Semantic} & 0.9604   & \textbf{0.9489}  & 0.8388     & 0.7878    & 0.9244 & 0.8219  & 0.8260   & 0.7888     & 0.5014     & 0.5673 & 0.6921  & 0.7892  \\
+MBS\cite{Multimode_Background_Subtraction}         & 0.9287   & 0.7915  & 0.8367     & 0.7568    & 0.8262 & 0.8194  & 0.7980   & 0.6350     & 0.5158     & 0.5520 & 0.5858  & 0.7288  \\
+WeSamBE\cite{2017_TCSVT_BG_7938679}     & 0.9413   & 0.7440  & 0.7976     & 0.7392    & 0.8999 & 0.7962  & 0.8608   & 0.6602     & 0.5929     & 0.3844 & 0.7737  & 0.7446  \\
+ShareM\cite{2015_ICME_ShareModel}      & 0.9522   & 0.8222  & 0.8141     & 0.6727    & 0.8898 & 0.8319  & 0.8480   & 0.7286     & 0.5419     & 0.3860 & 0.7339  & 0.7474  \\
+GMM\cite{Zivkovic2004}         & 0.8245   & 0.633   & 0.5969     & 0.5207    & 0.7370 & 0.6621  & 0.7380   & 0.5373     & 0.4097     & 0.1522 & 0.4663  & 0.5707  \\
+RMoG\cite{Varadarajan2013}        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
 Ours        & \textbf{0.9668}   & 0.8639  & 0.8446     & \textbf{0.9181}    & \textbf{0.9390} & \textbf{0.9268}  & \textbf{0.9265}   & 0.7338     & \textbf{0.7306}     & \textbf{0.5845} & 0.8761  & \textbf{0.8504} \\ \hline
@@
 Methods  & highway & office & Pedestrians & PETS2006 & Fall   & sofa   & overall \\ \hline
-GMM      & 0.5788  & 0.2338 & 0.5202      & 0.6011   & 0.8026 & 0.5225 & 0.5432  \\
-CodeBook & 0.8356  & 0.5939 & 0.7293      & 0.7808   & 0.3921 & 0.8149 & 0.6911  \\
-ViBe     & 0.7535  & 0.6676 & 0.8367      & 0.6668   & 0.6829 & 0.4298 & 0.6729  \\
-PBAS     & 0.8071  & 0.6839 & 0.7902      & 0.7280   & 0.3420 & 0.5768 & 0.6547  \\
-P2M      & 0.9160  & 0.3849 & 0.9121      & 0.7322   & 0.5819 & 0.4352 & 0.6604  \\
-DBMF     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
+GMM\cite{Stauffer1999}      & 0.5788  & 0.2338 & 0.5202      & 0.6011   & 0.8026 & 0.5225 & 0.5432  \\
+CodeBook\cite{WU2010739} & 0.8356  & 0.5939 & 0.7293      & 0.7808   & 0.3921 & 0.8149 & 0.6911  \\
+ViBe\cite{Barnich2011_2011_TIP}     & 0.7535  & 0.6676 & 0.8367      & 0.6668   & 0.6829 & 0.4298 & 0.6729  \\
+PBAS\cite{Hofmann2012Background}     & 0.8071  & 0.6839 & 0.7902      & 0.7280   & 0.3420 & 0.5768 & 0.6547  \\
+P2M\cite{Yang2016P2M}      & 0.9160  & 0.3849 & 0.9121      & 0.7322   & 0.5819 & 0.4352 & 0.6604  \\
+DBMF\cite{Yang2018DBMF}     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
 ours     & \textbf{0.9775}  & \textbf{0.9565} & \textbf{0.9652}      & \textbf{0.9681}   & \textbf{0.9157} & \textbf{0.8943} & \textbf{0.9462}  \\ \hline
@@
 \hline
-Methods  & MOG2 & FCI  & LBA-SOM & PBAS & SuBSENSE & ML-BGS & DECOLOR       & COROLA & FWFC          & Ours          \\ \hline
+Methods  & MOG2\cite{ZIVKOVIC2006773} & FCI\cite{Baf2008FCI}  & LBA-SOM\cite{LBA-SOM2008} & PBAS & SuBSENSE & ML-BGS\cite{ML-BGS2007} & DECOLOR\cite{DECOLOR2013}       & COROLA\cite{SHAKERI201628} & FWFC\cite{Li2018CAMO}          & Ours          \\ \hline
 Video 1  & 0.79 & 0.88 & 0.8     & 0.9  & 0.89     & 0.89   & 0.92          & 0.8    & \textbf{0.94} & \textbf{0.94} \\
@@
 
+In this paper, we proposed a noval background subtraction approach based on deep learning and the variation transformation learning.
+The DPVTL model include a FCN network and a noval variation transformation learing framework, which allows us to efficiently combine the temproal coherence and distribution information of pixels over a long period of time.
+Comparison with other traditional and deep learning methods shows that the DPVTL has good properties on several challenging scenes.
+The future work will be focused on improving the DPVTL in terms of network architecture updating and integration of local spatial coherence.
+
 % \section{Conclusions}

### 2018-07-06 draft.tex
updated figure1

@@
 %背景检测的背景介绍
-Background subtraction or foreground object detection, as a fundamental problem in computer vision\cite{Bouwmans201431}, has been much discussed with the increasing number of outdoor cameras over the last few decades.
+Background subtraction or foreground detection, as a fundamental problem in computer vision\ \cite{Bouwmans201431}, has been discussed over decades with the increasing number of outdoor cameras.
+%
 It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.g.
@@
 \centering
-    \includegraphics[width=\linewidth]{figure/idea.pdf}
+    \includegraphics[width=\linewidth]{figure/demo.pdf}
     % 图例里描述一下。
-    \caption{XXX.}
+    \caption{The demonstration of deep variation transformation.
+Due to the complexity of natural scenes, the original pixels' variation is hard to classify correctly.
+After transforming by deep learning network, the pixels in variation become easy to be classified as foreground and background correctly.}
     \label{idea}

### 2018-07-09 draft.tex
add comments

@@
 \usepackage[unicode,pdftex]{hyperref}
-
 \usepackage{xcolor}
@@
 
+\usepackage{todonotes} 
 \hyphenation{op-tical net-works semi-conduc-tor}
@@
 In the DVT model,
-the fully convolutional network (FCN)\cite{Shelhamer2017fcn} is untlized to transform the sequence of pixels' observations into a new representation of pixels' observations with more obvious features for classfication.
+the fully convolutional network (FCN) is untlized to transform the sequence of pixels' observations into a new representation of pixels' observations with more obvious features for classfication.
 %
@@
 vehicles and humans, thus saving us huge amount of computing resources.
-Typically, Background subtraction can be viewed as a binary classification that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.
+\todo{cited an article to support this sentence.}
+%
+Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
+However, background subtraction is still unsolved because of the complexity and the diversity of natural scenes.
+%
+Currenrly, plenty of previous work focus on anaylsing the pixels' variation for background subtraction,
+since the background subtraction is typically recognized as a binary classification that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.
+%
+However, due to the unpredictability and diversity of the pixels' variation in natural scenes,
+it is still a challenging problem to propose a good background subtraction in all complexly natural scenes.
 
 %实际应用中的挑战
+\todo{the main purpose of th second paragraph is showing our idea.
+But be careful that you should not mention any details of our method which is the content of third paragraph.
+Pls re-write this part according to figure 1.
+The main content should be the description of figure 1, as well as our idea, insight}
 Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
@@
 In these situations, the backgrounds are no longer being static, while in fact, the background can be dynamic and complex, which brings some severe challenges to the traditional methods.
+To solve this problem, we bring up a novel conception of pixel variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation.
+Each piece of pixel variation contains the complete temproal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.
 \begin{figure}[!t]	% FIGURE: figure/fig1 
@@
 %本文的想法和优势
-The previous methods have already made great progress in generating some sophisticated background models with given videos.
-Unfortunately, some instructive clues have been long put aside and neglected, since there is no efficient way to deal with them.
-For instance, the statistical methods\cite{Stauffer1999} model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream.
-To solve this problem, we bring up a novel conception of pixel variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation.
-Each piece of pixel variation contains the complete temproal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.
+% The previous methods have already made great progress in generating some sophisticated background models with given videos. 
+% Unfortunately, some instructive clues have been long put aside and neglected, since there is no efficient way to deal with them. 
+% For instance, the statistical methods\cite{Stauffer1999} model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream.
 
 %具体介绍
+% XXX 一句话，换一行！！！
 In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes. 
 In the DPVTL model, a Fully Convolutinal Network(FCN)\cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space.
-Our contributions can be summarized as follows:
+\todo{provide more details about our method, the details should be enough to summarize proposed approach.}
+%Our contributions can be summarized as follows:
+The contridbutions of proposed approach are shown as follows:
 \begin{itemize}
@@
 %文章结构
-The outline of this paper is as follows: In Section II, we give a brief discussion about the early and recent relevant works.
+%The outline of this paper is as follows: In Section II, we give a brief discussion about the early and recent relevant works. 
+% XXX 不会用引用可以问我或者曲师兄。
+The reset part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion about the early and recent relevant works. 
+%
 The details of the variation transformation are presented in Section III.
 The proposed fully convolutional network is illustrated in Section IV, followed by experiments and result comparison in Section V and conclude the paper in Section VI.
+\todo{please revise this part by using command refsec}
+
 \section{Related Work}
+\label{sec2}
 % XXX 引用文章的方式，Bouwmans2014 在ref.bib文件里,不懂去问曲师兄！！！！
@@
 %
+\todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
 \subsection{region-based approach}
@@
 Any foreground region that does not exist in map1 could be recovered from map2.
-\subsection{learning-based methods}
+\todo{disccuss the adavantage of proposed work.}
+
+% \subsection{learning-based methods}
+\subsection{Machine Learning based Methods}
+\todo{Please cite more papers on this paragraph since our work belongs to this category. This paragraph should be the main part of this section.}
 The last category of background subtraction methods apply traditional machine learning or deep learning on different features for the background modeling.
@@
 They also used spatial-median filtering as the post processing of the network outputs.
+
 \section{VARIATION TRANSFORMATION}

### 2018-07-16 draft.tex
revise

@@
 %
-Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including 
-% both deep learning and traditional methods.
+Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
 % 
@@
 It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.g.
-vehicles and humans, thus saving us huge amount of computing resources.
+vehicles and humans, thus saving us huge amount of computing resources\cite{Barnich2011_2011_TIP}.
 \todo{cited an article to support this sentence.}
@@
 %实际应用中的挑战
-\todo{the main purpose of th second paragraph is showing our idea.
+\todo{the main purpose of the second paragraph is showing our idea.
 But be careful that you should not mention any details of our method which is the content of third paragraph.
@@
 In these situations, the backgrounds are no longer being static, while in fact, the background can be dynamic and complex, which brings some severe challenges to the traditional methods.
-To solve this problem, we bring up a novel conception of pixel variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation.
+To solve this problem, we bring up a novel conception of variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation.
 Each piece of pixel variation contains the complete temproal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.
@@
 In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes. 
-In the DPVTL model, a Fully Convolutinal Network(FCN)\cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space.
+In the DVTL model, a Fully Convolutinal Network(FCN)\cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space, as shown in \reffig{idea}.
+The final prediction can be obtained by thresholding of the transformed variation.
 \todo{provide more details about our method, the details should be enough to summarize proposed approach.}
@@
 %
-The details of the variation transformation are presented in Section III.
-The proposed fully convolutional network is illustrated in Section IV, followed by experiments and result comparison in Section V and conclude the paper in Section VI.
+The details of the variation transformation are presented in \refsec{sec3}.
+The proposed fully convolutional network is illustrated in \refsec{sec4}, followed by experiments and result comparison in \refsec{sec5} and conclude the paper in \refsec{sec6}.
 \todo{please revise this part by using command refsec}
@@
 Based on low-level features, such as color and gradients, these methods are computationally efficient and easy to deploy.
-However, they demonstrate a comparatively poor performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
 
@@
 %
+
+However, Those assumptions of pixels' independence are incorrect or inapplicable to many real-world scenes.
+Hence they demonstrate a comparatively poor performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
+There is, in fact, a strong temporal coherence in image sequences that provides abundant hidden messages for the background model. 
+The proposed approach take advantage of the temporal coherence, and that is the reason that we have a relative better performance in challenging scenes.  
 \todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
@@
 Any foreground region that does not exist in map1 could be recovered from map2.
+
+Unfortunately, most region-based methods are not capable to make use of the temporal coherence, since they are merely adding some spatial constrains to the pixels-based methods. 
+We also notice that some methods are involved with optical flow field, which can be viewed as a limited temproal coherence message. 
+However, optical flow methods have some shortcommings like the high computation complexity, moreover they are very sensitive to illumination changing. 
+Compared with them, the proposed approach are more powerful in capturing the structural background variation and more efficient in computation due to the application of deep learning.
 \todo{disccuss the adavantage of proposed work.}
@@
 %
-In \cite{Babaee2017deep}, M.
+M.
 Babaee et al.
-present a novel CNN for background subtraction.
+\cite{Babaee2017deep} present a novel CNN for background subtraction.
 They also combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm, which is able to adaptively update the parameters used in the background model based on the motion changes in video stream.
 They also used spatial-median filtering as the post processing of the network outputs.
+%DBMF
+In \cite{Yang2018DBMF}, a FCN with the skip architecture is proposed for background modeling. 
+The authors also proposed a temproal approach to sample training images from the given video, thus providing the background model with limited temporal information.
+
+Above mentioned deep methods are based on the static images and static saliency characteristics. 
+As we've discussed earlier, their background models are trained with little or no temporal coherence involved.
+Different with their methods, with a relative simple structure of the network, the proposed approach is based on the time series modeling of each pixel.
+Hence the reliable performance of DVTL should be owing to the enhanced temporal coherence.
 
 \section{VARIATION TRANSFORMATION}
+\label{sec3}
 In this section, we will elaborate on the motivation of the proposed approach and how does the variation transformation works in background subtraction.
@@
 
-To give an intuitive understanding of the pixel variations, we plot the historical observations and corresponding groundtruth of a single pixel in Figure.1, with the X axis showing their range of variation and the Y axis representing the time.
+To give an intuitive understanding of the pixel variations, we plot the historical observations and corresponding groundtruth of a single pixel in  \reffig{variation_chart}, with the X axis showing their range of variation and the Y axis representing the time.
 As we can see, there are several lines in three colors: blue, red and green. 
@@
 
-For example, in Figure.1, it is noticeable that some foreground observations in blue line share the similarly value with background ones. 
+For example, in \reffig{variation_chart}, it is noticeable that some foreground observations in blue line share the similarly value with background ones. 
 In that case, those popular solutions will inevitably yield some sticky moments when separating the pixels in the blue line. 
@@
 Consequently, the classification of pixels can be viewed as a transformation of pixel variations, from the observation sequences to the prediction sequences. 
-In the specific implementation, we trained a FCN to learn a transformation for the pixel variations by mapping them into a new space where it is close to the groundtruth, just like the green line in Figure.1.
+In the specific implementation, we trained a FCN to learn a transformation for the pixel variations by mapping them into a new space where it is close to the groundtruth, just like the green line in \reffig{variation_chart}.
 After thresholding, we can easily get the labels of each observation. 
@@
 \section{BACKGROUND SUBTRACTION VIA DEEP VARIATION TRANSFORMATION}
+\label{sec4}
 In this section, we introduce the proposed approach that consists of a novel FCN network for background subtraction. 
@@
 
-The complete system is illustrated in Figure 1. 
+The complete system is illustrated in \reffig{flow_chart}. 
 Firstly, we temporally sample the input and ground truth images to generalize the pixel variations, and reshape them into fixed-size matrixes and fed them into the network. 
@@
 \DeclareGraphicsExtensions.
-    \caption{Fully convolutional networks can efficiently learn to make dense predictions for per-pixel tasks like semantic segmentation.}
+    \caption{Fully convolutional network can efficiently learn to make dense predictions for per-pixel tasks like semantic segmentation.}
     \label{flow_chart}
@@
 After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery. 
-And the major contribution is that we demonstrate the effectiveness of temporal information in background 
-subtraction.
+And the major contribution is that we demonstrate the effectiveness of temporal information in background subtraction.
 
@@
 
-Different with CNNs, fully convolution neural networks (FCNs) utilize convolutional layers with $1*1$ kernels to take the place of fully connected layers, which largely resolves these above-mentioned problems.
+Different with CNNs, fully convolution neural network (FCN) utilize convolutional layers with $1*1$ kernels to take the place of fully connected layers, which largely resolves these above-mentioned problems.
 First and foremost, the size of outputs are adjustable in FCNs, which allows an end-to-end mapping of pixel observation sequences and network outputs on the time sequence. 
@@
 Based on above-mentioned factors, FCN is designed as the alternative network architecture in this paper. 
-The structure of our FCN for background modeling is shown in Fig.1. 
+The structure of our FCN for background modeling is shown in \reffig{flow_chart}. 
 The proposed FCN contains 5 convolutional layers, 2 pool layers and a convolutional layer which have a filter size of $1*1$. 
@@
 \section{Experiments}
-
+\label{sec5}
 In this section, we ran comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW. 
@@
 
-The quantitative and qualitative comparisons are shown in \reftab{tab1} and Fig.3 respectively. 
+The quantitative and qualitative comparisons are shown in \reftab{tab1} and  \reffig{results_chart} respectively. 
 Due to the paper length, several typical videos are selected for the qualitative comparisons as well as the discussion. 
@@
 The main challenge comes from the dynamic background, in which it is so hard to describe the background by a single image. 
-In this condition, since the traditional background subtraction method such as the SharedModel and the WeSamBE do not have the enough ability to describe the complex dynamically background, they are fail to detect the people on the boat, as shown in the Fig.
-X. 
+In this condition, since the traditional background subtraction method such as the SharedModel and the WeSamBE do not have the enough ability to describe the complex dynamically background, they are fail to detect the people on the boat, as shown in the \reffig{results_chart}.
 Besides, the detected moving objects of the SharedModel are not accurate in boundary due to the utilization of texture features. 
@@
 \section{Conclusion}
-
+\label{sec6}
 In this paper, we proposed a noval background subtraction approach based on deep learning and the variation transformation learning.

### 2018-07-31 draft.tex
more discussion

@@
 \begin{abstract}
-%什么是背景检测 避免多次使用同一个词 generally
-Background subtraction is fundamentally considered as the binary classification of pixels in a video stream. 
-%之前方法 下一句用的focus on加ing，这就用ed，形成对比
-Previous works generally proposed the artificial model with the utilization of lowlevel or hand-crafted features to analyze the variation of pixels' observation in time sequence.
-% 为什么之前方法会失败
-However, due to the complexity and diversity of nature,
-the variation of observations becomes so hard to classify by hand-crafted features.
-    %in complexly natural scenes.
-%我们的改进
-In this paper, we focus on transforming the obserations sequence into another easier classfied space,
-and a novel background subtraction method based on Deep Variation Transformation (DVT) is proposed.
-% XXX 为什么是networks，不是network呢？
+%
+Previous work analyzes the variation of pixels for background subtraction which is generally considered as the binary classification of pixels in time sequence.
+%
+In this paper, we focus on transforming the variation into another space where the pixels are easier classified,
+with the consideration that the observations of pixels are usually so hard to analyze due to the unpredictability and complexity of natural scenes,
+and a novel background subtraction method called Deep Variation Transformation (DVT) is proposed.
+%
 In the DVT model,
-the fully convolutional network (FCN) is untlized to transform the sequence of pixels' observations into a new representation of pixels' observations with more obvious features for classfication.
+the variation is represented by the sequence of pixels' observations and used as the input of the fully convolutional network.
 %
-In particlar, 
-a the variation of observation represented by pixel sequence is reshaped into a image patch as the input of FCN network.
-%
-Then, the output of network is classfied and reverted to the corresponding sequence for the binary classfication of oberservations' variation.
-%
-Benefied from the ingenious utilization of FCN network leading by our clear congnition of essence about background subtractoin problem,
+The fully convolutional network is trained to learn the pattern of variation for transformation with the output leaded by grounthtruth data.
+% XXX 这句话还是有点问题
+Benefied from the ingenious utilization of FCN leading by our clear congnition of essence about background subtractoin problem,
 proposed approached adaptively generate superior peroformances in diversly complex scenes.
@@
 Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
+%
+% We also put
+% forward a novel background subtraction framework called the
+% Integration of Foreground and Background (IFB) cues.
+% % a video stream. 
+% %之前方法 下一句用的focus on加ing，这就用ed，形成对比
+% % Previous works generally proposed the artificial model with the utilization of lowlevel or hand-crafted features to analyze the variation of pixels' observation.
+% Previous work generally analyze the variation of pixels' observation with the u/cygdrive/c/Users/Ray/Downloads/3.iebktilization of hand-crafted features.
+%     %in time sequence.
+% % 为什么之前方法会失败
+% However, due to the complexity and diversity of nature,
+% the variation of observations becomes so hard to classify by hand-crafted features.
+%     %in complexly natural scenes.
+% %我们的改进
+% In this paper, we focus on transforming the obserations sequence into another easier classfied space,
+% and a novel background subtraction method based on Deep Variation Transformation (DVT) is proposed.
+% % XXX 为什么是networks，不是network呢？
+% In the DVT model,
+% the fully convolutional network (FCN) is untlized to transform the sequence of pixels' observations into a new representation of pixels' observations with more obvious features for classfication.
+% %
+% In particlar, 
+% a the variation of observation represented by pixel sequence is reshaped into a image patch as the input of FCN network.
+% %
+% Then, the output of network is classfied and reverted to the corresponding sequence for the binary classfication of oberservations' variation.
+% %
+% Benefied from the ingenious utilization of FCN network leading by our clear congnition of essence about background subtractoin problem,
+% proposed approached adaptively generate superior peroformances in diversly complex scenes.
+% %
+% Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
 % 
@@
 %背景检测的背景介绍
-Background subtraction or foreground detection, as a fundamental problem in computer vision\ \cite{Bouwmans201431}, has been discussed over decades with the increasing number of outdoor cameras.
+Background subtraction as a fundamental problem in computer vision\ \cite{Bouwmans201431} has been discussed over decades with the increasing number of cameras,
+which is widely used as the pre-processing step of video processing \cite{Barnich2011_2011_TIP}.
+% which can help us efficiently mark the region of interest,
+% thus saving us huge amount of computing resources\ \cite{Barnich2011_2011_TIP}.
+%\todo{cited an article to support this sentence.}
+% 现有的方法在简单场景中效果很好了
+Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes.
+However, it still remains a challenging problem in the scenes with high complexity and diversity.
+% 传统的方法是怎么做的，有什么问题
+Traditioanlly, background subtraction algorithms focus on anaylsing the pixels' variation for background subtraction,
+since the background subtraction is typically recognized as a binary classification that assigns each pixel in a video sequence with a label, 
+for either belonging to the background or foreground scene.
+% 总而言之，background subtraction依然有很多问题
+However, due to the unpredictability and complexity of the pixels' variation in natural scenes,
+the variation becomes so unordered which is hard to be analyzed for background subtraction.
+
+% 第二段重点阐述什么是deep variation learning
+% 在多样的自然场景中，前景可能产生和背景相似，甚至相同的像素，而这种像素很难去分析
+In the diversely natural scenes,
+it is possible that the moving objects produce the similar or even the same observations of pixels to that of background,
+and the variation of observations becomes so hard to analyze when it includes such observations.
+% similar to their counterparts of background but atually belong to foreground .
+% 如图所示，像素观测值C就和背景的值几乎一模一样，
+As shown in the \reffig{idea},
+the observation C is closely related to the observations belong to the background but it is actually produced by moving objects and should be classified as foreground.
+% 大多数情况下，他都会被划分成背景
+However, in most cases, it is highly possible that the observation C will be falsely classified as background by previous work due to the similarity with their counterparts of background.
+% 我们的就是希望把这个variation 转化到更简单的地方去
+In this work, we focus on transforming the variation of pixels' observation into a new variation where the observations are easier to classified,
+as shown in the bottom part of the \reffig{idea},
+with the motivation that the pattern of fragment consist of observations A-D can be learned by the network and transformed into another fragment where these observations are easily and correctly classified as foreground.
+% transformatin 之后，就很容易分类了，然后这就是我们的方法的核心了
+Based on this motivation, the Deep Variation Transformation model for background subtraction is proposed.
 % 
-It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.g.
-vehicles and humans, thus saving us huge amount of computing resources\cite{Barnich2011_2011_TIP}.
-\todo{cited an article to support this sentence.}
-%
-Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
-However, background subtraction is still unsolved because of the complexity and the diversity of natural scenes.
-%
-Currenrly, plenty of previous work focus on anaylsing the pixels' variation for background subtraction,
-since the background subtraction is typically recognized as a binary classification that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.
-%
-However, due to the unpredictability and diversity of the pixels' variation in natural scenes,
-it is still a challenging problem to propose a good background subtraction in all complexly natural scenes.
-
-%实际应用中的挑战
-\todo{the main purpose of the second paragraph is showing our idea.
+% %实际应用中的挑战
+% \todo{the main purpose of the second paragraph is showing our idea.
 But be careful that you should not mention any details of our method which is the content of third paragraph.
@@
 The main content should be the description of figure 1, as well as our idea, insight}
-Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
-However, background subtraction is still unsolved because of the complexity and the diversity of natural scenes.
-There are many forms of natrual scenes, for example, camera jitter, dynamic background, bad weather, illumination changing, intermittent object motion\cite{CDN2014}.
+% Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
+% However, background subtraction is still unsolved because of the complexity and the diversity of natural scenes.
+% There are many forms of natrual scenes, for example, camera jitter, dynamic background, bad weather, illumination changing, intermittent object motion\cite{CDN2014}.
 In these situations, the backgrounds are no longer being static, while in fact, the background can be dynamic and complex, which brings some severe challenges to the traditional methods.
-To solve this problem, we bring up a novel conception of variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation.
-Each piece of pixel variation contains the complete temproal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.
+% To solve this problem, we bring up a novel conception of variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation.
+Each piece of pixel variation contains the complete temporal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.
 \begin{figure}[!t]	% FIGURE: figure/fig1 
@@
 % XXX 一句话，换一行！！！
-In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes. 
-In the DVTL model, a Fully Convolutinal Network(FCN)\cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space, as shown in \reffig{idea}.
-The final prediction can be obtained by thresholding of the transformed variation.
-\todo{provide more details about our method, the details should be enough to summarize proposed approach.}
-%Our contributions can be summarized as follows:
-The contridbutions of proposed approach are shown as follows:
-\begin{itemize}
-\item We proposed the pixel observation matrix to describe the pixel variation, which encode both the intensity distribution and sequential information over time.
-The observation matrix is obtained by reshaping the vector of a pixel's historical observations, subtracted from the image stacks.
-Since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack, which promise that sufficient training data can be obtained with limited groundtruth.
-\item We propose a deep neural network for variation transformation.
-Our FCN network is trained to learn the pixel variation and generate a new representation in a new feature space.
-We take advantage of the strong learning ability of FCN to learn an end-to-end representation of the pixel observation matrixes in a new space where the pixels can be easily classified to background and foreground.
-\end{itemize}
+% In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes. 
+In the DVTL model, 
+the sequence of pixels' observations is used to represent the variation and input into the network for learning,
+which encode both the intensity distribution and sequential information.
+%
+Then, a Fully Convolutinal Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space.
+%
+In particular,
+we take advantage of the strong learning ability of FCN to learn an end-to-end representation of the pixel observation matrixes in a new space where the pixels can be easily classified to background and foreground.
+%
+Benefited from the strong learning ability of FCN,
+proposed approach works well in diversely complex scenes adaptively.
+%
+Moreover,
+since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
+% 
+% 
+% 
+% \todo{This paragraph is too short! provide comprehensive details of our work!}
+% % The final prediction can be obtained by thresholding of the transformed variation. 
+% %Our contributions can be summarized as follows:
+% The contridbutions of proposed approach are shown as follows:
+% \begin{itemize}
+% \item We proposed the pixel observation matrix to describe the pixel variation, which encode both the intensity distribution and sequential information over time.
+%     The observation matrix is obtained by reshaping the vector of a pixel's historical observations, subtracted from the image stacks. 
+% \item We propose a deep neural network for variation transformation. 
+%     Our FCN network is trained to learn the pixel variation and generate a new representation in a new feature space. 
+% \end{itemize}
+% 
+%文章结构
 
-%文章结构
 %The outline of this paper is as follows: In Section II, we give a brief discussion about the early and recent relevant works. 
@@
 The proposed fully convolutional network is illustrated in \refsec{sec4}, followed by experiments and result comparison in \refsec{sec5} and conclude the paper in \refsec{sec6}.
-\todo{please revise this part by using command refsec}
+% \todo{please revise this part by using command refsec}
 
@@
 Zoran Zivkovic\cite{Zivkovic2004} extend the GMM through the use of recursive equations, where the parameters keep constantly updating and the number of components are adaptable to each pixel. 
+%你的ICME那篇里面也用过extend through the use of 这句话的啊。 这里的改进就是用了一些回归方程，我也从别的文章里看过的。
 %codebook
-Another popular algorithms in pixel based category are based on Codebook.
+Some other popular algorithms in pixel based category are based on Codebook. 
 In \cite{Kim2005}, Kim et al present the codebook method to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model.
@@
 To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold R(x), which depended on the pixel position and a background dynamics metric.
-%
 
+%提出其他方法的问题，指出他们的缺陷
 However, Those assumptions of pixels' independence are incorrect or inapplicable to many real-world scenes. 
-Hence they demonstrate a comparatively poor performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
-There is, in fact, a strong temporal coherence in image sequences that provides abundant hidden messages for the background model. 
-The proposed approach take advantage of the temporal coherence, and that is the reason that we have a relative better performance in challenging scenes.  
+There is, in fact, a strong temporal coherence in image sequences that contains abundant hidden clues for the background model. 
+In most cases, pixels-based methods are only concerned with pixels distribution, and ignore the order information of input frames by default.
+%提出我们的改进,我们认为像素在时序上是互相依赖的
+To address this shortcoming, we introduce a novel framework of variation transformation learing, which assumpt that there is a tight interdependence in pixel's historical observations.
+%所以我们把像素整合到一起
+In this case, pixel's historical observations are embedded in a piece of pixel variation and sorted in chronological order as a whole to enter our DPVTL model.
+%这样的优点在于保留了数据的完整性，保留了数据的时序相关性。
+The benefit of bringing together the observations is to ensure the data integrity and preserve the temporal coherence of our training data.
+And that guarantee us the ability to take advantage of the temporal coherence.
+%所以我们方法比基于像素的要好。
+Hence we demonstrate a comparatively better performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
 \todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
@@
 
+%讲其他方法的缺点，不能利用时序相关性，只是在pixel-based方法上添加了空间约束
 Unfortunately, most region-based methods are not capable to make use of the temporal coherence, since they are merely adding some spatial constrains to the pixels-based methods. 
-We also notice that some methods are involved with optical flow field, which can be viewed as a limited temproal coherence message. 
-However, optical flow methods have some shortcommings like the high computation complexity, moreover they are very sensitive to illumination changing. 
-Compared with them, the proposed approach are more powerful in capturing the structural background variation and more efficient in computation due to the application of deep learning.
+%有的方法结合了光流，也算利用了时序相关性
+But we also notice that some methods are involved with optical flow field, which can be viewed as a limited temporal coherence message. 
+%但是他们也有几个缺点
+However, optical flow methods have some shortcommings like the high computation complexity and the sensitivity to illumination changing. 
+%最重要的是，他们的时序相关性太有限了。所以对与其他方法，并没有明显的优势。
+Moreover, their temporal coherence information is very limited. For each frame, only a few of neighbor frames are taken into account when computing the optical flow.
+This probably explains why they have no significant improvement compared to their competitors.    
+%讲我们方法的不同以及优点
+%我们的输入有足量的时序信息。
+In the proposed approach, by contrast, we present the pixel matrix, which contains the pixel variation over a longer period of time, to ensure that our DPVTL model has sufficient temporal coherence information to feed.
+%此外，我们借助神经网络可以更有效地计算和捕捉这种时序相关性。
+Furthermore, the proposed approach are more powerful in capturing the structural background variation and more efficient in computation due to the application of deep learning.
+
 \todo{disccuss the adavantage of proposed work.}
@@
 \todo{Please cite more papers on this paragraph since our work belongs to this category. This paragraph should be the main part of this section.}
+%我也想多引用一些，本来就不多的嘛。。。
 The last category of background subtraction methods apply traditional machine learning or deep learning on different features for the background modeling.
@@
 %DBMF
+%skip结构就是skip结构啊！！就是说前基层的输出在输进下一层的同时，会跳过下一层，输入到更后面去。
 In \cite{Yang2018DBMF}, a FCN with the skip architecture is proposed for background modeling. 
-The authors also proposed a temproal approach to sample training images from the given video, thus providing the background model with limited temporal information.
+The authors also proposed a temporal approach to sample training images from the given video, thus providing the background model with limited temporal information.
 
+%以上方法的缺点主要在于，他们都是基于静态的图像特征训练的。抛弃了时序相关性。
 Above mentioned deep methods are based on the static images and static saliency characteristics. 
 As we've discussed earlier, their background models are trained with little or no temporal coherence involved.
-Different with their methods, with a relative simple structure of the network, the proposed approach is based on the time series modeling of each pixel.
-Hence the reliable performance of DVTL should be owing to the enhanced temporal coherence.
+%所以他们在处理物体突然运动的时候会存在问题。
+And that cause the problem when target objects are doing sudden movement, for example, starting a car and get it out of the parking lot. 
+%尽管他们用了很好的结构和技巧，但是仍然不能解决这个问题，如何去检测运动，而不是把潜在的运动物体全标记出来。
+Even though they have made a lot of progress with optimized network architechtures and training tricks, it is still an unsolved problem that how to detect the motion rather than mark out all the possible moving objects.
+%我们的不同在与输入
+Different with their methods, the input of our DPVTL model is not the origin images. Instead, we take the pixel variation as the input to preseve the temporal coherence between the pixels.
+%因为我们的方法是基于时序建模的，所以我们的模型可以学习一段时间内的运动。
+Now, since the proposed approach is based on the time series modeling of each pixel, our model can learn the patterns of motion over a period of time.
+%此外，因为我们的网络结构相对比较简单，所以取得的效果应该归功于时序相关性带来的辅助。
+In addition, Our FCN is implemented with a relative simple structure, hence the reliable performance of our DPVTL should be owing to the enhanced temporal coherence.
 
@@
 In this paper, we proposed a noval background subtraction approach based on deep learning and the variation transformation learning.
-The DPVTL model include a FCN network and a noval variation transformation learing framework, which allows us to efficiently combine the temproal coherence and distribution information of pixels over a long period of time.
+The DPVTL model include a FCN network and a noval variation transformation learing framework, which allows us to efficiently combine the temporal coherence and distribution information of pixels over a long period of time.
 Comparison with other traditional and deep learning methods shows that the DPVTL has good properties on several challenging scenes.

### 2018-08-12 draft.tex
spatial context

@@
 with the consideration that the observations of pixels are usually so hard to analyze due to the unpredictability and complexity of natural scenes,
-and a novel background subtraction method called Deep Variation Transformation (DVT) is proposed.
+and a novel background subtraction method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
 %
-In the DVT model,
+In the DPVTL model,
 the variation is represented by the sequence of pixels' observations and used as the input of the fully convolutional network.
@@
 In the proposed approach, by contrast, we present the pixel matrix, which contains the pixel variation over a longer period of time, to ensure that our DPVTL model has sufficient temporal coherence information to feed.
+We also combine the pixel variation with its spatial neighbors to revise our prediction.
 %此外，我们借助神经网络可以更有效地计算和捕捉这种时序相关性。
@@
 %
-Recent years, deep learning start to flourish in many fields, such as face recognition and natural language processing, significantly improving the state-of-the-art.
+Recent years, deep learning starts to flourish in many fields, such as face recognition and natural language processing, significantly improving the state-of-the-art.
 A novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck\cite{Braham2016deep}.
-They employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth, or alternatively, segmentation results coming from other background subtraction methods.
-Patches are extracted around a pixel, then they are feed into the network and compared with a threshold.
+They employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth, or alternatively, segmentation results from other background subtraction methods.
+Those patches are extracted around a pixel, then they are feed into the network and compared with a threshold.
 %
@@
 %我们的不同在与输入
-Different with their methods, the input of our DPVTL model is not the origin images. Instead, we take the pixel variation as the input to preseve the temporal coherence between the pixels.
+Different with their methods, the input of our DPVTL model is not the origin images or patches.
+Instead, we regard the pixel variation as a whole for the network training to preseve the temporal coherence between the pixels' historical observations.
 %因为我们的方法是基于时序建模的，所以我们的模型可以学习一段时间内的运动。
 Now, since the proposed approach is based on the time series modeling of each pixel, our model can learn the patterns of motion over a period of time.
-%此外，因为我们的网络结构相对比较简单，所以取得的效果应该归功于时序相关性带来的辅助。
-In addition, Our FCN is implemented with a relative simple structure, hence the reliable performance of our DPVTL should be owing to the enhanced temporal coherence.
+%此外，我们还将pixel variation 与其空间上的近邻连接起来，从而利用空间上下文信息。
+In addition, we also cascade the pixel variation with its spatial neighbors to take advantage of the spatial context. 
+%因为我们的网络结构相对比较简单，所以取得的效果应该归功于Variation Transformation 框架。
+Our FCN is implemented with a relative simple structure, hence the reliable performance of our DPVTL should be owing to the framework of variation transformation.
 
@@
 
+%背景检测的难点
 Background subtraction is essentially an binary classification in time sequence, where pixels in a video stream are separated into two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops).
@@
 
+%图例解释困难点
 To give an intuitive understanding of the pixel variations, we plot the historical observations and corresponding groundtruth of a single pixel in  \reffig{variation_chart}, with the X axis showing their range of variation and the Y axis representing the time.
@@
 
+%传统方法的问题
 Under ideal conditions like indoor videos, previous methods perform quite effectively, when distributions of background and foreground observations are remarkably different and the backgrounds are normally keeping static.
@@
 
+%图例说明可能面临的挑战
 For example, in \reffig{variation_chart}, it is noticeable that some foreground observations in blue line share the similarly value with background ones. 
@@
 In other words, despite knowing that pixels from the background share some common patterns of variation in a temporal sequence, we still let the order information of sequential images all go to waste.
+%为了解决这些问题，我们必须利用好时序相关性
 To alleviate this, order information of pixels must be taken in consideration. 
@@
 
-In this paper, a method of background subtraction based on variation transformation are proposed. 
+%variation transformation 介绍。
+In this paper, a novel framework of pixel variation transformation are proposed. %用framework代替method?
 Pixel observations are no longer considered independent of each other but regarded as a whole, which we call the pixel variation. 
@@
 After thresholding, we can easily get the labels of each observation. 
+%方法的好处是
 The benefits from variation transformation are evident and clearly seen. 
@@
 % 公式表达
-And the definition of region searching method $G(x,y)$ is shown as follows:
-\begin{equation}
-    G(x,y) =  \mathop{\argmin}_{}{ \lVert I_t(m,n) - I_b(x,y) \rVert_{1}  } \quad  m,n \in x,y \pm R,
-\end{equation}
-where $x$ and $y$ is the location of pixels. And $I_t$ is the current frame, where $t$ is the
-time index.
+%And the definition of region searching method $G(x,y)$ is shown as follows:
+%\begin{equation}
+%    G(x,y) =  \mathop{\argmin}_{}{ \lVert I_t(m,n) - I_b(x,y) \rVert_{1}  } \quad  m,n \in x,y \pm R,
+%\end{equation}
+
+%where $x$ and $y$ is the location of pixels. And $I_t$ is the current frame, where $t$ is the
+%time index.
 
@@
 In this section, we introduce the proposed approach that consists of a novel FCN network for background subtraction. 
-We explain the details of the procedures of pixel matrixes, which is a specific form of pixel variation, and the architecture of our network.
+We explain the details of the procedures of pixel matrixes, which is a specific form of the pixel variation, and the architecture of our network.
 
 The complete system is illustrated in \reffig{flow_chart}. 
-Firstly, we temporally sample the input and ground truth images to generalize the pixel variations, and reshape them into fixed-size matrixes and fed them into the network. 
+Firstly, we temporally sample the input and ground truth images to generalize the pixel variations, and reshape them into fixed-size matrixes and feed them into the network with its spatial neighbors.
 After reassembling the matrixes into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
@@
 
+% 第一步是对原视频进行采样
 Given different videos, the number of frames are generally different. 
@@
 \end{equation}
+
 \begin{equation}
@@
 \end{equation}
+
+% 解释采样的细节
 Where $I_t$ represent the frame $t$ of the given video. 
@@
 
+% 第二步提取Pixel variation
 In order to make use of the temporal information of pixel historical observations, we regard the sampled observations from a single pixel as a whole, namely the pixel variation. 
@@
 \end{equation}
+
 Where $P_t^m$ denotes the numerical value of pixel $m$ at frame $t$ in the chosen stack. 
@@
 
+% 第三步变成矩阵形式，解释为什么要把variation 变形
 Our intention is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. 
 However, vectors are not appropriate for the network training and learning. 
-Besides, we hope the pixel observations can be interacted with their further compatriots in temporal sequence. 
+Besides, we also hope the pixel observations can be interacted with their further compatriots in temporal sequence. 
 Thus we reshape the variations into pixel matrixes as the input of our network. 
-A sample of pixel matrix $H$ is like this:
+A sample of pixel matrix $H^m$ is like this:
 \begin{equation}
-H=P_{i+j*d}=\begin{bmatrix}
- P_1& P_2  &\dots  &P_d \\ 
+H^m=P^m_{i+j*d}=\begin{bmatrix}
+ P^m_1& P^m_2  &\dots  &P^m_d \\ 
 \vdots &  &  &\vdots \\ 
- P_{1+(d-1)d}& \dots & \dots & P_D
-\end{bmatrix},\quad d^2=D,
+ P^m_{1+(d-1)d}& \dots & \dots & P^m_n
+\end{bmatrix},\quad d^2=n,
 \end{equation}
-Pixel observations are put into the $d*d$ matrix according to the order of top to bottom and left to right. 
+
+Pixel observations are put into the $d\times d$ matrix according to the order of top to bottom and left to right. 
 The parameter $i$ and $j$ represent the column and row respectively. 
-And the parameter $D$ is the total frame length of a variation. 
+And the parameter $n$ is the total frame length of a variation, as the same as the observation sequences. 
 To put it from another way, pixel matrix is just a specific form of the pixel variation. 
@@
 
+%第四步空间近邻随机采样。
+It is generally accepted that, neighboring background pixels share a similar temporal variation. 
+In order to benefit from the spatial context, we cascade the pixel matrix with 3 neighboring pixel matrixes randomly selected in 8 nearest neighbors, as shown in \reffig{flow_chart}. 
+Now, we have the input of our network, which size is $d\times d\times 4$.
+
 In the previous steps, videos are broken down into pixel matrixes which containing abundant background information. 
-Next, the groundtruth matrixes are obtained in the same way. 
+Next, the groundtruth matrixes are obtained in the same way, except the cascading process. 
 Both of them are put into the network for the training. 
-However, the size of the input will decreased after the network computing. 
-In order to make output the same size as input, we borrowed ideas from Image semantic segmentation, which is doing padding to the input before the training. 
+However, the size of the input will decreased in the forward computation. 
+In order to make output the same size as input, we borrowed ideas from Image Semantic Segmentation \cite{Shelhamer2017fcn}, which is doing padding to the input before the training. 
 After the forward computing, variations are transformed in a new space where they can be easily classified by thresholding. 
@@
 \end{equation}
+
 Where, $H_p$ denotes the output of network, which we call the prediction matrix, the forward computation of network is represented by $L$, and $E_x$ denotes the symmetric padding of pixel matrix where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel matrix $H$.
@@
   0,  \quad otherwise   \\
-\end{cases}.
+\end{cases},
 \end{equation}
+
 \begin{equation}
@@
 \end{equation}
+
 After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery. 
@@
 There is one more point I ought to touch on, that since the feature maps are no longer need to be converted into vectors, spatial information can be retained . 
-The last but not the least, FCNs have been used in sematic segmentation and researchers found FCNs have a strong learning ability which won’t lost to the traditional ones. 
-Meanwhile, it’s also a high efficient computation model.
+The last but not the least, FCNs have been used in sematic segmentation and researchers found FCNs have a strong learning ability which won't lost to the traditional ones. 
+Meanwhile, it's also a high efficient computation model.
 
@@
 %
+
 Where TP, FP, and FN are true positives, false positives, and false negatives respectively, computed in pixels of all test frames for each video.
@@
 Due to the paper length, several typical videos are selected for the qualitative comparisons as well as the discussion. 
-In the dynamic background scene, the video “canoe” is a typically challenging video which includes a large area of water rippling. 
+In the dynamic background scene, the video "canoe" is a typically challenging video which includes a large area of water rippling. 
 The main challenge comes from the dynamic background, in which it is so hard to describe the background by a single image. 
@@
 Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even the deep learning based algorithm is suffering from the detection of the boat shape.
-In contrast, the proposed approach performed superior than others in this scene, since the essence of background subtraction is considered as a binary classification of pixels’ observation in time sequence.
+In contrast, the proposed approach performed superior than others in this scene, since the essence of background subtraction is considered as a binary classification of pixels' observation in time sequence.
 Based on this insight, the FCN network focuses on learning the patterns of the pixel variation rather than a static background image, and proposed approach achieves promising performance in the canoe video.
@@
 \end{figure*}
-As for the case of shadow scene, ‘peopleInShade’ is a typical example with prevalent hard and soft shadows. 
+
+As for the case of shadow scene, "peopleInShade" is a typical example with prevalent hard and soft shadows. 
 In the traditional approaches, these shadow regions are usually segmented as foreground since it is also moving with the objects. 
 Therefore, traditional methods like the PAWCS, the WeSamBE and the SharedModel falsely segments part of shadows as moving objects. 
-In addition, the foreground provided by the UBSS is incomplete on the part of the pedestrian’s body due to the interference of shades, which can be owing to the severe dependency of texture features. 
+In addition, the foreground provided by the UBSS is incomplete on the part of the pedestrian's body due to the interference of shades, which can be owing to the severe dependency of texture features. 
 Whereas, the DeepBS performs well in this video benefited from the utilization of CNN. 
 However, the shape of pedestrians are slightly deformed as the result of their matrix-wise processing of CNN. 
-In contrast, derived from the fact that our DPVL focus on learning the pattern of pixels’ variation in the shadow regions, proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.
+In contrast, derived from the fact that our DPVL focus on learning the pattern of pixels' variation in the shadow regions, proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.
 
-In the video “corridor” among the Thermal scene, there is no color information since the videos are obtained through a Thermal camera. 
+In the video "corridor" among the Thermal scene, there is no color information since the videos are obtained through a Thermal camera. 
 Moreover, the moving objects in these videos are exceedingly fuzzy and indistinct, which is the main challenge of this category. 
@@
 However, due to the dependency of edge feature, a small object were missed in the detection result. 
-Fortunately, the proposed approach focus on the pattern of pixels’ variation, which should be theoretically effective even in the observation without the color information. 
+Fortunately, the proposed approach focus on the pattern of pixels' variation, which should be theoretically effective even in the observation without the color information. 
 Consequently, our DPVL performed much better than compared algorithms, with the situation that most parts of shadow are removed and the segmentation results are more accurate.
@@
 Videos      & baseline & dyna.bg & cam.jitter & int.obj.m & shadow & thermal & bad.weat & low f.rate & night vid. & PTZ    & turbul. & overall \\ \hline
-DeepBS\cite{Babaee2017deep}      & 0.9580   & 0.8761  & \textbf{0.8990}     & 0.6097    & 0.9304 & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & \textbf{0.8993}  & 0.7458  \\
+DeepBS\cite{Babaee2017deep}      & 0.9580   & 0.8761  & \textbf{0.8990}     & 0.6097    & \textbf{0.9304} & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & 0.8993  & 0.7458  \\
 IUTIS-5\cite{Bianco2017TEC}     & 0.9567   & 0.8902  & 0.8332     & 0.7296    & 0.9084 & 0.8303  & 0.8289   & \textbf{0.7911}     & 0.5132     & 0.4703 & 0.8507  & 0.7717  \\
@@
 RMoG\cite{Varadarajan2013}        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
-Ours        & \textbf{0.9668}   & 0.8639  & 0.8446     & \textbf{0.9181}    & \textbf{0.9390} & \textbf{0.9268}  & \textbf{0.9265}   & 0.7338     & \textbf{0.7306}     & \textbf{0.5845} & 0.8761  & \textbf{0.8504} \\ \hline
+DPVTL        & \textbf{0.9757}   & 0.9303  & 0.8850     & \textbf{0.9322}    & 0.9274 & \textbf{0.9348}  & \textbf{0.8659}   & 0.7489     & \textbf{0.7529}     & \textbf{0.5836} & \textbf{0.9005}  & \textbf{0.8636} \\ \hline
 \end{tabular}
@@
 DBMF\cite{Yang2018DBMF}     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
-ours     & \textbf{0.9775}  & \textbf{0.9565} & \textbf{0.9652}      & \textbf{0.9681}   & \textbf{0.9157} & \textbf{0.8943} & \textbf{0.9462}  \\ \hline
+DPVTL     & \textbf{0.9827}  & \textbf{0.9719} & \textbf{0.9729}      & \textbf{0.9753}   & \textbf{0.9269} & \textbf{0.9103} & \textbf{0.9567}  \\ \hline
 \end{tabular}

### 2018-08-14 draft.tex
update

@@
 In the DVTL model, 
-the sequence of pixels' observations is used to represent the variation and input into the network for learning,
+the sequence of pixel observations is used to represent the variation and input into the network for learning,
 which encode both the intensity distribution and sequential information.
@@
 In particular,
-we take advantage of the strong learning ability of FCN to learn an end-to-end representation of the pixel observation matrixes in a new space where the pixels can be easily classified to background and foreground.
+we take advantage of the strong learning ability of FCN to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
 %
@@
 %
-Moreover,
-since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
+%Moreover,
+%since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
 % 
@@
 And each of them is of fixed length $n$. 
-It is notable that the quantity of observation sequences is exactly the resolution of the given video, which means an abundance of training data can be obtained with just one image stack.
+It is notable that the quantity of observation sequences is exactly the resolution of the given video, which means an abundance of trainiing data can be obtained with just one image stack. 
+since the pixel sequences are extracted from individual pixel positions, a large number of pixel matrixes may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
 

### 2018-08-14 draft.tex
..

@@
 And each of them is of fixed length $n$. 
-It is notable that the quantity of observation sequences is exactly the resolution of the given video, which means an abundance of trainiing data can be obtained with just one image stack. 
-since the pixel sequences are extracted from individual pixel positions, a large number of pixel matrixes may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
+It is notable that observation sequences are extracted from individual pixel positions, which promises that sufficient training data can be obtained with only one image stack.
 
@@
 
-Pixel observations are put into the $d\times d$ matrix according to the order of top to bottom and left to right. 
+Pixel variations are put into the $d\times d$ matrix according to the order of top to bottom and left to right. 
 The parameter $i$ and $j$ represent the column and row respectively. 
 And the parameter $n$ is the total frame length of a variation, as the same as the observation sequences. 
-To put it from another way, pixel matrix is just a specific form of the pixel variation. 
-Although the pixel matrix and the observation sequence belong to different forms of the pixel variation, they are formed of the same components, and share the common temporal information from the pixel variation.
+To put it from another way, the pixel matrix is just a specific form of the pixel variation. 
+Although the observation matrix and the observation sequence belong to different forms of the pixel variation, they consist of the same components, and share the common temporal information from the pixel variation.
 Since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack.

### 2018-08-15 draft.tex
公式

@@
 %
-Then, a Fully Convolutinal Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space.
+Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space.
 %
@@
 ViBe is a sample based method, which consists of pixel samples from the video stream.
-Each pixel in the current frame is compared with N pixel samples from the corresponding background model.
-A pixel is labeled as the foreground only when there exist at least K samples with a distance to itself within a certain range R.
+Each pixel in the current frame is compared with N pixel samples from the corresponding background model and labeled as the foreground when there exist at least K samples with a distance to itself within a certain range R.
 %PBAS
@@
 \label{sec3}
-In this section, we will elaborate on the motivation of the proposed approach and how does the variation transformation works in background subtraction.
+In this section, we will elaborate on the motivation of the proposed approach and how does the variation transformation work in background subtraction.
 
@@
 %第四步空间近邻随机采样。
-It is generally accepted that, neighboring background pixels share a similar temporal variation. 
-In order to benefit from the spatial context, we cascade the pixel matrix with 3 neighboring pixel matrixes randomly selected in 8 nearest neighbors, as shown in \reffig{flow_chart}. 
-Now, we have the input of our network, which size is $d\times d\times 4$.
+It is generally accepted that neighboring background pixels share a similar temporal variation.
+In other words, there are some clues hidden in pixels' spatial neighbors. 
+In order to benefit from the spatial context, we concatenate the pixel matrix with 3 neighboring pixel matrixes, denoted as $SM_1$, $SM_2$ and $SM_3$ respectively.
+They are randomly selected in 8 nearest neighbors. 
+The input matrix of our network is defined as:
+\begin{equation}
+H = C(H^m, SM_1, SM_2, SM_3),
+\end{equation}
 
-In the previous steps, videos are broken down into pixel matrixes which containing abundant background information. 
-Next, the groundtruth matrixes are obtained in the same way, except the cascading process. 
+Where $C$ represents the concatenating process on the third dimension.
+And $H$ is the input matrix of our network, which size is $d\times d\times 4$.
+
+In the previous steps, videos are broken down into pixel matrixes which contain abundant background information. 
+Next, the groundtruth matrixes are obtained in the same way, except the concatenating process. 
 Both of them are put into the network for the training. 
 However, the size of the input will decreased in the forward computation. 
-In order to make output the same size as input, we borrowed ideas from Image Semantic Segmentation \cite{Shelhamer2017fcn}, which is doing padding to the input before the training. 
+In order to make output the same size as input, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input matribxes before the training. 
 After the forward computing, variations are transformed in a new space where they can be easily classified by thresholding. 
-The new representation of input pixel variation is defined as:
+The transformed pixel variation is defined as:
 \begin{equation}
@@
 
-Where, $H_p$ denotes the output of network, which we call the prediction matrix, the forward computation of network is represented by $L$, and $E_x$ denotes the symmetric padding of pixel matrix where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel matrix $H$.
+Where, $H_p$ denotes the output of network, which we call the prediction matrix, the forward computation of network is represented by $\mathcal L$, and $E_x$ denotes the symmetric padding of pixel matrix where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel matrix $H$.
 Another advantage of symmetric padding is that the order information still remains.

### 2018-08-16 draft.tex
revised the abstract

@@
 %
-Previous work analyzes the variation of pixels for background subtraction which is generally considered as the binary classification of pixels in time sequence.
+Previous approaches to background subtraction generally analyzes the variation of pixels' observation.
+%for background subtraction.
 %
-In this paper, we focus on transforming the variation into another space where the pixels are easier classified,
-with the consideration that the observations of pixels are usually so hard to analyze due to the unpredictability and complexity of natural scenes,
+%Background subtraction is generally considered as the binary classification of pixels' observations in time sequence,
+%and preivous work 
+%
+%Previous work analyzes the variation of pixels for background subtraction which is generally considered as the binary classification of pixels in time sequence.
+%
+%
+In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
 and a novel background subtraction method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
 %
-In the DPVTL model,
+% 
+%     
+%     
+%     another space where the observations of pixels are easier classified,
+% with the motivation to  that there is difference between the patterns of variation produced by the moving objects and the background.
+% %
+% We also put forward a novel background subtraction method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
+% %
+% with the consideration that the observations of pixels are usually so hard to analyze due to the unpredictability and complexity of natural scenes,
+%and a novel background subtraction method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
+%
+In particular,
 the variation is represented by the sequence of pixels' observations and used as the input of the fully convolutional network.
 %
-The fully convolutional network is trained to learn the pattern of variation for transformation with the output leaded by grounthtruth data.
+Then, the fully convolutional network is trained to learn the pattern of variation for the transformation followed by a liner classifier for labeling the pixels as foreground or background.
+%    with the supervision leaded by grounthtruth data.
 % XXX 这句话还是有点问题
-Benefied from the ingenious utilization of FCN leading by our clear congnition of essence about background subtractoin problem,
+Benefied from the ingenious utilization of deep learning network leading by our clear congnition of essence about background subtractoin problem,
 proposed approached adaptively generate superior peroformances in diversly complex scenes.

### 2018-08-20 draft.tex
re result

@@
 In other words, there are some clues hidden in pixels' spatial neighbors. 
-In order to benefit from the spatial context, we concatenate the pixel matrix with 3 neighboring pixel matrixes, denoted as $SM_1$, $SM_2$ and $SM_3$ respectively.
+In order to benefit from the spatial context, we concatenate the pixel matrix with 2 neighboring pixel matrixes, denoted as $SM_1$, $SM_2$ and $SM_3$ respectively.
 They are randomly selected in 8 nearest neighbors. 
@@
 \begin{equation}
-H = C(H^m, SM_1, SM_2, SM_3),
+H = C(H^m, SM_1, SM_2),
 \end{equation}
@@
 Where $C$ represents the concatenating process on the third dimension.
-And $H$ is the input matrix of our network, which size is $d\times d\times 4$.
+And $H$ is the input matrix of our network, which size is $d\times d\times 3$.
 
@@
 The structure of our FCN for background modeling is shown in \reffig{flow_chart}. 
-The proposed FCN contains 5 convolutional layers, 2 pool layers and a convolutional layer which have a filter size of $1*1$. 
+The proposed FCN contains 5 convolutional layers and a convolutional layer which have a filter size of $1*1$. 
 We use the Rectified Linear Unit (ReLU) as activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
@@
 Videos      & baseline & dyna.bg & cam.jitter & int.obj.m & shadow & thermal & bad.weat & low f.rate & night vid. & PTZ    & turbul. & overall \\ \hline
-DeepBS\cite{Babaee2017deep}      & 0.9580   & 0.8761  & \textbf{0.8990}     & 0.6097    & \textbf{0.9304} & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & 0.8993  & 0.7458  \\
+DeepBS\cite{Babaee2017deep}      & 0.9580   & 0.8761  & 0.8990     & 0.6097    & 0.9304 & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & 0.8993  & 0.7458  \\
 IUTIS-5\cite{Bianco2017TEC}     & 0.9567   & 0.8902  & 0.8332     & 0.7296    & 0.9084 & 0.8303  & 0.8289   & \textbf{0.7911}     & 0.5132     & 0.4703 & 0.8507  & 0.7717  \\
@@
 RMoG\cite{Varadarajan2013}        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
-DPVTL        & \textbf{0.9757}   & 0.9303  & 0.8850     & \textbf{0.9322}    & 0.9274 & \textbf{0.9348}  & \textbf{0.8659}   & 0.7489     & \textbf{0.7529}     & \textbf{0.5836} & \textbf{0.9005}  & \textbf{0.8636} \\ \hline
+DPVTL        & \textbf{0.9811}   & 0.9329  & \textbf{0.9014}     & \textbf{0.9595}    & \textbf{0.9467} & \textbf{0.9479}  & \textbf{0.8780}   & 0.7818     & \textbf{0.7737}     & \textbf{0.5957} & \textbf{0.9034}  & \textbf{0.8789} \\ \hline
 \end{tabular}
@@
 DBMF\cite{Yang2018DBMF}     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
-DPVTL     & \textbf{0.9827}  & \textbf{0.9719} & \textbf{0.9729}      & \textbf{0.9753}   & \textbf{0.9269} & \textbf{0.9103} & \textbf{0.9567}  \\ \hline
+DPVTL     & \textbf{0.9888}  & \textbf{0.9819} & \textbf{0.9728}      & \textbf{0.9808}   & \textbf{0.9394} & \textbf{0.9333} & \textbf{0.9662}  \\ \hline
 \end{tabular}
@@
 Methods  & MOG2\cite{ZIVKOVIC2006773} & FCI\cite{Baf2008FCI}  & LBA-SOM\cite{LBA-SOM2008} & PBAS & SuBSENSE & ML-BGS\cite{ML-BGS2007} & DECOLOR\cite{DECOLOR2013}       & COROLA\cite{SHAKERI201628} & FWFC\cite{Li2018CAMO}          & Ours          \\ \hline
-Video 1  & 0.79 & 0.88 & 0.8     & 0.9  & 0.89     & 0.89   & 0.92          & 0.8    & \textbf{0.94} & \textbf{0.94} \\
+Video 1  & 0.79 & 0.88 & 0.8     & 0.9  & 0.89     & 0.89   & 0.92          & 0.8    & 0.94 & \textbf{0.96} \\
 Video 2  & 0.82 & 0.79 & 0.8     & 0.82 & 0.88     & 0.8    & 0.83          & 0.58   & 0.96          & \textbf{0.98} \\
-Video 3  & 0.88 & 0.86 & 0.85    & 0.91 & 0.9      & 0.8    & 0.9           & 0.82   & \textbf{0.94} & \textbf{0.94} \\
-Video 4  & 0.89 & 0.9  & 0.76    & 0.93 & 0.78     & 0.88   & 0.95          & 0.87   & 0.94          & \textbf{0.97} \\
-Video 5  & 0.84 & 0.86 & 0.82    & 0.83 & 0.82     & 0.8    & 0.82          & 0.75   & 0.91          & \textbf{0.97} \\
-Video 6  & 0.93 & 0.87 & 0.77    & 0.95 & 0.92     & 0.95   & \textbf{0.97} & 0.72   & 0.94          & 0.96          \\
+Video 3  & 0.88 & 0.86 & 0.85    & 0.91 & 0.9      & 0.8    & 0.9           & 0.82   & 0.94 & \textbf{0.95} \\
+Video 4  & 0.89 & 0.9  & 0.76    & 0.93 & 0.78     & 0.88   & 0.95          & 0.87   & 0.94          & \textbf{0.98} \\
+Video 5  & 0.84 & 0.86 & 0.82    & 0.83 & 0.82     & 0.8    & 0.82          & 0.75   & 0.91          & \textbf{0.98} \\
+Video 6  & 0.93 & 0.87 & 0.77    & 0.95 & 0.92     & 0.95   & 0.97	      & 0.72   & 0.94          & \textbf{0.98}  \\
 Video 7  & 0.76 & 0.83 & 0.88    & 0.91 & 0.87     & 0.79   & 0.91          & 0.83   & 0.96          & \textbf{0.99} \\
-Video 8  & 0.83 & 0.87 & 0.85    & 0.87 & 0.93     & 0.86   & 0.86          & 0.68   & 0.96          & \textbf{0.98} \\
+Video 8  & 0.83 & 0.87 & 0.85    & 0.87 & 0.93     & 0.86   & 0.86          & 0.68   & \textbf{0.96}          & \textbf{0.96} \\
 Video 9  & 0.89 & 0.9  & 0.87    & 0.84 & 0.92     & 0.87   & 0.86          & 0.78   & 0.88          & \textbf{0.99} \\
@@
 More specifically, our FCN network is random initialized. 
-We train the network with mini-batches of size 100, a learning rate $α = 1 ∗ 10^{−3}$ over 20 epochs. 
+We train the network with mini-batches of size 200, a learning rate $α = 1 ∗ 10^{−3}$ over 20 epochs. 
 The last threshold $R$ is set to 0.6.

### 2018-08-21 draft.tex
n

@@
 \begin{document}
-\title{Background Subtraction via Deep Variation Transformation}
+\title{foreground detection via Deep Variation Transformation}
 
@@
 %
-Previous approaches to background subtraction generally analyzes the variation of pixels' observation.
-%for background subtraction.
+% 你这里的说法不对啊，原来的方法关注的是像素值的分布，我们关注的是像素值的变动。这是我们之间的区别啊!
+% 运动检测的已有方法主要关注于像素值的分布。
+Previous approaches to foreground detection generally focus on the distribution of pixel observations.
+% 本文中，我们分析了像素的变动，并提出了DPVTL方法。
+% In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
+In this paper, we analyze the variation of pixel observations, and a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
+% 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
+A fully convolutional network(FCN) is applied to find a transformation for pixel variations, which guarantees the linear separability of transformed pixels.
+% 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
+In particular,
+the pixel variation is represented by the sequence of pixel observations and used as the input of the FCN.
+% 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
+Then, the FCN is trained to learn the pattern of pixel variations for the transformation, followed by a liner classifier for labeling the pixels as foreground or background.
 %    
-%Background subtraction is generally considered as the binary classification of pixels' observations in time sequence,
-%and preivous work 
-%
-%Previous work analyzes the variation of pixels for background subtraction which is generally considered as the binary classification of pixels in time sequence.
-%
-%
-In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
-and a novel background subtraction method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
-%
-% 
-%     
-%     
-%     another space where the observations of pixels are easier classified,
-% with the motivation to  that there is difference between the patterns of variation produced by the moving objects and the background.
-% %
-% We also put forward a novel background subtraction method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
-% %
-% with the consideration that the observations of pixels are usually so hard to analyze due to the unpredictability and complexity of natural scenes,
-%and a novel background subtraction method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
-%
-In particular,
-the variation is represented by the sequence of pixels' observations and used as the input of the fully convolutional network.
-%
-Then, the fully convolutional network is trained to learn the pattern of variation for the transformation followed by a liner classifier for labeling the pixels as foreground or background.
-%    with the supervision leaded by grounthtruth data.
 % XXX 这句话还是有点问题
-Benefied from the ingenious utilization of deep learning network leading by our clear congnition of essence about background subtractoin problem,
+% 这句话我也没看懂。。。
+Benefied from the ingenious utilization of deep learning network leading by our clear cognition of essence about background subtractoin problem,
 proposed approached adaptively generate superior peroformances in diversly complex scenes.
@@
 %
-% We also put
-% forward a novel background subtraction framework called the
-% Integration of Foreground and Background (IFB) cues.
-% % a video stream. 
-% %之前方法 下一句用的focus on加ing，这就用ed，形成对比
-% % Previous works generally proposed the artificial model with the utilization of lowlevel or hand-crafted features to analyze the variation of pixels' observation.
-% Previous work generally analyze the variation of pixels' observation with the u/cygdrive/c/Users/Ray/Downloads/3.iebktilization of hand-crafted features.
-%     %in time sequence.
-% % 为什么之前方法会失败
-% However, due to the complexity and diversity of nature,
-% the variation of observations becomes so hard to classify by hand-crafted features.
-%     %in complexly natural scenes.
-% %我们的改进
-% In this paper, we focus on transforming the obserations sequence into another easier classfied space,
-% and a novel background subtraction method based on Deep Variation Transformation (DVT) is proposed.
-% % XXX 为什么是networks，不是network呢？
-% In the DVT model,
-% the fully convolutional network (FCN) is untlized to transform the sequence of pixels' observations into a new representation of pixels' observations with more obvious features for classfication.
-% %
-% In particlar, 
-% a the variation of observation represented by pixel sequence is reshaped into a image patch as the input of FCN network.
-% %
-% Then, the output of network is classfied and reverted to the corresponding sequence for the binary classfication of oberservations' variation.
-% %
-% Benefied from the ingenious utilization of FCN network leading by our clear congnition of essence about background subtractoin problem,
-% proposed approached adaptively generate superior peroformances in diversly complex scenes.
-% %
-% Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
-% 
-% 
-% 
-% videos are divided into fixed length image stacks by temporal sampling. 
-%     Next, image stacks is broken down into pixel observation matrixes as the input of the FCN to learn the patterns of pixel variation. 
-%     Each of the pixel matrixes contains a piece of temporal information about pixel variation over a period of time.  
-% The architecture of our FCN is devised from the semantic segmentation problem. 
-% %效果
-% Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ observations. 
-%     Compared with some state-of-the-art methods, both deep learning and traditional methods, the proposed approach outperform its conventional counterparts significantly owing to the utilizing of temporal information.
 \end{abstract}
@@
 \begin{IEEEkeywords} 
-    Background Subtraction, Feature Transformation, Deep Learning,
+    foreground detection, Feature Transformation, Deep Learning,
 \end{IEEEkeywords}
@@
 %背景检测的背景介绍
-Background subtraction as a fundamental problem in computer vision\ \cite{Bouwmans201431} has been discussed over decades with the increasing number of cameras,
+Foreground detection as a fundamental problem in computer vision\ \cite{Bouwmans201431} has been discussed over decades with the increasing number of cameras,
 which is widely used as the pre-processing step of video processing \cite{Barnich2011_2011_TIP}.
-% which can help us efficiently mark the region of interest,
-% thus saving us huge amount of computing resources\ \cite{Barnich2011_2011_TIP}.
-%\todo{cited an article to support this sentence.}
+Typically, it is recognized as a binary classification task that assigns each pixel in the video stream with a label, 
+for either belonging to the background or foreground scene.
 % 现有的方法在简单场景中效果很好了
@@
 % 传统的方法是怎么做的，有什么问题
-Traditioanlly, background subtraction algorithms focus on anaylsing the pixels' variation for background subtraction,
-since the background subtraction is typically recognized as a binary classification that assigns each pixel in a video sequence with a label, 
-for either belonging to the background or foreground scene.
-% 总而言之，background subtraction依然有很多问题
+%
+% 8.21 Ren: 你原来讲传统做法的时候是说它们关注与像素的变动，这不对啊，它们明明关注的是像素的分布，我们才更注重于变动。
+% 8.21 Ren: 还有我看有人说，论文里面不用加's 可以直接名词拼接，就像这样 pixel variation.
+F.
+名词修饰：在学术文章中，很多时候会用到直接用名词做修饰，而不用’s 或 ……of …… 的形式。常见的这类词有：reaction rate；reaction rate constant；reaction temperature；reaction condition  molecular weight distribution……
+%
+Traditionally, foreground detection algorithms focus on anaylsing the pixel distribution, establishing background models with statistical methods such as GMM and KDE.
+% 总而言之，foreground detection依然有很多问题
+% 8.21 Ren: 这里有个however,上上句也有个however.......怎么搞啊？
+% 8.21 Ren: 改到这里，不知道怎么改了，先更你确定一下吧，variation 跟 distribution 有没有区别？我的理解是variation就是有时间顺序的，之前的方法没有考虑道时间顺序性，所以就不能叫做variation.只能叫distribution.
+% 8.21 Ren  我觉得我们应该确定的是，传统统计学的方法只关注数据的分布概率，而我们更多考虑的是数据在时序上的变动。
+% 8.21 Ren  因为这一段跟你的理解有冲突，所以先商量后再改吧。
 However, due to the unpredictability and complexity of the pixels' variation in natural scenes,
-the variation becomes so unordered which is hard to be analyzed for background subtraction.
+the variation becomes so unordered which is hard to be analyzed for foreground detection.
 
@@
 % transformatin 之后，就很容易分类了，然后这就是我们的方法的核心了
-Based on this motivation, the Deep Variation Transformation model for background subtraction is proposed.
+Based on this motivation, the Deep Variation Transformation model for foreground detection is proposed.
 % 
@@
 % Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
-% However, background subtraction is still unsolved because of the complexity and the diversity of natural scenes.
+% However, foreground detection is still unsolved because of the complexity and the diversity of natural scenes.
 % There are many forms of natrual scenes, for example, camera jitter, dynamic background, bad weather, illumination changing, intermittent object motion\cite{CDN2014}.
@@
 % XXX 一句话，换一行！！！
-% In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes. 
+% In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for foreground detection in diversely natural scenes. 
 In the DVTL model, 
@@
 %
-Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space.
+Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantees the linear separability of transformed pixel variation generated by mapping in a new space.
 %
@@
 %\cite{Bouwmans2014}
-Over the last few decades, background subtraction has been well studied. Meanwhile, a huge number of background modeling methods have been proposed. 
+Over the last few decades, foreground detection has been well studied. Meanwhile, a huge number of background modeling methods have been proposed. 
 These methods can be broadly categorized into pixels-based, region-based and Learning-based methods.
@@
 %我也想多引用一些，本来就不多的嘛。。。
-The last category of background subtraction methods apply traditional machine learning or deep learning on different features for the background modeling.
+The last category of foreground detection methods apply traditional machine learning or deep learning on different features for the background modeling.
 
@@
 Recent years, deep learning starts to flourish in many fields, such as face recognition and natural language processing, significantly improving the state-of-the-art.
-A novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck\cite{Braham2016deep}.
-They employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth, or alternatively, segmentation results from other background subtraction methods.
+A novel approach for foreground detection with the use of CNN was proposed by Braham and Droogenbroeck\cite{Braham2016deep}.
+They employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth, or alternatively, segmentation results from other foreground detection methods.
 Those patches are extracted around a pixel, then they are feed into the network and compared with a threshold.
@@
 In \cite{wang2016PRL}, Wang et al.
-tried a CNN architecture combined with a Cascade model for segmentation in Background subtraction.
+tried a CNN architecture combined with a Cascade model for segmentation in foreground detection.
 Given 200 labelled images as training set, their model performed excellently in dataset2014.
@@
 Babaee et al.
-\cite{Babaee2017deep} present a novel CNN for background subtraction.
+\cite{Babaee2017deep} present a novel CNN for foreground detection.
 They also combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm, which is able to adaptively update the parameters used in the background model based on the motion changes in video stream.
@@
 \label{sec3}
-In this section, we will elaborate on the motivation of the proposed approach and how does the variation transformation work in background subtraction.
+In this section, we will elaborate on the motivation of the proposed approach and how does the variation transformation work in foreground detection.
 
 %背景检测的难点
-Background subtraction is essentially an binary classification in time sequence, where pixels in a video stream are separated into two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops).
+foreground detection is essentially an binary classification in time sequence, where pixels in a video stream are separated into two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops).
 In most cases, if we print out the historical observations of a single pixel, it is not hard to see that they usually keep their stability when belonging to the background. 
@@
 The green one, which we call the transformed variation curve, is made of the outputs of the proposed approach. 
-In practice, background subtraction is to produce a prediction curve, which is as near as possible to the groundtruth carve, by given the pixel variation carve.
+In practice, foreground detection is to produce a prediction curve, which is as near as possible to the groundtruth carve, by given the pixel variation carve.
 
@@
 %me
-\section{BACKGROUND SUBTRACTION VIA DEEP VARIATION TRANSFORMATION}
+\section{foreground detection VIA DEEP VARIATION TRANSFORMATION}
 \label{sec4}
-In this section, we introduce the proposed approach that consists of a novel FCN network for background subtraction. 
+In this section, we introduce the proposed approach that consists of a novel FCN network for foreground detection. 
 We explain the details of the procedures of pixel matrixes, which is a specific form of the pixel variation, and the architecture of our network.
@@
 After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery. 
-And the major contribution is that we demonstrate the effectiveness of temporal information in background subtraction.
+And the major contribution is that we demonstrate the effectiveness of temporal information in foreground detection.
 
@@
 In this section, we ran comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW. 
-The CDnet is the largest dataset for background subtraction so far as we are aware, containing 11 categories with several complexly challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
+The CDnet is the largest dataset for foreground detection so far as we are aware, containing 11 categories with several complexly challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
 The CAMO-UOW is another challenging benchmark which contains 10 high resolution videos. 
@@
 
-The proposed approach is compared with several existing traditional state-of-the-art background subtraction algorithms, including the IUTIS-5\cite{Bianco2017TEC}, the SuBSENSE\cite{St-Charles2015SuBSENSE}, the WeSamBE\cite{Jiang2017WeSamBE}, sharable GMM the SharedModel\cite{Chen2015SharedModel}, word-dictionaries-based method the PAWCS\cite{Charles2015PAWCS}, the SemanticBGS\cite{Braham2017Semantic}, the AAPSA\cite{RAMIREZALONSO2016990}, etc.
+The proposed approach is compared with several existing traditional state-of-the-art foreground detection algorithms, including the IUTIS-5\cite{Bianco2017TEC}, the SuBSENSE\cite{St-Charles2015SuBSENSE}, the WeSamBE\cite{Jiang2017WeSamBE}, sharable GMM the SharedModel\cite{Chen2015SharedModel}, word-dictionaries-based method the PAWCS\cite{Charles2015PAWCS}, the SemanticBGS\cite{Braham2017Semantic}, the AAPSA\cite{RAMIREZALONSO2016990}, etc.
 Moreover, two deep learning based algorithms are also compared with the proposed approach, which include DeepBS\cite{Babaee2017deep}, and DBMF\cite{Yang2018DBMF}. 
@@
 During the comparison, the F-measure(Fm) has been used for evaluation. 
-The Fm is a general international standard in background subtraction which measures the segmentation accuracy by considering both the recall and the precision. 
+The Fm is a general international standard in foreground detection which measures the segmentation accuracy by considering both the recall and the precision. 
 The definition of Fm is shown as follows:
@@
 The main challenge comes from the dynamic background, in which it is so hard to describe the background by a single image. 
-In this condition, since the traditional background subtraction method such as the SharedModel and the WeSamBE do not have the enough ability to describe the complex dynamically background, they are fail to detect the people on the boat, as shown in the \reffig{results_chart}.
+In this condition, since the traditional foreground detection method such as the SharedModel and the WeSamBE do not have the enough ability to describe the complex dynamically background, they are fail to detect the people on the boat, as shown in the \reffig{results_chart}.
 Besides, the detected moving objects of the SharedModel are not accurate in boundary due to the utilization of texture features. 
@@
 Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even the deep learning based algorithm is suffering from the detection of the boat shape.
-In contrast, the proposed approach performed superior than others in this scene, since the essence of background subtraction is considered as a binary classification of pixels' observation in time sequence.
+In contrast, the proposed approach performed superior than others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation in time sequence.
 Based on this insight, the FCN network focuses on learning the patterns of the pixel variation rather than a static background image, and proposed approach achieves promising performance in the canoe video.
@@
 \label{sec6}
-In this paper, we proposed a noval background subtraction approach based on deep learning and the variation transformation learning.
+In this paper, we proposed a noval foreground detection approach based on deep learning and the variation transformation learning.
 The DPVTL model include a FCN network and a noval variation transformation learing framework, which allows us to efficiently combine the temporal coherence and distribution information of pixels over a long period of time.
@@
 % In this paper,
-% we proposed the IFB framework for background subtraction for the case of a freely moving camera.
+% we proposed the IFB framework for foreground detection for the case of a freely moving camera.
 % Unlike previous work in which attempts were made to improve the accuracy of the estimation of motion,

### 2018-08-22 draft.tex
.

@@
 %\cite{Bouwmans2014}
-Over the last few decades, foreground detection has been well studied. Meanwhile, a huge number of background modeling methods have been proposed. 
-These methods can be broadly categorized into pixels-based, region-based and Learning-based methods.
-\subsection{pixels-based methods}
-Pixel-based techniques assume that the historical observations over time are independent at each pixel.
-Based on low-level features, such as color and gradients, these methods are computationally efficient and easy to deploy.
+% Ren:删去了冗余的一句话。
+Over the last few decades, a huge number of background modeling methods have been proposed. 
+These methods can be broadly categorized into pixel-based, region-based and learning-based methods.
+\subsection{pixel-based methods}
+% Ren:重新解释了pixel based methods
+Pixel-based methods assume that pixels are independent to each other and have no consideration of the spatial association with neighboring pixels. 
+Based on low-level features, such as color and gradients, pixel-based methods are computationally efficient and easy to deploy.
 
 %GMM 
-The most famous pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time.
+% Ren:这里你说over time 不专业，但是论文里用得挺多的啊，表示随时间推移。还有那一句 pixels are ....
+to be if there exists ....， 我也是在其他论文里借过来用的。原文是Incoming pixels from video frames are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound.
+The most popular pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time.
 Pixels are considered to be background if there exists a Gaussian includes their values with sufficient evidence.
 %GMM+
-Zoran Zivkovic\cite{Zivkovic2004} extend the GMM through the use of recursive equations, where the parameters keep constantly updating and the number of components are adaptable to each pixel. 
-%你的ICME那篇里面也用过extend through the use of 这句话的啊。 这里的改进就是用了一些回归方程，我也从别的文章里看过的。
+% Ren: 这里你说看不懂，我的意思是想说，GMM+里面参数会自动更新。并且每一个像素位置的高斯个数也会自适应调整。原文里说的是： Recursive equations are used to constantly update the parameters and but also to simultaneously select the appropriate number of components for each pixel.
+An improved GMM method is introduced by Zivkovic\cite{Zivkovic2004} with the utilization of recursive equations, which can automatically update the parameters and adjust the needed number of components of mixture for each pixel.
+%
 %codebook
-Some other popular algorithms in pixel based category are based on Codebook. 
-In \cite{Kim2005}, Kim et al present the codebook method to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model.
-The final foreground is detected by a distance measurement in a cylindrical color model.
+%Another popular algorithm in pixel based category is based on the Codebook. 
+%Ren: 干脆删掉这一句了。。。
+%Ren: 下面也重新写了。
+Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.  
+Then incoming pixels are compared with those of the codewords, to see if their distances lies within a certain bound. 
 %KDE
+% Ren这里确实没写好，因为有点看不太明白KDE.
 A non-parametric background model is proposed in \cite{Elgammal2000Non}.
-Elgammal et al.
-assume that each background pixel is drawn from a Probability Distribution Function(PDF).
-The PDF for each pixel is estimated with Kernel Density Estimation(KDE).
+Authors assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE).
 %Vibe
-Another non-parametric method is proposed by O.
-Barnich, called the Visual Background Extractor (ViBe)\cite{Barnich2011_2011_TIP}.
-ViBe is a sample based method, which consists of pixel samples from the video stream.
-Each pixel in the current frame is compared with N pixel samples from the corresponding background model and labeled as the foreground when there exist at least K samples with a distance to itself within a certain range R.
+% Ren: 关于这个Another我觉得没问题啊，因为之前一句是讲非参数的方法KDE,这里说另一个非参数的方法我觉得没毛病啊。
+% Ren: 还有 when there exists 这个短语确实没毛病啊，搜谷歌学术里这么用的也很多啊。
+Another non-parametric method is proposed by Barnich\cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe).
+The background model of ViBe consists of pixel samples from the video stream.
+Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists at least K samples with a distance to itself within a certain range R.
 %PBAS
+%
+% 这里上下两句话里，我用了一个R，一个R(X)，这两个东西是有关系的，ViBe里面要看距离是不是小于R, 下面这个论文是看距离是不是小于R(X),也就是说每个像素点位置，这个R是不一样的。
+%
 To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold R(x), which depended on the pixel position and a background dynamics metric.

### 2018-08-22 draft.tex
.

@@
 %
-% 这里上下两句话里，我用了一个R，一个R(X)，这两个东西是有关系的，ViBe里面要看距离是不是小于R, 下面这个论文是看距离是不是小于R(X),也就是说每个像素点位置，这个R是不一样的。
+% Ren :这里上下两句话里，我用了一个R，一个R(X)，这两个东西是有关系的，ViBe里面要看距离是不是小于R, 下面这个论文是看距离是不是小于R(X),也就是说每个像素点位置，这个R是不一样的。
 %
@@
 %提出其他方法的问题，指出他们的缺陷
-However, Those assumptions of pixels' independence are incorrect or inapplicable to many real-world scenes. 
-There is, in fact, a strong temporal coherence in image sequences that contains abundant hidden clues for the background model. 
-In most cases, pixels-based methods are only concerned with pixels distribution, and ignore the order information of input frames by default.
+However, The assumption that pixels are independent to their spatical neighbors is untenable in practice. 
+% Ren: 下面这一段，你说不知所云，我的意思是，之前的方法大多只考虑了像素值分布的概率，而不管它们变化过程中的顺序性。
+On the other hand, most pixels-based methods are only concerned with pixels distribution, and ignore the order information of input frames by default.
+But there is, in fact, a strong temporal coherence in image sequences that contains abundant hidden clues for the background model. 
 %提出我们的改进,我们认为像素在时序上是互相依赖的
-To address this shortcoming, we introduce a novel framework of variation transformation learing, which assumpt that there is a tight interdependence in pixel's historical observations.
+% tight interdependence 明明在google scholar里查得到很多用的好不好...
+To address this shortcoming, we introduce a novel framework of variation transformation learing, which assume that there is a tight interdependence in pixel's historical observations.
 %所以我们把像素整合到一起
+% In this case在google scholar里也查得到很多啊
 In this case, pixel's historical observations are embedded in a piece of pixel variation and sorted in chronological order as a whole to enter our DPVTL model.
@@
 \todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
+%
+%
+%
+%
+%
+%
 \subsection{region-based approach}
-Region-based approaches assume that the neighboring pixels have a similar variation as the pixel itself.
-Hence the spatial correlation is taken into consideration to refine the pixel-level classification.
+% Ren: 好的好的，不乱吹了，我看过有说have similar values的。。。。
+Region-based approaches assume that the neighboring pixels have similar intensities. Hence the spatial correlation is taken into consideration to refine the pixel-level classification.
 
 %(Regularized region-based)
-A region-based MoG is proposed by Varadarajan et al.\cite{2015_PR_Varadarajan20153488} Their model are derived from expectation maximization theory, which takes into consideration neighboring pixels while generating the model of the observed scene.
+A region-based MoG is proposed by Varadarajan et al.\cite{2015_PR_Varadarajan20153488}.
+Their model are derived from expectation maximization theory, which takes into consideration neighboring pixels while generating the model of the observed scene.
 % Spatiotemporal GMM

### 2018-08-22 draft.tex
.

@@
 % Spatiotemporal GMM
+%
+% 妈蛋。居然怀疑我没看过，我看过这篇论文啊，用最小生成树组织了层次化的superpixels,用来做spatial constrains我下面不是提了的吗，只是更抽象一点。。。
 Another GMM based method named Spatiotemporal GMM algorithm was proposed in \cite{2017_TPAMI_GANGWANG}.
-the authors combine the GMM with constrains of temporal and spatial information from the optical flow and superpixels.
+the authors combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
 %(Bayesian Modeling)
-In \cite{Sheikh2005Bayesian}, Sheikh et al. introduce a MAP-MRF framework, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
+In \cite{Sheikh2005Bayesian}, Sheikh et al. introduce a framework based on the Markov Random Field modeling with Maximum A Posteriori 
+probability (MAP-MRF) estimation, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
 %(Robust Foreground Object ICPR2010 Vikas Reddy )
-In \cite{Reddy2010Robust}, given frames are divided into overlapping blocks.
+In \cite{Reddy2010Robust}, origin images are divided into overlapping blocks.
 Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure, and a temporal correlation check.

### 2018-08-22 draft.tex
n

@@
 %(Robust Foreground Object ICPR2010 Vikas Reddy )
+% 这里原文就是用了三层的分类器，不同的方法，一层又一层。
 In \cite{Reddy2010Robust}, origin images are divided into overlapping blocks.
-Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure, and a temporal correlation check.
+Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure and a temporal correlation check.
 %( Robust Region-Based ICPR)
-Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color.
-Any foreground region that does not exist in map1 could be recovered from map2.
+Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color respectively.
+Any foreground region that does not exist in the first foreground map could be recovered from the other one.
 
@@
 %但是他们也有几个缺点
-However, optical flow methods have some shortcommings like the high computation complexity and the sensitivity to illumination changing. 
+However, optical flow methods have shortcommings like the high computation complexity and the sensitivity to illumination changing. 
 %最重要的是，他们的时序相关性太有限了。所以对与其他方法，并没有明显的优势。
 Moreover, their temporal coherence information is very limited. For each frame, only a few of neighbor frames are taken into account when computing the optical flow.
-This probably explains why they have no significant improvement compared to their competitors.    
+This could explain why they have no significant improvement compared to their competitors.    
 %讲我们方法的不同以及优点
@@
 
+%
+%
+%
+%
+%
 % \subsection{learning-based methods}
@@
 \todo{Please cite more papers on this paragraph since our work belongs to this category. This paragraph should be the main part of this section.}
-%我也想多引用一些，本来就不多的嘛。。。
-The last category of foreground detection methods apply traditional machine learning or deep learning on different features for the background modeling.
+The last category of foreground detection methods apply traditional machine learning and deep learning on different features for the background modeling.
 
+%
 %SVM
@@
 For example, in \cite{Han2012}, the authors integrate gradient, color, and Haar-like features to address the spatiotemporal variations for each pixel.
-A pixel wise background model is obtained for each feature in a kernel density framework and a SVM is employed for segmentation.
+A pixel wise background model is obtained for each feature in a kernel density framework and a SVM is employed for classification.
 
 %
-Recent years, deep learning starts to flourish in many fields, such as face recognition and natural language processing, significantly improving the state-of-the-art.
-A novel approach for foreground detection with the use of CNN was proposed by Braham and Droogenbroeck\cite{Braham2016deep}.
-They employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth, or alternatively, segmentation results from other foreground detection methods.
+% Ren: 这个CNN是cascade的结构，就是个层次化预测结果的组合。
+Recent years, deep learning starts to flourish in many computer vision fields, significantly improving the state-of-the-art.
+A novel approach for foreground detection with the use of CNN is proposed by Wang et al.
+They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which perform excellently in dataset2014 with sufficient training data.
+%
+% Ren: 这里我解释一下，为什么看上去这么冗余。这家伙先自己用中值滤波求了个平均背景，然后把平均背景 patches 跟对应的origin image patches 组合作为网络输入，他训练的groundtruth也可以来自其他比如GMM的分类结果图。
+%       所以我这里一连提了四个这篇论文训练要采集的patches。 patches 分别来自 平均背景，原始图像，真实图，或者其他算法算出的真实图。
+Braham and Droogenbroeck\cite{Braham2016deep} employ a scene-specific CNN, which is trained with corresponding image patches from the background image obtained from temporal median filtering, video frames and groundtruth, or alternatively, segmentation results from other foreground detection methods.
 Those patches are extracted around a pixel, then they are feed into the network and compared with a threshold.
-%
-In \cite{wang2016PRL}, Wang et al.
-tried a CNN architecture combined with a Cascade model for segmentation in foreground detection.
-Given 200 labelled images as training set, their model performed excellently in dataset2014.
-%
-M.
+% Ren: 下面这个家伙做法跟上面太类似了，就是背景图像不用中值滤波，而是用其他牛一点的方法去获取。MD
+A similar approach is presented by M.
 Babaee et al.
-\cite{Babaee2017deep} present a novel CNN for foreground detection.
-They also combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm, which is able to adaptively update the parameters used in the background model based on the motion changes in video stream.
-They also used spatial-median filtering as the post processing of the network outputs.
+\cite{Babaee2017deep}.
+Their background images combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm, which is able to adaptively update the parameters used in the background model.
+They also utilize spatial-median filtering as the post processing of the network predictions.
 %DBMF
@@
 %以上方法的缺点主要在于，他们都是基于静态的图像特征训练的。抛弃了时序相关性。
-Above mentioned deep methods are based on the static images and static saliency characteristics. 
+Methods in this category are generally based on the static images and static saliency characteristics. 
 As we've discussed earlier, their background models are trained with little or no temporal coherence involved.
 %所以他们在处理物体突然运动的时候会存在问题。
-And that cause the problem when target objects are doing sudden movement, for example, starting a car and get it out of the parking lot. 
+Problems will emerge in endlessly when the target object moves in an intermittent motion period, for example, starting a car and get it out of the parking lot. 
 %尽管他们用了很好的结构和技巧，但是仍然不能解决这个问题，如何去检测运动，而不是把潜在的运动物体全标记出来。
-Even though they have made a lot of progress with optimized network architechtures and training tricks, it is still an unsolved problem that how to detect the motion rather than mark out all the possible moving objects.
+Even though they have made a lot of progress with optimized network architechtures, it is still an unsolved problem that how to learn the patterns of motion rather than mark out all the possible moving objects.
 %我们的不同在与输入

### 2018-08-23 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.
 On branch master
 Changes to be committed:
	modified:   draft.aux
	modified:   draft.bbl
	modified:   draft.blg
	modified:   draft.log
	modified:   draft.out
	modified:   draft.pdf
	modified:   draft.tex
	deleted:    draft_with comments.pdf
	new file:   draft_with_comments_2018_08_22.pdf

@@
 % Ren:删去了冗余的一句话。
-Over the last few decades, a huge number of background modeling methods have been proposed. 
-These methods can be broadly categorized into pixel-based, region-based and learning-based methods.
+Over the last few decades, a huge number of background modeling methods have been proposed,
+which are broadly categorized into pixel-based, region-based and learning-based methods.
 \subsection{pixel-based methods}
 % Ren:重新解释了pixel based methods
-Pixel-based methods assume that pixels are independent to each other and have no consideration of the spatial association with neighboring pixels. 
-Based on low-level features, such as color and gradients, pixel-based methods are computationally efficient and easy to deploy.
+Pixel-based methods usually assume the independence between neighboring pxiels,
+and utilize the low-level features, such as color or gradients for background subtraction.
+% cqzhao:这两句连接性不强
+% Pixel-based methods assume that pixels are independent to each other and have no consideration of the spatial association with neighboring pixels. 
+% Based on low-level features, such as color and gradients, pixel-based methods are computationally efficient and easy to deploy.
 
 %GMM 
-% Ren:这里你说over time 不专业，但是论文里用得挺多的啊，表示随时间推移。还有那一句 pixels are ....
-to be if there exists ....， 我也是在其他论文里借过来用的。原文是Incoming pixels from video frames are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound.
-The most popular pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time.
-Pixels are considered to be background if there exists a Gaussian includes their values with sufficient evidence.
-%GMM+
+% Ren:这里你说over time 不专业，但是论文里用得挺多的啊，表示随时间推移。还有那一句 pixels are .... to be if there exists ....， 我也是在其他论文里借过来用的。i
+% 原文是Incoming pixels from video frames are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound. 
+% cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
+In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods,
+% 注意英语和汉语的表达习惯
+% The most popular pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, 
+which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel in time sequence.
+%over time. 
+Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence. 
+%GMM+i
+Moreover,
+Zivkovic et al.\ \cite{Zivkovic2004} improve the GMM method with the utilization of recursive equation
+to automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
+%
 % Ren: 这里你说看不懂，我的意思是想说，GMM+里面参数会自动更新。并且每一个像素位置的高斯个数也会自适应调整。原文里说的是： Recursive equations are used to constantly update the parameters and but also to simultaneously select the appropriate number of components for each pixel.
-An improved GMM method is introduced by Zivkovic\cite{Zivkovic2004} with the utilization of recursive equations, which can automatically update the parameters and adjust the needed number of components of mixture for each pixel.
+% An improved GMM method is introduced by Zivkovic\cite{Zivkovic2004} with the utilization of recursive equations, 
+% which can 
+% automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
 %
@@
 %Ren: 下面也重新写了。
-Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.  
-Then incoming pixels are compared with those of the codewords, to see if their distances lies within a certain bound. 
+Hence, Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.  
+Then incoming pixels are compared with these codewords to see if their distances lies within a certain bound.
+
 %KDE
@@
 %提出其他方法的问题，指出他们的缺陷
-However, The assumption that pixels are independent to their spatical neighbors is untenable in practice. 
+Unfortunately,
+the pixel-based methods ignore the spatial-temporal information due to their assumption of independence between pixels.
+%
+But there is, in fact, a strong temporal coherence in image sequences that contains abundant hidden clues for the background model. 
+%
+% However, The assumption that pixels are independent to their spatical neighbors is untenable in practice. 
 % Ren: 下面这一段，你说不知所云，我的意思是，之前的方法大多只考虑了像素值分布的概率，而不管它们变化过程中的顺序性。
-On the other hand, most pixels-based methods are only concerned with pixels distribution, and ignore the order information of input frames by default.
-But there is, in fact, a strong temporal coherence in image sequences that contains abundant hidden clues for the background model. 
+% cqzhao: 不能这么说，实际上专注于distribution的方法不多。
+% On the other hand, most pixels-based methods are only concerned with pixels distribution, 
+%
+%and ignore the order information of input frames by default.
+%But there is, in fact, a strong temporal coherence in image sequences that contains abundant hidden clues for the background model. 
 %提出我们的改进,我们认为像素在时序上是互相依赖的
@@
 Hence we demonstrate a comparatively better performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
-\todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
+%\todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
 %
@@
 % Ren: 好的好的，不乱吹了，我看过有说have similar values的。。。。
-Region-based approaches assume that the neighboring pixels have similar intensities. Hence the spatial correlation is taken into consideration to refine the pixel-level classification.
+Region-based approaches consider the similiary between neighboring pixels, which is utilized to refine the pixel-level classification.
+%
+% Region-based approaches assume that the neighboring pixels have similar intensities. Hence the spatial correlation is taken into consideration to refine the pixel-level classification.
 
 %(Regularized region-based)
-A region-based MoG is proposed by Varadarajan et al.\cite{2015_PR_Varadarajan20153488}.
-Their model are derived from expectation maximization theory, which takes into consideration neighboring pixels while generating the model of the observed scene.
+Varadarajan et al.\ \cite{2015_PR_Varadarajan20153488} proposed a region-based GMM model,
+which is derived from expectation maximization theory with the consideration of neighboring pixels while generating the model of the observed scene.
 % Spatiotemporal GMM
@@
 % 妈蛋。居然怀疑我没看过，我看过这篇论文啊，用最小生成树组织了层次化的superpixels,用来做spatial constrains我下面不是提了的吗，只是更抽象一点。。。
-Another GMM based method named Spatiotemporal GMM algorithm was proposed in \cite{2017_TPAMI_GANGWANG}.
-the authors combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
+In addition, 
+Chen et al. \cite{2017_TPAMI_GANGWANG} combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
+%Another GMM based method named Spatiotemporal GMM algorithm was proposed in \cite{2017_TPAMI_GANGWANG}. 
+%
+%The authors combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
 %(Bayesian Modeling)
-In \cite{Sheikh2005Bayesian}, Sheikh et al. introduce a framework based on the Markov Random Field modeling with Maximum A Posteriori 
+Moreover, 
+Sheikh et al.\ \cite{Sheikh2005Bayesian} introduce a framework based on the Markov Random Field modeling with Maximum A Posteriori 
 probability (MAP-MRF) estimation, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
@@
 % 这里原文就是用了三层的分类器，不同的方法，一层又一层。
-In \cite{Reddy2010Robust}, origin images are divided into overlapping blocks.
+Similarly, in \cite{Reddy2010Robust}, origin images are divided into overlapping blocks.
 Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure and a temporal correlation check.
 %( Robust Region-Based ICPR)
-Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color respectively.
+Hence, Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color respectively.
 Any foreground region that does not exist in the first foreground map could be recovered from the other one.
@@
 Furthermore, the proposed approach are more powerful in capturing the structural background variation and more efficient in computation due to the application of deep learning.
-
-\todo{disccuss the adavantage of proposed work.}
-
 %
@@
 \subsection{Machine Learning based Methods}
-\todo{Please cite more papers on this paragraph since our work belongs to this category. This paragraph should be the main part of this section.}
-The last category of foreground detection methods apply traditional machine learning and deep learning on different features for the background modeling.
+The last category of background subtraction methods apply traditional machine learning and deep learning on different features for the background modeling.
 
@@
 %以上方法的缺点主要在于，他们都是基于静态的图像特征训练的。抛弃了时序相关性。
+% cqzhao: 瞎说啥？？？SVM那个就是连续的几帧啊！他们的问题在于， 自然界太复杂，variation太多元，直接分析variation分析不出来，我们学到了variation的pattern，然后转换！
 Methods in this category are generally based on the static images and static saliency characteristics. 
@@
 %所以他们在处理物体突然运动的时候会存在问题。
+% cqzhao: 这句话有证据支持吗？先是他们没有抛弃时许相关性啊，然后抛弃后，为什么intermittent motion就会失败呢？不是要你回到我，是要你给我找到论文支持！一定要有论文支持才能写下判断的话！
 Problems will emerge in endlessly when the target object moves in an intermittent motion period, for example, starting a car and get it out of the parking lot. 
@@
 %我们的不同在与输入
+% cqzhao: 怎么就是一个输入不同呢？吹的太低的，给我拔高！
 Different with their methods, the input of our DPVTL model is not the origin images or patches.
@@
 %因为我们的方法是基于时序建模的，所以我们的模型可以学习一段时间内的运动。
+% cqzhao: 我们的方法是variation transformation，只是相比他们时许好点而已，不是说我们就只是个时序，吹的不够，拔高！
 Now, since the proposed approach is based on the time series modeling of each pixel, our model can learn the patterns of motion over a period of time.
 %此外，我们还将pixel variation 与其空间上的近邻连接起来，从而利用空间上下文信息。
+% cqzhao: 这句逻辑有点混乱，我感觉连不上。
 In addition, we also cascade the pixel variation with its spatial neighbors to take advantage of the spatial context. 
 %因为我们的网络结构相对比较简单，所以取得的效果应该归功于Variation Transformation 框架。
+% cqzhao: 你说我们的网络结构简单干嘛》不是不打自招？？？往死里吹，！！！
 Our FCN is implemented with a relative simple structure, hence the reliable performance of our DPVTL should be owing to the framework of variation transformation.

### 2018-08-24 draft.tex
.

@@
 %
-% 你这里的说法不对啊，原来的方法关注的是像素值的分布，我们关注的是像素值的变动。这是我们之间的区别啊!
-% 运动检测的已有方法主要关注于像素值的分布。
-Previous approaches to foreground detection generally focus on the distribution of pixel observations.
+% 运动检测的已有方法主要关注于像素值的变化。
+Previous approaches to foreground detection generally analyze the variation of pixel observations.
 % 本文中，我们分析了像素的变动，并提出了DPVTL方法。
@@
 % 这句话我也没看懂。。。
-Benefied from the ingenious utilization of deep learning network leading by our clear cognition of essence about background subtractoin problem,
-proposed approached adaptively generate superior peroformances in diversly complex scenes.
+Benefied from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
+the proposed approach adaptively generate superior peroformances in diversly complex scenes.
 %
@@
 which is widely used as the pre-processing step of video processing \cite{Barnich2011_2011_TIP}.
+% 传统的方法是怎么做的，有什么问题
 Typically, it is recognized as a binary classification task that assigns each pixel in the video stream with a label, 
 for either belonging to the background or foreground scene.
+Traditional foreground detection algorithms focus on anaylsing the pixel variation, establishing background models with statistical methods such as GMM and KDE.
+However, due to the unpredictability and rapidity of the pixels' variation in natural scenes,
+the variation becomes so unordered which is hard to be analyzed for foreground detection.
 % 现有的方法在简单场景中效果很好了
-Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes.
-However, it still remains a challenging problem in the scenes with high complexity and diversity.
-% 传统的方法是怎么做的，有什么问题
+%Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes.
 %
@@
 %
-Traditionally, foreground detection algorithms focus on anaylsing the pixel distribution, establishing background models with statistical methods such as GMM and KDE.
+
 % 总而言之，foreground detection依然有很多问题
@@
 % 8.21 Ren  因为这一段跟你的理解有冲突，所以先商量后再改吧。
-However, due to the unpredictability and complexity of the pixels' variation in natural scenes,
-the variation becomes so unordered which is hard to be analyzed for foreground detection.
 
@@
 In the diversely natural scenes,
-it is possible that the moving objects produce the similar or even the same observations of pixels to that of background,
-and the variation of observations becomes so hard to analyze when it includes such observations.
+it is possible that the moving objects produce the similar or even the same observations of pixels to that of background.
 % similar to their counterparts of background but atually belong to foreground .
@@
 % 我们的就是希望把这个variation 转化到更简单的地方去
-In this work, we focus on transforming the variation of pixels' observation into a new variation where the observations are easier to classified,
-as shown in the bottom part of the \reffig{idea},
-with the motivation that the pattern of fragment consist of observations A-D can be learned by the network and transformed into another fragment where these observations are easily and correctly classified as foreground.
+In this work, we focus on learning the pattern of pixels' variation and transforming the variations into a new space where the observations are easier to classified, rather than learning a classifier for individual pixels.
+As shown in the bottom part of the \reffig{idea}, the pattern of fragment consist of observations A-D can be learned by the network and transformed into another fragment where these observations are easily and correctly classified as foreground.
 % transformatin 之后，就很容易分类了，然后这就是我们的方法的核心了
@@
 %
-But there is, in fact, a strong temporal coherence in image sequences that contains abundant hidden clues for the background model. 
+But there is, in fact, a strong coherence in image sequences that contains abundant hidden clues for the background model. 
 %
@@
 The benefit of bringing together the observations is to ensure the data integrity and preserve the temporal coherence of our training data.
-And that guarantee us the ability to take advantage of the temporal coherence.
+And that guarantee us the ability to take advantage of the spatial-temporal context.
 %所以我们方法比基于像素的要好。
@@
 %有的方法结合了光流，也算利用了时序相关性
-But we also notice that some methods are involved with optical flow field, which can be viewed as a limited temporal coherence message. 
+But we also notice that some approaches are involved with optical flow field, which can be viewed as a limited temporal coherence message. 
 %但是他们也有几个缺点
@@
 Methods in this category are generally based on the static images and static saliency characteristics. 
-As we've discussed earlier, their background models are trained with little or no temporal coherence involved.
-%所以他们在处理物体突然运动的时候会存在问题。
-% cqzhao: 这句话有证据支持吗？先是他们没有抛弃时许相关性啊，然后抛弃后，为什么intermittent motion就会失败呢？不是要你回到我，是要你给我找到论文支持！一定要有论文支持才能写下判断的话！
-Problems will emerge in endlessly when the target object moves in an intermittent motion period, for example, starting a car and get it out of the parking lot. 
+However, due to the diversity and complexity of nature scenes, it could be rather difficult to analyze the pixel variations for classification. 
 %尽管他们用了很好的结构和技巧，但是仍然不能解决这个问题，如何去检测运动，而不是把潜在的运动物体全标记出来。
 Even though they have made a lot of progress with optimized network architechtures, it is still an unsolved problem that how to learn the patterns of motion rather than mark out all the possible moving objects.
-%我们的不同在与输入
+%我们的不同在于，我们的网络是训练去学习像素变动，并转换到新的空间去进行分类。
 % cqzhao: 怎么就是一个输入不同呢？吹的太低的，给我拔高！
-Different with their methods, the input of our DPVTL model is not the origin images or patches.
+Different with their methods, our network is trained to learn the patterns of pixel variations and transform them into a new space for classification.
+% 我们的输入XXX
+The input of our network is not the origin images or patches.
 Instead, we regard the pixel variation as a whole for the network training to preseve the temporal coherence between the pixels' historical observations.
-%因为我们的方法是基于时序建模的，所以我们的模型可以学习一段时间内的运动。
+%因为我们的方法是基于variation transformation建模的，所以我们的模型在时序建模上有更大的潜力。
 % cqzhao: 我们的方法是variation transformation，只是相比他们时许好点而已，不是说我们就只是个时序，吹的不够，拔高！
-Now, since the proposed approach is based on the time series modeling of each pixel, our model can learn the patterns of motion over a period of time.
+Now, since the proposed approach is based on the variation transformation, our DPVTL model has more potential in time series modeling on each pixel position.
 %此外，我们还将pixel variation 与其空间上的近邻连接起来，从而利用空间上下文信息。
 % cqzhao: 这句逻辑有点混乱，我感觉连不上。
-In addition, we also cascade the pixel variation with its spatial neighbors to take advantage of the spatial context. 
-%因为我们的网络结构相对比较简单，所以取得的效果应该归功于Variation Transformation 框架。
+In addition, we also concatenate the pixel variation with its spatial neighbors to take advantage of the spatial context. 
+%因为我们的网络没有借助于其他传统的背景建模方法，所以取得的效果应该归功于Variation Transformation 框架。
 % cqzhao: 你说我们的网络结构简单干嘛》不是不打自招？？？往死里吹，！！！
-Our FCN is implemented with a relative simple structure, hence the reliable performance of our DPVTL should be owing to the framework of variation transformation.
+Our DPVTL model is implemented without any assistance from other tradition background modeling methods, hence the reliable performance owing to the framework of variation transformation.
 

### 2018-08-24 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.
 On branch master
 Changes to be committed:
	modified:   draft.aux
	modified:   draft.log
	modified:   draft.pdf
	modified:   draft.tex
	new file:   draft_with_comments_2018_08_24.pdf

@@
 % cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
-In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods,
+In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods.
 % 注意英语和汉语的表达习惯
 % The most popular pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, 
-which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel in time sequence.
+It utilizes a mixture of weighted Gaussians to model the probability distribution of each pixel in time sequence.
 %over time. 
@@
 Hence, Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.
-Then incoming pixels are compared with these codewords to see if their distances lies within a certain bound.
+The incoming pixels are compared with these codewords to see if their distances lies within a certain bound.
 

### 2018-08-25 draft.tex
.

@@
 
-% XXX there is no such command of authorruning!!!!!!
-% XXX 根本就没有authorruning 命令！！！
 % \authorrunning{Lecture Notes in Computer Science: Chongqing University}
@@
 % 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
-A fully convolutional network(FCN) is applied to find a transformation for pixel variations, which guarantees the linear separability of transformed pixels.
+A fully convolutional network(FCN) is applied to find a transformation of pixel variations, which guarantees the linear separability of transformed pixels.
 % 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
@@
 %Moreover,
-%since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
+%since the pixel sequences are extracted from individual pixels, a large number of pixel patches may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
 % 
@@
 % %Our contributions can be summarized as follows:
-% The contridbutions of proposed approach are shown as follows:
+% The contridbutions of proposed approach is shown as follows:
 % \begin{itemize}
-% \item We proposed the pixel observation matrix to describe the pixel variation, which encode both the intensity distribution and sequential information over time.
-%     The observation matrix is obtained by reshaping the vector of a pixel's historical observations, subtracted from the image stacks. 
+% \item We proposed the pixel observation patch to describe the pixel variation, which encode both the intensity distribution and sequential information over time.
+%     The observation patch is obtained by reshaping the vector of a pixel's historical observations, subtracted from the image stacks. 
 % \item We propose a deep neural network for variation transformation. 
@@
 % XXX 不会用引用可以问我或者曲师兄。
-The reset part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion about the early and recent relevant works. 
+The rest part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion about the early and recent relevant works. 
 %
@@
 \label{sec2}
-% XXX 引用文章的方式，Bouwmans2014 在ref.bib文件里,不懂去问曲师兄！！！！
-%\cite{Bouwmans2014}
-% Ren:删去了冗余的一句话。
 Over the last few decades, a huge number of background modeling methods have been proposed,
@@
 and utilize the low-level features, such as color or gradients for background subtraction.
-% cqzhao:这两句连接性不强
-% Pixel-based methods assume that pixels are independent to each other and have no consideration of the spatial association with neighboring pixels. 
-% Based on low-level features, such as color and gradients, pixel-based methods are computationally efficient and easy to deploy.
 
 %GMM 
-% Ren:这里你说over time 不专业，但是论文里用得挺多的啊，表示随时间推移。还有那一句 pixels are .... to be if there exists ....， 我也是在其他论文里借过来用的。i
-% 原文是Incoming pixels from video frames are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound. 
 % cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
@@
 % 注意英语和汉语的表达习惯
-% The most popular pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, 
 It utilizes a mixture of weighted Gaussians to model the probability distribution of each pixel in time sequence.
-%over time. 
 Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence. 
@@
 %
-% Ren: 这里你说看不懂，我的意思是想说，GMM+里面参数会自动更新。并且每一个像素位置的高斯个数也会自适应调整。原文里说的是： Recursive equations are used to constantly update the parameters and but also to simultaneously select the appropriate number of components for each pixel.
-% An improved GMM method is introduced by Zivkovic\cite{Zivkovic2004} with the utilization of recursive equations, 
-% which can 
-% automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
-%
 %codebook
-%Another popular algorithm in pixel based category is based on the Codebook. 
-%Ren: 干脆删掉这一句了。。。
-%Ren: 下面也重新写了。
 Hence, Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.
 The incoming pixels are compared with these codewords to see if their distances lies within a certain bound. 
-
 %KDE
-% Ren这里确实没写好，因为有点看不太明白KDE.
-A non-parametric background model is proposed in \cite{Elgammal2000Non}. 
+A non-parametric background model is proposed by Elgammal et al. \cite{Elgammal2000Non}. 
 Authors assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE). 
 %Vibe
-% Ren: 关于这个Another我觉得没问题啊，因为之前一句是讲非参数的方法KDE,这里说另一个非参数的方法我觉得没毛病啊。
-% Ren: 还有 when there exists 这个短语确实没毛病啊，搜谷歌学术里这么用的也很多啊。
-Another non-parametric method is proposed by Barnich\cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe).
+Another non-parametric method is proposed by Barnich et al.
+\cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe).
 The background model of ViBe consists of pixel samples from the video stream.
-Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists at least K samples with a distance to itself within a certain range R.
+Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists sufficient samples with a distance to itself within a certain range.
 %PBAS
-%
-% Ren :这里上下两句话里，我用了一个R，一个R(X)，这两个东西是有关系的，ViBe里面要看距离是不是小于R, 下面这个论文是看距离是不是小于R(X),也就是说每个像素点位置，这个R是不一样的。
-%
-To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold R(x), which depended on the pixel position and a background dynamics metric.
+To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold, which depended on the pixel position and a background dynamics metric.
 
@@
 the pixel-based methods ignore the spatial-temporal information due to their assumption of independence between pixels.
-%
 But there is, in fact, a strong coherence in image sequences that contains abundant hidden clues for the background model. 
 %
-% However, The assumption that pixels are independent to their spatical neighbors is untenable in practice. 
-% Ren: 下面这一段，你说不知所云，我的意思是，之前的方法大多只考虑了像素值分布的概率，而不管它们变化过程中的顺序性。
-% cqzhao: 不能这么说，实际上专注于distribution的方法不多。
-% On the other hand, most pixels-based methods are only concerned with pixels distribution, 
-%
-%and ignore the order information of input frames by default.
-%But there is, in fact, a strong temporal coherence in image sequences that contains abundant hidden clues for the background model. 
 %提出我们的改进,我们认为像素在时序上是互相依赖的
 % tight interdependence 明明在google scholar里查得到很多用的好不好...
-To address this shortcoming, we introduce a novel framework of variation transformation learing, which assume that there is a tight interdependence in pixel's historical observations.
-%所以我们把像素整合到一起
-% In this case在google scholar里也查得到很多啊
-In this case, pixel's historical observations are embedded in a piece of pixel variation and sorted in chronological order as a whole to enter our DPVTL model.
+% To address this shortcoming, 在一篇2018的CVPR的摘要里有啊
+% “High Quality Estimation of Multiple Intermediate Frames for Video Interpolation”
+To address this shortcoming, we introduce a framework of variation transformation learing, where pixel's historical observations are embedded in a piece of pixel variation and sorted in chronological order as a whole to enter our DPVTL model.
 %这样的优点在于保留了数据的完整性，保留了数据的时序相关性。
-The benefit of bringing together the observations is to ensure the data integrity and preserve the temporal coherence of our training data.
-And that guarantee us the ability to take advantage of the spatial-temporal context.
+Bringing together the historical observations ensures the data integrity and preserves the temporal coherence of our training data. 
+Moreover, 
+the novel framework is more capable of learning the patterns of pixel variation and exploiting the spatial-temporal context, compared to those classifiers for individual observations. 
 %所以我们方法比基于像素的要好。
-Hence we demonstrate a comparatively better performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
+%Hence we demonstrate a comparatively better performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
 %\todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
@@
 %
-% Region-based approaches assume that the neighboring pixels have similar intensities. Hence the spatial correlation is taken into consideration to refine the pixel-level classification.
 
@@
 Varadarajan et al.\ \cite{2015_PR_Varadarajan20153488} proposed a region-based GMM model,
-which is derived from expectation maximization theory with the consideration of neighboring pixels while generating the model of the observed scene.
+which is derived from expectation maximization theory with the consideration of neighboring pixels.
 % Spatiotemporal GMM
-%
-% 妈蛋。居然怀疑我没看过，我看过这篇论文啊，用最小生成树组织了层次化的superpixels,用来做spatial constrains我下面不是提了的吗，只是更抽象一点。。。
 In addition, 
 Chen et al. \cite{2017_TPAMI_GANGWANG} combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
-%Another GMM based method named Spatiotemporal GMM algorithm was proposed in \cite{2017_TPAMI_GANGWANG}. 
-%
-%The authors combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
 %(Bayesian Modeling)
@@
 
-%讲其他方法的缺点，不能利用时序相关性，只是在pixel-based方法上添加了空间约束
-Unfortunately, most region-based methods are not capable to make use of the temporal coherence, since they are merely adding some spatial constrains to the pixels-based methods. 
-%有的方法结合了光流，也算利用了时序相关性
-But we also notice that some approaches are involved with optical flow field, which can be viewed as a limited temporal coherence message. 
-%但是他们也有几个缺点
-However, optical flow methods have shortcommings like the high computation complexity and the sensitivity to illumination changing. 
-%最重要的是，他们的时序相关性太有限了。所以对与其他方法，并没有明显的优势。
-Moreover, their temporal coherence information is very limited. For each frame, only a few of neighbor frames are taken into account when computing the optical flow.
-This could explain why they have no significant improvement compared to their competitors.    
-%讲我们方法的不同以及优点
-%我们的输入有足量的时序信息。
-In the proposed approach, by contrast, we present the pixel matrix, which contains the pixel variation over a longer period of time, to ensure that our DPVTL model has sufficient temporal coherence information to feed.
-We also combine the pixel variation with its spatial neighbors to revise our prediction.
-%此外，我们借助神经网络可以更有效地计算和捕捉这种时序相关性。
-Furthermore, the proposed approach are more powerful in capturing the structural background variation and more efficient in computation due to the application of deep learning.
-%
-%
+In this paper, we accept the assumption that neighboring blocks of background pixels should follow similar variations over time, and combine the pixel variation with its spatial neighbors to revise our prediction.
+Due to the application of deep learning, the proposed approach is more powerful in capturing the structural background variation and achieves significant improvement compared to its competitors.
 %
@@
 \subsection{Machine Learning based Methods}
-The last category of background subtraction methods apply traditional machine learning and deep learning on different features for the background modeling.
+The last category of background subtraction methods apply traditional machine learning and deep learning for the background modeling.
 
@@
 Traditional machine learning methods are commonly involved with support vector machines (SVM) and Bayesian methods\cite{Zhang2014Statis}.
-For example, in \cite{Han2012}, the authors integrate gradient, color, and Haar-like features to address the spatiotemporal variations for each pixel.
-A pixel wise background model is obtained for each feature in a kernel density framework and a SVM is employed for classification.
+For example, Han et al.
+\cite{Han2012} integrate gradient, color, and Haar-like features to address the spatiotemporal variations for each pixel.
+Their background model is obtained for each feature in a kernel density framework and a SVM is employed for classification.
 
 %
-% Ren: 这个CNN是cascade的结构，就是个层次化预测结果的组合。
-Recent years, deep learning starts to flourish in many computer vision fields, significantly improving the state-of-the-art.
-A novel approach for foreground detection with the use of CNN is proposed by Wang et al.
-They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which perform excellently in dataset2014 with sufficient training data.
+Recent years, deep learning methods start to flourish in many computer vision fields, and significantly improve the state-of-the-art in experiments.
+A novel approach for foreground detection with the use of CNN is proposed by Wang et al.\cite{wang2016PRL}.
+They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which perform excellently with sufficient training data.
 %
 % Ren: 这里我解释一下，为什么看上去这么冗余。这家伙先自己用中值滤波求了个平均背景，然后把平均背景 patches 跟对应的origin image patches 组合作为网络输入，他训练的groundtruth也可以来自其他比如GMM的分类结果图。
-%       所以我这里一连提了四个这篇论文训练要采集的patches。 patches 分别来自 平均背景，原始图像，真实图，或者其他算法算出的真实图。
-Braham and Droogenbroeck\cite{Braham2016deep} employ a scene-specific CNN, which is trained with corresponding image patches from the background image obtained from temporal median filtering, video frames and groundtruth, or alternatively, segmentation results from other foreground detection methods.
-Those patches are extracted around a pixel, then they are feed into the network and compared with a threshold.
+Braham et al.
+\cite{Braham2016deep} employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth.
+In particular, the background image is obtained by temporal median filtering, and the groundtruth be replaced with segmentation results from other foreground detection methods.
+Patches are extracted around a pixel, then they are feed into the network and compared with a threshold.
 % Ren: 下面这个家伙做法跟上面太类似了，就是背景图像不用中值滤波，而是用其他牛一点的方法去获取。MD
@@
 \cite{Babaee2017deep}.
-Their background images combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm, which is able to adaptively update the parameters used in the background model.
+Their background images combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm \cite{Wang2014FTSG}, which is able to adaptively update the parameters used in the background model.
 They also utilize spatial-median filtering as the post processing of the network predictions.
 %DBMF
-%skip结构就是skip结构啊！！就是说前基层的输出在输进下一层的同时，会跳过下一层，输入到更后面去。
-In \cite{Yang2018DBMF}, a FCN with the skip architecture is proposed for background modeling. 
+In \cite{Yang2018DBMF}, a fully convolutional network with the skip architecture is proposed for background modeling. 
 The authors also proposed a temporal approach to sample training images from the given video, thus providing the background model with limited temporal information.
 
-%以上方法的缺点主要在于，他们都是基于静态的图像特征训练的。抛弃了时序相关性。
 % cqzhao: 瞎说啥？？？SVM那个就是连续的几帧啊！他们的问题在于， 自然界太复杂，variation太多元，直接分析variation分析不出来，我们学到了variation的pattern，然后转换！
-Methods in this category are generally based on the static images and static saliency characteristics. 
-However, due to the diversity and complexity of nature scenes, it could be rather difficult to analyze the pixel variations for classification. 
-%尽管他们用了很好的结构和技巧，但是仍然不能解决这个问题，如何去检测运动，而不是把潜在的运动物体全标记出来。
-Even though they have made a lot of progress with optimized network architechtures, it is still an unsolved problem that how to learn the patterns of motion rather than mark out all the possible moving objects.
+Methods in this category have made a lot of progress, especially deep learning based approaches with optimized network architechtures. 
+However, due to the diversity and complexity of nature scenes, it is still difficult to analyze the pixel variations for classification. 
 %我们的不同在于，我们的网络是训练去学习像素变动，并转换到新的空间去进行分类。
-% cqzhao: 怎么就是一个输入不同呢？吹的太低的，给我拔高！
-Different with their methods, our network is trained to learn the patterns of pixel variations and transform them into a new space for classification.
-% 我们的输入XXX
-The input of our network is not the origin images or patches.
-Instead, we regard the pixel variation as a whole for the network training to preseve the temporal coherence between the pixels' historical observations.
-%因为我们的方法是基于variation transformation建模的，所以我们的模型在时序建模上有更大的潜力。
-% cqzhao: 我们的方法是variation transformation，只是相比他们时许好点而已，不是说我们就只是个时序，吹的不够，拔高！
-Now, since the proposed approach is based on the variation transformation, our DPVTL model has more potential in time series modeling on each pixel position.
-%此外，我们还将pixel variation 与其空间上的近邻连接起来，从而利用空间上下文信息。
-% cqzhao: 这句逻辑有点混乱，我感觉连不上。
-In addition, we also concatenate the pixel variation with its spatial neighbors to take advantage of the spatial context. 
-%因为我们的网络没有借助于其他传统的背景建模方法，所以取得的效果应该归功于Variation Transformation 框架。
-% cqzhao: 你说我们的网络结构简单干嘛》不是不打自招？？？往死里吹，！！！
-Our DPVTL model is implemented without any assistance from other tradition background modeling methods, hence the reliable performance owing to the framework of variation transformation.
+Different with their methods, we focus on creating a transformation, which guarantees the linear sparability of pixel variations in the mapping space, rather than building classifiers for individual observations.
+%
+Besides, our network is trained to learn the patterns of pixel variations, which promises a better performance in time series modeling on temporal coherence.
+%
+Moreover, our DPVTL model is implemented without any assistance from other tradition background modeling methods, hence the reliable performance owing to the noval framework of variation transformation.
 
@@
 Consequently, the classification of pixels can be viewed as a transformation of pixel variations, from the observation sequences to the prediction sequences. 
-In the specific implementation, we trained a FCN to learn a transformation for the pixel variations by mapping them into a new space where it is close to the groundtruth, just like the green line in \reffig{variation_chart}.
+In the specific implementation, we trained a FCN to learn a transformation of the pixel variations by mapping them into a new space where it is close to the groundtruth, just like the green line in \reffig{variation_chart}.
 After thresholding, we can easily get the labels of each observation. 
@@
 In this section, we introduce the proposed approach that consists of a novel FCN network for foreground detection. 
-We explain the details of the procedures of pixel matrixes, which is a specific form of the pixel variation, and the architecture of our network.
+We explain the details of the procedures of pixel patches, which is a specific form of the pixel variation, and the architecture of our network.
 
 The complete system is illustrated in \reffig{flow_chart}. 
-Firstly, we temporally sample the input and ground truth images to generalize the pixel variations, and reshape them into fixed-size matrixes and feed them into the network with its spatial neighbors.
-After reassembling the matrixes into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
+Firstly, we temporally sample the input and ground truth images to generalize the pixel variations, and reshape them into fixed-size patches and feed them into the network with its spatial neighbors. 
+After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
 \begin{figure*}[!t] % FIGURE: figure/fig1 
@@
 Besides, we also hope the pixel observations can be interacted with their further compatriots in temporal sequence. 
-Thus we reshape the variations into pixel matrixes as the input of our network. 
-A sample of pixel matrix $H^m$ is like this:
+Thus we reshape the variations into pixel patches as the input of our network. 
+A sample of pixel patch $H^m$ is like this:
 \begin{equation}
@@
 
-Pixel variations are put into the $d\times d$ matrix according to the order of top to bottom and left to right. 
+Pixel variations are put into the $d\times d$ patch according to the order of top to bottom and left to right. 
 The parameter $i$ and $j$ represent the column and row respectively. 
 And the parameter $n$ is the total frame length of a variation, as the same as the observation sequences. 
-To put it from another way, the pixel matrix is just a specific form of the pixel variation. 
-Although the observation matrix and the observation sequence belong to different forms of the pixel variation, they consist of the same components, and share the common temporal information from the pixel variation.
-Since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack.
+To put it from another way, the pixel patch is just a specific form of the pixel variation. 
+Although the observation patch and the observation sequence belong to different forms of the pixel variation, they consist of the same components, and share the common temporal information from the pixel variation.
+Since the pixel sequences are extracted from individual pixels, a large number of pixel patches may be extracted from only a single image stack.
 
@@
 In other words, there are some clues hidden in pixels' spatial neighbors. 
-In order to benefit from the spatial context, we concatenate the pixel matrix with 2 neighboring pixel matrixes, denoted as $SM_1$, $SM_2$ and $SM_3$ respectively.
-They are randomly selected in 8 nearest neighbors. 
-The input matrix of our network is defined as:
+In order to benefit from the spatial context, we concatenate the pixel patch with 2 neighboring pixel patches, denoted as $SM_1$, $SM_2$ and $SM_3$ respectively.
+They are randomly selected in the 8-connected neighborhood of each pixel position. 
+The input patch of our network is defined as:
 \begin{equation}
@@
 Where $C$ represents the concatenating process on the third dimension.
-And $H$ is the input matrix of our network, which size is $d\times d\times 3$.
+And $H$ is the input patch of our network, which size is $d\times d\times 3$.
 
-In the previous steps, videos are broken down into pixel matrixes which contain abundant background information. 
-Next, the groundtruth matrixes are obtained in the same way, except the concatenating process. 
+In the previous steps, videos are broken down into pixel patches which contain abundant background information. 
+Next, the groundtruth patches are obtained in the same way, except the concatenating process. 
 Both of them are put into the network for the training. 
@@
 
-Where, $H_p$ denotes the output of network, which we call the prediction matrix, the forward computation of network is represented by $\mathcal L$, and $E_x$ denotes the symmetric padding of pixel matrix where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel matrix $H$.
+Where, $H_p$ denotes the output of network, which we call the prediction patch, the forward computation of network is represented by $\mathcal L$, and $E_x$ denotes the symmetric padding of pixel patch where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel patch $H$.
 Another advantage of symmetric padding is that the order information still remains.
@@
 
-Where $H_{gt}$ denotes the groundtruth matrix which is given by the corresponding GT stack. 
-The SCE is calculated between the transformed matrixes and the corresponding groundtruth matrixes. 
+Where $H_{gt}$ denotes the groundtruth patch which is given by the corresponding GT stack. 
+The SCE is calculated between the transformed patches and the corresponding groundtruth patches. 
 Boundaries of moving objects and pixels that out of the region of interest are ignored in the cost function.
@@
 
-Different with CNNs, fully convolution neural network (FCN) utilize convolutional layers with $1*1$ kernels to take the place of fully connected layers, which largely resolves these above-mentioned problems.
+Different with CNNs, fully convolution neural network utilize convolutional layers with $1*1$ kernels to take the place of fully connected layers, which largely resolves these above-mentioned problems.
 First and foremost, the size of outputs are adjustable in FCNs, which allows an end-to-end mapping of pixel observation sequences and network outputs on the time sequence. 
@@
 Whereas, the DeepBS performs well in this video benefited from the utilization of CNN. 
-However, the shape of pedestrians are slightly deformed as the result of their matrix-wise processing of CNN. 
+However, the shape of pedestrians are slightly deformed as the result of their patch-wise processing of CNN. 
 In contrast, derived from the fact that our DPVL focus on learning the pattern of pixels' variation in the shadow regions, proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.
@@
 All these experiments of the proposed method were implemented in matlab and ran on the computer with Nvidia tasela K80 GPU and all images are keep their original resolution. 
-For each video in CDnet 2014, 100 training frames are extracted to produce the image matrix. 
+For each video in CDnet 2014, 100 training frames are extracted to produce the image patch. 
 It should be noted that the 100 frames only accounts for less than 10\% of total Groundtruth in CDnet 2014. 

### 2018-09-05 draft.tex
.

@@
 % In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
-In this paper, we analyze the variation of pixel observations, and a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
+In this paper, we focus on transforming the variation into another space where the entry of variation is easily classified, and a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
 % 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
-A fully convolutional network(FCN) is applied to find a transformation of pixel variations, which guarantees the linear separability of transformed pixels.
+A fully convolutional network(FCN) is applied to find a transformation of pixel variations.
 % 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
@@
 %
-Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
+Comprehensive experiments in several standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
 %
@@
 for either belonging to the background or foreground scene.
-Traditional foreground detection algorithms focus on anaylsing the pixel variation, establishing background models with statistical methods such as GMM and KDE.
+Traditional foreground detection algorithms focus on anaylsing the pixel variation, establishing background models with statistical methods such as GMM\cite{Stauffer1999} and KDE\cite{Elgammal2000Non}.
 However, due to the unpredictability and rapidity of the pixels' variation in natural scenes,
 the variation becomes so unordered which is hard to be analyzed for foreground detection.
+Therefore, the foreground detection is still a challenging problem in complex natural scenes.
 % 现有的方法在简单场景中效果很好了
@@
 As shown in the \reffig{idea},
-the observation C is closely related to the observations belong to the background but it is actually produced by moving objects and should be classified as foreground.
+the observation C is closely related to the observations which belong to the background. However, it is actually produced by moving objects and should be classified as foreground.
 % 大多数情况下，他都会被划分成背景
-However, in most cases, it is highly possible that the observation C will be falsely classified as background by previous work due to the similarity with their counterparts of background.
+Unfortunately, in most cases, it is highly possible that the observation C will be falsely classified due to the similarity with their counterparts of background.
 % 我们的就是希望把这个variation 转化到更简单的地方去
@@
     % 图例里描述一下。
-    \caption{The demonstration of deep variation transformation.
-Due to the complexity of natural scenes, the original pixels' variation is hard to classify correctly.
-After transforming by deep learning network, the pixels in variation become easy to be classified as foreground and background correctly.}
+    \caption{The demonstration of deep variation transformation. The pixels in the transformed variation become easier to be classified as foreground and background correctly.}
     \label{idea}
@@
 %
-Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantees the linear separability of transformed pixel variation generated by mapping in a new space.
+Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantees the linear separability of pixels in the transformed variation.
 %
 In particular,
-we take advantage of the strong learning ability of FCN to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
+we take advantage of the strong learning ability of the deep network to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
 %
-Benefited from the strong learning ability of FCN,
+Benefited from the noval framework of variation transformation,
 proposed approach works well in diversely complex scenes adaptively.
@@
 The details of the variation transformation are presented in \refsec{sec3}.
-The proposed fully convolutional network is illustrated in \refsec{sec4}, followed by experiments and result comparison in \refsec{sec5} and conclude the paper in \refsec{sec6}.
+The architecture of network is introduced in \refsec{sec4}, followed by experiments and result comparison in \refsec{sec5} and conclude the paper in \refsec{sec6}.
 % \todo{please revise this part by using command refsec}
@@
 \label{sec2}
-Over the last few decades, a huge number of background modeling methods have been proposed,
+Over the last few decades, a huge number of foreground detection methods have been proposed,
 which are broadly categorized into pixel-based, region-based and learning-based methods.
@@
 A non-parametric background model is proposed by Elgammal et al. \cite{Elgammal2000Non}. 
-Authors assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE). 
+They assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE). 
 %Vibe
@@
 % “High Quality Estimation of Multiple Intermediate Frames for Video Interpolation”
-To address this shortcoming, we introduce a framework of variation transformation learing, where pixel's historical observations are embedded in a piece of pixel variation and sorted in chronological order as a whole to enter our DPVTL model.
+To address this shortcoming, we introduce a framework of variation transformation learing, where pixel's historical observations are embedded in a piece of pixel patch and sorted in chronological order as a whole to enter our DPVTL model.
 %这样的优点在于保留了数据的完整性，保留了数据的时序相关性。
@@
 Moreover, 
-the novel framework is more capable of learning the patterns of pixel variation and exploiting the spatial-temporal context, compared to those classifiers for individual observations. 
+the novel framework is capable of learning the patterns of pixel variation and exploiting the spatial-temporal context, compared to those classifiers based on the assumption of pixel independence. 
 %所以我们方法比基于像素的要好。
@@
 % 这里原文就是用了三层的分类器，不同的方法，一层又一层。
-Similarly, in \cite{Reddy2010Robust}, origin images are divided into overlapping blocks.
+Similarly, in \cite{Reddy2010Robust}, original images are divided into overlapping blocks.
 Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure and a temporal correlation check.
@@
 
-In this paper, we accept the assumption that neighboring blocks of background pixels should follow similar variations over time, and combine the pixel variation with its spatial neighbors to revise our prediction.
+In contrast, we accept the assumption that neighboring blocks of background pixels should follow similar variations over time, and combine the pixel variation with its spatial neighbors to revise our prediction.
 Due to the application of deep learning, the proposed approach is more powerful in capturing the structural background variation and achieves significant improvement compared to its competitors.
@@
 \subsection{Machine Learning based Methods}
-The last category of background subtraction methods apply traditional machine learning and deep learning for the background modeling.
+The last category of background subtraction methods apply traditional machine learning and deep learning for the foreground detection.
 
@@
 %SVM
-Traditional machine learning methods are commonly involved with support vector machines (SVM) and Bayesian methods\cite{Zhang2014Statis}.
+Traditional machine learning methods are commonly involved with support vector machines (SVM)\cite{Han2012} and Bayesian methods\cite{Zhang2014Statis}.
 For example, Han et al.
@@
 %
-Recent years, deep learning methods start to flourish in many computer vision fields, and significantly improve the state-of-the-art in experiments.
-A novel approach for foreground detection with the use of CNN is proposed by Wang et al.\cite{wang2016PRL}.
+Recent years, deep learning methods start to flourish in several computer vision fields.
+A novel approach for foreground detection with the use of the Convolutional Neural Network(CNN) is proposed by Wang et al.\cite{wang2016PRL}.
 They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which perform excellently with sufficient training data.
@@
 \cite{Braham2016deep} employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth.
-In particular, the background image is obtained by temporal median filtering, and the groundtruth be replaced with segmentation results from other foreground detection methods.
-Patches are extracted around a pixel, then they are feed into the network and compared with a threshold.
+In particular, the background image is obtained by temporal median filtering, and the groundtruth can be replaced with segmentation results from other foreground detection methods.
 % Ren: 下面这个家伙做法跟上面太类似了，就是背景图像不用中值滤波，而是用其他牛一点的方法去获取。MD
@@
 %DBMF
-In \cite{Yang2018DBMF}, a fully convolutional network with the skip architecture is proposed for background modeling. 
+In \cite{Yang2018DBMF}, a fully convolutional network with the skip architecture is proposed for foreground detection. 
 The authors also proposed a temporal approach to sample training images from the given video, thus providing the background model with limited temporal information.
@@
 % cqzhao: 瞎说啥？？？SVM那个就是连续的几帧啊！他们的问题在于， 自然界太复杂，variation太多元，直接分析variation分析不出来，我们学到了variation的pattern，然后转换！
-Methods in this category have made a lot of progress, especially deep learning based approaches with optimized network architechtures. 
+Although some breakthroughs and progress have been made by applying those methods, especially deep learning based approaches with optimized network architechtures. 
 However, due to the diversity and complexity of nature scenes, it is still difficult to analyze the pixel variations for classification. 
@@
 %
-Moreover, our DPVTL model is implemented without any assistance from other tradition background modeling methods, hence the reliable performance owing to the noval framework of variation transformation.
+%Moreover, our DPVTL model is implemented without any assistance from other tradition foreground detection methods, hence the reliable performance owing to the noval framework of variation transformation.
 
@@
 \label{sec3}
-In this section, we will elaborate on the motivation of the proposed approach and how does the variation transformation work in foreground detection.
+In this section, we will elaborate on the proposed approach and how does the variation transformation work in foreground detection.
 
@@
 Generally, pixels from the background are sharing some common patterns of variation. 
-
 \begin{figure}[!t]	% FIGURE: figure/fig1 
@@
 %图例解释困难点
-To give an intuitive understanding of the pixel variations, we plot the historical observations and corresponding groundtruth of a single pixel in  \reffig{variation_chart}, with the X axis showing their range of variation and the Y axis representing the time.
+To give an intuitive understanding of the pixel variation, we plot the historical observations and corresponding groundtruth of a single pixel in  \reffig{variation_chart}, with the X axis showing their range of variation and the Y axis representing the time.
 As we can see, there are several lines in three colors: blue, red and green. 
-The blue one is called the pixel variation curve, which containing 100 original observations. 
-Accordingly, the red one, the groundtruth curve is made of a piece of groundtruth data corresponding to the observations. 
-The green one, which we call the transformed variation curve, is made of the outputs of the proposed approach. 
-In practice, foreground detection is to produce a prediction curve, which is as near as possible to the groundtruth carve, by given the pixel variation carve.
+The blue line consist of original observations, representing a piece of pixel variation. 
+Accordingly, the red line is made of the groundtruth data, corresponding to the observations from the blue one.  
+And the green line consist of the outputs of the proposed approach which represent the transformed variation.
+
+%In practice, foreground detection is to produce a prediction curve, which is as near as possible to the groundtruth carve, by given the pixel variation carve.
 
 %传统方法的问题
-Under ideal conditions like indoor videos, previous methods perform quite effectively, when distributions of background and foreground observations are remarkably different and the backgrounds are normally keeping static.
+Previous methods have a good performance when background and foreground observations are remarkably different and the backgrounds are normally keeping static. 
 While in fact, backgrounds can be rather turbulent and dynamic due to the complexity and diversity of nature scenes. 
@@
 For example, in \reffig{variation_chart}, it is noticeable that some foreground observations in blue line share the similarly value with background ones. 
-In that case, those popular solutions will inevitably yield some sticky moments when separating the pixels in the blue line. 
+In that case, those popular methods will inevitably yield some sticky moments when separating the pixels in the blue line. 
 Statistical methods, for instance, are no longer valid, because they only focus on establishing a statistical model for the background, while having little or no concern for the temporal coherence of these observations.
-Unfortunately, most previous methods, as far as we know, are not capable to take advantage of the temporal coherence of pixel variation. 
-In other words, despite knowing that pixels from the background share some common patterns of variation in a temporal sequence, we still let the order information of sequential images all go to waste.
-%为了解决这些问题，我们必须利用好时序相关性
-To alleviate this, order information of pixels must be taken in consideration. 
-More concretely, we must find an efficient method to model the patterns of background pixels variations.
+In other words, despite knowing that pixels from the background share some common patterns of variation in a temporal sequence, they still let the order information of sequential images all go to waste.
 
@@
 \label{sec4}
-In this section, we introduce the proposed approach that consists of a novel FCN network for foreground detection. 
-We explain the details of the procedures of pixel patches, which is a specific form of the pixel variation, and the architecture of our network.
+In this section, we will introduce the details of proposed approaches. 
+We explain the production of pixel patches, which is a specific form of the pixel variation, and the architecture of our network.
 
-The complete system is illustrated in \reffig{flow_chart}. 
-Firstly, we temporally sample the input and ground truth images to generalize the pixel variations, and reshape them into fixed-size patches and feed them into the network with its spatial neighbors. 
+The the flow chart is illustrated in \reffig{flow_chart}. 
+Firstly, we sample the input and ground truth images to generalize the pixel variations, and reshape them into patches and feed them into the network with its spatial neighbors. 
 After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
@@
 \DeclareGraphicsExtensions.
-    \caption{Fully convolutional network can efficiently learn to make dense predictions for per-pixel tasks like semantic segmentation.}
+    \caption{ Original videos break down into pixel patches for the training of the FCN, which 
+Fully convolutional network produces an efficient machine for end-to-end transformation learning.}
     \label{flow_chart}
@@
 % 第一步是对原视频进行采样
-Given different videos, the number of frames are generally different. 
-However, the size of our input is fixed, which means a sampling processing is required to keep the length of pixel variations invariant. 
-Therefore, image stacks are sampled form the given videos before the pixel variations are extracted. 
-The given video and image stacks can be defined as follows: 
+Given different videos, their numbers of frames are generally different. 
+In order to keep each piece of variation the same length, image stacks are sampled form the given videos before the pixel variations are extracted. 
+Let denote the frames sequence as $\{ I_1,I_2,I_3,\dots,I_L\}$.
+And image stacks can be defined as follows: 
 \begin{equation}
-	Given \  Video=\{ I_1,I_2,I_3,\dots,I_L\} ,
+Stack_{(x)}=\{I_x,I_{(x+p)},I_{(x+2p)},\dots,I_L \},\quad p\times l=L,\quad 1\leq   x\leq p , 
 \end{equation}
-
-\begin{equation}
-Stack_{(x)}=\{I_x,I_{(x+p)},I_{(x+2p)},\dots,I_L \},\quad p*l=L,\quad 1\leq   x\leq p , 
-\end{equation}
-
 % 解释采样的细节
-Where $I_t$ represent the frame $t$ of the given video. 
+where $I_t$ is the frame $t$ of the given video. 
 And $p$ is an integer number depended on the video frames length. 
 For each video, we can produce multiple image stacks and choose one of them for the training. 
-In addition, thanks to the temporal sampling, we can get compact pixel historical observations containing more temporal information than the continuous pixel sequences. 
-This works well when it comes to some situation where the moving objects keep stationary for a long time.
+In addition, we can get compact pixel variations, which contain more temporal information than the continuous pixel sequences, by using equal interval sampling.
 
 % 第二步提取Pixel variation
-In order to make use of the temporal information of pixel historical observations, we regard the sampled observations from a single pixel as a whole, namely the pixel variation. 
-After the temporal sampling, a large number of observation sequences, or pixel variations, are extracted from the chosen stack, which is shown as follows:
+After the sampling process, a large number of observation sequences, or pixel variations, are extracted from the chosen stack at each pixel position, which is shown as follows: 
 \begin{equation}
@@
 \end{equation}
-
-Where $P_t^m$ denotes the numerical value of pixel $m$ at frame $t$ in the chosen stack. 
+where $P_t^m$ denotes the numerical value of pixel $m$ at frame $t$ in the chosen stack. 
 Each of the pixel variation is a piece of temporal information which containing the changing patterns of background pixels. 
@@
 % 第三步变成矩阵形式，解释为什么要把variation 变形
-Our intention is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. 
+Our motivation is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. 
 However, vectors are not appropriate for the network training and learning. 
@@
 Thus we reshape the variations into pixel patches as the input of our network. 
-A sample of pixel patch $H^m$ is like this:
+A sample of the pixel patch is like this:
 \begin{equation}
-H^m=P^m_{i+j*d}=\begin{bmatrix}
+H^m=P^m_{i+j\times d}=\begin{bmatrix}
  P^m_1& P^m_2  &\dots  &P^m_d \\ 
@@
  P^m_{1+(d-1)d}& \dots & \dots & P^m_n
-\end{bmatrix},\quad d^2=n,
+\end{bmatrix},\quad d^2=n.
 \end{equation}
-
-Pixel variations are put into the $d\times d$ patch according to the order of top to bottom and left to right. 
-The parameter $i$ and $j$ represent the column and row respectively. 
-And the parameter $n$ is the total frame length of a variation, as the same as the observation sequences. 
-To put it from another way, the pixel patch is just a specific form of the pixel variation. 
-Although the observation patch and the observation sequence belong to different forms of the pixel variation, they consist of the same components, and share the common temporal information from the pixel variation.
-Since the pixel sequences are extracted from individual pixels, a large number of pixel patches may be extracted from only a single image stack.
+where the pixel patch is denoted as $H^m$, and the parameter $i$ and $j$ is the column and row of the pixel patch. 
+Observations are put into the $d\times d$ patch from top to bottom and left to right.
+To put it another way, the pixel patch is just a specific form of the pixel variation. 
+%Although the observation patch and the observation sequence belong to different forms of the pixel variation, they consist of the same components, and share the common temporal information from the pixel variation.
+Since the pixel sequences are extracted from each pixel position, a large number of pixel patches can be extracted from only one single image stack, which promises sufficient training data for our network.
 
 %第四步空间近邻随机采样。
-It is generally accepted that neighboring background pixels share a similar temporal variation.
-In other words, there are some clues hidden in pixels' spatial neighbors. 
-In order to benefit from the spatial context, we concatenate the pixel patch with 2 neighboring pixel patches, denoted as $SM_1$, $SM_2$ and $SM_3$ respectively.
-They are randomly selected in the 8-connected neighborhood of each pixel position. 
-The input patch of our network is defined as:
+It is generally accepted that neighboring background pixels share a similar temporal distribution.
+%In other words, there are some clues hidden in pixels' spatial neighbors. 
+In order to benefit from the spatial context, we concatenate the pixel patch with 2 neighboring pixel patches, which are randomly selected in the 8-connected neighborhood of each pixel position. 
+The input patch $I$ of our network is defined as:
 \begin{equation}
-H = C(H^m, SM_1, SM_2),
+I = C(H^m, SM_1, SM_2),
 \end{equation}
+where the $C$ represents the concatenating process on the third dimension.
+And neighboring patches are denoted as $SM_1$ and $SM_2$ respectively.
 
-Where $C$ represents the concatenating process on the third dimension.
-And $H$ is the input patch of our network, which size is $d\times d\times 3$.
-
-In the previous steps, videos are broken down into pixel patches which contain abundant background information. 
-Next, the groundtruth patches are obtained in the same way, except the concatenating process. 
-Both of them are put into the network for the training. 
-However, the size of the input will decreased in the forward computation. 
-In order to make output the same size as input, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input matribxes before the training. 
-After the forward computing, variations are transformed in a new space where they can be easily classified by thresholding. 
-The transformed pixel variation is defined as:
+%In the previous steps, original videos are broken down into pixel patches which contain abundant background information. 
+Correspondingly, the groundtruth patches are obtained in a similar way as the input ones, except the concatenating process, as shown in the \reffig{flow_chart}. 
+Both of them are fed into the network for the training to find a end-to-end transformation at each pixel position. 
+However, the size of feature maps will shrink quickly during forward computation. 
+In order to make our prediction the same size as the input patches, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input patches before the training. 
+After the forward computing, observations in input patches are mapped into a new space where they can be easily classified by thresholding. 
+The transformed pixel patch is defined as:
 \begin{equation}
@@
 \end{equation}
-
-Where, $H_p$ denotes the output of network, which we call the prediction patch, the forward computation of network is represented by $\mathcal L$, and $E_x$ denotes the symmetric padding of pixel patch where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel patch $H$.
+where, $H_p$ is the prediction of the network, and the forward computation of network is represented by $\mathcal L$.
+The symmetric padding process is denoted as $E_x$, where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel patch $H$.
 Another advantage of symmetric padding is that the order information still remains.
@@
     \begin{aligned}
-        & \ell_{H_p, H_{gt}} =  \sum\limits_{x \in X, y \in Y}^{} H_{gt}(x,y) log(Sigmoid(H_p(x,y)))  \\
-        & + (1 - H_{gt}(x,y)) log(1 - Sigmoid(H_p(x,y))) \\
-        & Sigmoid(x) =\frac{1}{1+e^{-x}}\  ,
+        & \ell_{H_p, H_{gt}} =  \sum\limits_{x \in X, y \in Y}^{} H_{gt}(x,y) log(S(H_p(x,y)))  \\
+        & + (1 - H_{gt}(x,y)) log(1 - S(H_p(x,y))) \\
+        & S(x) =\frac{1}{1+e^{-x}}\  ,
     \end{aligned}
 \end{equation}
-
-Where $H_{gt}$ denotes the groundtruth patch which is given by the corresponding GT stack. 
+where $H_{gt}$ denotes the groundtruth patch which is given by the corresponding groundtruth stack, and $S$ represents the sigmoid function. 
 The SCE is calculated between the transformed patches and the corresponding groundtruth patches. 
@@
 Finally, we get the transformed variation through the FCN, which are easier for classification.
-We globally threshold the values for each observation in order to map them to $\{0,1\}$ . 
+
+As shown in the \reffig{flow_chart}, the prediction maps can be reconstructed from the prediction patches.
+Then a global threshold $r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
 The threshold function is given by
@@
 \begin{equation}
-M(x,y)=g(H_p,r) ,
+F=g(M,r) ,
 \end{equation}
-
+where $M$ is the prediction map, and the $F$ denotes the final foreground map given by our DPVTL model.
 After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery.
-And the major contribution is that we demonstrate the effectiveness of temporal information in foreground detection.
 
@@
 
-Different with CNNs, fully convolution neural network utilize convolutional layers with $1*1$ kernels to take the place of fully connected layers, which largely resolves these above-mentioned problems.
-First and foremost, the size of outputs are adjustable in FCNs, which allows an end-to-end mapping of pixel observation sequences and network outputs on the time sequence. 
+Different with CNNs, FCNs utilize convolutional layers with $1\times 1$ kernels to take the place of fully connected layers, which provides several benefits. 
+First and foremost, the size of outputs are adjustable in FCNs, which allows an end-to-end mapping of input patches and prediction patches at each pixel position. 
 We hope to determine the label of a pixel through the comparison of its compatriot in time sequence. 
-There is one more point I ought to touch on, that since the feature maps are no longer need to be converted into vectors, spatial information can be retained . 
+There is one more point I ought to touch on, that since the feature maps are no longer need to be converted into vectors, spatial information can be retained. 
 The last but not the least, FCNs have been used in sematic segmentation and researchers found FCNs have a strong learning ability which won't lost to the traditional ones. 
@@
 Based on above-mentioned factors, FCN is designed as the alternative network architecture in this paper. 
-The structure of our FCN for background modeling is shown in \reffig{flow_chart}. 
-The proposed FCN contains 5 convolutional layers and a convolutional layer which have a filter size of $1*1$. 
+The structure of our FCN for foreground detection is shown in \reffig{flow_chart}. 
+The proposed FCN contains 5 convolutional layers and a convolutional layer which has a filter size of $1\times 1$. 
 We use the Rectified Linear Unit (ReLU) as activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
@@
 \label{sec5}
-In this section, we ran comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW. 
+In this section, we ran comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW\cite{CAMO}. 
 The CDnet is the largest dataset for foreground detection so far as we are aware, containing 11 categories with several complexly challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
@@
 %
-
-Where TP, FP, and FN are true positives, false positives, and false negatives respectively, computed in pixels of all test frames for each video.
+where TP, FP, and FN are true positives, false positives, and false negatives respectively, computed in pixels of all test frames for each video.
 
@@
 \centering
-\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CDnet 2014.}
+\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CDnet 2014.
+For each video, 100 frames were taken for the training of our FCN.}
 \label{tab1}
@@
 \centering
-\caption{The performance comparison of the proposed approach and some classical methods and deep-based method DBMF .}
+\caption{The performance comparison of the proposed approach and some classical methods and deep-based method DBMF. For each video, 64 frames were taken for the training of our FCN.}
 \label{tab2}

### 2018-09-06 draft.tex
.

@@
 \begin{document}
-\title{foreground detection via Deep Variation Transformation}
+\title{Foreground Detection via Deep Variation Transformation}
 
@@
     % 图例里描述一下。
-    \caption{The demonstration of deep variation transformation. The pixels in the transformed variation become easier to be classified as foreground and background correctly.}
+    \caption{The demonstration of deep variation transformation.
+Due to the complexity of natural scenes, the original pixels' variation is hard to classify correctly.
+After transforming by deep learning network, the pixels in variation become easy to be classified as foreground and background correctly.}
     \label{idea}
 \end{figure}
-
+%The demonstration of deep variation transformation. The pixels in the transformed variation become easier to be classified as foreground and background correctly
 %本文的想法和优势
@@
 In this paper, a novel framework of pixel variation transformation are proposed. %用framework代替method?
-Pixel observations are no longer considered independent of each other but regarded as a whole, which we call the pixel variation. 
-Consequently, the classification of pixels can be viewed as a transformation of pixel variations, from the observation sequences to the prediction sequences. 
-In the specific implementation, we trained a FCN to learn a transformation of the pixel variations by mapping them into a new space where it is close to the groundtruth, just like the green line in \reffig{variation_chart}.
-After thresholding, we can easily get the labels of each observation. 
+The pixel variation is now regarded as a whole to safeguard data integrity.
+Consequently, the classification of pixels can be viewed as a transformation of pixel variations. 
+More specifically, a FCN is trained to learn the patterns of pixel variations and mapping them into a new space where it is close to the groundtruth data.
+The transformed variation is presented by the green line in \reffig{variation_chart}. 
+%After thresholding, we can easily get the labels of each observation. 
 %方法的好处是
@@
 It is hard to distinguish a foreground observation when its value are similar to the background ones. 
-However, classification on the transformed variation is much convenient and intuitive, due to the advantage of temporal information. 
-With the aid of deep learning method, the proposed approach can be effectively implemented.
+However, classification on the observations in a transformed variation is much convenient and intuitive, benefit from the strong learning ability of the FCN model. 
+%With the aid of deep learning method, the proposed approach can be effectively implemented.
 
@@
 First and foremost, the size of outputs are adjustable in FCNs, which allows an end-to-end mapping of input patches and prediction patches at each pixel position. 
-We hope to determine the label of a pixel through the comparison of its compatriot in time sequence. 
+We hope to determine the label of an observation through the comparison of its compatriot in time sequence. 
 There is one more point I ought to touch on, that since the feature maps are no longer need to be converted into vectors, spatial information can be retained. 
@@
 Therefore, traditional methods like the PAWCS, the WeSamBE and the SharedModel falsely segments part of shadows as moving objects. 
-In addition, the foreground provided by the UBSS is incomplete on the part of the pedestrian's body due to the interference of shades, which can be owing to the severe dependency of texture features. 
+In addition, the foreground provided by the IUTIS-5 is incomplete on the part of the pedestrian's body due to the interference of shades, which can be owing to the severe dependency of texture features.
 Whereas, the DeepBS performs well in this video benefited from the utilization of CNN. 
@@
 The quantitative evaluation of proposed approach on CDnet 2014 is shown in the \reftab{tab1}. 
-It can be inferred that the proposed approach significantly outperformed all of the compared state-of-the-art algorithms in most of complex scenes and achieved 6\% gain in FM over the second one on the whole dataset.
-Moreover, in order to compare proposed approach with the DBMF, which is also based on deep learning and only publish their results in several special vides. 
+It can be inferred that the proposed approach significantly outperformed all of the compared state-of-the-art algorithms in most of complex scenes and achieved 11.37\% gain in FM over the second one on the whole dataset.
+Moreover, in order to compare proposed approach with the DBMF, which is also based on deep learning and only publish their results in  specific videos. 
 The proposed approach has also ran in these video and the results are shown in Table 2. 
@@
 However, the proposed approach focused on the pixels variation in temporal sequence rather than low-level static features such as color, edges and textures, which gives us the ability to avoid the shortcomings of the background models.
-Consequently, the proposed approach still get considerably better results, which over 10.46\% in FM metrics compared with the DeepBS and over 6.38\% compared with the DBMF.
+Consequently, the proposed approach still get considerably better results, which over 17.85\% in FM metrics compared with the DeepBS and over 9.50\% compared with the DBMF.
 The evaluation of proposed approach in CAMO-UOW dataset is shown in the \reftab{tab3}. 
@@
 In contrast, 90\% of data were used as training samples in the DBMF, which suggest that the proposed approach achieves well performance with limited training frames. 
-Considering that the videos in CAMO-UOW have fewer frames, we reduce the number of training frames to 49. 
+Considering that the videos in CAMO-UOW have fewer frames, we reduce the number of training frames to 64 for each video. 
 During the experience, the training set and testing set are completely separated. 
 More specifically, our FCN network is random initialized. 
-We train the network with mini-batches of size 200, a learning rate $α = 1 ∗ 10^{−3}$ over 20 epochs. 
+We train the network with mini-batches of size 200, a learning rate $\alpha  = 1 \times 10^{{−3}}$ over 20 epochs. 
 The last threshold $R$ is set to 0.6.

### 2018-09-06 draft.tex
.

@@
 In particular,
-we take advantage of the strong learning ability of the deep network to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
+we take advantage of the strong learning ability of the deep neural network to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
 %
@@
 %背景检测的难点
-foreground detection is essentially an binary classification in time sequence, where pixels in a video stream are separated into two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops).
+foreground detection is essentially an binary classification in time sequence, where pixels in a video stream are classified as two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops).
 In most cases, if we print out the historical observations of a single pixel, it is not hard to see that they usually keep their stability when belonging to the background. 
@@
 %图例解释困难点
-To give an intuitive understanding of the pixel variation, we plot the historical observations and corresponding groundtruth of a single pixel in  \reffig{variation_chart}, with the X axis showing their range of variation and the Y axis representing the time.
+To give an intuitive understanding of the pixel variation, we plot the historical observations and corresponding groundtruth of a single pixel in  \reffig{variation_chart}.
+% with the X axis showing their range of variation and the Y axis representing the time. 
 As we can see, there are several lines in three colors: blue, red and green. 
@@
 The benefits from variation transformation are evident and clearly seen. 
+Benefit from the strong learning ability of the FCN model, we are able to learn the variation patterns of background and foreground over a long period of time.
+And the variation patterns, in turn, contribute to the variation transformation where the value of each observation is adjusted according to its compatriot in time sequence.
 It is hard to distinguish a foreground observation when its value are similar to the background ones. 
-However, classification on the observations in a transformed variation is much convenient and intuitive, benefit from the strong learning ability of the FCN model. 
+Classification on the transformed variation, however, is much more convenient and intuitive.
+
 %With the aid of deep learning method, the proposed approach can be effectively implemented.

### 2018-09-08 draft.tex
.
none

@@
 % 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
-A fully convolutional network(FCN) is applied to find a transformation of pixel variations.
 % 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
-In particular,
-the pixel variation is represented by the sequence of pixel observations and used as the input of the FCN.
+In particular, the pixel variation is represented by the sequence of pixel observations, which is used as the input of fully convolutional network to find a transformation of pixels' variation.
 % 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
@@
 Foreground detection as a fundamental problem in computer vision\ \cite{Bouwmans201431} has been discussed over decades with the increasing number of cameras,
-which is widely used as the pre-processing step of video processing \cite{Barnich2011_2011_TIP}.
+which is widely used in the applications of video processing \cite{Barnich2011_2011_TIP}.
 % 传统的方法是怎么做的，有什么问题
@@
 %KDE
-A non-parametric background model is proposed by Elgammal et al. \cite{Elgammal2000Non}. 
+In addition, a non-parametric background model is proposed by Elgammal et al. \cite{Elgammal2000Non}. 
 They assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE). 
@@
     % 图例里描述一下。
-    \caption{It is hard to separate the foreground pixels from the background precisely in a time sequence.}
+    \caption{Comparison of the original pixel variation, groundtruth and transformed variation. They are represented by the blue line, red line and green line respectively.}
     \label{variation_chart}
 \end{figure}
+% It is hard to separate the foreground pixels from the background precisely in a time sequence.
 
@@
 
-The the flow chart is illustrated in \reffig{flow_chart}. 
+The flow chart of proposed approach is illustrated in \reffig{flow_chart}. 
 Firstly, we sample the input and ground truth images to generalize the pixel variations, and reshape them into patches and feed them into the network with its spatial neighbors. 

### 2018-11-13 draft.tex
.

@@
 % 这句话我也没看懂。。。
-Benefied from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
-the proposed approach adaptively generate superior peroformances in diversly complex scenes.
+Benefited from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
+the proposed approach adaptively generates superior performances in diverse nature scenes.
 %
@@
 for either belonging to the background or foreground scene.
-Traditional foreground detection algorithms focus on anaylsing the pixel variation, establishing background models with statistical methods such as GMM\cite{Stauffer1999} and KDE\cite{Elgammal2000Non}.
+Traditional foreground detection algorithms focus on analyzing the pixel variation, establishing background models with statistical methods such as GMM\cite{Stauffer1999} and KDE\cite{Elgammal2000Non}.
 However, due to the unpredictability and rapidity of the pixels' variation in natural scenes,
@@
 it is possible that the moving objects produce the similar or even the same observations of pixels to that of background.
-% similar to their counterparts of background but atually belong to foreground .
+% similar to their counterparts of background but actually belong to foreground .
 % 如图所示，像素观测值C就和背景的值几乎一模一样，
@@
 %
-Benefited from the noval framework of variation transformation,
+Benefited from the novel framework of variation transformation,
 proposed approach works well in diversely complex scenes adaptively.
@@
 % Ren:重新解释了pixel based methods
-Pixel-based methods usually assume the independence between neighboring pxiels,
+Pixel-based methods usually assume the independence between neighboring pixels,
 and utilize the low-level features, such as color or gradients for background subtraction.
@@
 % “High Quality Estimation of Multiple Intermediate Frames for Video Interpolation”
-To address this shortcoming, we introduce a framework of variation transformation learing, where pixel's historical observations are embedded in a piece of pixel patch and sorted in chronological order as a whole to enter our DPVTL model.
+To address this shortcoming, we introduce a framework of variation transformation learning, where pixel's historical observations are embedded in a piece of pixel patch and sorted in chronological order as a whole for the training of our DPVTL model.
 %这样的优点在于保留了数据的完整性，保留了数据的时序相关性。
 Bringing together the historical observations ensures the data integrity and preserves the temporal coherence of our training data. 
-Moreover, 
-the novel framework is capable of learning the patterns of pixel variation and exploiting the spatial-temporal context, compared to those classifiers based on the assumption of pixel independence. 
+On the other hand, the application of neural network guarantee the strong learning ability of our model.
+Thus, the proposed approach is more capable of learning the patterns of pixel variation and exploiting the spatial-temporal context, compared to those classifiers based on the assumption of pixel independence.
 %所以我们方法比基于像素的要好。
@@
 % Ren: 好的好的，不乱吹了，我看过有说have similar values的。。。。
-Region-based approaches consider the similiary between neighboring pixels, which is utilized to refine the pixel-level classification.
+Region-based approaches consider the similarity between neighboring pixels, which is utilized to refine the pixel-level classification.
 %
@@
 % cqzhao: 瞎说啥？？？SVM那个就是连续的几帧啊！他们的问题在于， 自然界太复杂，variation太多元，直接分析variation分析不出来，我们学到了variation的pattern，然后转换！
-Although some breakthroughs and progress have been made by applying those methods, especially deep learning based approaches with optimized network architechtures. 
-However, due to the diversity and complexity of nature scenes, it is still difficult to analyze the pixel variations for classification. 
+Some breakthroughs and progress have been achieved by applying those methods, especially deep learning based approaches with optimized network architectures. 
+However, due to the diversity of nature scenes, pixel variations can be very complex, leading to difficulty in analyzing specific pixel variation patterns.
 %我们的不同在于，我们的网络是训练去学习像素变动，并转换到新的空间去进行分类。
-Different with their methods, we focus on creating a transformation, which guarantees the linear sparability of pixel variations in the mapping space, rather than building classifiers for individual observations.
+Unlike existing ones, our method focus on creating a transformation, which guarantees the linear separability of pixel variations in the mapping space, rather than building classifiers for individual observations.
 %
@@
 %
-%Moreover, our DPVTL model is implemented without any assistance from other tradition foreground detection methods, hence the reliable performance owing to the noval framework of variation transformation.
+%Moreover, our DPVTL model is implemented without any assistance from other tradition foreground detection methods, hence the reliable performance owing to the novel framework of variation transformation.
 
@@
 %variation transformation 介绍。
-In this paper, a novel framework of pixel variation transformation are proposed. %用framework代替method?
-The pixel variation is now regarded as a whole to safeguard data integrity.
-Consequently, the classification of pixels can be viewed as a transformation of pixel variations. 
-More specifically, a FCN is trained to learn the patterns of pixel variations and mapping them into a new space where it is close to the groundtruth data.
+In this paper, a novel framework of pixel variation transformation is proposed. %用framework代替method?
+
+Different from existing methods, we decide to shift our attention form single pixel classification to variation transformation.
+%the pixel variation is now regarded as a whole to safeguard the data integrity.
+More specifically, a FCN is employed to learn the patterns of pixel variations and mapping them into a new space where they are close to the groundtruth data.
 The transformed variation is presented by the green line in \reffig{variation_chart}. 
@@
 %方法的好处是
-The benefits from variation transformation are evident and clearly seen. 
-Benefit from the strong learning ability of the FCN model, we are able to learn the variation patterns of background and foreground over a long period of time.
-And the variation patterns, in turn, contribute to the variation transformation where the value of each observation is adjusted according to its compatriot in time sequence.
+The benefits are evident and clearly seen. 
 It is hard to distinguish a foreground observation when its value are similar to the background ones. 
 Classification on the transformed variation, however, is much more convenient and intuitive. 
+With the strong learning ability of the FCN, we are able to learn the diverse variation patterns of background and foreground over a long period of time.
+And the variation patterns, in turn, contribute to the variation transformation where the value of each observation is adjusted according to its compatriot in time sequence.
 
@@
 \begin{equation}
-Stack_{(x)}=\{I_x,I_{(x+p)},I_{(x+2p)},\dots,I_L \},\quad p\times l=L,\quad 1\leq   x\leq p , 
+    \begin{aligned}
+&Stack_{(x)}=\{I_x,I_{(x+p)},I_{(x+2p)},\dots,I_L \},\\
+&\quad p\times l=L,\quad 1\leq   x\leq p , 
+    \end{aligned}
 \end{equation}
@@
 However, the size of feature maps will shrink quickly during forward computation. 
-In order to make our prediction the same size as the input patches, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input patches before the training. 
+In preprocessing, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input patches before the training. 
 After the forward computing, observations in input patches are mapped into a new space where they can be easily classified by thresholding. 
@@
 The CDnet is the largest dataset for foreground detection so far as we are aware, containing 11 categories with several complexly challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
-The CAMO-UOW is another challenging benchmark which contains 10 high resolution videos. 
+The CAMO-UOW is a challenging benchmark for camouflaged foreground detection, which contains 10 high resolution videos. 
 For each video, one or two persons appear in the scene with the clothes in the similar color as the background.
@@
 RMoG\cite{Varadarajan2013}        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
-DPVTL        & \textbf{0.9811}   & 0.9329  & \textbf{0.9014}     & \textbf{0.9595}    & \textbf{0.9467} & \textbf{0.9479}  & \textbf{0.8780}   & 0.7818     & \textbf{0.7737}     & \textbf{0.5957} & \textbf{0.9034}  & \textbf{0.8789} \\ \hline
+DPVT        & \textbf{0.9811}   & 0.9329  & \textbf{0.9014}     & \textbf{0.9595}    & \textbf{0.9467} & \textbf{0.9479}  & \textbf{0.8780}   & 0.7818     & \textbf{0.7737}     & \textbf{0.5957} & \textbf{0.9034}  & \textbf{0.8789} \\ \hline
 \end{tabular}
@@
 DBMF\cite{Yang2018DBMF}     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
-DPVTL     & \textbf{0.9888}  & \textbf{0.9819} & \textbf{0.9728}      & \textbf{0.9808}   & \textbf{0.9394} & \textbf{0.9333} & \textbf{0.9662}  \\ \hline
+DPVT     & \textbf{0.9888}  & \textbf{0.9819} & \textbf{0.9728}      & \textbf{0.9808}   & \textbf{0.9394} & \textbf{0.9333} & \textbf{0.9662}  \\ \hline
 \end{tabular}
@@
 \hline
-Methods  & MOG2\cite{ZIVKOVIC2006773} & FCI\cite{Baf2008FCI}  & LBA-SOM\cite{LBA-SOM2008} & PBAS & SuBSENSE & ML-BGS\cite{ML-BGS2007} & DECOLOR\cite{DECOLOR2013}       & COROLA\cite{SHAKERI201628} & FWFC\cite{Li2018CAMO}          & Ours          \\ \hline
+Methods  & MOG2\cite{ZIVKOVIC2006773} & FCI\cite{Baf2008FCI}  & LBA-SOM\cite{LBA-SOM2008} & PBAS & SuBSENSE & ML-BGS\cite{ML-BGS2007} & DECOLOR\cite{DECOLOR2013}       & COROLA\cite{SHAKERI201628} & FWFC\cite{Li2018CAMO}          & DPVT          \\ \hline
 Video 1  & 0.79 & 0.88 & 0.8     & 0.9  & 0.89     & 0.89   & 0.92          & 0.8    & 0.94 & \textbf{0.96} \\
@@
 \label{sec6}
-In this paper, we proposed a noval foreground detection approach based on deep learning and the variation transformation learning.
-The DPVTL model include a FCN network and a noval variation transformation learing framework, which allows us to efficiently combine the temporal coherence and distribution information of pixels over a long period of time.
+In this paper, we proposed a novel foreground detection approach based on deep learning and the variation transformation learning.
+The DPVTL model include a FCN network and a novel variation transformation learning framework, which allows us to efficiently combine the temporal coherence and distribution information of pixels over a long period of time.
 Comparison with other traditional and deep learning methods shows that the DPVTL has good properties on several challenging scenes.

### 2018-11-15 draft.tex
.

@@
 %
-Comprehensive experiments in several standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
+Comprehensive experiments in several standard benchmarks demonstrate the superiority of the proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
 %
@@
 In the diversely natural scenes,
-it is possible that the moving objects produce the similar or even the same observations of pixels to that of background.
+it is possible that moving objects produce the similar or even the same observations of pixels to that of background.
 % similar to their counterparts of background but actually belong to foreground .
@@
 % 我们的就是希望把这个variation 转化到更简单的地方去
-In this work, we focus on learning the pattern of pixels' variation and transforming the variations into a new space where the observations are easier to classified, rather than learning a classifier for individual pixels.
-As shown in the bottom part of the \reffig{idea}, the pattern of fragment consist of observations A-D can be learned by the network and transformed into another fragment where these observations are easily and correctly classified as foreground.
+In this work, we focus on learning the pattern of pixels' variation and transforming the variations into a new space where the observations are easier to classify, rather than learning a classifier for individual pixels.
+As shown in the bottom part of the \reffig{idea}, the pattern of fragment consists of observations A-D can be learned by the network and transformed into another fragment where these observations are easily and correctly classified as foreground.
 % transformatin 之后，就很容易分类了，然后这就是我们的方法的核心了
-Based on this motivation, the Deep Variation Transformation model for foreground detection is proposed.
-% 
+Based on this, the Deep Variation Transformation model for foreground detection is proposed.
+% motivation
 % %实际应用中的挑战
@@
 %
-Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantees the linear separability of pixels in the transformed variation.
+Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn patterns of the pixel variation and find a transformation which guarantees the linear separability of pixels in the transformed variation.
 %
@@
 %
-Benefited from the novel framework of variation transformation,
+Benefited from the innovative framework of variation transformation,
 proposed approach works well in diversely complex scenes adaptively.
@@
 % XXX 不会用引用可以问我或者曲师兄。
-The rest part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion about the early and recent relevant works. 
+The rest part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion of the early and recent relevant works. 
 %
@@
 Moreover,
-Zivkovic et al.\ \cite{Zivkovic2004} improve the GMM method with the utilization of recursive equation
+Zivkovic et al.\ \cite{Zivkovic2004} improve the GMM method with the utilization of the recursive equation
 to automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
@@
 Hence, Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.
-The incoming pixels are compared with these codewords to see if their distances lies within a certain bound. 
+The incoming pixels are compared with these codewords to see if their distances lie within a certain bound. 
 %KDE
@@
 The background model of ViBe consists of pixel samples from the video stream.
-Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists sufficient samples with a distance to itself within a certain range.
+Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exist sufficient samples with a distance to itself within a certain range.
 %PBAS
@@
 Bringing together the historical observations ensures the data integrity and preserves the temporal coherence of our training data. 
-On the other hand, the application of neural network guarantee the strong learning ability of our model.
+On the other hand, the application of neural network guarantees the strong learning ability of our model.
 Thus, the proposed approach is more capable of learning the patterns of pixel variation and exploiting the spatial-temporal context, compared to those classifiers based on the assumption of pixel independence.
@@
 Varadarajan et al.\ \cite{2015_PR_Varadarajan20153488} proposed a region-based GMM model,
-which is derived from expectation maximization theory with the consideration of neighboring pixels.
+which is derived from expectation-maximization (EM) theory with the consideration of neighboring pixels.
 % Spatiotemporal GMM
@@
 \subsection{Machine Learning based Methods}
-The last category of background subtraction methods apply traditional machine learning and deep learning for the foreground detection.
+The last category of background subtraction methods applies traditional machine learning and deep learning for the foreground detection.
 
@@
 %
-Recent years, deep learning methods start to flourish in several computer vision fields.
+Recent years, deep learning methods begin to flourish in several computer vision fields.
 A novel approach for foreground detection with the use of the Convolutional Neural Network(CNN) is proposed by Wang et al.\cite{wang2016PRL}.
-They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which perform excellently with sufficient training data.
+They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which performs excellently with sufficient training data.
 %
@@
 %DBMF
-In \cite{Yang2018DBMF}, a fully convolutional network with the skip architecture is proposed for foreground detection. 
-The authors also proposed a temporal approach to sample training images from the given video, thus providing the background model with limited temporal information.
+In \cite{Yang2018DBMF}, a fully convolutional network with the skip architecture is proposed. 
+The authors also utilize a temporal approach to sample training images from the given video, thus providing the background model with limited temporal information.
 
@@
 %
-Besides, our network is trained to learn the patterns of pixel variations, which promises a better performance in time series modeling on temporal coherence.
+Besides, our network is trained to learn patterns of pixel variations, which promise a better performance in time series modeling on temporal coherence.
 %
@@
 %背景检测的难点
-foreground detection is essentially an binary classification in time sequence, where pixels in a video stream are classified as two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops).
+Foreground detection is essentially a binary classification in time sequence, where pixels in a video stream are classified as two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops).
 In most cases, if we print out the historical observations of a single pixel, it is not hard to see that they usually keep their stability when belonging to the background. 
-However, there are some exceptions: historical observations varies regularly when belonging to some dynamic background scenes(e.g. 
+However, there are some exceptions: historical observations vary regularly when belonging to some dynamic background scenes(e.g. 
 waves, swaying tree leaves). 
@@
 %图例解释困难点
-To give an intuitive understanding of the pixel variation, we plot the historical observations and corresponding groundtruth of a single pixel in  \reffig{variation_chart}.
+To give an intuitive understanding of the pixel variation, we plot the historical observations and the corresponding groundtruth of a single pixel in  \reffig{variation_chart}.
 % with the X axis showing their range of variation and the Y axis representing the time. 
 As we can see, there are several lines in three colors: blue, red and green. 
-The blue line consist of original observations, representing a piece of pixel variation. 
+The blue line consists of original observations, representing a piece of pixel variation. 
 Accordingly, the red line is made of the groundtruth data, corresponding to the observations from the blue one.  
-And the green line consist of the outputs of the proposed approach which represent the transformed variation.
+And the green line consists of the outputs of the proposed approach which represent the transformed variation.
 
@@
 %图例说明可能面临的挑战
-For example, in \reffig{variation_chart}, it is noticeable that some foreground observations in blue line share the similarly value with background ones. 
+For example, in \reffig{variation_chart}, it is noticeable that some foreground observations in blue line share the same or similarly value with background ones. 
 In that case, those popular methods will inevitably yield some sticky moments when separating the pixels in the blue line. 
@@
 
-Different from existing methods, we decide to shift our attention form single pixel classification to variation transformation.
+Different from existing methods, we decide to shift our attention from single pixel classification to variation transformation.
 %the pixel variation is now regarded as a whole to safeguard the data integrity.
-More specifically, a FCN is employed to learn the patterns of pixel variations and mapping them into a new space where they are close to the groundtruth data.
+More specifically, a FCN is employed to learn patterns of pixel variations and mapping them into a new space where they are close to the groundtruth data.
 The transformed variation is presented by the green line in \reffig{variation_chart}. 
@@
 The benefits are evident and clearly seen. 
-It is hard to distinguish a foreground observation when its value are similar to the background ones. 
+It is hard to distinguish a foreground observation when its value is similar to the background ones. 
 Classification on the transformed variation, however, is much more convenient and intuitive. 
@@
 In this section, we will introduce the details of proposed approaches. 
-We explain the production of pixel patches, which is a specific form of the pixel variation, and the architecture of our network.
+We explain the production of the pixel patch, which is a specific form of the pixel variation, and the architecture of our network.
 
-The flow chart of proposed approach is illustrated in \reffig{flow_chart}. 
+The flow chart of the proposed approach is illustrated in \reffig{flow_chart}. 
 Firstly, we sample the input and ground truth images to generalize the pixel variations, and reshape them into patches and feed them into the network with its spatial neighbors. 
@@
 Given different videos, their numbers of frames are generally different. 
-In order to keep each piece of variation the same length, image stacks are sampled form the given videos before the pixel variations are extracted. 
+In order to keep each piece of variation the same length, image stacks are sampled from the given videos before the pixel variations are extracted. 
 Let denote the frames sequence as $\{ I_1,I_2,I_3,\dots,I_L\}$.
@@
 However, vectors are not appropriate for the network training and learning. 
-Besides, we also hope the pixel observations can be interacted with their further compatriots in temporal sequence. 
+Besides, we also hope pixel observations can be interacted with their further compatriots in temporal sequence. 
 Thus we reshape the variations into pixel patches as the input of our network. 
@@
 \end{equation}
-where the $C$ represents the concatenating process on the third dimension.
+where the $C$ represents the concatenation process on the third dimension.
 And neighboring patches are denoted as $SM_1$ and $SM_2$ respectively.
@@
 %In the previous steps, original videos are broken down into pixel patches which contain abundant background information. 
-Correspondingly, the groundtruth patches are obtained in a similar way as the input ones, except the concatenating process, as shown in the \reffig{flow_chart}. 
-Both of them are fed into the network for the training to find a end-to-end transformation at each pixel position. 
+Correspondingly, the groundtruth patches are obtained in a similar way as the input ones, except the concatenation process, as shown in the \reffig{flow_chart}. 
+Both of them are fed into the network for training to find a end-to-end transformation at each pixel position. 
 However, the size of feature maps will shrink quickly during forward computation. 
@@
 The SCE is calculated between the transformed patches and the corresponding groundtruth patches. 
-Boundaries of moving objects and pixels that out of the region of interest are ignored in the cost function.
-Finally, we get the transformed variation through the FCN, which are easier for classification.
+Boundaries of moving objects and pixels that out of the region of interest are not taken into account in the cost function.
+Finally, we get the transformed variation through the FCN, which are a lot easier for classification.
 
@@
 
-Different with CNNs, FCNs utilize convolutional layers with $1\times 1$ kernels to take the place of fully connected layers, which provides several benefits. 
-First and foremost, the size of outputs are adjustable in FCNs, which allows an end-to-end mapping of input patches and prediction patches at each pixel position. 
+Different with CNNs, FCNs utilize convolutional layers with $1\times 1$ kernels to take the place of fully connected layers, which provide several benefits. 
+First and foremost, the size of output is adjustable in FCNs, which allows an end-to-end mapping of input patches and prediction patches at each pixel position. 
 We hope to determine the label of an observation through the comparison of its compatriot in time sequence. 
-There is one more point I ought to touch on, that since the feature maps are no longer need to be converted into vectors, spatial information can be retained. 
-The last but not the least, FCNs have been used in sematic segmentation and researchers found FCNs have a strong learning ability which won't lost to the traditional ones. 
-Meanwhile, it's also a high efficient computation model.
+There is one more point I ought to touch on, that since the feature maps are no longer needed to be converted into vectors, spatial information can be retained. 
+The last but not the least, FCNs have been used in sematic segmentation and researchers found FCNs have a strong learning ability which won't lose to the traditional ones. 
+Meanwhile, it's also a highly efficient computation model.
 
@@
 The structure of our FCN for foreground detection is shown in \reffig{flow_chart}. 
-The proposed FCN contains 5 convolutional layers and a convolutional layer which has a filter size of $1\times 1$. 
-We use the Rectified Linear Unit (ReLU) as activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
+The proposed FCN contains 6 convolutional layers, and the last convolutional layer has a filter size of $1\times 1$. 
+We use the Rectified Linear Unit (ReLU) as the activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
 We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
@@
 The main challenge comes from the dynamic background, in which it is so hard to describe the background by a single image. 
-In this condition, since the traditional foreground detection method such as the SharedModel and the WeSamBE do not have the enough ability to describe the complex dynamically background, they are fail to detect the people on the boat, as shown in the \reffig{results_chart}.
-Besides, the detected moving objects of the SharedModel are not accurate in boundary due to the utilization of texture features. 
+In this condition, since the traditional foreground detection method such as the SharedModel and the WeSamBE do not have enough ability to describe the complex dynamically background, they are fail to detect the people on the boat, as shown in the \reffig{results_chart}.
+Besides, the detected moving objects of the SharedModel are not accurate in the boundary due to the utilization of texture features. 
 In contrast, benefited from the strong learning ability of Deep Learning network, the DeepBS successfully detected the people. 
@@
 In the video "corridor" among the Thermal scene, there is no color information since the videos are obtained through a Thermal camera. 
-Moreover, the moving objects in these videos are exceedingly fuzzy and indistinct, which is the main challenge of this category. 
+Moreover, moving objects in these videos are exceedingly fuzzy and indistinct, which is the main challenge of this category. 
 The WeSamBE, the SharedModel and the PAWCS successfully detect the target objects, owing to a stable background in this indoor video. 
-However, they fail to remove the reflections since their modeling ability have already reached a limit under the extreme condition of thermal map. 
+However, they fail to remove the reflections since their modeling ability has already reached a limit under the extreme condition of thermal map. 
 The DeepBS, by contrast, succeeds in eliminating most of the reflections. 
-Meanwhile, the moving objects are also clearly divided from the background thanks to the strong modeling ability of CNN. 
-However, due to the dependency of edge feature, a small object were missed in the detection result. 
+Meanwhile, moving objects are also clearly divided from the background thanks to the strong modeling ability of CNN. 
+However, due to the dependency of the edge feature, a small object were missed in the detection result. 
 Fortunately, the proposed approach focus on the pattern of pixels' variation, which should be theoretically effective even in the observation without the color information. 
-Consequently, our DPVL performed much better than compared algorithms, with the situation that most parts of shadow are removed and the segmentation results are more accurate.
+Consequently, our DPVL performed much better than compared algorithms, with the situation that most parts of the shadow are removed and the segmentation results are more accurate.
 
@@
 
-The quantitative evaluation of proposed approach on CDnet 2014 is shown in the \reftab{tab1}. 
+The quantitative evaluation of the proposed approach on CDnet 2014 is shown in the \reftab{tab1}. 
 It can be inferred that the proposed approach significantly outperformed all of the compared state-of-the-art algorithms in most of complex scenes and achieved 11.37\% gain in FM over the second one on the whole dataset.
-Moreover, in order to compare proposed approach with the DBMF, which is also based on deep learning and only publish their results in  specific videos. 
-The proposed approach has also ran in these video and the results are shown in Table 2. 
+Moreover, in order to compare the proposed approach with the DBMF, which is also based on deep learning and only publish their results in  specific videos. 
+The proposed approach has also ran in these videos and the results are shown in Table 2. 
 Again, the proposed approach has noticeably better performance than the DBMF and some other classical background approaches.
@@
 From our own perspective, that good performance should attribute to the stronger modeling ability and learning adaptation of CNN and FCN. 
-However, the proposed approach focused on the pixels variation in temporal sequence rather than low-level static features such as color, edges and textures, which gives us the ability to avoid the shortcomings of the background models.
-Consequently, the proposed approach still get considerably better results, which over 17.85\% in FM metrics compared with the DeepBS and over 9.50\% compared with the DBMF.
-The evaluation of proposed approach in CAMO-UOW dataset is shown in the \reftab{tab3}. 
-Unlike the CDnet dataset, the videos of CAMO-UOW dataset are specially proposed for the moving objects with camouflage, which is the main challenge of this dataset. 
+However, the proposed approach focused on the pixels variation in temporal sequence rather than low-level static features such as color, edges and textures, which give us the ability to avoid the shortcomings of the background models.
+Consequently, the proposed approach still gets considerably better results, which over 17.85\% in FM metrics compared with the DeepBS and over 9.50\% compared with the DBMF.
+The evaluation of the proposed approach in CAMO-UOW dataset is shown in the \reftab{tab3}. 
+Unlike the CDnet dataset, the videos of CAMO-UOW dataset are specially proposed for moving objects with camouflage, which is the main challenge of this dataset. 
 As shown in the \reftab{tab3} proposed approach achieves better performance compared to its competitions, with an average F-measure of 0.97, compared to values between 0.77 and 0.94 for the other methods.
-Therefore, it is fair to say that proposed approach performs better compared with their peers.
+Therefore, it is fair to say that the proposed approach performs better compared with their peers.
 
-In this dataset, target objects have the similar color and textures with the background, which brings a lot of difficulties and obstacles to traditional methods. 
+In this dataset, target objects have similar color and textures with the background, which brings a lot of difficulties and obstacles to traditional methods. 
 However, our FCN is a powerful Neural Network model which is good at capturing the non-linearities of the manifold of pixel variations.
 
-All these experiments of the proposed method were implemented in matlab and ran on the computer with Nvidia tasela K80 GPU and all images are keep their original resolution. 
+All these experiments of the proposed method were implemented in matlab and ran on the computer with Nvidia tasla K80 GPU and all images keep their original resolution. 
 For each video in CDnet 2014, 100 training frames are extracted to produce the image patch. 
@@
 In contrast, 90\% of data were used as training samples in the DBMF, which suggest that the proposed approach achieves well performance with limited training frames. 
-Considering that the videos in CAMO-UOW have fewer frames, we reduce the number of training frames to 64 for each video. 
+Considering that videos in CAMO-UOW have fewer frames, we reduce the number of training frames to 64 for each video. 
 During the experience, the training set and testing set are completely separated. 
@@
 In this paper, we proposed a novel foreground detection approach based on deep learning and the variation transformation learning.
-The DPVTL model include a FCN network and a novel variation transformation learning framework, which allows us to efficiently combine the temporal coherence and distribution information of pixels over a long period of time.
+The DPVTL model includes a FCN network and a novel variation transformation learning framework, which allows us to efficiently combine the temporal coherence and distribution information of pixels over a long period of time.
 Comparison with other traditional and deep learning methods shows that the DPVTL has good properties on several challenging scenes.

### 2018-11-20 draft.tex
.

@@
 In order to keep each piece of variation the same length, image stacks are sampled from the given videos before the pixel variations are extracted. 
-Let denote the frames sequence as $\{ I_1,I_2,I_3,\dots,I_L\}$.
+Let denote the frames sequence as:
+\begin{equation}
+    \mathcal{I} = \{I_1, I_2, \cdots, I_T\} \\\\
+\end{equation}
+
 And image stacks can be defined as follows: 
 \begin{equation}
-    \begin{aligned}
-&Stack_{(x)}=\{I_x,I_{(x+p)},I_{(x+2p)},\dots,I_L \},\\
-&\quad p\times l=L,\quad 1\leq   x\leq p , 
-    \end{aligned}
+    \mathcal{I}^d = \mathcal{D}(\mathcal{I})=  \{I_1, I_{[2 \cdot \frac{T}{N}]}, \cdots, I_{[(N - 1) \cdot \frac{T}{N}]} \}
 \end{equation}
@@
 where $I_t$ is the frame $t$ of the given video. 
-And $p$ is an integer number depended on the video frames length. 
+$T$ and $N$ represent respectively the totall number of the video frames and the number of image stacks. 
 For each video, we can produce multiple image stacks and choose one of them for the training. 
@@
 % 第二步提取Pixel variation
-After the sampling process, a large number of observation sequences, or pixel variations, are extracted from the chosen stack at each pixel position, which is shown as follows: 
-\begin{equation}
-Sq_{(m)}=\{P_1^m,P_2^m,P_3^m,\dots,P_n^m\},
-\end{equation}
-where $P_t^m$ denotes the numerical value of pixel $m$ at frame $t$ in the chosen stack. 
+After the sampling process, a large number of observation sequences, or pixel variations, can be extracted from the chosen stack at each pixel position.
 Each of the pixel variation is a piece of temporal information which containing the changing patterns of background pixels. 
-And each of them is of fixed length $n$. 
+And each of them is of fixed length $\cdot \frac{T}{N}$. 
 It is notable that observation sequences are extracted from individual pixel positions, which promises that sufficient training data can be obtained with only one image stack.
@@
 % 第三步变成矩阵形式，解释为什么要把variation 变形
-Our motivation is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. 
+Our task is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. 
 However, vectors are not appropriate for the network training and learning. 
@@
 \begin{equation}
-H^m=P^m_{i+j\times d}=\begin{bmatrix}
- P^m_1& P^m_2  &\dots  &P^m_d \\ 
-\vdots &  &  &\vdots \\ 
- P^m_{1+(d-1)d}& \dots & \dots & P^m_n
-\end{bmatrix},\quad d^2=n.
+    S_{x,y}(m,n) = \mathcal{C}(\mathcal{I}^d, R) = \mathcal{I}_{m \times R + n} (x,y)
 \end{equation}
-where the pixel patch is denoted as $H^m$, and the parameter $i$ and $j$ is the column and row of the pixel patch. 
-Observations are put into the $d\times d$ patch from top to bottom and left to right.
+where the pixel patch is denoted as $S_{x,y}(m,n)$, at the pixel positionthe pixel position $(x,y)$. 
+And the parameter $R$ is the column and row of pixel patches. 
+the column and row of the pixel patch. 
+Observations are put into the $R\times R$ patch from top to bottom and left to right.
 To put it another way, the pixel patch is just a specific form of the pixel variation. 
@@
 In order to benefit from the spatial context, we concatenate the pixel patch with 2 neighboring pixel patches, which are randomly selected in the 8-connected neighborhood of each pixel position. 
-The input patch $I$ of our network is defined as:
+The input patch of our network is defined as:
 \begin{equation}
-I = C(H^m, SM_1, SM_2),
+    S_{x,y}(m,n) = \mathcal{C}o(S_{x,y}(m,n), S_{x', y'}(m,n), S_{x'', y ''}(m, n))
 \end{equation}
-where the $C$ represents the concatenation process on the third dimension.
-And neighboring patches are denoted as $SM_1$ and $SM_2$ respectively.
+where the $\mathcal{C}o$ represents the concatenation process on the third dimension.
+And neighboring patches are at pixel position $(x',y')$ and $(x'',y'')$ respectively.
 
@@
 \begin{equation}
-H_p= \mathcal L (E_x (H)),
+    \begin{split}
+        S'(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} (Pad(S(m,n))) \cdots  ) )  \\
+          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(S(m,n))
+    \end{split}
 \end{equation}
-where, $H_p$ is the prediction of the network, and the forward computation of network is represented by $\mathcal L$.
-The symmetric padding process is denoted as $E_x$, where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel patch $H$.
+where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$.
+The symmetric padding process is denoted as $Pad$, where we have lost none of the pixel information to make the output $S'(m,n)$ the same size as the pixel patch $S(m,n)$.
 Another advantage of symmetric padding is that the order information still remains.
@@
     \begin{aligned}
-        & \ell_{H_p, H_{gt}} =  \sum\limits_{x \in X, y \in Y}^{} H_{gt}(x,y) log(S(H_p(x,y)))  \\
-        & + (1 - H_{gt}(x,y)) log(1 - S(H_p(x,y))) \\
-        & S(x) =\frac{1}{1+e^{-x}}\  ,
+        & \mathcal{L}(S'(x,y), S^{gt}(x,y))  =  \sum_{x=1}^{m}\sum_{y=1}^{n} S^{gt}(x,y) log(Sig(S'(x,y)))  \\
+        & + (1 - S^{gt}(x,y)) log(1 - Sig(S'(x,y))) \\
+        & Sig(x) =\frac{1}{1+e^{-x}}\  ,
     \end{aligned}
 \end{equation}
-where $H_{gt}$ denotes the groundtruth patch which is given by the corresponding groundtruth stack, and $S$ represents the sigmoid function. 
+where $S^{gt}(x,y)$ denotes the groundtruth patch which is given by the corresponding groundtruth stack, and $Sig$ represents the sigmoid function. 
 The SCE is calculated between the transformed patches and the corresponding groundtruth patches. 
@@
 As shown in the \reffig{flow_chart}, the prediction maps can be reconstructed from the prediction patches.
-Then a global threshold $r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
+Then a global threshold $T_r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
 The threshold function is given by
@@
 \begin{equation}
-F=g(M,r) ,
+    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R))
 \end{equation}
-where $M$ is the prediction map, and the $F$ denotes the final foreground map given by our DPVTL model.
+where the $M$ denotes the final foreground map given by our DPVTL model.
 After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery.
@@
 Consequently, the proposed approach still gets considerably better results, which over 17.85\% in FM metrics compared with the DeepBS and over 9.50\% compared with the DBMF.
+
 The evaluation of the proposed approach in CAMO-UOW dataset is shown in the \reftab{tab3}. 
@@
 Comparison with other traditional and deep learning methods shows that the DPVTL has good properties on several challenging scenes.
-The future work will be focused on improving the DPVTL in terms of network architecture updating and integration of local spatial coherence.
+%The future work will be focused on improving the DPVTL in terms of network architecture updating and integration of local spatial coherence.
 

### 2018-11-20 draft.tex
.

@@
 % 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
-In particular, the pixel variation is represented by the sequence of pixel observations, which is used as the input of fully convolutional network to find a transformation of pixels' variation.
+In particular, the pixel variation is represented by the sequence of pixel observations, which is used as the input of fully convolutional network(FCN) to find a transformation of pixels' variation.
 % 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
@@
 for either belonging to the background or foreground scene.
-Traditional foreground detection algorithms focus on analyzing the pixel variation, establishing background models with statistical methods such as GMM\cite{Stauffer1999} and KDE\cite{Elgammal2000Non}.
+Traditional foreground detection algorithms focus on analyzing the pixel variation, establishing background models with statistical methods such as GMM\cite{Stauffer1999}\cite{lee2005} and KDE\cite{Elgammal2000Non}.
 However, due to the unpredictability and rapidity of the pixels' variation in natural scenes,
@@
 % cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
-In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods.
+In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods\cite{Goyal2018}.
 % 注意英语和汉语的表达习惯
@@
 %GMM+i
-Moreover,
 Zivkovic et al.\ \cite{Zivkovic2004} improve the GMM method with the utilization of the recursive equation
@@
 %codebook
-Hence, Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.
+Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.
 The incoming pixels are compared with these codewords to see if their distances lie within a certain bound. 
@@
 % Ren: 好的好的，不乱吹了，我看过有说have similar values的。。。。
-Region-based approaches consider the similarity between neighboring pixels, which is utilized to refine the pixel-level classification.
+Region-based approaches are usually performed at block-level resolution, in order to exploit the spatial context between neighboring pixels.
 %
@@
 \begin{equation}
-    \mathcal{I} = \{I_1, I_2, \cdots, I_T\} \\\\
+    \mathcal{I} = \{I_1, I_2, \cdots, I_T\}, \\\\
 \end{equation}
@@
 \begin{equation}
-    \mathcal{I}^d = \mathcal{D}(\mathcal{I})=  \{I_1, I_{[2 \cdot \frac{T}{N}]}, \cdots, I_{[(N - 1) \cdot \frac{T}{N}]} \}
+    \mathcal{I}^d = \mathcal{D}(\mathcal{I})=  \{I_1, I_{[2 \cdot \frac{T}{N}]}, \cdots, I_{[(N - 1) \cdot \frac{T}{N}]}, \}
 \end{equation}
@@
 \begin{equation}
-    S_{x,y}(m,n) = \mathcal{C}(\mathcal{I}^d, R) = \mathcal{I}_{m \times R + n} (x,y)
+    S_{x,y}(m,n) = \mathcal{C}(\mathcal{I}^d, R) = \mathcal{I}_{m \times R + n} (x,y),
 \end{equation}
@@
 \begin{equation}
-    S_{x,y}(m,n) = \mathcal{C}o(S_{x,y}(m,n), S_{x', y'}(m,n), S_{x'', y ''}(m, n))
+    S_{x,y}(m,n) = \mathcal{C}o(S_{x,y}(m,n), S_{x', y'}(m,n), S_{x'', y ''}(m, n)),
 \end{equation}
@@
         S'(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} (Pad(S(m,n))) \cdots  ) )  \\
-          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(S(m,n))
+          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(S(m,n)),
     \end{split}
@@
 \begin{equation}
-    \begin{aligned}
-        & \mathcal{L}(S'(x,y), S^{gt}(x,y))  =  \sum_{x=1}^{m}\sum_{y=1}^{n} S^{gt}(x,y) log(Sig(S'(x,y)))  \\
-        & + (1 - S^{gt}(x,y)) log(1 - Sig(S'(x,y))) \\
-        & Sig(x) =\frac{1}{1+e^{-x}}\  ,
-    \end{aligned}
+    \begin{split}
+         \mathcal{L}(S'(x,y),& S^{gt}(x,y))  =  \sum_{x=1}^{m}\sum_{y=1}^{n} S^{gt}(x,y) log(Sig(S'(x,y)))  \\
+        & + (1 - S^{gt}(x,y)) log(1 - Sig(S'(x,y))), 
+    \end{split}
+\end{equation}
+\begin{equation}
+       Sig(x) =\frac{1}{1+e^{-x}},
 \end{equation}
@@
 \begin{equation}
-    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R))
+    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R)),
 \end{equation}

### 2018-11-22 draft.tex
.

@@
 for either belonging to the background or foreground scene.
-Traditional foreground detection algorithms focus on analyzing the pixel variation, establishing background models with statistical methods such as GMM\cite{Stauffer1999}\cite{lee2005} and KDE\cite{Elgammal2000Non}.
+Traditional foreground detection algorithms focus on analyzing the pixel variation, establishing background models with statistical methods such as GMM\cite{Stauffer1999}\cite{lee2005} and KDE\cite{Elgammal2000Non}\cite{Mittal2004KDE}.
 However, due to the unpredictability and rapidity of the pixels' variation in natural scenes,
@@
 %SVM
-Traditional machine learning methods are commonly involved with support vector machines (SVM)\cite{Han2012} and Bayesian methods\cite{Zhang2014Statis}.
+Traditional machine learning methods are commonly involved with support vector machines (SVM)\cite{Chen2011}\cite{Han2012} and Bayesian methods\cite{Sheikh2005Bayesian}\cite{2012_TIP_OP_6099616}\cite{Zhang2014Statis}.
 For example, Han et al.
@@
 %
-Recent years, deep learning methods begin to flourish in several computer vision fields.
+In recent years, deep learning methods begin to flourish in several computer vision fields, and have demonstrated effective capabilities to handle time-series problems\cite{Mobahi2009}\cite{LANGKVIST201411}.
 A novel approach for foreground detection with the use of the Convolutional Neural Network(CNN) is proposed by Wang et al.\cite{wang2016PRL}.
@@
 
-Here we make a detailed introduction to the deep learning model we used and explain why we choose it.
+%Here we make a detailed introduction to the deep learning model we used and explain why we choose it.
 
-Different with CNNs, FCNs utilize convolutional layers with $1\times 1$ kernels to take the place of fully connected layers, which provide several benefits. 
+%Different with CNNs, FCNs utilize convolutional layers with $1\times 1$ kernels to take the place of fully connected layers, which provide several benefits.
 First and foremost, the size of output is adjustable in FCNs, which allows an end-to-end mapping of input patches and prediction patches at each pixel position.
-We hope to determine the label of an observation through the comparison of its compatriot in time sequence. 
-There is one more point I ought to touch on, that since the feature maps are no longer needed to be converted into vectors, spatial information can be retained. 
-The last but not the least, FCNs have been used in sematic segmentation and researchers found FCNs have a strong learning ability which won't lose to the traditional ones. 
-Meanwhile, it's also a highly efficient computation model.
+%We hope to determine the label of an observation through the comparison of its compatriot in time sequence. 
+%There is one more point I ought to touch on, that since the feature maps are no longer needed to be converted into vectors, spatial information can be retained. 
+%The last but not the least, FCNs have been used in sematic segmentation and researchers found FCNs have a strong learning ability which won't lose to the traditional ones. 
+%Meanwhile, it's also a highly efficient computation model. 
+%Based on above-mentioned factors, FCN is designed as the alternative network architecture in this paper.
 
-Based on above-mentioned factors, FCN is designed as the alternative network architecture in this paper. 
 The structure of our FCN for foreground detection is shown in \reffig{flow_chart}. 
@@
 
+\begin{figure*}[!t]	\centering
+    \includegraphics[width=\textwidth]{figure/fig3}
+\DeclareGraphicsExtensions.
+    \caption{The qualitative evaluation of the proposed method. All the results is followed in the CDnet 2014.}
+    \label{results_chart}
+\end{figure*}
+
 The quantitative and qualitative comparisons are shown in \reftab{tab1} and  \reffig{results_chart} respectively. 
@@
 Based on this insight, the FCN network focuses on learning the patterns of the pixel variation rather than a static background image, and proposed approach achieves promising performance in the canoe video.
-
-\begin{figure*}[!t]	\centering
-    \includegraphics[width=\textwidth]{figure/fig3}
-\DeclareGraphicsExtensions.
-    \caption{The qualitative evaluation of the proposed method. All the results is followed in the CDnet 2014.}
-    \label{results_chart}
-\end{figure*}
 

### 2018-11-22 exp1.m

@@ -1,0 +1,38 @@
+clear all
+close all
+clc
+
+data = load('lines.mat');
+
+
+data = data.lines;
+
+l1 = data{1};
+l2 = data{2};
+l3 = data{3};
+
+
+l1 = l1(1:3:120);
+l2 = l2(1:3:120);
+l3 = l3(1:3:120);
+
+len = max(size(l1));
+
+x = 1:len;
+
+
+figure
+% set(gca,'FontSize',30)
+set (gcf,'Position',[0 0 800 600], 'color','w')
+plot(x, l2, '-o', 'Color', [0.5 0.5 1], 'LineWidth', 2,'markerfacecolor',[0.5 0.5 1])
+hold on
+plot(x, l3, '-o', 'Color', [0.5 1 0.5], 'LineWidth', 2,'markerfacecolor',[0.5 1 0.5])
+hold on
+plot(x, l1, '-o', 'Color', [1 0.5 0.5], 'LineWidth', 2,'markerfacecolor',[1 0.5 0.5])
+legend('pixel variation','transfromed variation','groundtruth', 'Location', 'southeast')
+ylim([-50 300])
+
+set(gca,'FontName','Times New Roman','FontSize',16)
+
+print(gcf,'-r600','-dpng','lines.png');
+%saveas(gcf,'lines.png');

### 2018-12-02 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.
 On branch master
 Changes to be committed:
	modified:   draft.aux
	modified:   draft.log
	modified:   draft.out
	modified:   draft.pdf
	modified:   draft.tex

@@
 %me
-\section{foreground detection VIA DEEP VARIATION TRANSFORMATION}
+\section{Foreground Detection via Deep Variation Transformation}
 \label{sec4}
-In this section, we will introduce the details of proposed approaches. 
-We explain the production of the pixel patch, which is a specific form of the pixel variation, and the architecture of our network.
+In this section, the details of proposed approach is explained.
+%
+The flow chart of the proposed approach is illustrated in \reffig{flow_chart}.
+%
+We firstly introduce the procedure of generating pixels patch,
+which is feed into the network as well as the description of pixel variation.
+%
+Then,
+the architecture of the network, which is used for variation transformation, is explained.
+%
+%We explain the production of the pixel patch, 
+%which is a specific form of the pixel variation, and the architecture of our network. 
+%
 
-The flow chart of the proposed approach is illustrated in \reffig{flow_chart}. 
-Firstly, we sample the input and ground truth images to generalize the pixel variations, and reshape them into patches and feed them into the network with its spatial neighbors. 
-After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
 \begin{figure*}[!t] % FIGURE: figure/fig1 
@@
 \end{figure*}
+% Firstly, we sample the input and ground truth images to generalize the pixel variations, 
+% and reshape them into patches and feed them into the network with its spatial neighbors. 
+% %
+% After reassembling the patches into the complete output frame, 
+% it is post-processed, yielding the final segmentation of the respective video frame.
 
 % 第一步是对原视频进行采样
-Given different videos, their numbers of frames are generally different. 
-In order to keep each piece of variation the same length, image stacks are sampled from the given videos before the pixel variations are extracted. 
-Let denote the frames sequence as:
-\begin{equation}
-    \mathcal{I} = \{I_1, I_2, \cdots, I_T\}, \\\\
-\end{equation}
-
-And image stacks can be defined as follows: 
+There are usually large numbers of frames in a particular video.
+%
+In order to capture the global representation of pixel's variation,
+the training frames are sampled from the whole frame sequenece uniformly.
+%
+Let us denote the frame sequence as $\mathcal{I} = \{I_1, I_2, \cdots, I_T\}$,
+where $\mathcal{I}$ is denoted as the set of frames and $T$ is the numbers of frames.
+%
+The uniform sampling procedure is shown as follows:
+% 
+% Given different videos, their numbers of frames are generally different. 
+% In order to keep each piece of variation the same length,
+% image stacks are sampled from the given videos before the pixel variations are extracted. 
+% Let denote the frames sequence as:
+% \begin{equation}
+%     \mathcal{I} = \{I_1, I_2, \cdots, I_T\}, \\\\
+% \end{equation}
+% 
+% And image stacks can be defined as follows: 
 \begin{equation}
@@
 \end{equation}
+where $\mathcal{I}^d$ is the set of training frames,
+the $T$ and the $N$ represents the frame number of whole video and the training set respectively,
+and the $\mathcal{D}()$ is denoted as the sampling function.
+
+%
+
 % 解释采样的细节

### 2018-12-03 draft.tex
revised the thrid paragraph

@@
 % 第一步是对原视频进行采样
-There are usually large numbers of frames in a particular video.
+There are usually large numbers of frames in a particular video,
+and the number of frames for different videos are also different.
 %
@@
 and the $\mathcal{D}()$ is denoted as the sampling function.
+% 
+% 
+% %
+% 
+% 
+% 
+% % 解释采样的细节
+% where $I_t$ is the frame $t$ of the given video. 
+% $T$ and $N$ represent respectively the totall number of the video frames and the number of image stacks. 
+% For each video, we can produce multiple image stacks and choose one of them for the training. 
+% In addition, we can get compact pixel variations, which contain more temporal information than the continuous pixel sequences, by using equal interval sampling.
 
+After sampling the training frames,
+the training patches, which are used as the input of the network, are captured.
 %
-
-% 解释采样的细节
-where $I_t$ is the frame $t$ of the given video. 
-$T$ and $N$ represent respectively the totall number of the video frames and the number of image stacks. 
-For each video, we can produce multiple image stacks and choose one of them for the training. 
-In addition, we can get compact pixel variations, which contain more temporal information than the continuous pixel sequences, by using equal interval sampling.
-
-% 第二步提取Pixel variation
-After the sampling process, a large number of observation sequences, or pixel variations, can be extracted from the chosen stack at each pixel position.
-Each of the pixel variation is a piece of temporal information which containing the changing patterns of background pixels. 
-And each of them is of fixed length $\cdot \frac{T}{N}$. 
-It is notable that observation sequences are extracted from individual pixel positions, which promises that sufficient training data can be obtained with only one image stack.
-
-% 第三步变成矩阵形式，解释为什么要把variation 变形
-Our task is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. 
-However, vectors are not appropriate for the network training and learning. 
-Besides, we also hope pixel observations can be interacted with their further compatriots in temporal sequence. 
-Thus we reshape the variations into pixel patches as the input of our network. 
-A sample of the pixel patch is like this:
+The training patch is the description of the pixels' variation,
+which is captured by reshaping the observations in a particular pixel into a square patch.
+%
+Since the patch can be captured from each pixel, 
+a large number of training patches can be extracted with the training frames
+and each of these patches is of fixed numbers of pixels as $\frac{T}{N}$.
+%
+In addition, for each pixel included in the patch, a label of foreground or background is needed for training.
+%
+Therefore,
+there are labeling patches, which are captured by the similar procedure in the ground truth frames,
+are used as the output for training our network,
+and our network is actually an end-to-end transformation from pixels to labels.
+%
+Mathematically, the generation procedure of training patches is shown as follows:
 \begin{equation}
@@
 Since the pixel sequences are extracted from each pixel position, a large number of pixel patches can be extracted from only one single image stack, which promises sufficient training data for our network.
+
+% 
+% Mathmatically,
+% 
+% 
+% the labeling patches are also captured by the similar procedure in the groundtruth frames.
+% %
+% 
+% 
+% 
+% the frames of ground truth are 
+% 
+% 
+% which describe the variation of pixels' observations, are captured.
+% %
+% The pathces 
+% 
+% 
+% % 第二步提取Pixel variation
+% After the sampling process, a large number of observation sequences, or pixel variations, can be extracted from the chosen stack at each pixel position.
+% Each of the pixel variation is a piece of temporal information which containing the changing patterns of background pixels. 
+% And each of them is of fixed length $\cdot \frac{T}{N}$. 
+% It is notable that observation sequences are extracted from individual pixel positions, which promises that sufficient training data can be obtained with only one image stack.
+% 
+% % 第三步变成矩阵形式，解释为什么要把variation 变形
+% Our task is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. 
+% However, vectors are not appropriate for the network training and learning. 
+% Besides, we also hope pixel observations can be interacted with their further compatriots in temporal sequence. 
+% Thus we reshape the variations into pixel patches as the input of our network. 
+% A sample of the pixel patch is like this:
+% \begin{equation}
+%     S_{x,y}(m,n) = \mathcal{C}(\mathcal{I}^d, R) = \mathcal{I}_{m \times R + n} (x,y),
+% \end{equation}
+% where the pixel patch is denoted as $S_{x,y}(m,n)$, at the pixel positionthe pixel position $(x,y)$. 
+% And the parameter $R$ is the column and row of pixel patches. 
+% the column and row of the pixel patch. 
+% Observations are put into the $R\times R$ patch from top to bottom and left to right.
+% To put it another way, the pixel patch is just a specific form of the pixel variation. 
+% %Although the observation patch and the observation sequence belong to different forms of the pixel variation, they consist of the same components, and share the common temporal information from the pixel variation.
+% Since the pixel sequences are extracted from each pixel position, a large number of pixel patches can be extracted from only one single image stack, which promises sufficient training data for our network.
 

### 2018-12-09 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Your branch is up-to-date with 'origin/master'.
 Changes to be committed:
	modified:   draft.aux
	modified:   draft.blg
	modified:   draft.log
	modified:   draft.out
	modified:   draft.pdf
	modified:   draft.tex

@@
 \label{sec4}
-In this section, the details of proposed approach is explained.
+In this section, the details of proposed approach have been explained.
 %
-The flow chart of the proposed approach is illustrated in \reffig{flow_chart}.
+The pipeline of proposed approach is shown in the \reffig{flow_chart},
+which can be divided into three parts.
 %
-We firstly introduce the procedure of generating pixels patch,
-which is feed into the network as well as the description of pixel variation.
+Firstly, the procedure of the generation of pixels patch, 
+which is feed into the network for training as well as the description of pixel variation,
+is introduced.
 %
 Then,
-the architecture of the network, which is used for variation transformation, is explained.
+the architecture of the network, which is devised for transforming the variation of pixels' observations, is demonstrated.
+%
+Next,
+a reverse procedure of the generation of training data is used to reconstruct the foreground image from the transformed results.
 %
@@
 
+\subsection*{Training Data Generation}
 % 第一步是对原视频进行采样
+%从描述事实开始
+Fundamentally, 
+background subtraction is a classification of pixels' observations in time sequence.
+% 我们的动机
+In this work,
+the deep learning network is utilized to learn the pattern of variations implied in the observations of pixels.
+% 基于这个动机，我们是怎么做的
+Therefore,
+the training data feed into network is one kinds of description of pixels' variation,
+which is actually patches consist of pixels' observations.
+%
+In contrast, the output of the network is the probability of corresponding pixels belong to foreground or background,
+and the network is devised with an end-to-end architecture to transform the intensity of pixels to the probability of category the pixels belong to.
+
+% 用数学化的语言描述具体过程
+Let us denote the frame sequence in a video as $\mathcal{I} = \{I_1, I_2, \cdots, I_T\}$,
+where $\mathcal{I}$ is denoted as the set of frames and $T$ is the numbers of frames.
+%
 There are usually large numbers of frames in a particular video,
@@
 In order to capture the global representation of pixel's variation,
-the training frames are sampled from the whole frame sequenece uniformly.
+the training frames are sampled from the whole frame sequence uniformly.
 %
-Let us denote the frame sequence as $\mathcal{I} = \{I_1, I_2, \cdots, I_T\}$,
-where $\mathcal{I}$ is denoted as the set of frames and $T$ is the numbers of frames.
+% Let us denote the frame sequence as $\mathcal{I} = \{I_1, I_2, \cdots, I_T\}$,
+% where $\mathcal{I}$ is denoted as the set of frames and $T$ is the numbers of frames.
 %
@@
 
-After sampling the training frames,
+After sampling training frames,
 the training patches, which are used as the input of the network, are captured.
@@
 Therefore,
-there are labeling patches, which are captured by the similar procedure in the ground truth frames,
+the labeling patches, which are captured by the similar procedure in the ground truth frames,
 are used as the output for training our network,
@@
 \end{equation}
-where the pixel patch is denoted as $S_{x,y}(m,n)$, at the pixel positionthe pixel position $(x,y)$. 
-And the parameter $R$ is the column and row of pixel patches. 
-the column and row of the pixel patch. 
-Observations are put into the $R\times R$ patch from top to bottom and left to right.
-To put it another way, the pixel patch is just a specific form of the pixel variation. 
-%Although the observation patch and the observation sequence belong to different forms of the pixel variation, they consist of the same components, and share the common temporal information from the pixel variation.
-Since the pixel sequences are extracted from each pixel position, a large number of pixel patches can be extracted from only one single image stack, which promises sufficient training data for our network.
-
+where the $S_{x,y}(m,n)$ is denoted as the training patch extracted from the observations of pixel located at $(x,y)$,
+The $R$ is the user argument to control the radius of training patches
+and $\mathcal{C}(\mathcal{I}^d, R)$ is the function to covert the observations of pixels to training patches.
+% where the pixel patch is denoted as $S_{x,y}(m,n)$, at the pixel positionthe pixel position $(x,y)$. 
+% And the parameter $R$ is the column and row of pixel patches. 
+% the column and row of the pixel patch. 
+% Observations are put into the $R\times R$ patch from top to bottom and left to right.
+% To put it another way, the pixel patch is just a specific form of the pixel variation. 
+% %Although the observation patch and the observation sequence belong to different forms of the pixel variation, they consist of the same components, and share the common temporal information from the pixel variation.
+% Since the pixel sequences are extracted from each pixel position, a large number of pixel patches can be extracted from only one single image stack, which promises sufficient training data for our network.
+% 
 % 
@@
 %第四步空间近邻随机采样。
-It is generally accepted that neighboring background pixels share a similar temporal distribution.
-%In other words, there are some clues hidden in pixels' spatial neighbors. 
-In order to benefit from the spatial context, we concatenate the pixel patch with 2 neighboring pixel patches, which are randomly selected in the 8-connected neighborhood of each pixel position. 
-The input patch of our network is defined as:
+It is generally accepted that the pixels are no independent but related to it is neighborhoods,
+and the similarly neighboring pixels share the similar variations.
+%
+Therefore,
+the spatial information should be benefit for learning the pattern of pixels' variation.
+%
+With this motivation,
+several training patches extracted from neighboring pixels are combined to improve the efficiency of proposed approach.
+%
+In the experiment, three training patches are combined which is shown as follows:
 \begin{equation}
@@
 And neighboring patches are at pixel position $(x',y')$ and $(x'',y'')$ respectively.
+% Ii is generally accepted that neighboring background pixels share a similar temporal distribution.
+% %In other words, there are some clues hidden in pixels' spatial neighbors. 
+% In order to benefit from the spatial context, we concatenate the pixel patch with 2 neighboring pixel patches, 
+% 
+% which are randomly selected in the 8-connected neighborhood of each pixel position. 
+% The input patch of our network is defined as:
+% \begin{equation}
+%     S_{x,y}(m,n) = \mathcal{C}o(S_{x,y}(m,n), S_{x', y'}(m,n), S_{x'', y ''}(m, n)),
+% \end{equation}
+% where the $\mathcal{C}o$ represents the concatenation process on the third dimension.
+% And neighboring patches are at pixel position $(x',y')$ and $(x'',y'')$ respectively.
+% 
+%In the previous steps, original videos are broken down into pixel patches which contain abundant background information.
 
-%In the previous steps, original videos are broken down into pixel patches which contain abundant background information. 
-Correspondingly, the groundtruth patches are obtained in a similar way as the input ones, except the concatenation process, as shown in the \reffig{flow_chart}. 
-Both of them are fed into the network for training to find a end-to-end transformation at each pixel position. 
-However, the size of feature maps will shrink quickly during forward computation. 
-In preprocessing, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input patches before the training. 
-After the forward computing, observations in input patches are mapped into a new space where they can be easily classified by thresholding. 
-The transformed pixel patch is defined as:
+\subsection*{Network Work Architecture and Variation Transformation}
+As shown in the \reffig{flow_chart},
+a end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels.
+%
+The input of network is the training patches $S(m,n)$ extracted from different pixels
+and the output of network is the labeled patches captured from Groundtruth frames.
+%
+The training procedure is the transformation from the training patches to the labelling patches,
+which is shown as follows:
+% 
+% the architecture of network 
+% 
+% Correspondingly, the groundtruth patches are obtained in a similar way as the input ones, except the concatenation process, as shown in the \reffig{flow_chart}. 
+% Both of them are fed into the network for training to find a end-to-end transformation at each pixel position. 
+% However, the size of feature maps will shrink quickly during forward computation. 
+% In preprocessing, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input patches before the training. 
+% After the forward computing, observations in input patches are mapped into a new space where they can be easily classified by thresholding. 
+% The transformed pixel patch is defined as:
 \begin{equation}
@@
 
-For the loss function, we choose the Sigmoid Cross Entropy (SCE), which are helpful to address the learning slowdown. 
+For the loss function, the Sigmoid Cross Entropy (SCE) loss is used, which are helpful to address the learning slowdown. 
 The formulation is as follows:
@@
 
-As shown in the \reffig{flow_chart}, the prediction maps can be reconstructed from the prediction patches.
+\subsection{Foreground Detection}
+%As shown in the \reffig{flow_chart}, 
+Then, the prediction maps can be reconstructed from the prediction patches.
+%
 Then a global threshold $T_r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
+%
 The threshold function is given by

### 2018-12-10 draft.tex
revised to the paragraph 1 of second subsection in IV

@@
 \subsection*{Network Work Architecture and Variation Transformation}
+% 先描述动机
+As we mentioned above,
+the main purpose of our DPVTL is trying to transform the sequence of pixels' observations 
+into another space where the observations are easier classified.
+% 分析问题，提出解决的方案，要用数学化的形式
+Therefore,
+our network entails learning a mapping from the input observations of pixels $x \in \mathcal{X}$ 
+to the probability of the corresponding pixel belong to foreground or background.
+
 As shown in the \reffig{flow_chart},

### 2018-12-16 draft.tex
revised to the first paragraph of Network architecture

@@
 the training data feed into network is one kinds of description of pixels' variation,
-which is actually patches consist of pixels' observations.
+which is actually patches consist of pixels' temporal observations.
 %
@@
 Therefore,
-our network entails learning a mapping from the input observations of pixels $x \in \mathcal{X}$ 
-to the probability of the corresponding pixel belong to foreground or background.
-
-As shown in the \reffig{flow_chart},
-a end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels.
+our network entails learning a mapping from the input observations of pixels $s \in \mathcal{S}$ 
+to the probability $p \in \mathcal{P}$ of the corresponding pixel belong to foreground or background,
+and a end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels as shown in the \reffig{flow_chart}.
 %
-The input of network is the training patches $S(m,n)$ extracted from different pixels
-and the output of network is the labeled patches captured from Groundtruth frames.
-%
-The training procedure is the transformation from the training patches to the labelling patches,
-which is shown as follows:
-% 
-% the architecture of network 
-% 
-% Correspondingly, the groundtruth patches are obtained in a similar way as the input ones, except the concatenation process, as shown in the \reffig{flow_chart}. 
-% Both of them are fed into the network for training to find a end-to-end transformation at each pixel position. 
-% However, the size of feature maps will shrink quickly during forward computation. 
-% In preprocessing, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input patches before the training. 
-% After the forward computing, observations in input patches are mapped into a new space where they can be easily classified by thresholding. 
-% The transformed pixel patch is defined as:
+Mathematically, the training procedure is shown as follows:
 \begin{equation}
     \begin{split}
-        S'(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} (Pad(S(m,n))) \cdots  ) )  \\
-          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(S(m,n)),
+        \mathcal{P}(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} ( \mathcal{S}(m,n)) \cdots  ) )  \\
+          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(\mathcal{S}(m,n)),
     \end{split}
 \end{equation}
-where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$.
+where $\mathcal{P}(x,y)$ is denoted as the probability, $\mathcal{S}(m,n)$ is the input patch of network and $f_{\theta_i}$ is represents different layers of network.
+% where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$.
 The symmetric padding process is denoted as $Pad$, where we have lost none of the pixel information to make the output $S'(m,n)$ the same size as the pixel patch $S(m,n)$.
-Another advantage of symmetric padding is that the order information still remains.
+% Another advantage of symmetric padding is that the order information still remains.
 
@@
 Finally, we get the transformed variation through the FCN, which are a lot easier for classification.
+
+The network used in this work is devised as an end-to-end architecture,
+
+% 
+% 
+% As shown in the \reffig{flow_chart},
+% %
+% The input of network is the training patches $S(m,n)$ extracted from different pixels
+% and the output of network is the labeled patches captured from Groundtruth frames.
+% %
+% The training procedure is the transformation from the training patches to the labelling patches,
+% which is shown as follows:
+% % 
+% % the architecture of network 
+% % 
+% % Correspondingly, the groundtruth patches are obtained in a similar way as the input ones, except the concatenation process, as shown in the \reffig{flow_chart}. 
+% % Both of them are fed into the network for training to find a end-to-end transformation at each pixel position. 
+% % However, the size of feature maps will shrink quickly during forward computation. 
+% % In preprocessing, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input patches before the training. 
+% % After the forward computing, observations in input patches are mapped into a new space where they can be easily classified by thresholding. 
+% % The transformed pixel patch is defined as:
+% \begin{equation}
+%     \begin{split}
+%         S'(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} (Pad(S(m,n))) \cdots  ) )  \\
+%           & = f_{ \prod_{n=1}^{N}\theta_n   }^n(S(m,n)),
+%     \end{split}
+% \end{equation}
 

### 2018-12-16 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.aux 	modified:   draft.log 	modified:   draft.out 	modified:   draft.pdf 	modified:   draft.tex

@@
     S_{x,y}(m,n) = \mathcal{C}(\mathcal{I}^d, R) = \mathcal{I}_{m \times R + n} (x,y),
+    \label{eq_reshape}
 \end{equation}
@@
 
-The network used in this work is devised as an end-to-end architecture,
+% 描述网络结构
+The network used in this work is devised as an end-to-end architecture XXX
+The structure of our FCN for foreground detection is shown in \reffig{flow_chart}. 
+The proposed FCN contains 6 convolutional layers, and the last convolutional layer has a filter size of $1\times 1$. 
+We use the Rectified Linear Unit (ReLU) as the activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
+We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
+\todo{please improve the English of this paragraph}
 
@@
 %As shown in the \reffig{flow_chart}, 
+After the transformation of observations of pixels,
+pixel patches feed into the network are transformed into the probability patches,
+which are compared with a threshold $T_r$ for classification and then used to reconstruct the foreground for final results.
+%
+The comparison with threshold is mathematically shown as follows:
+\begin{equation}
+    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R)),
+\end{equation}
+where XXX
+
+Then the reverse procedure of \refeq{eq_reshape}
+
+used to reconstruct the foreground image for the final results.
+%
+
+The network devised in proposed approach
+
 Then, the prediction maps can be reconstructed from the prediction patches.
@@
 
-\begin{equation}
-    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R)),
-\end{equation}
 where the $M$ denotes the final foreground map given by our DPVTL model.
@@
 %Based on above-mentioned factors, FCN is designed as the alternative network architecture in this paper.
-
-The structure of our FCN for foreground detection is shown in \reffig{flow_chart}. 
-The proposed FCN contains 6 convolutional layers, and the last convolutional layer has a filter size of $1\times 1$. 
-We use the Rectified Linear Unit (ReLU) as the activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
-We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
 

### 2019-01-21 draft.tex
all done except the description of network architecture

--- 2018-12-16 draft.tex
@@
 As we mentioned above,
-the main purpose of our DPVTL is trying to transform the sequence of pixels' observations 
-into another space where the observations are easier classified.
+the main purpose of our DPVTL is the transformation between the sequence of pixels' observations with possibility of pixels belong to foreground or background.
+% the main purpose of our DPVTL is trying to transform the sequence of pixels' observations 
+% into another space where the observations are easier classified.
 % 分析问题，提出解决的方案，要用数学化的形式
@@
 
-The network used in this work is devised as an end-to-end architecture,
+% 描述网络结构
+The network used in this work is devised as an end-to-end architecture XXX
+The structure of our FCN for foreground detection is shown in \reffig{flow_chart}. 
+The proposed FCN contains 6 convolutional layers, and the last convolutional layer has a filter size of $1\times 1$. 
+We use the Rectified Linear Unit (ReLU) as the activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
+We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
+After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery. 
+\todo{please giving a comprehensive description of the details about the network architecture.}
 
@@
 %As shown in the \reffig{flow_chart}, 
-Then, the prediction maps can be reconstructed from the prediction patches.
+After the transformation from observations to the probability belong to foreground or background,
+the foreground is detected from the final binary mask.
 %
-Then a global threshold $T_r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
+During the transformation,
+the pixel patches are feed into the network and transformed into the probability patches,
+which are compared with a threshold $T_r$ for classification and then used to reconstruct the foreground for final results.
 %
-The threshold function is given by
+The comparison with threshold is mathematically shown as follows:
+\begin{equation}
+    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R)),
+\end{equation}
+where the $\mathcal{M}(x,y)$ is the final binary mask.
+%
+The $S'(x,y)$ is the probability patches output by the network,
+the $\mathcal{C}^{-1}$ is the reversed procedure of the reshape procedure shown in the \refeq{eq_reshape} and $R$ is the parameter for the reversing procedure of reshape.
+%
+The $T_f$ is the threshold given by user and the $g()$ is the thresholding function which is shown as follows:
+% Then the reverse procedure of \refeq{eq_reshape}
+% 
+% used to reconstruct the foreground image for the final results.
+% %
+% 
+% 
+% The network devised in proposed approach 
+% 
+% 
+% Then, the prediction maps can be reconstructed from the prediction patches.
+% %
+% Then a global threshold $T_r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
+% %
+% The threshold function is given by
 \begin{equation}
@@
 \end{equation}
-
-\begin{equation}
-    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R)),
-\end{equation}
-where the $M$ denotes the final foreground map given by our DPVTL model.
-After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery.
+%
+%where the $M$ denotes the final foreground map given by our DPVTL model.
 

### 2019-01-22 draft.tex
.

@@
 % 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
-Then, the FCN is trained to learn the pattern of pixel variations for the transformation, followed by a liner classifier for labeling the pixels as foreground or background.
+Then, the FCN is trained to learn the pattern of pixel variations for the transformation, followed by a linear classifier for labeling the pixels as foreground or background.
 %    
@@
 % 描述网络结构
-The network used in this work is devised as an end-to-end architecture XXX
-The structure of our FCN for foreground detection is shown in \reffig{flow_chart}. 
-The proposed FCN contains 6 convolutional layers, and the last convolutional layer has a filter size of $1\times 1$. 
-We use the Rectified Linear Unit (ReLU) as the activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
+%The network used in this work is devised as an end-to-end architecture XXX
+The architecture of our FCN for foreground detection is illustrated in \reffig{flow_chart}. 
+The proposed FCN contains 6 convolutional layers without pooling, and the filter size of the first five layers is set to $3\times 3$, compared to the last convolutional layer which has a filter size of $1\times 1$.
+We use the Rectified Linear Unit (ReLU) as the activation function after first three convolutional layers.
+And the Sigmoid Cross Entropy loss function is applied to measures the performance of our network after the last convolutional layer.
 We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
-After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery. 
+After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without extra optimization mechanism.
 \todo{please giving a comprehensive description of the details about the network architecture.}

### 2019-01-22 DPVT_Code_6_nopool/demo.m

@@ -1,0 +1,115 @@
+run('~/tools/matconvnet-1.0-beta23/matlab/vl_setupnn.m');
+
+addpath('./common_plus/');
+addpath('./function/');
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 参数                                                              %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+                                                                                %
+% 数据集的绝对位置　和视频的相对位置                                            %
+video_path = 'lowFramerate/turnpike_0_5fps/';
+path_cdnet = '~/dataset/dataset2014/';
+
+im_pa = sprintf('%s%s%s', path_cdnet, video_path,'input/');
+gt_pa = sprintf('%s%s%s', path_cdnet, video_path,'groundtruth/');
+
+im_ft = 'jpg';
+gt_ft = 'png';
+
+% 网络保存的位置
+sv_pa = ['./network/' video_path];
+
+% 测试结果保存路径
+if ~exist(['./result/' video_path])
+    mkdir(['./result/' video_path]);
+end
+
+% 　选择　len * len 帧图像
+len = 10;
+
+global g_len g_epoch g_imMean;
+g_len = len;
+%imMean = getVideoMean_plus(im_pa);
+imMean = 0;
+%g_imMean = imMean;
+
+% 网络的循环次数                                                                %
+g_epoch = 20;                                                                    %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 程序运行部分 　　                                                             %
[…]

### 2019-01-22 DPVT_Code_6_nopool/demo_delay.m

@@ -1,0 +1,115 @@
+run('~/tools/matconvnet-1.0-beta23/matlab/vl_setupnn.m');
+
+addpath('./common_plus/');
+addpath('./function/');
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 参数                                                              %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+pause(1000)                                                                                %
+% 数据集的绝对位置　和视频的相对位置                                            %
+video_path = 'badWeather/blizzard/';
+path_cdnet = '~/dataset/dataset2014/';
+
+im_pa = sprintf('%s%s%s', path_cdnet, video_path,'input/');
+gt_pa = sprintf('%s%s%s', path_cdnet, video_path,'groundtruth/');
+
+im_ft = 'jpg';
+gt_ft = 'png';
+
+% 网络保存的位置
+sv_pa = ['./network/' video_path];
+
+% 测试结果保存路径
+if ~exist(['./result/' video_path])
+    mkdir(['./result/' video_path]);
+end
+
+% 　选择　len * len 帧图像
+len = 10;
+
+global g_len g_epoch g_imMean;
+g_len = len;
+%imMean = getVideoMean_plus(im_pa);
+imMean = 0;
+%g_imMean = imMean;
+
+% 网络的循环次数                                                                %
+g_epoch = 20;                                                                    %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 程序运行部分 　　                                                             %
[…]

### 2019-01-22 DPVT_Code_6_nopool/evaluationOnly.m

@@ -1,0 +1,66 @@
+run('~/tools/matconvnet-1.0-beta23/matlab/vl_setupnn.m');
+
+addpath('./common_plus/');
+addpath('./function/');
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 参数                                                              %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+                                                                                %
+% 数据集的绝对位置　和视频的相对位置                                            %
+video_path = 'lowFramerate/port_0_17fps/';
+path_cdnet = '~/dataset/dataset2014/';
+
+im_pa = sprintf('%s%s%s', path_cdnet, video_path,'input/');
+gt_pa = sprintf('%s%s%s', path_cdnet, video_path,'groundtruth/');
+
+im_ft = 'jpg';
+gt_ft = 'png';
+
+% 网络保存的位置
+sv_pa = ['./network/' video_path];
+
+% 测试结果保存路径
+if ~exist(['./result/' video_path])
+    mkdir(['./result/' video_path]);
+end
+
+% 　选择　len * len 帧图像
+len = 10;
+
+global g_len g_epoch g_imMean;
+g_len = len;
+%imMean = getVideoMean_plus(im_pa);
+imMean = 0;
+%g_imMean = imMean;
+
+% 网络的循环次数                                                                %
+g_epoch = 20;                                                                    %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 程序运行部分 　　                                                             %
[…]

### 2019-01-22 DPVT_Code_6_nopool/evaluation_translate.m

@@ -1,0 +1,88 @@
+%clc
+function [result ] = evaluation_translate(path_cdnet,video_path,array_tr)
+
+threshold_fg = 0.6;
+
+avg_all = [];
+avg_nor = [];
+
+all_entry = [];
+nor_entry = [];
+
+result = [];
+videos = {};
+
+% D:/dataset/homography_multi/PTZ/continuousPan/truthimg
+% D:/dataset/homography_multi/PTZ/continuousPan/similar
+
+all_result = [];
+
+%path_sim = '~/dataset/homography_multi/PTZ/continuousPan/similar';
+%path_sim = '~/dataset/homography_multi/PTZ/continuousPan/fgimg';
+%path_sim = '~/dataset/result/translate';
+%path_sim = '~/dataset/result/PETS2006_q';
+path_sim = ['./result/' video_path ];
+format_sim = 'bmp';
+
+
+%path_tru = 'D:/dataset/FBMS_Testset/Testset/cars1/GroundTruth';
+%path_tru = '/home/renxinyu/dataset/dataset2014/baseline/PETS2006/groundtruth';
+%path_tru = '~/dataset/Pixels_900_3n/groundtruth/save2';
+
+path_tru =['~/dataset/dataset2014/' video_path 'groundtruth']
+path_tru1 =['~/dataset/dataset2014/' video_path 'groundtruth']
+path_msk = path_tru1;
+format_tru = 'png';
+
+
+addpath('~/projects/imageprocessing/common/');
+
+temp = importdata([path_cdnet video_path '/temporalROI.txt']);
+head_f = temp(1);
+end_f  = temp(2);
+length_f = end_f - head_f + 1;
+
+[files_tru data_tru] = loadData_plus(path_tru,format_tru);
+[files_sim data_sim] = loadData_num(path_sim,format_sim,head_f);
+% 截取测试的真实样本
+files_tru = files_tru(head_f:end_f);
+data_tru  = data_tru(:,:,:,head_f:end_f);
+% 截取有效的预测图
+files_sim = files_sim(1:length_f); 
+data_sim  = data_sim(:,:,:,1:length_f); 
+
+size(data_tru)
+size(data_sim)
+data_tru(:,:,:,array_tr)=0;
+data_sim(:,:,:,array_tr)=0;
+
+im = [];
+% if size(files_smi) ~= size(files_tru)
+%    im(:,:) =   
+% end
+
[…]

### 2019-01-22 DPVT_Code_6_nopool/expLine.m

@@ -1,0 +1,114 @@
+function [] =  expLine(video_path,path_cdnet)
+run('~/tools/matconvnet-1.0-beta23/matlab/vl_setupnn.m');
+
+addpath('./common_plus/');
+addpath('./function/');
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 参数                                                              %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+                                                                                %
+% 数据集的绝对位置　和视频的相对位置                                            %
+
+im_pa = sprintf('%s%s%s', path_cdnet, video_path,'input/');
+gt_pa = sprintf('%s%s%s', path_cdnet, video_path,'groundtruth/');
+
+im_ft = 'jpg';
+gt_ft = 'png';
+
+% 网络保存的位置
+sv_pa = ['./network/' video_path];
+
+% 测试结果保存路径
+if ~exist(['./result/' video_path])
+    mkdir(['./result/' video_path]);
+end
+
+% 　选择　len * len 帧图像
+len = 10;
+
+global g_len g_epoch g_imMean;
+g_len = len;
+%imMean = getVideoMean_plus(im_pa);
+imMean = 0;
+%g_imMean = imMean;
+
+% 网络的循环次数                                                                %
+g_epoch = 20;                                                                    %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 程序运行部分 　　                                                             %
[…]

### 2019-01-22 DPVT_Code_6_nopool/function/vl_simplenn_fake.m

@@ -1,0 +1,258 @@
+function res = vl_simplenn(net, x, dzdy, res, varargin)
+% VL_SIMPLENN  Evaluates a simple CNN
+%   RES = VL_SIMPLENN(NET, X) evaluates the convnet NET on data X.
+%   RES = VL_SIMPLENN(NET, X, DZDY) evaluates the convnent NET and its
+%   derivative on data X and output derivative DZDY.
+%
+%   The network has a simple (linear) topology, i.e. the computational
+%   blocks are arranged in a sequence of layers. Please note that
+%   there is no need to use this wrapper, which is provided for
+%   convenience. Instead, the individual CNN computational blocks can
+%   be evaluated directly, making it possible to create significantly
+%   more complex topologies, and in general allowing greater
+%   flexibility.
+%
+%   The NET structure contains two fields:
+%
+%   - net.layers: the CNN layers.
+%   - net.normalization: information on how to normalize input data.
+%
+%   The network expects the data X to be already normalized. This
+%   usually involves rescaling the input image(s) and subtracting a
+%   mean.
+%
+%   RES is a structure array with one element per network layer plus
+%   one representing the input. So RES(1) refers to the zeroth-layer
+%   (input), RES(2) refers to the first layer, etc. Each entry has
+%   fields:
+%
+%   - res(i+1).x: the output of layer i. Hence res(1).x is the network
+%     input.
+%
+%   - res(i+1).aux: auxiliary output data of layer i. For example,
+%     dropout uses this field to store the dropout mask.
+%
+%   - res(i+1).dzdx: the derivative of the network output relative to
+%     variable res(i+1).x, i.e. the output of layer i. In particular
+%     res(1).dzdx is the derivative of the network output with respect
+%     to the network input.
+%
+%   - res(i+1).dzdw: the derivative of the network output relative to
+%     the parameters of layer i. It can be a cell array for multiple
+%     parameters.
+%
+%   net.layers is a cell array of network layers. The following
[…]

### 2019-01-22 DPVT_Code_6_nopool/getTrainingData.m

@@ -1,0 +1,23 @@
+function re_imdb = getTrainingData(im_pa, im_ft, gt_pa, gt_ft, array_tr, len, imMean)
+
+
+patches_im = img2pix_plus(im_pa, im_ft, array_tr, len, 1,imMean);
+patches_gt = img2pix_plus(gt_pa, gt_ft, array_tr, len, 0,imMean);
+
+
+[fs ffs] = loadFiles_plus(im_pa, im_ft);
+[row_im column_im byte_im] = size(imread(ffs{1}));
+
+
+[row_t column_t byte_t frames_t] = size(patches_im);
+
+imdb.images.data        = single(patches_im);
+imdb.images.labs        = single(patches_gt);
+imdb.images.meanPixel   = single(getVidMeans(patches_im));
+imdb.images.set         = single(ones(1,frames_t));
+imdb.images.iminfo      = single([row_im column_im byte_im]);
+
+imdb.mask        = single(ones(row_t,column_t));
+
+re_imdb = imdb;
+

### 2019-01-22 DPVT_Code_6_nopool/img2pix_plus.m

@@ -1,0 +1,83 @@
+function patch = img2pix_plus(im_pa,im_ft, im_array, len, im_flag,im_Mean)
+
+%==============================================================================
+% Author: Ryan  
+% DATE: 2017/05/17
+% inputDir: the Dir of your opt-flow data 
+% extention: 'jpg','bmp'
+% outputPath: where to save opt-flow image
+% dataName: theName of the vedio
+% descript: This function will make a new form of pixel-motion data base on videos.
+% 
+% Reviser: HalfofStupid
+% ===========================================================================
+imMean = im_Mean;
+
+% 验证是否需要用mask
+mask = imread([im_pa '/../ROI.bmp']);
+if  mean(mean(mask)) == 255
+    f_mask = 0;
+else
+    f_mask = 1;
+end
+
+if strcmp(im_ft,'jpg')
+    mask = repmat(mask,[1,1,3]);
+end
+
+% 读取image
+[fs ffs] = loadFiles_plus(im_pa, im_ft);
+ft_idx = im_array;
+[row_im column_im byte_im] = size(single(imread(ffs{1})));
+block_im = zeros(row_im, column_im, byte_im, len^2);
+lengthF = size(ffs,2);
+
+for i = 1:numel(ft_idx)
+    idx = ft_idx(i);
+    if idx<lengthF+1
+        im = double(imread(ffs{idx}));
+    else
+        im = double(imread(ffs{1}));
+        im(:,:,:) = 0;
+    end
+    if f_mask == 1
+        im(mask ~= 255) = 0;
+    end
+    block_im(:,:,:,i) = im;
+end
+
+% 减去平均图像
+%if im_flag == 1
+%    imMean(mask ~= 255) = 0;
+%    imMean = repmat(imMean,[1,1,1,len*len]);
+%    block_im = abs (block_im - imMean);
+%else
+%    block_im = 255 - block_im;
+%end
+
+% 变形成patches
+block_im = permute(block_im,[4 3 2 1]);
+patch = reshape(block_im,len,len,byte_im,row_im*column_im);
+
+%[row_t column_t byte_t frames_t] = size(patch);
+
+%re_patch = zeros(row_t*rate, column_t*rate, byte_t, frames_t);
+
+%if rate == 1
+%    disp('no need to resize image');
+%end
+
+%if im_flag == 1 
+    %for i = 1:frames_t
[…]

### 2019-01-22 DPVT_Code_6_nopool/img2pix_plus_2.m

@@ -1,0 +1,90 @@
+function patch = img2pix(im_pa,im_ft, head_num, len, rate,im_flag,imMean)
+
+%==============================================================================
+% Author: Ryan  
+% DATE: 2017/05/17
+% inputDir: the Dir of your opt-flow data 
+% extention: 'jpg','bmp'
+% outputPath: where to save opt-flow image
+% dataName: theName of the vedio
+% descript: This function will make a new form of pixel-motion data base on videos.
+% 
+% Reviser: HalfofStupid
+% ===========================================================================
+
+if nargin == 4
+    rate = 3;
+end
+
+if nargin == 3
+    rate = 3;
+    len = 5;
+end
+
+if nargin == 2
+    rate = 3;
+    len = 5;
+    head_num = 800;
+end
+
+mask = imread([im_pa '/../ROI.bmp']);
+if  mean(mean(mask)) == 255
+    f_mask = 0;
+else
+    f_mask = 1;
+end
+if strcmp(im_ft,'jpg')
+    mask = repmat(mask,[1,1,3]);
+end
+
+
+[fs ffs] = loadFiles_plus(im_pa, im_ft);
+ft_idx = head_num:head_num + len^2 - 1;
+
+[row_im column_im byte_im] = size(single(imread(ffs{1})));
+
+block_im = zeros(row_im, column_im, byte_im, len^2);
+
+
+for i = 1:numel(ft_idx)
+    idx = ft_idx(i);
+
+    im = double(imread(ffs{idx}));
+    if f_mask == 1
+        im(mask ~= 255) = 0;
+    end
+    block_im(:,:,:,i) = im;
+end
+
+% 减去平均图像
+if im_flag == 1
+    imMean(mask ~= 255) = 0;
+    imMean = repmat(imMean,[1,1,1,len*len]);
+    block_im = abs(block_im - imMean);
+end
+
+block_im = permute(block_im,[4 3 2 1]);
+patch = reshape(block_im,len,len,byte_im,row_im*column_im);
+patch = uint8(patch);
+%[row_t column_t byte_t frames_t] = size(patch);
+
+%re_patch = zeros(row_t*rate, column_t*rate, byte_t, frames_t);
+
+%if rate == 1
+%    disp('no need to resize image');
+%end
+
+%if im_flag == 1 
+    %for i = 1:frames_t
+        %mean_im = mean(mean(double(patch(:,:,:,i))));
[…]

### 2019-01-22 DPVT_Code_6_nopool/network_testing.m

@@ -1,0 +1,57 @@
+function re_block = network_testing(net_pa, imdb)
+
+patches_im = imdb.images.data;
+patches_gt = imdb.images.labs;
+
+ g_epoch = 20;
+ffs_net = sprintf([net_pa 'net-epoch-%i.mat'], g_epoch);
+net = load(ffs_net);
+net = net.net;
+net.layers{end} = struct('name', 'data_hat_sigmoid', ...
+    'type', 'sigmoid'         );
+
+net       = vl_simplenn_move(net,'gpu');
+meanPixel = getVidMeans(patches_im);
+
+[row_t column_t byte_t frames_t] = size(patches_im);
+
+
+patches_map = patches_gt;
+
+
+
+row  = imdb.images.iminfo(1);
+column  = imdb.images.iminfo(2);
+
+for kk = 1:frames_t
+%    im = patches_im(:,:,:,kk);
+   
+        n = kk;
+        x_n = fix((n-1)/column+1);
+        y_n = n-column*(x_n-1);
+
+        if x_n>1&&x_n<row&&y_n>1&&y_n<column
+            spaNabor = [n-column-1,n-column,n-column+1,n-1,n+1,n+column-1,n+column,n+column+1];
+            sampleNabor = spaNabor(randperm(length(spaNabor),3));
+        else
+            sampleNabor = [n,n,n];
+        end
+
+        im(:,:,1:3) = patches_im(:,:,:,n);
+        im(:,:,4:6) = patches_im(:,:,:,sampleNabor(1));
+        im(:,:,7:9) = patches_im(:,:,:,sampleNabor(2));
+    
+    im_large = padarray(im,[5,5],'symmetric');
+    im_large = bsxfun(@minus, im_large, meanPixel);
+    im_large = gpuArray(im_large);
+    
+    A = vl_simplenn_fake(net, im_large);
+    B = gather(A(end).x);
+    
+    map_im = uint8(B * 255);    
+
+    patches_map(:,:,:,kk) = map_im;
+end
+
+ g_rate = 1;
+re_block = pix2img_plus(imdb.images.iminfo, patches_map, g_rate);

### 2019-01-22 DPVT_Code_6_nopool/network_training.m

@@ -1,0 +1,67 @@
+function network_training(sv_pa, imdb)
+
+global g_epoch;
+opts.expDir = sv_pa; 
+opts.train.batchSize = 200;
+opts.train.numEpochs = g_epoch;
+opts.train.continue = true;
+opts.train.useGpu = true ;
+opts.train.learningRate = 1e-3;
+opts.train.expDir = opts.expDir ;
+
+
+net = fcn_init();
+
+
+[net,info] = cnn_train_adagrad(net, imdb, @getBatch,...
+    opts.train,'errorType','euclideanloss',...
+    'conserveMemory', true);
+end
+
+
+
+function [im, labels] = getBatch(imdb, batch)
+% --------------------------------------------------------------------
+    data    = imdb.images.data;
+    labs  = imdb.images.labs;
+    meanPixel = imdb.images.meanPixel;
+    iminfo = imdb.images.iminfo;
+    row = iminfo(1);
+    column = iminfo(2);
+    
+    global g_len;
+
+    for ii = 1:numel(batch)
+ %       im_ii = data(:,:,:,batch(ii));
+        roi   = labs(:,:,:,batch(ii));
+
+        n = batch(ii);
+        x_n = fix((n-1)/column+1);
+        y_n = n-column*(x_n-1);
+
+        if x_n>1&&x_n<row&&y_n>1&&y_n<column
+            spaNabor = [n-column-1,n-column,n-column+1,n-1,n+1,n+column-1,n+column,n+column+1];
+            sampleNabor = spaNabor(randperm(length(spaNabor),3));
+        else
+            sampleNabor = [n,n,n];
+        end
+
+        im_ii(:,:,1:3) = data(:,:,:,n);
+        im_ii(:,:,4:6) = data(:,:,:,sampleNabor(1));
+        im_ii(:,:,7:9) = data(:,:,:,sampleNabor(2));
+
+        labels_ii = zeros(size(roi,1),size(roi,2));
+        labels_ii( roi == 50 )  = 0.25;       %shade
+        labels_ii( roi == 170 ) = 0.75;       %object boundary
+        labels_ii( roi == 255 ) = 1;          %foreground           
+        
+        im_large = padarray(im_ii,[5, 5],'symmetric');
+        im_e = bsxfun(@minus, im_large, meanPixel);
+        
+        im(:,:,:,ii) = im_e;
+        labels(:,:,1,ii) = labels_ii;
+        labels(:,:,2,ii) = double(imdb.mask);
+    end
+end
+
+

### 2019-01-22 DPVT_Code_6_nopool/pipeline_PTZ.m

@@ -1,0 +1,14 @@
+
+
+path_cdnet = '~/dataset/dataset2014/';
+video_path = 'PTZ/continuousPan/';
+expLine(video_path,path_cdnet);
+
+video_path = 'PTZ/intermittentPan/';
+expLine(video_path,path_cdnet);
+
+video_path = 'PTZ/twoPositionPTZCam/';
+expLine(video_path,path_cdnet);
+
+video_path = 'PTZ/zoomInZoomOut/';
+expLine(video_path,path_cdnet);

### 2019-01-22 DPVT_Code_6_nopool/pipeline_bad.m

@@ -1,0 +1,14 @@
+
+
+path_cdnet = '~/dataset/dataset2014/';
+video_path = 'badWeather/blizzard/';
+expLine(video_path,path_cdnet);
+
+video_path = 'badWeather/skating/';
+expLine(video_path,path_cdnet);
+
+video_path = 'badWeather/snowFall/';
+expLine(video_path,path_cdnet);
+
+video_path = 'badWeather/wetSnow/';
+expLine(video_path,path_cdnet);

### 2019-01-22 DPVT_Code_6_nopool/pipeline_base.m

@@ -1,0 +1,14 @@
+
+
+path_cdnet = '~/dataset/dataset2014/';
+video_path = 'baseline/highway/';
+%expLine(video_path,path_cdnet);
+
+video_path = 'baseline/office/';
+%expLine(video_path,path_cdnet);
+
+video_path = 'baseline/pedestrians/';
+%expLine(video_path,path_cdnet);
+
+video_path = 'baseline/PETS2006/';
+expLine(video_path,path_cdnet);

### 2019-01-22 DPVT_Code_6_nopool/pipeline_dyna.m

@@ -1,0 +1,20 @@
+
+
+path_cdnet = '~/dataset/dataset2014/';
+video_path = 'dynamicBackground/boats/';
+%expLine(video_path,path_cdnet);
+
+video_path = 'dynamicBackground/canoe/';
+%expLine(video_path,path_cdnet);
+
+video_path = 'dynamicBackground/fall/';
+%expLine(video_path,path_cdnet);
+
+video_path = 'dynamicBackground/fountain01/';
+%expLine(video_path,path_cdnet);
+
+video_path = 'dynamicBackground/fountain02/';
+%expLine(video_path,path_cdnet);
+
+video_path = 'dynamicBackground/overpass/';
+expLine(video_path,path_cdnet);

### 2019-01-22 DPVT_Code_6_nopool/pipeline_inter.m

@@ -1,0 +1,20 @@
+
+
+path_cdnet = '~/dataset/dataset2014/';
+video_path = 'intermittentObjectMotion/abandonedBox/';
+expLine(video_path,path_cdnet);
+
+video_path = 'intermittentObjectMotion/parking/';
+expLine(video_path,path_cdnet);
+
+video_path = 'intermittentObjectMotion/sofa/';
+expLine(video_path,path_cdnet);
+
+video_path = 'intermittentObjectMotion/streetLight/';
+expLine(video_path,path_cdnet);
+
+video_path = 'intermittentObjectMotion/tramstop/';
+expLine(video_path,path_cdnet);
+
+video_path = 'intermittentObjectMotion/winterDriveway/';
+expLine(video_path,path_cdnet);

### 2019-01-22 DPVT_Code_6_nopool/pipeline_low.m

@@ -1,0 +1,15 @@
+
+
+path_cdnet = '~/dataset/dataset2014/';
+
+video_path = 'lowFramerate/port_0_17fps/';
+expLine(video_path,path_cdnet);
+
+video_path = 'lowFramerate/tramCrossroad_1fps/';
+expLine(video_path,path_cdnet);
+
+video_path = 'lowFramerate/tunnelExit_0_35fps/';
+expLine(video_path,path_cdnet);
+
+video_path = 'lowFramerate/turnpike_0_5fps/';
+expLine(video_path,path_cdnet);

### 2019-01-22 DPVT_Code_6_nopool/pipeline_nigt.m

@@ -1,0 +1,20 @@
+
+
+path_cdnet = '~/dataset/dataset2014/';
+video_path = 'nightVideos/bridgeEntry/';
+expLine(video_path,path_cdnet);
+
+video_path = 'nightVideos/busyBoulvard/';
+expLine(video_path,path_cdnet);
+
+video_path = 'nightVideos/fluidHighway/';
+expLine(video_path,path_cdnet);
+
+video_path = 'nightVideos/streetCornerAtNight/';
+expLine(video_path,path_cdnet);
+
+video_path = 'nightVideos/tramStation/';
+expLine(video_path,path_cdnet);
+
+video_path = 'nightVideos/winterStreet/';
+expLine(video_path,path_cdnet);

### 2019-01-22 DPVT_Code_6_nopool/pipeline_shad.m

@@ -1,0 +1,22 @@
+
+
+path_cdnet = '~/dataset/dataset2014/';
+video_path = 'shadow/backdoor/';
+%expLine(video_path,path_cdnet);
+
+video_path = 'shadow/bungalows/';
+%expLine(video_path,path_cdnet);
+
+video_path = 'shadow/busStation/';
+expLine(video_path,path_cdnet);
+
+video_path = 'shadow/copyMachine/';
+expLine(video_path,path_cdnet);
+
+video_path = 'shadow/cubicle/';
+expLine(video_path,path_cdnet);
+
+video_path = 'shadow/peopleInShade/';
+expLine(video_path,path_cdnet);
+
+

### 2019-01-22 DPVT_Code_6_nopool/pipeline_ther.m

@@ -1,0 +1,17 @@
+
+
+path_cdnet = '~/dataset/dataset2014/';
+video_path = 'thermal/corridor/';
+%expLine(video_path,path_cdnet);
+
+video_path = 'thermal/diningRoom/';
+expLine(video_path,path_cdnet);
+
+video_path = 'thermal/lakeSide/';
+expLine(video_path,path_cdnet);
+
+video_path = 'thermal/library/';
+expLine(video_path,path_cdnet);
+
+video_path = 'thermal/park/';
+expLine(video_path,path_cdnet);

### 2019-01-22 DPVT_Code_6_nopool/pipeline_turb.m

@@ -1,0 +1,15 @@
+
+
+path_cdnet = '~/dataset/dataset2014/';
+video_path = 'turbulence/turbulence0/';
+expLine(video_path,path_cdnet);
+
+video_path = 'turbulence/turbulence1/';
+expLine(video_path,path_cdnet);
+
+video_path = 'turbulence/turbulence2/';
+expLine(video_path,path_cdnet);
+
+video_path = 'turbulence/turbulence3/';
+expLine(video_path,path_cdnet);
+

### 2019-01-22 DPVT_Code_6_nopool/pix2img_plus.m

@@ -1,0 +1,28 @@
+function re_block = pix2img_plus(iminfo, patches_map, rate)
+
+[row_t column_t byte_t frames_t] = size(patches_map);
+
+% [row_im column_im byte_im] = iminfo;
+row_im      = iminfo(1);
+column_im   = iminfo(2);
+byte_im     = iminfo(3);
+
+len = (row_t/rate)^2;
+re_block = zeros(row_im, column_im, len);
+
+count = 1;
+
+for j = 1:rate:column_t
+    for i = 1:rate:row_t
+        data = patches_map(i:i+rate-1,j:j+rate-1,:);
+        data = mean(data,1);
+        data = mean(data,2);
+
+        im = reshape(data, column_im, row_im);
+        im = im';
+        
+        re_block(:,:,count) = im;
+
+        count = count + 1;
+    end
+end

### 2019-01-22 DPVT_Code_6_nopool/plot3line.m

@@ -1,0 +1,48 @@
+video = 'baseline/highway';
+path_in = ['~/dataset/dataset2014/' video '/input/']
+path_gt = ['~/dataset/dataset2014/' video '/groundtruth/']
+path_re = ['./result/' video '/'];
+
+addpath('~/projects/imageprocessing/common/');
+
+[files_gt data_gt] = loadData_plus(path_gt,'png');
+[files_re data_re] = loadData_num(path_re,'bmp',470);
+[files_in data_in] = loadData_plus(path_in,'jpg');
+
+
+% 截取测试的真实样本
+data_gt  = data_gt(:,:,:,801:1000);
+data_in  = data_in(:,:,:,801:1000);
+% 截取有效的预测图
+data_re  = data_re(:,:,:,331:530); 
+size(data_re)
+gt = data_gt(135,125,:,:);
+in = data_in(135,125,:,:);
+re = data_re(135,125,:,:);
+
+in = mean(in,3);
+
+gt = squeeze(gt);
+in = squeeze(in);
+re = squeeze(re);
+
+
+lines = {gt,in,re};
+save('lines.mat','lines');
+%{
+size(gt)
+size(in)
+size(re)
+y = 1:50;
+plot(y,gt,'-ro','LineWidth',5);
+hold on;
+plot(y,re,'-go','LineWidth',5);
+hold on;
+plot(y,in,'-bo','LineWidth',5)
+hold;
+print (gcf,'-dpng','lines.png');
+max(max(max(max(gt))))
+max(max(max(max(re))))
+max(max(max(max(in))))
+
+%}

### 2019-01-22 DPVT_Code_6_nopool/showPixels.m

@@ -1,0 +1,77 @@
+run('~/tools/matconvnet-1.0-beta23/matlab/vl_setupnn.m');
+
+addpath('./common_plus/');
+addpath('./function/');
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 参数                                                              %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+                                                                                %
+% 数据集的绝对位置　和视频的相对位置                                            %
+video_path = 'baseline/highway/';
+path_cdnet = '~/dataset/dataset2014/';
+
+im_pa = sprintf('%s%s%s', path_cdnet, video_path,'input/');
+gt_pa = sprintf('%s%s%s', path_cdnet, video_path,'groundtruth/');
+
+im_ft = 'jpg';
+gt_ft = 'png';
+
+% 网络保存的位置
+sv_pa = ['./network/' video_path];
+
+% 测试结果保存路径
+if ~exist(['./result/' video_path])
+    mkdir(['./result/' video_path]);
+end
+
+% 　选择　len * len 帧图像
+len = 10;
+
+global g_len g_epoch g_imMean;
+g_len = len;
+%imMean = getVideoMean_plus(im_pa);
+imMean = 0;
+g_imMean = imMean;
+
+% 网络的循环次数                                                                %
+g_epoch = 20;                                                                    %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 程序运行部分 　　                                                             %
[…]

### 2019-01-22 DPVT_Code_6_nopool/test.m

@@ -1,0 +1,5 @@
+
+for i = 1:frames_t
+    im = uint8(block_im(:,:,i));
+    imwrite(im,['./result/' int2str(i) '.bmp'],'bmp');
+end

### 2019-01-22 DPVT_Code_6_nopool/testOnly.m

@@ -1,0 +1,111 @@
+run('~/tools/matconvnet-1.0-beta23/matlab/vl_setupnn.m');
+addpath('./common_plus/');
+addpath('./function/');
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 参数                                                              %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+                                                                                %
+% 数据集的绝对位置　和视频的相对位置                                            %
+video_path = 'baseline/highway/';
+path_cdnet = '~/dataset/dataset2014/';
+
+im_pa = sprintf('%s%s%s', path_cdnet, video_path,'input/');
+gt_pa = sprintf('%s%s%s', path_cdnet, video_path,'groundtruth/');
+
+im_ft = 'jpg';
+gt_ft = 'png';
+
+% 网络保存的位置
+sv_pa = ['./network/' video_path];
+
+% 测试结果保存路径
+if ~exist(['./result/' video_path])
+    mkdir(['./result/' video_path]);
+end
+
+% 　选择　len * len 帧图像
+len = 10;
+
+global g_len g_epoch g_imMean;
+g_len = len;
+%imMean = getVideoMean_plus(im_pa);
+imMean = 0;
+g_imMean = imMean;
+
+% 网络的循环次数                                                                %
+g_epoch = 20;                                                                    %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 程序运行部分 　　                                                             %
[…]

### 2019-01-22 DPVT_Code_6_nopool/testOnly_p.m

@@ -1,0 +1,97 @@
+run('~/tools/matconvnet-1.0-beta23/matlab/vl_setupnn.m');
+
+addpath('./common_plus/');
+addpath('./function/');
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 这一大坨都是参数                                                              %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+                                                                                %
+% 数据集的绝对位置　和视频的相对位置                                            %
+video_path = 'nightVideos/streetCornerAtNight/';
+path_cdnet = '~/dataset/dataset2014/';
+
+im_pa = sprintf('%s%s%s', path_cdnet, video_path,'input/');
+gt_pa = sprintf('%s%s%s', path_cdnet, video_path,'groundtruth/');
+
+im_ft = 'jpg';
+gt_ft = 'png';
+
+% 网络保存的位置
+sv_pa = ['./network/' video_path];
+
+head_num = 1470;
+len = 12;
+
+% 放大３倍，XXX 个人严重不同意这么搞，没道理，而且消耗大量的时间
+rate = 1;
+
+global g_head_num g_len g_rate g_epoch g_imMean;
+g_head_num = head_num;
+g_len = len;
+g_rate = rate;
+
+g_imMean = getVideoMean_plus(im_pa);
+% 网络的循环次数                                                                %
+g_epoch = 20;                                                                    %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
[…]

### 2019-01-29 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.aux 	modified:   draft.log 	modified:   draft.out 	modified:   draft.pdf 	modified:   draft.tex

@@
 \begin{document}
-\title{Foreground Detection via Deep Variation Transformation}
+\title{Deep Variation Transformation for Foreground Detection}
 
@@
         Xinyu Ren, 
-        Chenqiu Zhao}
+        Chenqiu Zhao,
+        Anup Basu}
 
@@
 % 运动检测的已有方法主要关注于像素值的变化。
-Previous approaches to foreground detection generally analyze the variation of pixel observations.
+Previous approaches to foreground detection generally analyzed the variation of pixel observations.
 % 本文中，我们分析了像素的变动，并提出了DPVTL方法。
 % In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
-In this paper, we focus on transforming the variation into another space where the entry of variation is easily classified, and a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
+In this paper, we focus on transforming the variation into another space where the entry of variation is easily classified, using a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL).
 % 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
 % 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
-In particular, the pixel variation is represented by the sequence of pixel observations, which is used as the input of fully convolutional network(FCN) to find a transformation of pixels' variation.
+In particular, the pixel variation is represented by the sequence of pixel space, which is used as the input for a fully convolutional network(FCN) to find a transformation of pixels' variation.
 % 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
@@
 % 这句话我也没看懂。。。
+    \textcolor{red}{
 Benefited from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
-the proposed approach adaptively generates superior performances in diverse nature scenes.
+    the proposed approach adaptively generates superior performances in diverse nature scenes.}
 %
-Comprehensive experiments in several standard benchmarks demonstrate the superiority of the proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
+Comprehensive experiments on several standard benchmark demonstrate the superiority of the proposed approach compared with state-of-the-art deep learning and traditional methods.
 %
@@
 %背景检测的背景介绍
-Foreground detection as a fundamental problem in computer vision\ \cite{Bouwmans201431} has been discussed over decades with the increasing number of cameras,
-which is widely used in the applications of video processing \cite{Barnich2011_2011_TIP}.
+Foreground detection is a fundamental problem in computer vision\ \cite{Bouwmans201431} that has been approached over decades with an increasing number of cameras.
+It is widely used in applications involving video processing \cite{Barnich2011_2011_TIP}.
 % 传统的方法是怎么做的，有什么问题
@@
 Traditional foreground detection algorithms focus on analyzing the pixel variation, establishing background models with statistical methods such as GMM\cite{Stauffer1999}\cite{lee2005} and KDE\cite{Elgammal2000Non}\cite{Mittal2004KDE}.
-However, due to the unpredictability and rapidity of the pixels' variation in natural scenes,
-the variation becomes so unordered which is hard to be analyzed for foreground detection.
-Therefore, the foreground detection is still a challenging problem in complex natural scenes.
+However, due to the unpredictability and peed of pixel variations in natural scenes,
+the variation becomes so unordered and is hard to analyze for foreground detection.
+Therefore, foreground detection is still a challenging problem in complex natural scenes.
 % 现有的方法在简单场景中效果很好了
@@
 % 在多样的自然场景中，前景可能产生和背景相似，甚至相同的像素，而这种像素很难去分析
-In the diversely natural scenes,
-it is possible that moving objects produce the similar or even the same observations of pixels to that of background.
+In diversely natural scenes,
+it is possible that moving objects produce similar or even the same observations of pixels compared to the background.
 % similar to their counterparts of background but actually belong to foreground .
@@
 % 大多数情况下，他都会被划分成背景
-Unfortunately, in most cases, it is highly possible that the observation C will be falsely classified due to the similarity with their counterparts of background.
+Unfortunately, in most cases, it is highly possible that C will be falsely classified due to the similarity with counterparts of the background.
 % 我们的就是希望把这个variation 转化到更简单的地方去
 In this work, we focus on learning the pattern of pixels' variation and transforming the variations into a new space where the observations are easier to classify, rather than learning a classifier for individual pixels.
-As shown in the bottom part of the \reffig{idea}, the pattern of fragment consists of observations A-D can be learned by the network and transformed into another fragment where these observations are easily and correctly classified as foreground.
+As shown in the bottom part of \reffig{idea}, the pattern of a fragment consisting of observations A-D can be learned by the network and transformed into another fragment where these observations are easily and correctly classified as foreground.
 % transformatin 之后，就很容易分类了，然后这就是我们的方法的核心了
-Based on this, the Deep Variation Transformation model for foreground detection is proposed.
+Based on this, the Deep Pixel Variation Transformation Learning model for foreground detection is proposed.
 % motivation
@@
 % XXX 一句话，换一行！！！
-% In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for foreground detection in diversely natural scenes. 
-In the DVTL model, 
+% In this paper, we propose a novel Deep Variation Transformation Learning (DPVTL) model for foreground detection in diversely natural scenes. 
+In the DPVTL model, 
 the sequence of pixel observations is used to represent the variation and input into the network for learning,
-which encode both the intensity distribution and sequential information.
+which encodes both the intensity distribution and the sequential information.
 %
@@
 In particular,
-we take advantage of the strong learning ability of the deep neural network to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
+we take advantage of the strong learning ability of deep neural networks to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified as background or foreground.
 %
-Benefited from the innovative framework of variation transformation,
-proposed approach works well in diversely complex scenes adaptively.
+Utilizing the innovative framework of variation transformation,
+the proposed approach works well in diverse complex scenes adaptively.
 %
@@
 % XXX 不会用引用可以问我或者曲师兄。
-The rest part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion of the early and recent relevant works. 
+The rest part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion of both early and recent relevant literature. 
 %
-The details of the variation transformation are presented in \refsec{sec3}.
-The architecture of network is introduced in \refsec{sec4}, followed by experiments and result comparison in \refsec{sec5} and conclude the paper in \refsec{sec6}.
+Details on the variation transformation are presented in \refsec{sec3}.
+The architecture of the network is introduced in \refsec{sec4}, followed by experiments and comparison result in \refsec{sec5}, before concluding the paper in \refsec{sec6}.
 % \todo{please revise this part by using command refsec}
@@
 \label{sec2}
-Over the last few decades, a huge number of foreground detection methods have been proposed,
+Over the last few decades, a large number of foreground detection methods have been proposed,
 which are broadly categorized into pixel-based, region-based and learning-based methods.
@@
 % 注意英语和汉语的表达习惯
-It utilizes a mixture of weighted Gaussians to model the probability distribution of each pixel in time sequence.
-Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence. 
+It utilizes a mixture of weighted Gaussians to model the probability distribution of each pixel over a time sequence.
+%
+\textcolor{red}{Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence.} 
 %GMM+i
-Zivkovic et al.\ \cite{Zivkovic2004} improve the GMM method with the utilization of the recursive equation
-to automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
+Zivkovic et al.\ \cite{Zivkovic2004} improved the GMM method by utilizing a recursive equation
+to automatically update the parameters and adjust the number of components of the mixture needed for each pixel. 
 %
 %codebook
-Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.
+Kim et al.\cite{Kim2005} presented the codebook method, which records the sampling background values on codewords for each pixel position.
 The incoming pixels are compared with these codewords to see if their distances lie within a certain bound. 
@@
 In addition, a non-parametric background model is proposed by Elgammal et al. \cite{Elgammal2000Non}. 
-They assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE). 
+They assume that each background pixel is drawn from a probability distribution function, which is estimated Kernel Density Estimation space (KDE). 
 %Vibe
-Another non-parametric method is proposed by Barnich et al.
-\cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe).
+Another non-parametric method is proposed by Barnich et al. \cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe). 
+%
 The background model of ViBe consists of pixel samples from the video stream. 
-Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exist sufficient samples with a distance to itself within a certain range.
+%
+Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists sufficient samples with a distance to itself within a certain range.
 %PBAS
-To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold, which depended on the pixel position and a background dynamics metric.
+To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improved ViBe by presenting an adaptive threshold, 
+which depends on the pixel position and a background dynamics metric.
 
@@
 Unfortunately,
-the pixel-based methods ignore the spatial-temporal information due to their assumption of independence between pixels.
-But there is, in fact, a strong coherence in image sequences that contains abundant hidden clues for the background model. 
+the pixel-based methods ignore the spatio-temporal information due to their assumption of independence between pixels.
+But there is, in fact, a strong coherence in image sequences that contain abundant hidden clues for the background model. 
 %
@@
 % “High Quality Estimation of Multiple Intermediate Frames for Video Interpolation”
-To address this shortcoming, we introduce a framework of variation transformation learning, where pixel's historical observations are embedded in a piece of pixel patch and sorted in chronological order as a whole for the training of our DPVTL model.
+To address this shortcoming, we introduce a framework of variation transformation learning, 
+where a pixel's historical observations are embedded into a piece of pixel patch and sorted in chronological order as a whole for the training of our DPVTL model.
 %这样的优点在于保留了数据的完整性，保留了数据的时序相关性。
-Bringing together the historical observations ensures the data integrity and preserves the temporal coherence of our training data. 
-On the other hand, the application of neural network guarantees the strong learning ability of our model.
-Thus, the proposed approach is more capable of learning the patterns of pixel variation and exploiting the spatial-temporal context, compared to those classifiers based on the assumption of pixel independence.
+Bringing together the historical observations ensures data integrity and preserves the temporal coherence of our training data. 
+On the other hand, the application of a neural network guarantees strong learning ability of our model.
+Thus, the proposed approach is more capable of learning the patterns of pixel variation and exploiting the spatio-temporal context, compared to those classifiers based on the assumption of pixel independence.
 %所以我们方法比基于像素的要好。
@@
 %
-\subsection{region-based approach}
+\subsection{Region-based approaches}
 % Ren: 好的好的，不乱吹了，我看过有说have similar values的。。。。
@@
 In addition, 
-Chen et al. \cite{2017_TPAMI_GANGWANG} combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
+Chen et al. \cite{2017_TPAMI_GANGWANG} combined the GMM with constraints of temporal and spatial information from the optical flow and hierarchical superpixels.
 %(Bayesian Modeling)
 Moreover, 
-Sheikh et al.\ \cite{Sheikh2005Bayesian} introduce a framework based on the Markov Random Field modeling with Maximum A Posteriori 
-probability (MAP-MRF) estimation, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
+Sheikh et al.\ \cite{Sheikh2005Bayesian} introduced a framework based on the Markov Random Field modeling with Maximum A Posteriori 
+probability (MAP-MRF) estimation, which incorporates the pixel location into background and foreground KDEs for the detection based on spatial context.
 %(Robust Foreground Object ICPR2010 Vikas Reddy )
@@
 %( Robust Region-Based ICPR)
-Hence, Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color respectively.
+Hence, Izadi et al.\cite{Izadi2008Robust} presented a robust region-based approach, which generates a pair of foreground maps based on gradient and color respectively.
 Any foreground region that does not exist in the first foreground map could be recovered from the other one.
 
-In contrast, we accept the assumption that neighboring blocks of background pixels should follow similar variations over time, and combine the pixel variation with its spatial neighbors to revise our prediction.
+In contrast, we accept the assumption that neighboring blocks of background pixels should follow similar variations over time, 
+and combined the pixel variation with its spatial neighbors to revise our prediction. 
 Due to the application of deep learning, the proposed approach is more powerful in capturing the structural background variation and achieves significant improvement compared to its competitors.
@@
 Traditional machine learning methods are commonly involved with support vector machines (SVM)\cite{Chen2011}\cite{Han2012} and Bayesian methods\cite{Sheikh2005Bayesian}\cite{2012_TIP_OP_6099616}\cite{Zhang2014Statis}.
-For example, Han et al.
-\cite{Han2012} integrate gradient, color, and Haar-like features to address the spatiotemporal variations for each pixel.
+For example, Han et al. \cite{Han2012} integrated gradient, color, and Haar-like features to address the spatio-temporal variations for each pixel. 
 Their background model is obtained for each feature in a kernel density framework and a SVM is employed for classification.
@@
 %
-In recent years, deep learning methods begin to flourish in several computer vision fields, and have demonstrated effective capabilities to handle time-series problems\cite{Mobahi2009}\cite{LANGKVIST201411}.
-A novel approach for foreground detection with the use of the Convolutional Neural Network(CNN) is proposed by Wang et al.\cite{wang2016PRL}.
-They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which performs excellently with sufficient training data.
+In recent years, deep learning methods begin to flourish in several computer vision fields, 
+and have demonstrated effective capabilities to handle time-series problems\cite{Mobahi2009}\cite{LANGKVIST201411}. 
+%
+A novel approach for foreground detection with the use of the Convolutional Neural Network (CNN) is proposed by Wang et al.\cite{wang2016PRL}.
+They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which performs very well with sufficient training data.
 %
@@
 In \cite{Yang2018DBMF}, a fully convolutional network with the skip architecture is proposed. 
-The authors also utilize a temporal approach to sample training images from the given video, thus providing the background model with limited temporal information.
+The authors also utilize a temporal approach to sample training images from the given video, 
+thereby providing the background model with limited temporal information.
 
 % cqzhao: 瞎说啥？？？SVM那个就是连续的几帧啊！他们的问题在于， 自然界太复杂，variation太多元，直接分析variation分析不出来，我们学到了variation的pattern，然后转换！
-Some breakthroughs and progress have been achieved by applying those methods, especially deep learning based approaches with optimized network architectures. 
-However, due to the diversity of nature scenes, pixel variations can be very complex, leading to difficulty in analyzing specific pixel variation patterns.
+Some breakthroughs and progress have been achieved by applying the methods above, especially deep learning based approaches with optimized network architectures. 
+However, due to the diversity of natural scenes, pixel variations can be very complex, leading to difficulty in analyzing specific pixel variation patterns.
 %我们的不同在于，我们的网络是训练去学习像素变动，并转换到新的空间去进行分类。
-Unlike existing ones, our method focus on creating a transformation, which guarantees the linear separability of pixel variations in the mapping space, rather than building classifiers for individual observations.
+Unlike existing ones, our method focuses on creating a transformation, which guarantees the linear separability of pixel variations in the mapping space, rather than building classifiers for individual observations.
 %
-Besides, our network is trained to learn patterns of pixel variations, which promise a better performance in time series modeling on temporal coherence.
+Besides, our network is trained to learn patterns of pixel variations, which result in a better performance in time series modeling on temporal coherence.
 %
@@
 \label{sec3}
-In this section, we will elaborate on the proposed approach and how does the variation transformation work in foreground detection.
+In this section, we will elaborate on the proposed approach and how the variation transformation works in foreground detection.
 
 %背景检测的难点
-Foreground detection is essentially a binary classification in time sequence, where pixels in a video stream are classified as two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops).
-In most cases, if we print out the historical observations of a single pixel, it is not hard to see that they usually keep their stability when belonging to the background. 
-However, there are some exceptions: historical observations vary regularly when belonging to some dynamic background scenes(e.g. 
-waves, swaying tree leaves). 
-Generally, pixels from the background are sharing some common patterns of variation. 
+Foreground detection is essentially a binary classification in time sequence, 
+where pixels in a video stream are classified into two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops).
+%
+In most cases, if we print out the historical observations of a single pixel, 
+it is not hard to see that they usually keep their stability when belonging to the background.
+%
+However, there are some exceptions: historical observations vary regularly when belonging to some dynamic background scenes (e.g. waves, swaying tree leaves).
+%
+In general, pixels from the background share some common patterns of variation.
 \begin{figure}[!t]	% FIGURE: figure/fig1 
@@
 %传统方法的问题
-Previous methods have a good performance when background and foreground observations are remarkably different and the backgrounds are normally keeping static. 
-While in fact, backgrounds can be rather turbulent and dynamic due to the complexity and diversity of nature scenes. 
-Especially when illumination and camouflages are involved, background and foreground observations are easily confused and mixed up.
+Previous methods have good performance when background and foreground observations are remarkably different and the backgrounds are normally static. 
+While in fact, backgrounds can be rather turbulent and dynamic due to the complexity and diversity of natural scenes. 
+Especially when illumination and camouflage are involved, background and foreground observations are easily confused and mixed up.
 
 %图例说明可能面临的挑战
-For example, in \reffig{variation_chart}, it is noticeable that some foreground observations in blue line share the same or similarly value with background ones. 
-In that case, those popular methods will inevitably yield some sticky moments when separating the pixels in the blue line. 
+For example, in \reffig{variation_chart}, it is noticeable that some foreground observations in blue line share the same or similar value with background ones. 
+In this case, popular methods will inevitably yield some sticky moments when separating the pixels in the blue line. 
 Statistical methods, for instance, are no longer valid, because they only focus on establishing a statistical model for the background, while having little or no concern for the temporal coherence of these observations.
 In other words, despite knowing that pixels from the background share some common patterns of variation in a temporal sequence, they still let the order information of sequential images all go to waste.
-
 %variation transformation 介绍。
-In this paper, a novel framework of pixel variation transformation is proposed. %用framework代替method?
+%In this paper, a novel framework of pixel variation transformation is proposed. %用framework代替method?
 
@@
 %方法的好处是
-The benefits are evident and clearly seen. 
+The benefits are evident and can be clearly seen. 
 It is hard to distinguish a foreground observation when its value is similar to the background ones. 
@@
 With the strong learning ability of the FCN, we are able to learn the diverse variation patterns of background and foreground over a long period of time.
-And the variation patterns, in turn, contribute to the variation transformation where the value of each observation is adjusted according to its compatriot in time sequence.
+The variation patterns, in turn, contribute to the variation transformation where the value of each observation is adjusted according to its compatriot in time sequence.
 
@@
 \label{sec4}
-In this section, the details of proposed approach have been explained.
+In this section, details of the proposed aren explained.
 %
-The pipeline of proposed approach is shown in the \reffig{flow_chart},
+The pipeline of the proposed approach is shown in the \reffig{flow_chart},
 which can be divided into three parts.
 %
-Firstly, the procedure of the generation of pixels patch, 
-which is feed into the network for training as well as the description of pixel variation,
+First, the procedure generating pixel patches,
+which are fed into the network for training as well as the description of pixel variation,
 is introduced.
@@
 In this work,
-the deep learning network is utilized to learn the pattern of variations implied in the observations of pixels.
+a deep learning network is utilized to learn the pattern of variations implied in the observations of pixels.
 % 基于这个动机，我们是怎么做的
 Therefore,
-the training data feed into network is one kinds of description of pixels' variation,
-which is actually patches consist of pixels' temporal observations.
+the training data fed into the network is a type of description of pixels' variation,
+which are actually patches consisting of pixels' temporal observations.
 %
-In contrast, the output of the network is the probability of corresponding pixels belong to foreground or background,
-and the network is devised with an end-to-end architecture to transform the intensity of pixels to the probability of category the pixels belong to.
+In contrast, the output of the network is the probability of corresponding pixels belonging to foreground or background,
+and the network is devised with an end-to-end architecture to transform the intensity of pixels to the probability of the category the pixels belong to.
 
@@
 Let us denote the frame sequence in a video as $\mathcal{I} = \{I_1, I_2, \cdots, I_T\}$,
-where $\mathcal{I}$ is denoted as the set of frames and $T$ is the numbers of frames.
+where $\mathcal{I}$ denotes as the set of frames and $T$ is the numbers of frames.
 %
@@
 where $\mathcal{I}^d$ is the set of training frames,
-the $T$ and the $N$ represents the frame number of whole video and the training set respectively,
+$T$ the $N$ represent the frame number of whole video and the training set respectively,
 and the $\mathcal{D}()$ is denoted as the sampling function.
@@
 Since the patch can be captured from each pixel, 
-a large number of training patches can be extracted with the training frames
-and each of these patches is of fixed numbers of pixels as $\frac{T}{N}$.
+a large number of training patches can be extracted with the training frames;
+and each of these patches is for $\frac{T}{N}$ pixels.
 %
-In addition, for each pixel included in the patch, a label of foreground or background is needed for training.
+In addition, for each pixel included in the patch, a label of the foreground or background is needed for training.
 %
 Therefore,
-the labeling patches, which are captured by the similar procedure in the ground truth frames,
-are used as the output for training our network,
-and our network is actually an end-to-end transformation from pixels to labels.
+the labeling patches, which are captured by a similar procedure in the ground truth frames,
+are used as the output for training our network.
+Our network is actually an end-to-end transformation from pixels to labels.
 %
-Mathematically, the generation procedure of training patches is shown as follows:
+Mathematically, the generation procedure of training patches can be shown as follows:
 \begin{equation}
@@
 \end{equation}
-where the $S_{x,y}(m,n)$ is denoted as the training patch extracted from the observations of pixel located at $(x,y)$,
-The $R$ is the user argument to control the radius of training patches
-and $\mathcal{C}(\mathcal{I}^d, R)$ is the function to covert the observations of pixels to training patches.
+where $S_{x,y}(m,n)$ denotes the training patch extracted from the observations of pixel located at $(x,y)$,
+$R$ is the user argument to control the radius of training patches
+and $\mathcal{C}(\mathcal{I}^d, R)$ is the function to convert the observations of pixels to training patches.
 % where the pixel patch is denoted as $S_{x,y}(m,n)$, at the pixel positionthe pixel position $(x,y)$. 
@@
 %第四步空间近邻随机采样。
-It is generally accepted that the pixels are no independent but related to it is neighborhoods,
-and the similarly neighboring pixels share the similar variations.
+It is generally accepted that a pixel is not independent but related to its neighborhood,
+and similar neighboring pixels share similar variations.
 %
 Therefore,
-the spatial information should be benefit for learning the pattern of pixels' variation.
+the spatial information should benefit from learning the pattern of pixels' variation.
 %
 With this motivation,
-several training patches extracted from neighboring pixels are combined to improve the efficiency of proposed approach.
+several training patches extracted from neighboring pixels are combined to improve the efficiency of the proposed approach.
 %
-In the experiment, three training patches are combined which is shown as follows:
+In the experiments, three training patches are combined as follows:
 \begin{equation}
@@
 
-\subsection*{Network Work Architecture and Variation Transformation}
+\subsection*{Network Architecture and Variation Transformation}
 % 先描述动机
 As we mentioned above,
-the main purpose of our DPVTL is the transformation between the sequence of pixels' observations with possibility of pixels belong to foreground or background.
+the main purpose of our DPVTL algorithm is the transformation between the sequence of pixels' observations with possibility of pixels belonging to foreground or background.
 % the main purpose of our DPVTL is trying to transform the sequence of pixels' observations 
@@
 our network entails learning a mapping from the input observations of pixels $s \in \mathcal{S}$ 
-to the probability $p \in \mathcal{P}$ of the corresponding pixel belong to foreground or background,
-and a end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels as shown in the \reffig{flow_chart}.
+to the probability $p \in \mathcal{P}$ of the corresponding pixel belonging to foreground or background.
 %
-Mathematically, the training procedure is shown as follows:
+An end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels, as shown in the \reffig{flow_chart}.
+%
+Mathematically, the training procedure is as follows:
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{P}(x,y)$ is denoted as the probability, $\mathcal{S}(m,n)$ is the input patch of network and $f_{\theta_i}$ is represents different layers of network.
+where $\mathcal{P}(x,y)$ is the probability, $\mathcal{S}(m,n)$ is the input patch of the network and $f_{\theta_i}$ represents different layers of the network.
 % where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$.
@@
 
-For the loss function, the Sigmoid Cross Entropy (SCE) loss is used, which are helpful to address the learning slowdown. 
+For the loss function, Sigmoid Cross Entropy (SCE) loss is used, which helps address the learning slowdown. 
 The formulation is as follows:
@@
 where $S^{gt}(x,y)$ denotes the groundtruth patch which is given by the corresponding groundtruth stack, and $Sig$ represents the sigmoid function. 
-The SCE is calculated between the transformed patches and the corresponding groundtruth patches. 
-Boundaries of moving objects and pixels that out of the region of interest are not taken into account in the cost function.
-Finally, we get the transformed variation through the FCN, which are a lot easier for classification.
+SCE is calculated between the transformed patches and the corresponding groundtruth patches. 
+Boundaries of moving objects and pixels that are out of the region of interest are not taken into account in the cost function.
+Finally, we get the transformed variation through the FCN, which is much easier for classification.
 
@@
 %The network used in this work is devised as an end-to-end architecture XXX
-The architecture of our FCN for foreground detection is illustrated in \reffig{flow_chart}. 
+\textcolor{red}{The architecture of our FCN for foreground detection is illustrated in \reffig{flow_chart}. 
 The proposed FCN contains 6 convolutional layers without pooling, and the filter size of the first five layers is set to $3\times 3$, compared to the last convolutional layer which has a filter size of $1\times 1$.
@@
 After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without extra optimization mechanism.
-\todo{please giving a comprehensive description of the details about the network architecture.}
+}
 
@@
 %As shown in the \reffig{flow_chart}, 
-After the transformation from observations to the probability belong to foreground or background,
+After the transformation from observations to the probability of belonging to foreground or background,
 the foreground is detected from the final binary mask.
@@
 During the transformation,
-the pixel patches are feed into the network and transformed into the probability patches,
-which are compared with a threshold $T_r$ for classification and then used to reconstruct the foreground for final results.
+the pixel patches are fed into the network and transformed into the probability patches,
+which are compared with a threshold $T_r$ for classification and then used to reconstruct the foreground to obtain the final results.
 %
-The comparison with threshold is mathematically shown as follows:
+The comparison with a threshold is mathematically shown as:
 \begin{equation}
@@
 %
-The $S'(x,y)$ is the probability patches output by the network,
+The $S'(x,y)$ is the probability of patches output by the network,
 the $\mathcal{C}^{-1}$ is the reversed procedure of the reshape procedure shown in the \refeq{eq_reshape} and $R$ is the parameter for the reversing procedure of reshape.
 %
-The $T_f$ is the threshold given by user and the $g()$ is the thresholding function which is shown as follows:
+$T_f$ is the threshold given by a user and $g()$ is the thresholding function shown in \refeq{piecewise_fg}.
 % Then the reverse procedure of \refeq{eq_reshape}

### 2019-01-30 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.aux 	modified:   draft.log 	modified:   draft.pdf 	modified:   draft.tex

@@
 \DeclareGraphicsExtensions.
-    \caption{ Original videos break down into pixel patches for the training of the FCN, which 
-Fully convolutional network produces an efficient machine for end-to-end transformation learning.}
+    \caption{ Original videos broken down into pixel patches for training of the FCN, which 
+produces an efficient machine for end-to-end transformation learning.}
     \label{flow_chart}
@@
 In this section, we ran comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW\cite{CAMO}.
-The CDnet is the largest dataset for foreground detection so far as we are aware, containing 11 categories with several complexly challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
-The CAMO-UOW is a challenging benchmark for camouflaged foreground detection, which contains 10 high resolution videos. 
-For each video, one or two persons appear in the scene with the clothes in the similar color as the background.
+%
+The CDnet is the largest dataset for foreground detection as far as we are aware, containing 11 categories with several complex challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
+The CAMO-UOW is a challenging benchmark for camouflaged foreground detection, containing 10 high resolution videos. 
+For each video, one or two persons appear in the scene with the clothes having similar color as the background.
 
-The proposed approach is compared with several existing traditional state-of-the-art foreground detection algorithms, including the IUTIS-5\cite{Bianco2017TEC}, the SuBSENSE\cite{St-Charles2015SuBSENSE}, the WeSamBE\cite{Jiang2017WeSamBE}, sharable GMM the SharedModel\cite{Chen2015SharedModel}, word-dictionaries-based method the PAWCS\cite{Charles2015PAWCS}, the SemanticBGS\cite{Braham2017Semantic}, the AAPSA\cite{RAMIREZALONSO2016990}, etc.
-Moreover, two deep learning based algorithms are also compared with the proposed approach, which include DeepBS\cite{Babaee2017deep}, and DBMF\cite{Yang2018DBMF}. 
-All the results of compared algorithms are provided by authors.
+The proposed approach is compared with several existing traditional state-of-the-art foreground detection algorithms, including IUTIS-5\cite{Bianco2017TEC}, SuBSENSE\cite{St-Charles2015SuBSENSE}, WeSamBE\cite{Jiang2017WeSamBE}, sharable GMM the SharedModel\cite{Chen2015SharedModel}, word-dictionaries-based method like PAWCS\cite{Charles2015PAWCS}, SemanticBGS\cite{Braham2017Semantic}, AAPSA\cite{RAMIREZALONSO2016990}, etc.
+Moreover, two deep learning based algorithms are also compared with the proposed approach, which including DeepBS\cite{Babaee2017deep}, and DBMF\cite{Yang2018DBMF}. 
+\textcolor{red}{All the results of compared algorithms are provided by authors.}
 
-During the comparison, the F-measure(Fm) has been used for evaluation. 
-The Fm is a general international standard in foreground detection which measures the segmentation accuracy by considering both the recall and the precision. 
-The definition of Fm is shown as follows:
+During the comparison, the F-measure Space (Fm) has been used for evaluation. 
+Fm is a general international standard in foreground detection which measures the segmentation accuracy by considering both recall and precision. 
+The definition of Fm is as follows:
 \begin{equation}
@@
 
-The quantitative and qualitative comparisons are shown in \reftab{tab1} and  \reffig{results_chart} respectively. 
-Due to the paper length, several typical videos are selected for the qualitative comparisons as well as the discussion. 
-In the dynamic background scene, the video "canoe" is a typically challenging video which includes a large area of water rippling. 
-The main challenge comes from the dynamic background, in which it is so hard to describe the background by a single image. 
-In this condition, since the traditional foreground detection method such as the SharedModel and the WeSamBE do not have enough ability to describe the complex dynamically background, they are fail to detect the people on the boat, as shown in the \reffig{results_chart}.
+Quantitative and qualitative comparisons are shown in \reftab{tab1} and  \reffig{results_chart} respectively. 
+TO keep the length of this paper XXX, only several typical videos are selected for the qualitative comparisons and discussion. 
+In the dynamic background scene, the video ``canoe'' is a typical challenging video which includes a large area of rippling water. 
+The main challenge comes from the dynamic background, in which it is hard to describe the background by a single image. 
+For this condition, since traditional foreground detection methods such as the SharedModel and the WeSamBE cannot describe the complex dynamical background, they fail to detect the people on the boat, as shown in the \reffig{results_chart}.
 Besides, the detected moving objects of the SharedModel are not accurate in the boundary due to the utilization of texture features. 
-In contrast, benefited from the strong learning ability of Deep Learning network, the DeepBS successfully detected the people. 
-Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even the deep learning based algorithm is suffering from the detection of the boat shape.
-In contrast, the proposed approach performed superior than others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation in time sequence.
-Based on this insight, the FCN network focuses on learning the patterns of the pixel variation rather than a static background image, and proposed approach achieves promising performance in the canoe video.
+In contrast, benefiting from the strong learning ability of Deep Learning networks, DeepBS successfully detects the people. 
+Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even this algorithm suffers from poor detection of the boat shape. 
+In contrast, the proposed approach performs superior to others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation over a time sequence.
+Based on this insight, the FCN network focuses on learning the patterns of pixel variation rather than a static background image.
+Thus proposed approach achieves promising performance for the canoe video.
 
-As for the case of shadow scene, "peopleInShade" is a typical example with prevalent hard and soft shadows. 
-In the traditional approaches, these shadow regions are usually segmented as foreground since it is also moving with the objects. 
-Therefore, traditional methods like the PAWCS, the WeSamBE and the SharedModel falsely segments part of shadows as moving objects. 
-In addition, the foreground provided by the IUTIS-5 is incomplete on the part of the pedestrian's body due to the interference of shades, which can be owing to the severe dependency of texture features.
-Whereas, the DeepBS performs well in this video benefited from the utilization of CNN. 
-However, the shape of pedestrians are slightly deformed as the result of their patch-wise processing of CNN. 
-In contrast, derived from the fact that our DPVL focus on learning the pattern of pixels' variation in the shadow regions, proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.
+As for the case of shadow scene, ``peopleInShade'' is a typical example with prevalent hard and soft shadows. 
+For traditional approaches, these shadow regions are usually segmented as foreground since they also movie with the objects. 
+Therefore, traditional methods like PAWCS, WeSamBE and SharedModel falsely segment part of shadows as moving objects. 
+In addition, the foreground provided by IUTIS-5 is incomplete on part of the pedestrian's body due to the interference of shades, 
+because of the severe dependency on texture features. 
+Whereas, DeepBS performs well for this video benefiting from the utilization of CNN. 
+However, the shape of pedestrians are slightly deformed as a result of the patch-wise processing in CNN. 
+In contrast, since our DPVL focusses on learning the pattern of pixels' variation in the shadow regions, 
+the proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.
 
-In the video "corridor" among the Thermal scene, there is no color information since the videos are obtained through a Thermal camera. 
-Moreover, moving objects in these videos are exceedingly fuzzy and indistinct, which is the main challenge of this category. 
-The WeSamBE, the SharedModel and the PAWCS successfully detect the target objects, owing to a stable background in this indoor video. 
-However, they fail to remove the reflections since their modeling ability has already reached a limit under the extreme condition of thermal map. 
-The DeepBS, by contrast, succeeds in eliminating most of the reflections. 
+In the video ``corridor'' among the Thermal scene, there is no color information since the videos are obtained through a Thermal camera. 
+Moreover, moving objects in these videos are exceedingly fuzzy and unclean, which is the main challenge for this category. 
+WeSamBE, SharedModel and PAWCS successfully detect the target objects, because of a stable background in this indoor video. 
+However, they fail to remove the reflections since their modeling ability has already reached a limit under the extreme condition of the thermal map. 
+DeepBS, by contrast, succeeds in eliminating most of the reflections. 
 Meanwhile, moving objects are also clearly divided from the background thanks to the strong modeling ability of CNN. 
-However, due to the dependency of the edge feature, a small object were missed in the detection result. 
-Fortunately, the proposed approach focus on the pattern of pixels' variation, which should be theoretically effective even in the observation without the color information. 
-Consequently, our DPVL performed much better than compared algorithms, with the situation that most parts of the shadow are removed and the segmentation results are more accurate.
+However, due to the dependency of the edge feature, a small object was missed in the detection result. 
+Fortunately, the proposed approach utilizes the pattern of pixels' variation, which is theoretically effective even in observations without color information. 
+Consequently, our DPVL performs much better than other algorithms, with the most parts of the shadow being removed and the segmentation results become more accurate.
 
@@
 
-The quantitative evaluation of the proposed approach on CDnet 2014 is shown in the \reftab{tab1}. 
-It can be inferred that the proposed approach significantly outperformed all of the compared state-of-the-art algorithms in most of complex scenes and achieved 11.37\% gain in FM over the second one on the whole dataset.
-Moreover, in order to compare the proposed approach with the DBMF, which is also based on deep learning and only publish their results in  specific videos. 
+The quantitative evaluation of the proposed approach on CDnet 2014 is shown in \reftab{tab1}. 
+It can be seen that the proposed approach significantly outperforms all of the compared state-of-the-art algorithms in most of complex scenes and achieves 11.37\% gain in FM over the second one on the whole dataset.
+\textcolor{red}{Moreover, in order to compare the proposed approach with the DBMF, which is also based on deep learning and only publish their results in  specific videos. 
 The proposed approach has also ran in these videos and the results are shown in Table 2. 
-Again, the proposed approach has noticeably better performance than the DBMF and some other classical background approaches.
+Again, the proposed approach has noticeably better performance than the DBMF and some other classical background approaches.}
 
-	As shown in the \reftab{tab1} and \reftab{tab2}, previous deep learning based methods like the DeepBS and the DBMF achieve well performance. 
-From our own perspective, that good performance should attribute to the stronger modeling ability and learning adaptation of CNN and FCN. 
-However, the proposed approach focused on the pixels variation in temporal sequence rather than low-level static features such as color, edges and textures, which give us the ability to avoid the shortcomings of the background models.
-Consequently, the proposed approach still gets considerably better results, which over 17.85\% in FM metrics compared with the DeepBS and over 9.50\% compared with the DBMF.
+As shown in \reftab{tab1} and \reftab{tab2}, previous deep learning based methods like DeepBS and DBMF achieve good performance. 
+From our perspective, this good performance can be attributed to the stronger modeling ability and learning adaptation of CNN and FCN. 
+However, the proposed approach utilizes the pixel variations in a temporal sequence rather than low-level static features such as color, edges and textures, which give us the ability to avoid the shortcomings of the background models.
+Consequently, the proposed approach produces considerably better results, with improvement over 17.85\% in FM metrics compared to DeepBS and over 9.50\% compared to DBMF.
 
-The evaluation of the proposed approach in CAMO-UOW dataset is shown in the \reftab{tab3}. 
+The evaluation of the proposed approach in CAMO-UOW dataset is shown in \reftab{tab3}. 
 Unlike the CDnet dataset, the videos of CAMO-UOW dataset are specially proposed for moving objects with camouflage, which is the main challenge of this dataset. 
-As shown in the \reftab{tab3} proposed approach achieves better performance compared to its competitions, with an average F-measure of 0.97, compared to values between 0.77 and 0.94 for the other methods.
-Therefore, it is fair to say that the proposed approach performs better compared with their peers.
+As shown in \reftab{tab3}, the proposed approach achieves better performance compared to its competitions, 
+with an average F-measure of 0.97, compared to values between 0.77 and 0.94 for other methods. 
+Therefore, it is fair to say that the proposed approach performs better compared to the state-of-the-art.
 
-In this dataset, target objects have similar color and textures with the background, which brings a lot of difficulties and obstacles to traditional methods. 
+In CAMO-UOW dataset, target objects have similar color and textures as the background, which create many difficulties and obstacles for traditional methods. 
 However, our FCN is a powerful Neural Network model which is good at capturing the non-linearities of the manifold of pixel variations.
 
-All these experiments of the proposed method were implemented in matlab and ran on the computer with Nvidia tasla K80 GPU and all images keep their original resolution. 
+All of the experiments of the proposed method were implemented in matlab and ran on a computer with Nvidia Tasla K80 GPU with all images kept at their original resolution. 
 For each video in CDnet 2014, 100 training frames are extracted to produce the image patch. 
-It should be noted that the 100 frames only accounts for less than 10\% of total Groundtruth in CDnet 2014. 
-In contrast, 90\% of data were used as training samples in the DBMF, which suggest that the proposed approach achieves well performance with limited training frames. 
-Considering that videos in CAMO-UOW have fewer frames, we reduce the number of training frames to 64 for each video. 
-During the experience, the training set and testing set are completely separated. 
-More specifically, our FCN network is random initialized. 
-We train the network with mini-batches of size 200, a learning rate $\alpha  = 1 \times 10^{{−3}}$ over 20 epochs. 
+It should be noted that the 100 frames only account for less than 10\% of total Groundtruth in CDnet 2014. 
+In contrast, 90\% of data was used as training samples in DBMF, which suggest that the proposed approach achieves better performance with limited training frames. 
+Considering that videos in CAMO-UOW have fewer frames, we reduced the number of training frames to 64 for each video. 
+During the experiments, the training and testing sets are completely separated. 
+More specifically, our FCN network is randomly initialized. 
+We train the network with mini-batches of size 200, and a learning rate of $\alpha  = 1 \times 10^{{−3}}$ over 20 epochs. 
 The last threshold $R$ is set to 0.6.
@@
 \label{sec6}
-In this paper, we proposed a novel foreground detection approach based on deep learning and the variation transformation learning.
-The DPVTL model includes a FCN network and a novel variation transformation learning framework, which allows us to efficiently combine the temporal coherence and distribution information of pixels over a long period of time.
-Comparison with other traditional and deep learning methods shows that the DPVTL has good properties on several challenging scenes.
+In this paper, we proposed a novel foreground detection approach based on proposed variation transformation learning. 
+The DPVTL model includes a FCN network and a novel variation transformation learning framework, 
+which allows us to efficiently combine the temporal coherence and distribution information of pixels over a long period of time. 
+Comparisons with other traditional and deep learning methods shows that DPVTL significantly improves performance on several challenging scenes.
 %The future work will be focused on improving the DPVTL in terms of network architecture updating and integration of local spatial coherence.

### 2019-02-01 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.log 	modified:   draft.pdf 	modified:   draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.aux 	modified:   draft.log 	modified:   draft.pdf 	modified:   draft.tex

@@
 \usepackage{xcolor}
+\usepackage{setspace}
 
@@
         Chenqiu Zhao,
-        Anup Basu}
+        Anup Basu
+        \thanks{Yongxin Ge is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.}
+        \thanks{Xinyu Ren is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.}
+        \thanks{Chenqiu Zhao is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.}
+        \thanks{Anup Basu is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.}
+        }
 
@@
 
+\begin{spacing}{2.0}
 \begin{abstract}
@@
 % 这句话我也没看懂。。。
-    \textcolor{red}{
-Benefited from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
-    the proposed approach adaptively generates superior performances in diverse nature scenes.}
+Due to the global analyse of pixel variations and the strong learning ability of deep learning network,
+the proposed approach adaptively learned a good transformation from pixel variation to labels and generates well performances in diverse natural scenes.
+%    \textcolor{red}{
+% Benefited from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
+%    the proposed approach adaptively generates superior performances in diverse nature scenes.}
 %
@@
 % 大多数情况下，他都会被划分成背景
-Unfortunately, in most cases, it is highly possible that C will be falsely classified due to the similarity with counterparts of the background.
+Unfortunately, in most cases, it is quite possible that C will be falsely classified due to the similarity with counterparts of the background.
 % 我们的就是希望把这个variation 转化到更简单的地方去
@@
 %
-\textcolor{red}{Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence.} 
+Pixels are considered as background when the probability generated by Gaussians are higher than a user threshold.
+% \textcolor{red}{Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence.} 
 %GMM+i
@@
 \label{sec4}
-In this section, details of the proposed aren explained.
+In this section, details of the proposed approach are explained.
 %
@@
 %The network used in this work is devised as an end-to-end architecture XXX
-\textcolor{red}{The architecture of our FCN for foreground detection is illustrated in \reffig{flow_chart}. 
+The architecture of our FCN for foreground detection is illustrated in \reffig{flow_chart}. 
 The proposed FCN contains 6 convolutional layers without pooling, and the filter size of the first five layers is set to $3\times 3$, compared to the last convolutional layer which has a filter size of $1\times 1$.
-We use the Rectified Linear Unit (ReLU) as the activation function after first three convolutional layers.
-And the Sigmoid Cross Entropy loss function is applied to measures the performance of our network after the last convolutional layer.
+We use the Rectified Linear Unit (ReLU) as the activation function after first three convolutional layers，
+and the Sigmoid Cross Entropy loss function is applied to measures the performance of our network after the last convolutional layer. 
 We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
 After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without extra optimization mechanism.
-}
 
@@
 Moreover, two deep learning based algorithms are also compared with the proposed approach, which including DeepBS\cite{Babaee2017deep}, and DBMF\cite{Yang2018DBMF}. 
-\textcolor{red}{All the results of compared algorithms are provided by authors.}
+The results of the compared algorithms are captured by the implementation provided by authors.
+% \textcolor{red}{All the results of compared algorithms are provided by authors.}
 
@@
 Quantitative and qualitative comparisons are shown in \reftab{tab1} and  \reffig{results_chart} respectively. 
-TO keep the length of this paper XXX, only several typical videos are selected for the qualitative comparisons and discussion. 
+To keep the length of this paper reasonable, only several typical videos are selected for the qualitative comparisons and discussion. 
 In the dynamic background scene, the video ``canoe'' is a typical challenging video which includes a large area of rippling water. 
@@
 It can be seen that the proposed approach significantly outperforms all of the compared state-of-the-art algorithms in most of complex scenes and achieves 11.37\% gain in FM over the second one on the whole dataset.
-\textcolor{red}{Moreover, in order to compare the proposed approach with the DBMF, which is also based on deep learning and only publish their results in  specific videos. 
-The proposed approach has also ran in these videos and the results are shown in Table 2. 
-Again, the proposed approach has noticeably better performance than the DBMF and some other classical background approaches.}
+%
+Moreover,
+since the DBMF only publish their results in several specific videos instead of whole dataset,
+the proposed approach has also ran in these videos to compare with the DBMF and the results are shown in Table 2,
+which also demonstrates the superiority of the proposed approach.
+% \textcolor{red}{Moreover, in order to compare the proposed approach with the DBMF, which is also based on deep learning and only publish their results in  specific videos. 
+% The proposed approach has also ran in these videos and the results are shown in Table 2. 
+% Again, the proposed approach has noticeably better performance than the DBMF and some other classical background approaches.}
 
@@
 In this paper, we proposed a novel foreground detection approach based on proposed variation transformation learning.
-The DPVTL model includes a FCN network and a novel variation transformation learning framework, 
-which allows us to efficiently combine the temporal coherence and distribution information of pixels over a long period of time. 
+%
+The transformation learning focus on learning a transformation from pixel variation to the probability of pixels belong to foreground or background.
+%
+The global variation pattern of pixel observation is learned for better classification of pixels.
+%
+In particular, a FCN network and a novel variation transformation learning framework is proposed to efficiently combine the temporal coherence and distribution information of pixels over a long period of time.
+%
 Comparisons with other traditional and deep learning methods shows that DPVTL significantly improves performance on several challenging scenes.
@@
 %
+
+\end{spacing}
+
 \ifCLASSOPTIONcaptionsoff

### 2019-02-08 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.aux 	modified:   draft.log 	modified:   draft.pdf 	modified:   draft.tex

@@
 \usepackage{xcolor}
-\usepackage{setspace}
+% \usepackage{setspace}
 
@@
 
-\begin{spacing}{2.0}
+% \begin{spacing}{2.0}
 \begin{abstract}
@@
 % 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
-In particular, the pixel variation is represented by the sequence of pixel space, which is used as the input for a fully convolutional network(FCN) to find a transformation of pixels' variation.
+    In particular, the pixel variation is represented by the sequence of pixel space, which is used as the input to a fully convolutional network \textcolor{blue}{space} (FCN) to find a transformation of pixels' variation.
 % 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
@@
 % 这句话我也没看懂。。。
-Due to the global analyse of pixel variations and the strong learning ability of deep learning network,
-the proposed approach adaptively learned a good transformation from pixel variation to labels and generates well performances in diverse natural scenes.
+Resulting from the global analysis of pixel variations and the strong learning ability of deep learning networks,
+the proposed approach adaptively learns a good transformation from pixel variations to label and generate good performance in diverse natural scenes.
 %    \textcolor{red}{
@@
 %
-Comprehensive experiments on several standard benchmark demonstrate the superiority of the proposed approach compared with state-of-the-art deep learning and traditional methods.
+Comprehensive experiments on several standard benchmarks demonstrate the superiority of the proposed approach compared to state-of-the-art deep learning and traditional methods.
 %
@@
 % 传统的方法是怎么做的，有什么问题
-Typically, it is recognized as a binary classification task that assigns each pixel in the video stream with a label, 
+Typically, it is recognized as a binary classification task that assigns a label to each pixel in the video stream,
 for either belonging to the background or foreground scene.
-Traditional foreground detection algorithms focus on analyzing the pixel variation, establishing background models with statistical methods such as GMM\cite{Stauffer1999}\cite{lee2005} and KDE\cite{Elgammal2000Non}\cite{Mittal2004KDE}.
-However, due to the unpredictability and peed of pixel variations in natural scenes,
-the variation becomes so unordered and is hard to analyze for foreground detection.
+Traditional foreground detection algorithms focus on analyzing pixel variations, establishing background models with statistical methods such as GMM\cite{Stauffer1999}\cite{lee2005} and KDE\cite{Elgammal2000Non}\cite{Mittal2004KDE}.
+However, due to the unpredictability and speed of pixel variations in natural scenes,
+the variation becomes unordered and is hard to analyze for foreground detection.
 Therefore, foreground detection is still a challenging problem in complex natural scenes.
@@
 % 如图所示，像素观测值C就和背景的值几乎一模一样，
-As shown in the \reffig{idea},
-the observation C is closely related to the observations which belong to the background. However, it is actually produced by moving objects and should be classified as foreground.
+As shown in \reffig{idea},
+observation C is closely related to the observations which belong to the background. However, it is actually produced by moving objects and should be classified as foreground.
 % 大多数情况下，他都会被划分成背景
@@
     % 图例里描述一下。
-    \caption{The demonstration of deep variation transformation.
+    \caption{Demonstration of deep variation transformation.
 Due to the complexity of natural scenes, the original pixels' variation is hard to classify correctly.
-After transforming by deep learning network, the pixels in variation become easy to be classified as foreground and background correctly.}
+After transforming by a deep learning network, the pixels in variation become easy to be correctly classified as foreground and background correctly.}
     \label{idea}
@@
 In the DPVTL model, 
-the sequence of pixel observations is used to represent the variation and input into the network for learning,
+the sequence of pixel observations is used to represent the variations and input into the network for learning,
 which encodes both the intensity distribution and the sequential information.
 %
-Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn patterns of the pixel variation and find a transformation which guarantees the linear separability of pixels in the transformed variation.
+Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn patterns of pixel variations and find a transformation which guarantees the linear separability of pixels in the transformed variation.
 %
@@
 Utilizing the innovative framework of variation transformation,
-the proposed approach works well in diverse complex scenes adaptively.
+the proposed approach works well for a diverse range of complex scenes.
+% in diverse complex scenes adaptively.
 %
@@
 % XXX 不会用引用可以问我或者曲师兄。
-The rest part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion of both early and recent relevant literature. 
+The rest part of this paper is organized as follows: In \refsec{sec2}, we briefly discuss both early and recent relevant literature. 
 %
 Details on the variation transformation are presented in \refsec{sec3}.
-The architecture of the network is introduced in \refsec{sec4}, followed by experiments and comparison result in \refsec{sec5}, before concluding the paper in \refsec{sec6}.
+The architecture of the network is introduced in \refsec{sec4}, This is followed by experiments and comparison results in \refsec{sec5}, before concluding the paper in \refsec{sec6}.
 % \todo{please revise this part by using command refsec}
@@
 which are broadly categorized into pixel-based, region-based and learning-based methods.
-\subsection{pixel-based methods}
+\subsection{Pixel-based methods}
 % Ren:重新解释了pixel based methods
 Pixel-based methods usually assume the independence between neighboring pixels,
-and utilize the low-level features, such as color or gradients for background subtraction.
+and utilize low-level features, such as color or gradients for background subtraction.
 
@@
 In addition, a non-parametric background model is proposed by Elgammal et al. \cite{Elgammal2000Non}. 
-They assume that each background pixel is drawn from a probability distribution function, which is estimated Kernel Density Estimation space (KDE). 
+They assume that each background pixel is drawn from a probability distribution function, which is estimated in the Kernel Density Estimation space (KDE). 
 %Vibe
@@
 %
-Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists sufficient samples with a distance to itself within a certain range.
+Each pixel in the current frame is compared with sample pixels from the corresponding background model and labelled as the foreground when there exists sufficient samples with a distance to itself within a certain range.
 %PBAS
@@
 
-\end{spacing}
+% \end{spacing}
 

### 2019-02-09 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.
 On branch master
 Changes to be committed:
	modified:   draft.tex

@@
 Varadarajan et al.\ \cite{2015_PR_Varadarajan20153488} proposed a region-based GMM model,
-which is derived from expectation-maximization (EM) theory with the consideration of neighboring pixels.
+which is derived using the expectation-maximization (EM) theory considering neighboring pixels.
 % Spatiotemporal GMM
 In addition, 
-Chen et al. \cite{2017_TPAMI_GANGWANG} combined the GMM with constraints of temporal and spatial information from the optical flow and hierarchical superpixels.
+Chen et al. \cite{2017_TPAMI_GANGWANG} combined GMM with constraints on temporal and spatial information from the optical flow and hierarchical superpixels.
 %(Bayesian Modeling)
@@
 \subsection{Machine Learning based Methods}
-The last category of background subtraction methods applies traditional machine learning and deep learning for the foreground detection.
+The last category of background subtraction methods applies traditional machine learning and deep learning for foreground detection.
 
@@
 %
-In recent years, deep learning methods begin to flourish in several computer vision fields, 
+In recent years, deep learning methods have begain began to flourish in several computer vision fields, 
 and have demonstrated effective capabilities to handle time-series problems\cite{Mobahi2009}\cite{LANGKVIST201411}. 
@@
 % Ren: 这里我解释一下，为什么看上去这么冗余。这家伙先自己用中值滤波求了个平均背景，然后把平均背景 patches 跟对应的origin image patches 组合作为网络输入，他训练的groundtruth也可以来自其他比如GMM的分类结果图。
-Braham et al.
-\cite{Braham2016deep} employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth.
-In particular, the background image is obtained by temporal median filtering, and the groundtruth can be replaced with segmentation results from other foreground detection methods.
+Braham et al. \cite{Braham2016deep} employed a scene-specific CNN, 
+which is trained with corresponding image patches from the background image, video frames and groundtruth. 
+In particular, the background image is obtained by temporal median filtering, and the groundtruth can be replaced by segmentation results from other foreground detection methods.
 % Ren: 下面这个家伙做法跟上面太类似了，就是背景图像不用中值滤波，而是用其他牛一点的方法去获取。MD
-A similar approach is presented by M.
-Babaee et al.
-\cite{Babaee2017deep}.
-Their background images combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm \cite{Wang2014FTSG}, which is able to adaptively update the parameters used in the background model.
-They also utilize spatial-median filtering as the post processing of the network predictions.
+A similar approach is presented by M. Babaee et al. \cite{Babaee2017deep}. 
+Their background images combine the segmentation mask from the SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm \cite{Wang2014FTSG}, which is able to adaptively update the parameters used in the background model.
+They also utilize spatial-median filtering for post processing of the network predictions.
 %DBMF
@@
 %
-Besides, our network is trained to learn patterns of pixel variations, which result in a better performance in time series modeling on temporal coherence.
+Besides, our network is trained to learn patterns of pixel variations, which results in a better performance in time series modeling on temporal coherence.
 %
@@
     % 图例里描述一下。
-    \caption{Comparison of the original pixel variation, groundtruth and transformed variation. They are represented by the blue line, red line and green line respectively.}
+    \caption{Comparison of the original pixel variation, groundtruth and transformed variation. They are represented by the blue, red and green lines respectively.}
     \label{variation_chart}
@@
 Accordingly, the red line is made of the groundtruth data, corresponding to the observations from the blue one.  
-And the green line consists of the outputs of the proposed approach which represent the transformed variation.
+And the green line consists of the outputs of the proposed approach which represents the transformed variation.
 
@@
 %传统方法的问题
-Previous methods have good performance when background and foreground observations are remarkably different and the backgrounds are normally static. 
+Previous methods have good performance when background and foreground observations are significantly different and the backgrounds are normally static. 
 While in fact, backgrounds can be rather turbulent and dynamic due to the complexity and diversity of natural scenes. 
@@
 %图例说明可能面临的挑战
-For example, in \reffig{variation_chart}, it is noticeable that some foreground observations in blue line share the same or similar value with background ones. 
+For example, in \reffig{variation_chart}, it is noticeable that some foreground observations on the blue line share the same or similar value with background ones. 
 In this case, popular methods will inevitably yield some sticky moments when separating the pixels in the blue line. 
 Statistical methods, for instance, are no longer valid, because they only focus on establishing a statistical model for the background, while having little or no concern for the temporal coherence of these observations.
-In other words, despite knowing that pixels from the background share some common patterns of variation in a temporal sequence, they still let the order information of sequential images all go to waste.
+In other words, despite knowing that pixels from the background share some common patterns of variation in a temporal sequence, they still let the order information of sequential images be ignored. 
 %variation transformation 介绍。
@@
 
-Different from existing methods, we decide to shift our attention from single pixel classification to variation transformation.
+Differring from existing methods, we decided to shift our attention from single pixel classification to variation transformation.
 %the pixel variation is now regarded as a whole to safeguard the data integrity.
 More specifically, a FCN is employed to learn patterns of pixel variations and mapping them into a new space where they are close to the groundtruth data.
-The transformed variation is presented by the green line in \reffig{variation_chart}. 
+The transformed variation is shown by the green line in \reffig{variation_chart}. 
 %After thresholding, we can easily get the labels of each observation. 
@@
 %
-The pipeline of the proposed approach is shown in the \reffig{flow_chart},
+The pipeline of the proposed approach is shown in \reffig{flow_chart},
 which can be divided into three parts.
@@
 Next,
-a reverse procedure of the generation of training data is used to reconstruct the foreground image from the transformed results.
+a reverse procedure for the generation of training data is used to reconstruct the foreground image from the transformed results.
 %
@@
 % 用数学化的语言描述具体过程
-Let us denote the frame sequence in a video as $\mathcal{I} = \{I_1, I_2, \cdots, I_T\}$,
-where $\mathcal{I}$ denotes as the set of frames and $T$ is the numbers of frames.
+Let us denote the frames in a video sequence as $\mathcal{I} = \{I_1, I_2, \cdots, I_T\}$,
+where $\mathcal{I}$ denotes the set of frames and $T$ is the numbers of frames.
 %
@@
 where $\mathcal{I}^d$ is the set of training frames,
-$T$ the $N$ represent the frame number of whole video and the training set respectively,
-and the $\mathcal{D}()$ is denoted as the sampling function.
+$T$ the $N$ represent the frame numbers of the entire video and the training set respectively,
+and $\mathcal{D}()$ denotes the sampling function.
 % 

### 2019-02-09 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.
 On branch master
 Changes to be committed:
	modified:   draft.aux
	modified:   draft.blg
	modified:   draft.log
	modified:   draft.out
	modified:   draft.pdf
	modified:   draft.tex

@@
 After sampling training frames,
-the training patches, which are used as the input of the network, are captured.
+the training patches, which are used as the input to the network, are captured.
 %
@@
 a large number of training patches can be extracted with the training frames;
-and each of these patches is for $\frac{T}{N}$ pixels.
+and each of these patches has $\frac{T}{N}$ pixels.
 %
-In addition, for each pixel included in the patch, a label of the foreground or background is needed for training.
+In addition, for each pixel included in a patch, a label of the foreground or background is needed for training.
 %
@@
 Therefore,
-the spatial information should benefit from learning the pattern of pixels' variation.
+spatial information should benefit from learning the pattern of pixels' variation.
 %
@@
 \end{equation}
-where the $\mathcal{C}o$ represents the concatenation process on the third dimension.
+where $\mathcal{C}o$ represents the concatenation process on the third dimension.
 And neighboring patches are at pixel position $(x',y')$ and $(x'',y'')$ respectively.
@@
 %
-An end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels, as shown in the \reffig{flow_chart}.
+An end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels, as shown in \reffig{flow_chart}.
 %
@@
 and the Sigmoid Cross Entropy loss function is applied to measures the performance of our network after the last convolutional layer. 
-We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
-After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without extra optimization mechanism.
+We do not use any other adjustment in our network training and the experimental results prove that the proposed approach is feasible and very effective.
+After the thresholding calculations, our experiments show that a randomly initialized FCNs, 
+trained end-to-end on feature learning can achieve state-of-the-art performance without any extra optimization mechanism.
 
@@
 %
-The comparison with a threshold is mathematically shown as:
+Comparison with a threshold can be mathematically shown as:
 \begin{equation}
@@
 %
-The $S'(x,y)$ is the probability of patches output by the network,
-the $\mathcal{C}^{-1}$ is the reversed procedure of the reshape procedure shown in the \refeq{eq_reshape} and $R$ is the parameter for the reversing procedure of reshape.
+$S'(x,y)$ is the probability of patches output by the network,
+$\mathcal{C}^{-1}$ is the reverse of the reshape procedure shown in \refeq{eq_reshape} and $R$ is the parameter for the reversing reshape procedure.
 %
@@
 \label{sec5}
-In this section, we ran comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW\cite{CAMO}.
+In this section, we describe comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW\cite{CAMO}.
 %
-The CDnet is the largest dataset for foreground detection as far as we are aware, containing 11 categories with several complex challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
+CDnet is the largest dataset for foreground detection as far as we are kown, containing 11 categories with several complex challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
 The CAMO-UOW is a challenging benchmark for camouflaged foreground detection, containing 10 high resolution videos. 
-For each video, one or two persons appear in the scene with the clothes having similar color as the background.
+For each video, one or two persons appear in the scene with clothes having color similar to the background.
 
-The proposed approach is compared with several existing traditional state-of-the-art foreground detection algorithms, including IUTIS-5\cite{Bianco2017TEC}, SuBSENSE\cite{St-Charles2015SuBSENSE}, WeSamBE\cite{Jiang2017WeSamBE}, sharable GMM the SharedModel\cite{Chen2015SharedModel}, word-dictionaries-based method like PAWCS\cite{Charles2015PAWCS}, SemanticBGS\cite{Braham2017Semantic}, AAPSA\cite{RAMIREZALONSO2016990}, etc.
-Moreover, two deep learning based algorithms are also compared with the proposed approach, which including DeepBS\cite{Babaee2017deep}, and DBMF\cite{Yang2018DBMF}. 
-The results of the compared algorithms are captured by the implementation provided by authors.
+The proposed approach is compared with several existing traditional state-of-the-art foreground detection algorithms, including IUTIS-5\cite{Bianco2017TEC}, SuBSENSE\cite{St-Charles2015SuBSENSE}, WeSamBE\cite{Jiang2017WeSamBE}, sharable GMM the SharedModel\cite{Chen2015SharedModel}, word-dictionaries-based method like PAWCS\cite{Charles2015PAWCS}, SemanticBGS\cite{Braham2017Semantic} and AAPSA\cite{RAMIREZALONSO2016990}.
+Moreover, two deep learning based algorithms are also compared with the proposed approach, including DeepBS\cite{Babaee2017deep}, and DBMF\cite{Yang2018DBMF}. 
+The results of the compared algorithms are captured by the implementation provided by the authors.
 % \textcolor{red}{All the results of compared algorithms are provided by authors.}
 
-During the comparison, the F-measure Space (Fm) has been used for evaluation. 
+For comparison, the F-measure Space (Fm) is used for evaluation. 
 Fm is a general international standard in foreground detection which measures the segmentation accuracy by considering both recall and precision. 
@@
 %
-where TP, FP, and FN are true positives, false positives, and false negatives respectively, computed in pixels of all test frames for each video.
+where TP, FP, and FN are true positives, false positives, and false negatives respectively, computed on the pixels of all the test frames for each video.
 
@@
 The main challenge comes from the dynamic background, in which it is hard to describe the background by a single image. 
-For this condition, since traditional foreground detection methods such as the SharedModel and the WeSamBE cannot describe the complex dynamical background, they fail to detect the people on the boat, as shown in the \reffig{results_chart}.
+For this condition, since traditional foreground detection methods such as the SharedModel and the WeSamBE cannot describe the complex dynamical background, they fail to detect the people on the boat, as shown in \reffig{results_chart}.
 Besides, the detected moving objects of the SharedModel are not accurate in the boundary due to the utilization of texture features. 
@@
 Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even this algorithm suffers from poor detection of the boat shape. 
-In contrast, the proposed approach performs superior to others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation over a time sequence.
+In contrast, the proposed approach performs better from others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation over a time sequence.
 Based on this insight, the FCN network focuses on learning the patterns of pixel variation rather than a static background image.
-Thus proposed approach achieves promising performance for the canoe video.
+Thus the proposed approach achieves promising performance for the canoe video.
 
-As for the case of shadow scene, ``peopleInShade'' is a typical example with prevalent hard and soft shadows. 
+As for the case of the shadow scene, ``peopleInShade'' is a typical example with prevalent hard and soft shadows. 
 For traditional approaches, these shadow regions are usually segmented as foreground since they also movie with the objects. 
@@
 because of the severe dependency on texture features. 
-Whereas, DeepBS performs well for this video benefiting from the utilization of CNN. 
+On the other hand, DeepBS performs well for this video benefiting from the utilization of CNN. 
 However, the shape of pedestrians are slightly deformed as a result of the patch-wise processing in CNN. 
@@
 In the video ``corridor'' among the Thermal scene, there is no color information since the videos are obtained through a Thermal camera. 
-Moreover, moving objects in these videos are exceedingly fuzzy and unclean, which is the main challenge for this category. 
+Moreover, moving objects in these videos are exceedingly fuzzy and unclear, which is the main challenge for this category. 
 WeSamBE, SharedModel and PAWCS successfully detect the target objects, because of a stable background in this indoor video. 
@@
 Fortunately, the proposed approach utilizes the pattern of pixels' variation, which is theoretically effective even in observations without color information. 
-Consequently, our DPVL performs much better than other algorithms, with the most parts of the shadow being removed and the segmentation results become more accurate.
+Consequently, our DPVTL performs much better than other algorithms, with most parts of the shadow being removed and the segmentation results become more accurate.
 
@@
 \centering
-\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CDnet 2014.
-For each video, 100 frames were taken for the training of our FCN.}
+\caption{Performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CDnet 2014.
+For each video, 100 frames were taken for training our FCN.}
 \label{tab1}
@@
 \centering
-\caption{The performance comparison of the proposed approach and some classical methods and deep-based method DBMF. For each video, 64 frames were taken for the training of our FCN.}
+\caption{Performance comparison of the proposed approach and some classical methods and deep-based method DBMF. For each video, 64 frames were taken for training our FCN.}
 \label{tab2}
@@
 \centering
-\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CAMO-UOW.}
+\caption{Performance comparison of the proposed approach and some state-of-the-art algorithms on video sequences from different categories in CAMO-UOW.}
 \label{tab3}
@@
 The quantitative evaluation of the proposed approach on CDnet 2014 is shown in \reftab{tab1}. 
-It can be seen that the proposed approach significantly outperforms all of the compared state-of-the-art algorithms in most of complex scenes and achieves 11.37\% gain in FM over the second one on the whole dataset.
+It can be seen that the proposed approach significantly outperforms all of the compared state-of-the-art algorithms in most of the complex scenes and achieves 11.37\% gain in FM over the second one on the whole dataset.
 %
 Moreover,
-since the DBMF only publish their results in several specific videos instead of whole dataset,
-the proposed approach has also ran in these videos to compare with the DBMF and the results are shown in Table 2,
-which also demonstrates the superiority of the proposed approach.
+since DBMF only published their results in several specific videos instead of the whole dataset,
+the proposed approach was also ran in these videos to compare with DBMF with the results shown in Table 2.
+This also demonstrates the superiority of the proposed approach.
 % \textcolor{red}{Moreover, in order to compare the proposed approach with the DBMF, which is also based on deep learning and only publish their results in  specific videos. 
@@
 From our perspective, this good performance can be attributed to the stronger modeling ability and learning adaptation of CNN and FCN. 
-However, the proposed approach utilizes the pixel variations in a temporal sequence rather than low-level static features such as color, edges and textures, which give us the ability to avoid the shortcomings of the background models.
+However, the proposed approach utilizes pixel variations in a temporal sequence rather than low-level static features such as color, edges and textures, which give us the ability to avoid the shortcomings of the background models.
 Consequently, the proposed approach produces considerably better results, with improvement over 17.85\% in FM metrics compared to DeepBS and over 9.50\% compared to DBMF.
@@
 
-In CAMO-UOW dataset, target objects have similar color and textures as the background, which create many difficulties and obstacles for traditional methods. 
+In the CAMO-UOW dataset, target objects have similar color and textures as the background. This creates many difficulties and obstacles for traditional methods. 
 However, our FCN is a powerful Neural Network model which is good at capturing the non-linearities of the manifold of pixel variations.
 
-All of the experiments of the proposed method were implemented in matlab and ran on a computer with Nvidia Tasla K80 GPU with all images kept at their original resolution. 
+All of the experiments of the proposed method were implemented in Matlab and run on a computer with Nvidia Tasla K80 GPU with all images kept at their original resolution. 
 For each video in CDnet 2014, 100 training frames are extracted to produce the image patch. 
 It should be noted that the 100 frames only account for less than 10\% of total Groundtruth in CDnet 2014. 
-In contrast, 90\% of data was used as training samples in DBMF, which suggest that the proposed approach achieves better performance with limited training frames. 
+In contrast, 90\% of data was used as training samples in DBMF, which suggests that the proposed approach achieves better performance with limited training frames. 
 Considering that videos in CAMO-UOW have fewer frames, we reduced the number of training frames to 64 for each video. 
@@
 \label{sec6}
-In this paper, we proposed a novel foreground detection approach based on proposed variation transformation learning.
+In this paper, we proposed a novel foreground detection approach based on our proposed variation transformation learning.
 %
-The transformation learning focus on learning a transformation from pixel variation to the probability of pixels belong to foreground or background.
+Transformation learning focused on learning a transformation from pixel variations to the probability of pixels belonging to foreground or background.
 %
-The global variation pattern of pixel observation is learned for better classification of pixels.
+The global variation patterns of pixel observation is learned for better classification of pixels.
 %
@@
 %
-Comparisons with other traditional and deep learning methods shows that DPVTL significantly improves performance on several challenging scenes.
+Comparisons with other traditional and deep learning methods shows that our DPVTL algorithms significantly improves performance on several challenging scenes.
 %The future work will be focused on improving the DPVTL in terms of network architecture updating and integration of local spatial coherence.

### 2019-02-11 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.blg 	modified:   draft.log 	modified:   draft.pdf 	modified:   draft.tex

@@
 % 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
-    In particular, the pixel variation is represented by the sequence of pixel space, which is used as the input to a fully convolutional network \textcolor{blue}{space} (FCN) to find a transformation of pixels' variation.
+    In particular, the pixel variation is represented by the sequence of pixel space, which is used as the input to a fully convolutional network space (FCN) to find a transformation of pixels' variation.
 % 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
@@
 %
-CDnet is the largest dataset for foreground detection as far as we are kown, containing 11 categories with several complex challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
+CDnet is the largest dataset for foreground detection as far as we know, containing 11 categories with several complex challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on.
 The CAMO-UOW is a challenging benchmark for camouflaged foreground detection, containing 10 high resolution videos. 
@@
 Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even this algorithm suffers from poor detection of the boat shape. 
-In contrast, the proposed approach performs better from others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation over a time sequence.
+In contrast, the proposed approach performs better than others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation over a time sequence.
 Based on this insight, the FCN network focuses on learning the patterns of pixel variation rather than a static background image.
@@
 %
-Transformation learning focused on learning a transformation from pixel variations to the probability of pixels belonging to foreground or background.
+Transformation learning focused on learning a transformation from pixel variations to the probability of pixels belonging to the foreground or background.
 %
@@
 %
-Comparisons with other traditional and deep learning methods shows that our DPVTL algorithms significantly improves performance on several challenging scenes.
+Comparisons with other traditional and deep learning methods shows that our DPVTL algorithm significantly improves performance on several challenging scenes.
 %The future work will be focused on improving the DPVTL in terms of network architecture updating and integration of local spatial coherence.
@@
 
-% \end{spacing}
-
 \ifCLASSOPTIONcaptionsoff

### 2019-03-08 draft.tex
.

@@
 RMoG\cite{Varadarajan2013}        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
-DPVT        & \textbf{0.9811}   & 0.9329  & \textbf{0.9014}     & \textbf{0.9595}    & \textbf{0.9467} & \textbf{0.9479}  & \textbf{0.8780}   & 0.7818     & \textbf{0.7737}     & \textbf{0.5957} & \textbf{0.9034}  & \textbf{0.8789} \\ \hline
+DPVTL        & \textbf{0.9811}   & 0.9329  & \textbf{0.9014}     & \textbf{0.9595}    & \textbf{0.9467} & \textbf{0.9479}  & \textbf{0.8780}   & 0.7818     & \textbf{0.7737}     & \textbf{0.5957} & \textbf{0.9034}  & \textbf{0.8789} \\ \hline
 \end{tabular}
@@
 DBMF\cite{Yang2018DBMF}     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
-DPVT     & \textbf{0.9888}  & \textbf{0.9819} & \textbf{0.9728}      & \textbf{0.9808}   & \textbf{0.9394} & \textbf{0.9333} & \textbf{0.9662}  \\ \hline
+DPVTL     & \textbf{0.9888}  & \textbf{0.9819} & \textbf{0.9728}      & \textbf{0.9808}   & \textbf{0.9394} & \textbf{0.9333} & \textbf{0.9662}  \\ \hline
 \end{tabular}
@@
 \hline
-Methods  & MOG2\cite{ZIVKOVIC2006773} & FCI\cite{Baf2008FCI}  & LBA-SOM\cite{LBA-SOM2008} & PBAS & SuBSENSE & ML-BGS\cite{ML-BGS2007} & DECOLOR\cite{DECOLOR2013}       & COROLA\cite{SHAKERI201628} & FWFC\cite{Li2018CAMO}          & DPVT          \\ \hline
+Methods  & MOG2\cite{ZIVKOVIC2006773} & FCI\cite{Baf2008FCI}  & LBA-SOM\cite{LBA-SOM2008} & PBAS & SuBSENSE & ML-BGS\cite{ML-BGS2007} & DECOLOR\cite{DECOLOR2013}       & COROLA\cite{SHAKERI201628} & FWFC\cite{Li2018CAMO}          & DPVTL          \\ \hline
 Video 1  & 0.79 & 0.88 & 0.8     & 0.9  & 0.89     & 0.89   & 0.92          & 0.8    & 0.94 & \textbf{0.96} \\

### 2019-03-08 draft.tex
.

@@
 However, the shape of pedestrians are slightly deformed as a result of the patch-wise processing in CNN. 
-In contrast, since our DPVL focusses on learning the pattern of pixels' variation in the shadow regions, 
+In contrast, since our DPVTL focusses on learning the pattern of pixels' variation in the shadow regions, 
 the proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.

### 2019-03-11 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.
 On branch master
 Changes to be committed:
	modified:   draft.log
	modified:   draft.pdf
	modified:   draft.tex

@@
         Xinyu Ren, 
-        Chenqiu Zhao,
-        Anup Basu
-        \thanks{Yongxin Ge is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.}
-        \thanks{Xinyu Ren is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.}
-        \thanks{Chenqiu Zhao is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.}
-        \thanks{Anup Basu is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.}
+        Chenqiu Zhao, ~\IEEEmembership{Student Member,~IEEE}
+        Anup Basu, ~\IEEEmembership{Senior Member,~IEEE}
+        \thanks{Yongxin Ge is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.(e-mail: yongxinge@cqu.edu.cn)}
+        \thanks{Xinyu Ren is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.(e-mail: hsinyujen@gmail.com)}
+        \thanks{Chenqiu Zhao is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.(e-mail: zhao.chenqiu@ualberta.ca)}
+        \thanks{Anup Basu is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.(e-mail: basu@ualberta.ca)}
         }
